---
title: "ContractTermination"
author: "Greg Sanders"
date: "Wednesday, February 8, 2017"
output:
  html_document:
    keep_md: yes
--- 

Modeling Likelihood of Contract Termination
============================================================================

#Setup
```{r InputFiles, echo = TRUE}
library(csis360)
library(ggplot2)
library(scales)
library(Hmisc)
library(plyr)
library(arm)
library(R2WinBUGS)
library(lme4)

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations

Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  


##Prepare Data
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.

```{r ReadInData, echo = TRUE}
  load(file="Data/defense_contract_CSIScontractID_detail.Rdata")
  

head(DefenseModelAndDetail)
```

###Data Transformations
After the data is loaded, we perform a series of transformations, creating derived variables that fit our purposes.

* sqrtCrai is a transformation of the Ceiling Raise percentage. Negative changes are eliminated beause they are not ceiling breaches. The sqrt of other values is taken to focuse on small percent changes and not large outliers.
* lCeil is the natural log of the initial contract cost ceiling (UnmodifiedContractBaseAndAllOptionsValue).
* lDays is the natural log of the initial maximum contract duration in days (UnmodifiedDays)
* nFixed transforms the factor that reports whether a contract was fixed price or cost-based (FxCB) to a numberical value. 0 for cost-based, 0.5 or "combination or other", 1 for any fixed price (excluding fixed-price level of effort which is classified as cost-based).
* nIncent transforms the factor that reports the fee type (Fee) to a numerical value. 1 for incentive fee or cost sharing, 0.5 or "combination or other", 0 for all remaining types
*  nComp transforms the factor that reports the fee type (Comp) to a numerical value. 1 for Competed, 0 for not competed.
*  nIntl transforms the factor that reports the location (Intl) to a numerical value. 1 for Any International obligations, 0 for All in U.S.
*  nIntl transforms the factor that reports the use of undefinitized contract awards (UCA) to a numerical value. 1 for UCA, 0 for otherwise.
*  lOffer is the natural log of the number of offers received. Uncompeted contracts are classified as having received one offer.


In addition, lCeil and lDays are rescaled to have an average value of 0 and a standard deviation of one. This standardizes interpretation and prevents a "very large eigen value" error later when lCeil:lDay is introduced.

```{r TransformData}

#sqrtCrai
DefenseModelAndDetail$sqrtCrai<-DefenseModelAndDetail$sqrtCrai
DefenseModelAndDetail$sqrtCrai[DefenseModelAndDetail$sqrtCrai<0]<-0
DefenseModelAndDetail$sqrtCrai<-sqrt(DefenseModelAndDetail$sqrtCrai)

#lCeil
DefenseModelAndDetail$lCeil<-log(DefenseModelAndDetail$UnmodifiedContractBaseAndAllOptionsValue)
DefenseModelAndDetail$lCeil[is.infinite(DefenseModelAndDetail$lCeil)]<-NA

#lDays
DefenseModelAndDetail$lDays<-log(DefenseModelAndDetail$UnmodifiedDays)
DefenseModelAndDetail$lDays[is.infinite(DefenseModelAndDetail$lDays)]<-NA



#nFixed

DefenseModelAndDetail$nFixed<-DefenseModelAndDetail$FxCb
levels(DefenseModelAndDetail$nFixed)<- list("1"=c("Fixed-Price"), 
       "0.5"=c("Combination or Other"),
       "0"=c("Cost-Based"))
DefenseModelAndDetail$nFixed<-as.integer(as.character(DefenseModelAndDetail$nFixed))

 #nIncent
DefenseModelAndDetail$nIncent<-DefenseModelAndDetail$Fee
levels(DefenseModelAndDetail$nIncent) <-
  list("1"=c("Incentive"), 
       "0.5"=c("Combination or Other"),
       "0"=c("Award Fee", "FFP or No Fee", "Fixed Fee"))
DefenseModelAndDetail$nIncent<-as.integer(as.character(DefenseModelAndDetail$nIncent))


#nComp
DefenseModelAndDetail$nComp<-DefenseModelAndDetail$SingleOffer #Fix in Rdata, and add back comp
levels(DefenseModelAndDetail$nComp)


#nIntl
DefenseModelAndDetail$nIntl<-DefenseModelAndDetail$Intl
DefenseModelAndDetail$nIntl[DefenseModelAndDetail$nIntl=="Unlabeled"]<-NA
levels(DefenseModelAndDetail$nIntl) <-
  list("0"=c("Just U.S."), 
       "1"=c("Any International"))
DefenseModelAndDetail$nIntl<-as.integer(as.character(DefenseModelAndDetail$nIntl))



#nUCA
DefenseModelAndDetail$nUCA<-DefenseModelAndDetail$UCA
levels(DefenseModelAndDetail$nUCA) <-
  list("0"=c("Not UCA"), 
       "1"=c("UCA"))
DefenseModelAndDetail$nUCA<-as.integer(as.character(DefenseModelAndDetail$nUCA))




#lOffer
DefenseModelAndDetail$lOffer<-log(DefenseModelAndDetail$UnmodifiedNumberOfOffersReceived)
DefenseModelAndDetail$lOffer[is.infinite(DefenseModelAndDetail$lDays)]<-NA

# DefenseModelAndDetail$DecisionTree<-as.character(DefenseModelAndDetail$MaxOfDecisionTree)
# DefenseModelAndDetail$DecisionTree[
#   DefenseModelAndDetail$DecisionTree=="Excluded"|
#     is.na(DefenseModelAndDetail$DecisionTree)]<-"All Other"
# DefenseModelAndDetail$DecisionTree<-factor(DefenseModelAndDetail$DecisionTree,levels=c("OCO","Disaster","ARRA","All Other"))
# 
# if(!"Is.Defense" %in% colnames(DefenseModelAndDetail)){
#   DefenseModelAndDetail$Is.Defense<-as.character(DefenseModelAndDetail$Who)
#   DefenseModelAndDetail$Is.Defense[DefenseModelAndDetail$Is.Defense %in%
#                                      c("Air Force","Army",
#                                        "Navy","Other DoD","Uncategorized"  )
#                                    ]<-"Defense"
#   DefenseModelAndDetail$Is.Defense<-factor(DefenseModelAndDetail$Is.Defense)
# }


```

Next, we eliminate missing data entries and then draw a sample. The final computation uses all of the data, but as a computation shortcut, only a subset of the data is needed to allow for processing of models in minutes rather than hours.

```{r Sample}
smp<-DefenseModelAndDetail[!is.na(DefenseModelAndDetail$sqrtCrai  ),]

smp[,names(smp) %in% c("lCeil","lDays")]<-scale(smp[,names(smp) %in% c("lCeil","lDays")])


smp<-smp[sample(nrow(smp),250000),]
detach(2)
R2WinBUGS::attach.all(smp)
```

#Estimate Model

##Model 1: Cost Ceiling

The model starts by examing the influence of large ceilings on contracts, the core idea here, as observed in the fixed priced paper, is that larger contracts are at greater risk of termination. This can be explained by both the inherent risk in the contract and high transaction costs of contract termination which discourage making the effort for smaller contracts.

```{r Model01}

CRai01 <- lmer (sqrtCrai   ~ lCeil +
               (1 | PSR) + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY))
display(CRai01)


```

##Model 2: Maximum Duration

```{r Model02}
CRai02 <- lmer (sqrtCrai   ~ lCeil + 
               lDays  +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY))
display(CRai02)

```
The initial model results are as expected, but the relationship between initial contract ceiling and terminations is weak compared to what was observed in data exploration. This may be because of the interaction between the two terms. Both initial ceiling and duration are seperately associated with a higher risk of termination, but what is the influence of contracts that are expected to be both long lasting and large?

##Model 3: Interation of Ceiling and Duration
```{r Model03}

CRai03 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + lCeil:lDays +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai03)
```

The combination of ceiling and duration improves the model only very slightly and is not significant in its own right. We will be leaving it out going forward.

##Model 4: Fixed-Price Contracts

The next step adds a measure for whether the contract was cost-based or fixed-price. Prior CSIS research has found that fixed-price contracts do face a higher risk of termination across the board.

```{r Model04}

CRai04 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai04)
```

And fixed price contracts do indeed have a appreciably higher termination rate. This does not improve the overall AIC of the model, but it captures another important dynamic and has a coefficient that greatly exceeds its standard error. 

##Model 5: Fixed-Price and Maximum Duration
Past CSIS research has found that fixed-price contracts do appear to be at higher risk if they have a longer maximum duration. Fixed-price contracting does require upfront estimation of likely costs, and thus a longer duration means more opportunity for changed circumstance.

```{r Model05}

CRai05 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIntl + nUCA + lOffer + lDays:nFixed +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai05)

```
No strong relationship is suggested by the coefficient and the direction is opposite the one expected. This suggests that both maximum duration and fixed price contracting are termination increasing factors, but that they operate independently.


##Model 6: Incentive Fees

```{r Model06}

CRai06 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIncent +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai06)
```
Fee type appears to have no effect on terminations. In the performance of the defense acquisition system report, the benefits found were reduced cost overruns. That could help avoid terminations, but it's an indirect connection at best. Nonetheless, because they are closely connected, it's worth testing the interaction with fixed price.


##Model 7: Fixed Price and Incentive Fee

```{r Model07}

CRai07 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIncent + nFixed:nIncent +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai07)

```

Adding the intersection of Fixed and Incent does not improve the model and results in a failure to converge. Leaving it out.

##Model 8: International work

```{r Model08}

CRai08 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIntl +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai08)

```

The lower termination rate of international contrats is somewhat surprising, given their potentially greater risks. The coefficient exceeds the standard deviation, though missing data reduced the number of observations, reducing both the AIC and DIC. An alternative would be to treat all missing international labels as domestic. 

##Model 9: Undefinitized Contract Awards
Undefinitized Contract Awards allow for quick action in situations where there is not time or information to establish all of a contracts properties at the time of signing. They have been found by the GAO and the Performance of the Defense Acquisition studies to contain notable risks, primarily relating to cost overruns. Will these risks also carry into terminations?

```{r Model09}

CRai09 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIntl + nUCA +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai09)

```

Use of UCA significantly increases risks of termination, well in excess of the error term. Interestingly, while this addition further reduceds the AIC and DIC of the model, it also increases the coefficient for fixed price contracts.

##Model 10: Competition


```{r Model10}

CRai10 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIntl + nUCA + Comp +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai10)

```

###Model 11: Number of offers for Competed Contracts

```{r Model11}
CRai11 <- lmer (data=subset(smp,Comp==1),
              sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIntl + nUCA +  lOffer +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai11)

```

The results are quite surprising, even setting aside the existing finding that competition leads to higher risk of termination, those competed contracts with more offers were at even greater risk. Bid protests, which can result in a partial or complete terminations, may be one driver although the magnitude is unlikely to be sufficient to explain the phenomenon. Another may be that when multiple offers are available, there are more alternatives for the government to turn to rather than being stuck in a contract.

###Model 12: Competition and Fixed Price 

```{r Model12}
CRai12 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIntl + nUCA +  Comp + Comp:nFixed +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai12)

```
THese results are not sufficiently signficiant to justify inclusion, but the interaction between fixed price and competition is potentially interesting and suggests that the demographics of competed contrats may be one factor driving their increase in termination risk. Specifically, one possibility may be that competitive fixed-price contracts are at greater risk of aggressive bids that increase contract risk. 

###Model 13: Fixed Price and Number of Offers

```{r Model13}
CRai13 <- lmer (data=subset(smp,Comp==1),
              sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIntl + nUCA +  lOffer + lOffer:nFixed +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai13)

```

Focusing again on only those contracts that were competed, there does not appear to be a relationship between fixed price contracting and the number of offers. This undercuts the idea that the competition dynamics can be explained as simply relating to aggressive bidding on fixed price contracts.

###Model 14: Competition and Contract Ceiling
```{r Model14}
CRai14 <- lmer (sqrtCrai   ~ lCeil + 
               lDays + nFixed + nIntl + nUCA +  Comp + Comp:lCeil +
               (1 | PSR)  + (1 | What) + (1 | Veh) + (1 | Who) + (1 | StartFY), family=binomial(link="logit"))
display(CRai14)


```

Size does not appear to have a strong relationship with competition when it comes to determining results.



