---
title: "empty_model_multilevel_check"
author: "Greg Sanders"
date: "August 15, 2018"
output: html_document
---


# Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(Hmisc)
library(sjstats)
source("DIIGstat.r")
source("NAICS.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```

## Load in data
```{r Sample}
 load(file="data//def_sample.Rdata")
# save(smp,smp1m,file="data//def_sample.Rdata")



# complete<-!is.na(def$b_Term)&
#   !is.na(def$b_CBre)&
#   !is.na(def$n_Comp)&
#   !is.na(def$l_Ceil)&
#   !is.na(def$l_Days)&
#   !is.na(def$Veh) &
#   !is.na(def$n_Fixed)&
#   !is.na(def$b_Intl)&
#   !is.na(def$b_UCA)&
#   !is.na(def$NAICS)&
#   !is.na(def$NAICS2)&
#   !is.na(def$cl_def6_HHI_lag1)&
#   !is.na(def$US6_avg_sal_lag1)
# # 
# smp<-def[complete,]
# #8818392  to 8818392
# 13057769 to 8335209
# nrow(def[!complete,])/nrow(def)
# sum(def[!complete,]$Action.Obligation,na.rm=TRUE)/sum(def$Action.Obligation,na.rm=TRUE)
# 
# smp1m<-smp[sample(nrow(smp),1000000),]
# smp<-smp[sample(nrow(smp),250000),]
# save(file="data//def_sample.Rdata",smp,smp1m)

# levels(smp$Intl)<- list("Just U.S."=c("Just U.S."), 
#                                 "Any Intl."=c("Any International"))
# levels(smp1m$Intl)<- list("Just U.S."=c("Just U.S."), 
#                                 "Any Intl."=c("Any International"))


```

#ICC Testing
## NAICS
### NAICS level 6
```{r NAICSlevel6}
load(file="Output//naics_empty_models.rdata")

if(!exists("naics06_term"))
naics06_term <- glmer(data=smp,
                 b_Term ~ (1 | NAICS)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,naics06_term)

if(!exists("naics06_cbre"))
naics06_cbre <- glmer(data=smp,
                 b_CBre ~ (1 | NAICS)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,naics06_cbre)

if(!exists("naics06_comp"))
naics06_comp <- glmer(data=smp,
                 b_Comp ~ (1 | NAICS)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,naics06_comp)

```

### NAICS level 5
```{r NAICSlevel5}

if(!exists("naics05_term"))
  naics05_term <- glmer(data=smp,
                 b_Term ~ (1 | NAICS5)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,naics05_term)

if(!exists("naics05_cbre"))
naics05_cbre <- glmer(data=smp,
                 b_CBre ~ (1 | NAICS5)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,naics05_cbre)


if(!exists("naics05_comp"))
naics05_comp <- glmer(data=smp,
                 b_Comp ~ (1 | NAICS5)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,naics05_comp)
```

### NAICS level 4
```{r NAICSlevel4}

if(!exists("naics04_term"))
  naics04_term <- glmer(data=smp,
                        b_Term ~ (1 | NAICS4)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics04_term)

if(!exists("naics04_cbre"))
  naics04_cbre <- glmer(data=smp,
                        b_CBre ~ (1 | NAICS4)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics04_cbre)

if(!exists("naics04_comp"))
  naics04_comp <- glmer(data=smp,
                        b_Comp ~ (1 | NAICS4)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics04_comp)
```

### NAICS level 3
```{r NAICSlevel3}

if(!exists("naics03_term"))
  naics03_term <- glmer(data=smp,
                        b_Term ~ (1 | NAICS3)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics03_term)

if(!exists("naics03_cbre"))
  naics03_cbre <- glmer(data=smp,
                        b_CBre ~ (1 | NAICS3)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics03_cbre)

if(!exists("naics03_comp"))
  naics03_comp <- glmer(data=smp,
                        b_Comp ~ (1 | NAICS3)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics03_comp)
```
### NAICS level 2
```{r NAICSlevel2}

if(!exists("naics02_term"))
  naics02_term <- glmer(data=smp,
                        b_Term ~ (1 | NAICS2)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics02_term)

if(!exists("naics02_cbre"))
  naics02_cbre <- glmer(data=smp,
                        b_CBre ~ (1 | NAICS2)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics02_cbre)

if(!exists("naics02_comp"))
  naics02_comp<- glmer(data=smp,
                       b_Comp ~ (1 | NAICS2)
                       , family=binomial(link="logit"))

get_icc(display=TRUE,naics02_comp)
```


### NAICS 2/3/6
```{r NAICSlevel23456}
smp$NAICS<-factor(smp$NAICS)
smp$NAICS3<-factor(smp$NAICS3)
smp$NAICS<-factor(smp$NAICS)
smp$NAICS2<-factor(smp$NAICS2)
# naics23456_term <- glmer(data=smp,
#                  b_Term ~ (1 | NAICS2/NAICS3/NAICS4/NAICS5/NAICS)
#                   , family=binomial(link="logit"))
#Fails even when everything is a factor Error: couldn't evaluate grouping factor NAICS:(NAICS5:(NAICS4:(NAICS3:NAICS2))) within model frame: try adding grouping factor to data frame explicitly if possible
# naics2346_term <- glmer(data=smp,
#                  b_Term ~ (1 | NAICS2/NAICS3/NAICS4/NAICS)
#                   , family=binomial(link="logit"))
#Fails even when everything is a factor Error: couldn't evaluate grouping factor NAICS:(NAICS4:(NAICS3:NAICS2)) within model frame: try adding grouping factor to data frame explicitly if possible

if(!exists("naics236_term"))
  naics236_term <- glmer(data=smp,
                         b_Term ~ (1 | NAICS2/NAICS3/NAICS)
                         , family=binomial(link="logit"))
get_icc(display=TRUE,naics236_term)

if(!exists("naics236_cbre"))
  naics236_cbre <- glmer(data=smp,
                         b_CBre ~ (1 | NAICS2/NAICS3/NAICS)
                         , family=binomial(link="logit"))
get_icc(display=TRUE,naics236_cbre)

if(!exists("naics236_comp"))
  naics236_comp <- glmer(data=smp,
                         b_Comp ~ (1 | NAICS2/NAICS3/NAICS)
                         , family=binomial(link="logit"))
get_icc(display=TRUE,naics236_comp)


```
### NAICS 2/6
```{r NAICSlevel26}

if(!exists("naics26_term"))
  naics26_term <- glmer(data=smp,
                        b_Term ~ (1 | NAICS2/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics26_term)

if(!exists("naics26_cbre"))
  naics26_cbre <- glmer(data=smp,
                        b_CBre ~ (1 | NAICS2/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics26_cbre)

if(!exists("naics26_comp"))
  naics26_comp <- glmer(data=smp,
                        b_Comp ~ (1 | NAICS2/NAICS)
                        , family=binomial(link="logit"))

get_icc(display=TRUE,naics26_comp)
```
### NAICS 3/6
```{r NAICSlevel36}

if(!exists("naics36_term"))
  naics36_term <- glmer(data=smp,
                        b_Term ~ (1 | NAICS3/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_term)

if(!exists("naics36_cbre"))
  naics36_cbre <- glmer(data=smp,
                        b_CBre ~ (1 | NAICS3/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cbre)

if(!exists("naics36_comp"))
  naics36_comp <- glmer(data=smp,
                        b_Comp ~ (1 | NAICS3/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cbre)
```


### NAICS 4/6
```{r NAICSlevel46}

if(!exists("naics46_term"))
  naics46_term <- glmer(data=smp,
                        b_Term ~ (1 | NAICS4/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics46_term)

if(!exists("naics46_cbre"))
  naics46_cbre <- glmer(data=smp,
                        b_CBre ~ (1 | NAICS4/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics46_cbre)

if(!exists("naics46_comp"))
  naics46_comp <- glmer(data=smp,
                        b_Comp ~ (1 | NAICS4/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics46_comp)
```

### Compare NAICS

```{r Empty_Compare}

save(naics02_cbre,naics02_term,naics02_comp,
     naics03_cbre,naics03_term,naics03_comp,
     naics04_cbre,naics04_term,naics04_comp,
     naics05_cbre,naics05_term,naics05_comp,
     naics06_cbre,naics06_term,naics06_comp,
     naics26_cbre,naics26_term,naics26_comp,
     naics36_cbre,naics36_term,naics36_comp,
     naics46_cbre,naics46_term,naics46_comp,
     naics236_cbre,naics236_term,naics236_comp,
     file="Output//naics_empty_models.rdata")


get_icc(naics02_cbre)
get_icc(naics03_cbre)
get_icc(naics04_cbre)
get_icc(naics05_cbre)
get_icc(naics06_cbre)
get_icc(naics26_cbre)
get_icc(naics36_cbre)
get_icc(naics46_cbre)
get_icc(naics236_cbre)

get_icc(naics02_term)
get_icc(naics03_term)
get_icc(naics04_term)
get_icc(naics05_term)
get_icc(naics06_term)
get_icc(naics26_term)
get_icc(naics36_term)
get_icc(naics46_term)
get_icc(naics236_term)

get_icc(naics02_comp)
get_icc(naics03_comp)
get_icc(naics04_comp)
get_icc(naics05_comp)
get_icc(naics06_comp)
get_icc(naics26_comp)
get_icc(naics36_comp)
get_icc(naics46_comp)
get_icc(naics236_comp)

```
The ideal levels varies some depending on the output variable. On the whole NAICS 3 and NAICS 6 combined seem to explain comparatively high levels of variance when summed and are reasonably balanced between the two levels.

Fiscal year generally has more explanatory power than calendar year.

## Start Year

### Calendar Year
```{r StartCY}
load(file="Output//when_empty_models.rdata")

if(!exists("StartCY_term"))
  StartCY_term <- glmer(data=smp,
                        b_Term ~ (1 | StartCY)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,StartCY_term)

if(!exists("StartCY_cbre"))
  StartCY_cbre <- glmer(data=smp,
                        b_CBre ~ (1 | StartCY)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,StartCY_cbre)

if(!exists("StartCY_term"))
  StartCY_comp <- glmer(data=smp,
                        b_Comp ~ (1 | StartCY)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,StartCY_term)

```

The ICC is highest for ceiling breaches and is backloaded, with 2015 and 2016 having lower than usual odds. This is likely an artifact of those years having fewer completed longer contracts. That said, this should be largely compensated for with the inclusion of initial duration. If this proves challenges to manage, it may be worth considering dropping 2016. 

### Month Unnested
```{r StartMonth}
smp$SignedMonth<-lubridate::month(smp$MinOfSignedDate)

if(!exists("SignedMonth_term"))
  SignedMonth_term <- glmer(data=smp,
                            b_Term ~ (1 | StartCY:SignedMonth)
                            , family=binomial(link="logit"))
get_icc(display=TRUE,SignedMonth_term)

if(!exists("SignedMonth_cbre"))
  SignedMonth_cbre <- glmer(data=smp,
                            b_CBre ~ (1 | StartCY:SignedMonth)
                            , family=binomial(link="logit"))
get_icc(display=TRUE,SignedMonth_cbre)

if(!exists("SignedMonth_comp"))
  SignedMonth_comp <- glmer(data=smp,
                            b_Comp ~ (1 | StartCY:SignedMonth)
                            , family=binomial(link="logit"))
get_icc(display=TRUE,SignedMonth_comp)

```

### Month Nested
```{r NestedMonth}

if(!exists("NestedMonth_term"))
NestedMonth_term <- glmer(data=smp,
                 b_Term ~ (1 | StartCY/SignedMonth)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,NestedMonth_term)

if(!exists("NestedMonth_cbre"))
NestedMonth_cbre <- glmer(data=smp,
                 b_CBre ~ (1 | StartCY/SignedMonth)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,NestedMonth_cbre)

if(!exists("NestedMonth_comp"))
NestedMonth_comp <- glmer(data=smp,
                 b_Comp ~ (1 | StartCY/SignedMonth)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,NestedMonth_comp)

```

### NAICS and Calendar Year
```{r NAICS_StartCY}

if(!exists("NAICS_StartCY_term"))
  NAICS_StartCY_term <- glmer(data=smp,
                              b_Term ~  (1 | NAICS3/NAICS) + (1 | StartCY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_StartCY_term)

if(!exists("NAICS_StartCY_cbre"))
  NAICS_StartCY_cbre <- glmer(data=smp,
                              b_CBre ~  (1 | NAICS3/NAICS) + (1 | StartCY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_StartCY_cbre)

if(!exists("NAICS_StartCY_comp"))
  NAICS_StartCY_comp <- glmer(data=smp,
                              b_Comp ~  (1 | NAICS3/NAICS) + (1 | StartCY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_StartCY_comp)

```

### Compare Signed Dates
```{r Empty_Compare_When}

save(StartCY_cbre,StartCY_term,StartCY_comp,
     SignedMonth_cbre,SignedMonth_term,SignedMonth_comp,
     NestedMonth_cbre,NestedMonth_term,NestedMonth_comp,
     NAICS_StartCY_cbre,NAICS_StartCY_term,NAICS_StartCY_comp,
     file="Output//when_empty_models.rdata")

get_icc(naics36_cbre)
get_icc(StartCY_cbre)
get_icc(SignedMonth_cbre)
get_icc(NestedMonth_cbre)
get_icc(NAICS_StartCY_cbre)

get_icc(naics36_term)
get_icc(StartCY_term)
get_icc(SignedMonth_term)
get_icc(NestedMonth_term)
get_icc(NAICS_StartCY_term)

get_icc(naics36_comp)
get_icc(StartCY_comp)
coef(StartCY_comp)
get_icc(SignedMonth_comp)
get_icc(NestedMonth_comp)
get_icc(NAICS_StartCY_comp)

```
Signed month has ICC values typically below 0.03 and it appears it can be safely left out as start calendar year captures most of the variance. Interestingly, while start year had been most prominent for ceiling breaches no longer stands out once NAICS are incoporated in the model.
##Customer
### Office
```{r Office}

load(file="Output//who_empty_models.rdata")

if(!exists("Office_term"))
  Office_term <- glmer(data=smp,
                       b_Term ~ (1 | Agency:Office)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Office_term)

if(!exists("Office_cbre"))
  Office_cbre <- glmer(data=smp,
                       b_CBre ~ (1 | Agency:Office)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Office_cbre)

if(!exists("Office_comp"))
  Office_comp <- glmer(data=smp,
                       b_Comp ~ (1 | Agency:Office)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Office_comp)

```

### Agency
```{r Agency}
if(!exists("Agency_term"))
  Agency_term <- glmer(data=smp,
                       b_Term ~ (1 | Agency)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Agency_term)

if(!exists("Agency_cbre"))
  Agency_cbre <- glmer(data=smp,
                       b_CBre ~ (1 | Agency)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Agency_cbre)

if(!exists("Agency_comp"))
  Agency_comp <- glmer(data=smp,
                       b_Comp ~ (1 | Agency)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Agency_comp)

```

### Nested Office
```{r NestedOffice}
if(!exists("NestedOffice_term"))
  NestedOffice_term <- glmer(data=smp,
                             b_Term ~ (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,NestedOffice_term)

if(!exists("NestedOffice_cbre"))
  NestedOffice_cbre <- glmer(data=smp,
                             b_CBre ~ (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,NestedOffice_cbre)

if(!exists("NestedOffice_comp"))
  NestedOffice_comp <- glmer(data=smp,
                             b_Comp ~ (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,NestedOffice_comp)

```

### NAICS36 Office
```{r NAICS36_Office}
if(!exists("naics36_Office_term"))
  naics36_Office_term <- glmer(data=smp,
                             b_Term ~  (1 | NAICS3/NAICS) + (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_Office_term)

if(!exists("naics36_Office_cbre"))
  naics36_Office_cbre <- glmer(data=smp,
                             b_CBre ~  (1 | NAICS3/NAICS) + (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_Office_cbre)

if(!exists("naics36_Office_comp"))
  naics36_Office_comp <- glmer(data=smp,
                             b_Comp ~  (1 | NAICS3/NAICS) + (1 | Agency:Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_Office_comp)

```
Office turns out to explain much of the variation previously captured by NAICS36, double checking next out NAICS6 alone holds up.

### NAICS06 Office
```{r NAICS06_Office}
if(!exists("naics06_Office_term"))
  naics06_Office_term <- glmer(data=smp,
                             b_Term ~  (1 | NAICS) + (1 | Agency:Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics06_Office_term)

if(!exists("naics06_Office_cbre"))
  naics06_Office_cbre <- glmer(data=smp,
                             b_CBre ~  (1 | NAICS) + (1 | Agency:Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics06_Office_cbre)

if(!exists("naics06_Office_comp"))
  naics06_Office_comp <- glmer(data=smp,
                             b_Comp ~  (1 | NAICS) + (1 | Agency:Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics06_Office_comp)

```
NAICS06 does come in a bit higher in summed VIF than NAICS36, but only a little.

### NAICS 4/6 Office
```{r naics46_Office}
if(!exists("naics46_Office_term"))
  naics46_Office_term <- glmer(data=smp,
                             b_Term ~  (1 | NAICS4/NAICS) + (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics46_Office_term)

if(!exists("naics46_Office_cbre"))
  naics46_Office_cbre <- glmer(data=smp,
                             b_CBre ~  (1 | NAICS4/NAICS) + (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics46_Office_cbre)

if(!exists("naics46_Office_comp"))
  naics46_Office_comp <- glmer(data=smp,
                             b_Comp ~  (1 | NAICS4/NAICS) + (1 | Agency:Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics46_Office_comp)

```


### NAICS When Office
```{r naics36_When_Office}
# if(!exists("naics36_When_Office_term"))
#   naics36_When_Office_term <- glmer(data=smp,
#                              b_Term ~  (1 | NAICS3/NAICS) + (1 | StartCY) + (1 | Agency:Office)
#                              , family=binomial(link="logit"))
# get_icc(display=TRUE,naics36_When_Office_term)
# 
# if(!exists("naics36_When_Office_cbre"))
#   naics36_When_Office_cbre <- glmer(data=smp,
#                              b_CBre ~  (1 | NAICS3/NAICS)+ (1 | StartCY) + (1 | Agency;Office)
#                              , family=binomial(link="logit"))
# get_icc(display=TRUE,naics36_When_Office_cbre)
# 
# if(!exists("naics36_When_Office_comp"))
#   naics36_When_Office_comp <- glmer(data=smp,
#                              b_Comp ~  (1 | NAICS3/NAICS)+ (1 | StartCY) + (1 | Agency:Office)
#                              , family=binomial(link="logit"))
# get_icc(display=TRUE,naics36_When_Office_comp)

```


### Compare Who
```{r Empty_Compare_Who}

save(Office_cbre,Office_term,Office_comp,
     Agency_cbre,Agency_term,Agency_comp,
     NestedOffice_cbre,NestedOffice_term,NestedOffice_comp,
     naics36_Office_cbre,naics36_Office_term,naics36_Office_comp,
     naics06_Office_cbre,naics06_Office_term,naics06_Office_comp,
     naics46_Office_cbre,naics46_Office_term,naics46_Office_comp,
     # naics36_When_Office_cbre,naics36_When_Office_term,naics36_When_Office_comp,
     file="Output//who_empty_models.rdata")


get_icc(naics36_term)
get_icc(NAICS_StartCY_term)
get_icc(Office_term)
get_icc(Agency_term)
get_icc(NestedOffice_term)
get_icc(naics36_Office_term)
get_icc(naics06_Office_term)
get_icc(naics46_Office_term)
# get_icc(naics36_When_Office_term)


get_icc(naics36_cbre)
get_icc(NAICS_StartCY_cbre)
get_icc(Office_cbre)
get_icc(Agency_cbre)
get_icc(NestedOffice_cbre)
get_icc(naics36_Office_cbre)
get_icc(naics06_Office_cbre)
get_icc(naics46_Office_term)
# get_icc(naics36_When_Office_cbre)

get_icc(naics36_comp)
get_icc(NAICS_StartCY_comp)
get_icc(Office_comp)
get_icc(Agency_comp)
get_icc(NestedOffice_comp)
get_icc(naics36_Office_comp)
get_icc(naics06_Office_comp)
get_icc(naics46_Office_term)
# get_icc(naics36_When_Office_comp)

```
There is some contradiction in which model best serves this category. For Comp, the nested office has the largest summed ICC, but for term this results in an failure to converge and a 0 ICC for agency. Agency:Office alone is respectable for all three so that is used in the combination attempt.
