---
title: "Contract Termination"
author: "Greg Sanders"
date: "Wednesday, February 8, 2017"
output:
  html_document:
    keep_md: yes
--- 

Modeling Likelihood of Contract Termination
============================================================================

#Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(Hmisc)
library(sjstats)
source("DIIGstat.r")
source("NAICS.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start.

## Contract Competition

Modeling comepetition with logit model requires limiting to two staes. We limit it to 0 for sole source and 1 for competition, whether there is 1 or more offers.

##Prepare Data
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.


###Data Transformations and Summary



```{r ReadInData, echo = TRUE}
 # load(file="Data/defense_contract_complete.Rdata")
# head(def)
# debug(transform_contract)
# def<-transform_contract(def)  
 # save(file="Data/transformed_def.Rdata",def)
load(file="Data/transformed_def.Rdata")

```


* b_Crai is a binary variable that has a value of 1 for a ceiling Breach of any size has occured, 0 otherwise. ('r summary(def$b_Crai)
NA_stats(def,"b_Crai"))
* b_Term is a binary variable that has a value of 1 for any contracts that have experienced a partial or complete termination, 0 otherwise. ('r summary(def$b_Term)
NA_stats(def,"b_Term"))
* cl_Offr is a binary variable based on competition. It has a value of 0 for uncompeted contracts and a value of 1 for competition, regardless of number of offers. 'r  summary(def$cl_Offr);
NA_stats(def,"cl_Offr")'
* n_Comp is a numeric variable based on competition and number of offers. It has a value of 0 for uncompeted contracts and a value of 1 for single-offer competition, and a value of 2 for multi-offer competition. 'r summary(def$n_Comp);
NA_stats(def,"n_Comp")'
* n_Offr is a numeric variable based on competition and with more granularity on number offers. It has a value of 0 for uncompeted contracts and a value of 1 for single-offer competition, and a value of 2 for 2-offers, 3 for 3-4 offers, and 4 for 5+ offers. 'r summary(def$n_Offr);
NA_stats(def,"n_Offr")'
* l_Offr is the natural log of the number of offers received. Uncompeted contracts are classified as having received one offer. 'r summary(def$l_Offr);
NA_stats(def,"l_Offr")'
* cl_Ceil is the natural log of the initial contract cost ceiling, in then-year dollars. 'r centered_log_description(def$l_Ceil,"dollars");
NA_stats(def,"l_Ceil")'
* cl_Days is the natural log of the initial maximum duration of the contract, in days. The variable is centered, by subtracting its mean ('r centered_log_description(def$l_Days,"days");
NA_stats(def,"l_Days")' 
* SIDV, MIDV, and OIDV are dummy variables based on the contract vehicle. They correspond to Single-Award IDVs, Multi-Award IDVs, and Other IDVs, respectively, having a value of 1 when the task order has that vehicle type, and having a 0 other. The remaining types, definitive contracts and purchase orders, are intentionally left out. ('r summary(def$SIDV);
summary(def$MIDV);
summary(def$OIDV);
NA_stats(def,"Veh")'
* n_Fixed is a numeric variable based on contract pricing. It has a value of 0 for cost-based, 0.5 or "combination or other", 1 for any fixed price (excluding fixed-price level of effort which is classified as cost-based). ('r summary(def$n_Fixed);
NA_stats(def,"n_Fixed")')
* n_Incent is a numeric variable based on fee type. Ig has a value. 1 for incentive fee or cost sharing, 0.5 or "combination or other", 0 for all remaining types. ('r summary(def$n_Incent);
NA_stats(def,"n_Incent")')
* b_UCA is a binary variable with a value of 1 for contracts/task orders that begin as letter contracts or undefinitized contract awards (UCA) and a value of 0 otherwise. 'r
summary(def$b_UCA);
NA_stats(def,"b_UCA")'
* b_Intl is a binary variable with a value of 1 for contracts/task orders with any transactions performed internationally and a value of 0 otherwise. 'r
summary(def$b_Intl);
NA_stats(def,"b_Intl")'
* PSR is a factor reporting whether a contract is primarily for products/services/R&D. 'r
summary(def$PSR);
NA_stats(def,"PSR")'
* ProdServ is a factor reporting the top Product or Service Code of each contract. 'r
summary(def$ProdServ);
NA_stats(def,"ProdServ")'
* NAICS is a factor reporting the top North American Industrial Classification Code of each contract. 'r
summary(def$NAICS);
NA_stats(def,"NAICS")'
* Agency is a factor reporting the top Contracting Agency of each contract. 'r
summary(def$Agency);
NA_stats(def,"Agency")'
* Office is a factor reporting the top Contracting office of each contract. 'r
summary(def$Office);
NA_stats(def,"Office")'


In addition, l_Ceil and l_Days are rescaled to have an average value of 0 and a standard deviation of one. This standardizes interpretation and prevents a "very large eigen value" error later when l_Ceil:lDay is introduced.


Next, we eliminate missing data entries and then draw a sample. The final computation uses all of the data, but as a computation shortcut, only a subset of the data is needed to allow for processing of models in minutes rather than hours.

###Computational Sample Creation
```{r Sample}
 load(file="data//def_sample.Rdata")


levels(smp$EffComp)
smp$cl_Offr<-smp$EffComp
levels(smp$cl_Offr)<-list("0"=c("No Comp.","1 Offer"),
                           "1"="2+ Offers")
summary(smp$cl_Offr)
summary(smp$EffComp)
smp$cl_Offr<-as.numeric(as.character(smp$cl_Offr))

levels(smp$EffComp)
smp$cl_Offr<-smp$EffComp
levels(smp$cl_Offr)<-list("0"=c("No Comp.","1 Offer"),
                           "1"="2+ Offers")
summary(smp$cl_Offr)
summary(smp$EffComp)
smp$cl_Offr<-as.numeric(as.character(smp$cl_Offr))


# save(smp,smp,file="data//def_sample.Rdata")
#Code to update sample w/o recreating.
# smp<-smp["CSIScontractID"]
# smp<-left_join(smp,def)
# smp<-smp["CSIScontractID"]
# smp<-left_join(smp,def)

  
# complete<-!is.na(def$b_Term)&
#   !is.na(def$cl_Offr)&
#   !is.na(def$n_Comp)&
#   !is.na(def$l_Ceil)&
#   !is.na(def$l_Days)&
#   !is.na(def$Veh) &
#   !is.na(def$n_Fixed)&
#   !is.na(def$b_Intl)&
#   !is.na(def$b_UCA)&
#   !is.na(def$NAICS)&
#   !is.na(def$NAICS2)&
#   !is.na(def$cl_def6_HHI_lag1)&
#   !is.na(def$US6_avg_sal_lag1)
# # 
# smp<-def[complete,]
# #8818392  to 8818392
# 13057769 to 8335209
# nrow(def[!complete,])/nrow(def)
# sum(def[!complete,]$Action.Obligation,na.rm=TRUE)/sum(def$Action.Obligation,na.rm=TRUE)
# 
# smp<-smp[sample(nrow(smp),1000000),]
# smp<-smp[sample(nrow(smp),250000),]
# save(file="data//def_sample.Rdata",smp,smp)

# levels(smp$Intl)<- list("Just U.S."=c("Just U.S."), 
#                                 "Any Intl."=c("Any International"))
# levels(smp$Intl)<- list("Just U.S."=c("Just U.S."), 
#                                 "Any Intl."=c("Any International"))


```

#Initial Logit Model

## Study Variable Consolidation

### Level 6
#### Model NCS6A: def6_HHI_lag1
The expectation of the hypotheses is that a lower rate of consolidation will estimate higher levels of competition.

```{r ModelNCS6A_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"def6_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"def5_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"def4_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"def3_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"def2_HHI_lag1")

#Model
Comp_Cons_NCS6A <- glm (data=smp,
                 cl_Offr ~c_def6_HHI_lag1)
display(Comp_Cons_NCS6A)


# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")



#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6A,type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS6A,Comp_Cons_NCS6A)

```
Both the summary statistics and the results are surprising. More consolidated sectors are more likely to have competition.

#### Model NCS6B: l_def6_HHI_lag1

Expectations are  unchanged.
```{r ModelNCS6A_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"l_def6_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"l_def5_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"l_def4_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"l_def3_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"l_def2_HHI_lag1")


#Model
Comp_Cons_NCS6B <- glm (data=smp,
                 cl_Offr ~cl_def6_HHI_lag1)
display(Comp_Cons_NCS6B)


# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")
# 


#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6A,Comp_Cons_NCS6B,type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS6A,Comp_Cons_NCS6B)
ggplot(Comp_Cons_NCS6B)+geom_point(aes(x=.fitted, y=.resid))




```
Switching to log reomves the uneven distribution with most entries on the lefthand side from the residuals though it doesn't shrink them. 

#### Model NCS6C: Defense to Overall ratio
The lower the ratio of defense obligations to reciepts in the overall economy, the more potential competitors, but also the less developed industrial base. Given the difficulties the DoD has access many more traditional firms, a very low ratio may estimate a lower rate of competition. Interestingly both contradictory expectations find some support in the exploratory statistics, which show a sweet spot well below 5% where competition seems to peak.
```{r ModelNCS6C_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"capped_def6_ratio_lag1")
      summary_continuous_plot(metric="comp",smp,"l_def6_ratio_lag1")
      summary_continuous_plot(metric="comp",smp,"capped_def5_ratio_lag1")
      summary_continuous_plot(metric="comp",smp,"l_def5_ratio_lag1")
      
      summary_continuous_plot(metric="comp",smp,"capped_def4_ratio_lag1")
      summary_continuous_plot(metric="comp",smp,"l_def4_ratio_lag1")
      summary_continuous_plot(metric="comp",smp,"capped_def3_ratio_lag1")
      summary_continuous_plot(metric="comp",smp,"l_def3_ratio_lag1")
      summary_continuous_plot(metric="comp",smp,"capped_def2_ratio_lag1")
      summary_continuous_plot(metric="comp",smp,"l_def2_ratio_lag1")
      


#Model
Comp_Cons_NCS6C <- glm (data=smp,
                 cl_Offr ~cl_def6_HHI_lag1+cl_def6_ratio_lag1
                 )
glmer_examine(Comp_Cons_NCS6C,display=TRUE)

# 
# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")




#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6B,Comp_Cons_NCS6C,
                       type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS6B,Comp_Cons_NCS6C)



```
The results align with the hypothesis and are significant, although the magnitude is minimal.


#### Model NCS6D: cl_def6_obl_lag1
Defense sector obligations are added to better adjust for the fact that larger sectors tend to have lower HHI indices if only because they include a broader range of activities. In addition, the industrial base is likely more diverse when markets are larger. Thus greater defense in a given sector are expected to estimate a greater likelihood over multi-offer competition. The descriptive statistics tell a somewhat different story for the vary largest defense sectors, which have lower numbers of offers.
Expectations are  unchanged.
```{r ModelNCS6D_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"def6_obl_lag1")


summary_continuous_plot(metric="comp",smp,"l_def6_obl_lag1")
summary_continuous_plot(metric="comp",smp,"def5_obl_lag1")

summary_continuous_plot(metric="comp",smp,"l_def5_obl_lag1")
summary_continuous_plot(metric="comp",smp,"def4_obl_lag1")

summary_continuous_plot(metric="comp",smp,"l_def4_obl_lag1")
summary_continuous_plot(metric="comp",smp,"def3_obl_lag1")

summary_continuous_plot(metric="comp",smp,"l_def4_obl_lag1")
summary_continuous_plot(metric="comp",smp,"def2_obl_lag1")

summary_continuous_plot(metric="comp",smp,"l_def2_obl_lag1")

#Model
Comp_Cons_NCS6D <- glm (data=smp,
                 cl_Offr ~cl_def6_HHI_lag1+cl_def6_obl_lag1+cl_def6_ratio_lag1)
glmer_examine(Comp_Cons_NCS6D)



#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6C,Comp_Cons_NCS6D,
                       
                       type="text",digits=2)


summary_regression_compare(Comp_Cons_NCS6C,Comp_Cons_NCS6D)



```
Estimated results occur. Residuals increase in magnitude for consolidation but reduce for competition.


#### Model NCS6E: Average Salary
Average salary can be an proxy for unobserved skill requirements and thus complexity. We expect that a greater skill requirement will estimate fewer available competitors and thus fewer offers. The descriptive statistics appear to contradict this belief.
```{r ModelNCS6E_Comp}
#Frequency Plot for unlogged ceiling


summary_continuous_plot(metric="comp",smp,"US6_avg_sal_lag1")

summary_continuous_plot(metric="comp",smp,"l_US6_avg_sal_lag1")

summary_continuous_plot(metric="comp",smp,"US5_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US4_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US3_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US2_avg_sal_lag1")

#Model
#cl_def6_obl_lag1

Comp_Cons_NCS6E <- glm (data=smp,
                 cl_Offr ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 )
glmer_examine(Comp_Cons_NCS6E)



# 
# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")




#Plot residuals versus fitted
 stargazer::stargazer(Comp_Cons_NCS6C,Comp_Cons_NCS6D,Comp_Cons_NCS6E,
                       
                       type="text",digits=2)



summary_regression_compare(Comp_Cons_NCS6D,Comp_Cons_NCS6E)




```
The results were significant but in the opposite direction expected. This also reverses the sign on ratio, contrary to hypothesis. That said, the reversal of sign for HHI is in keeping with the hypothesis.


### Level 5
#### Model NCS5A: cl_def5_HHI
```{r ModelNCS5A_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"l_def6_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"l_def5_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"l_def4_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"l_def3_HHI_lag1")
summary_continuous_plot(metric="comp",smp,"l_def2_HHI_lag1")


#Model
Comp_Cons_NCS5A <- glm (data=smp,
                 cl_Offr ~cl_def5_HHI_lag1)
glmer_examine(Comp_Cons_NCS5A)


# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")
# 


#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6B,Comp_Cons_NCS6D,Comp_Cons_NCS6E,Comp_Cons_NCS5A,type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS6B,Comp_Cons_NCS5A)


```
More significant HHI to offers than 6, but still the opposite of expecations.

#### Model NCS5B: Defense to Overall ratio
The higher the ratio of defense obligations to reciepts in the overall economy, the DoD holds a monosopy over a sector. Given the challenges of monosopy, the a higher ratio estimates a greater  risk of ceiling breaches.
```{r ModelNCS5Bl_Offr}
#Frequency Plot for unlogged ceiling




summary_continuous_plot(metric="comp",smp,"capped_def5_ratio_lag1")
summary_continuous_plot(metric="comp",smp,"l_def5_ratio_lag1")

#Model
Comp_Cons_NCS5B <- glm (data=smp,
                 cl_Offr ~cl_def5_HHI_lag1+cl_def5_ratio_lag1 
                 )
glmer_examine(Comp_Cons_NCS5B)

# 
# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")




#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6C,Comp_Cons_NCS6E,Comp_Cons_NCS5A,Comp_Cons_NCS5B,
                       type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS5A,Comp_Cons_NCS5B)
summary_regression_compare(Comp_Cons_NCS6D,Comp_Cons_NCS5B)



```
The results align with the hypothesis, although the magnitude is minimal, if larger in magnitude than the level 6 version.

#### Model NCS5C: cl_def5_obl_lag1
Defense sector obligations are added to better adjust for the fact that larger sectors tend to have lower HHI indices if only because they include a broader range of activities. In addition, Acting somewhat as a proxy for MDAP status, larger sectors may also have a greater risk of cascading problems. Thus greater defense obligations in a given sector are expected to estimate a greater likelihood over ceiling breaches,
Expectations are  unchanged.
```{r ModelNCSD_Comp}


#Model
Comp_Cons_NCS5C <- glm (data=smp,
                 cl_Offr ~cl_def5_HHI_lag1+cl_def5_ratio_lag1+cl_def5_obl_lag1)
glmer_examine(Comp_Cons_NCS5C)


# 
# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")




#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6D,Comp_Cons_NCS6E,Comp_Cons_NCS5A,Comp_Cons_NCS5B,Comp_Cons_NCS5C,
                       type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS5B,Comp_Cons_NCS5C)


```
Size seems to ad less to the model at level 5 than level 6.

#### Model NCS5D: Average Salary
Average salary can be an proxy for unobserved skill requirements and thus complexity. We expect that a greater skill requirement will estimate fewer available competitors and thus fewer offers. The descriptive statistics appear to contradict this belief.
```{r ModelNCS5D_Comp}
#Frequency Plot for unlogged ceiling



summary_continuous_plot(metric="comp",smp,"US5_avg_sal_lag1")

#Model
#cl_def5_obl_lag1

Comp_Cons_NCS5D <- glm (data=smp,
                 cl_Offr ~cl_def5_HHI_lag1+cl_def5_ratio_lag1+cl_def5_obl_lag1+
                  cl_US5_avg_sal_lag1 )
glmer_examine(Comp_Cons_NCS5D)



# 
# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")




#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6E,Comp_Cons_NCS5A,Comp_Cons_NCS5B,Comp_Cons_NCS5C,Comp_Cons_NCS5D,
                       type="text",
                       digits=2)




summary_regression_compare(Comp_Cons_NCS5C,Comp_Cons_NCS5D)




```
The results were significant but in the opposite direction expected. This also reverses the sign on everthing else, contrary to expectations in hte case of ratio and obl. That said, the reversal of sign for HHI is in keeping with the hypothesis.

### Level 4
#### Model NCS4A: cl_def4_HHI
```{r ModelNCS4A_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"l_def4_HHI_lag1")


#Model
Comp_Cons_NCS4A <- glm (data=smp,
                 cl_Offr ~cl_def4_HHI_lag1)
display(Comp_Cons_NCS4A)


# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")
# 


#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6B,Comp_Cons_NCS6D,Comp_Cons_NCS6E,Comp_Cons_NCS5A,Comp_Cons_NCS4A,type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS6B,Comp_Cons_NCS4A)


```

Level 4 HHI seems to slightly out perform level 6 and 5. Though is still opposite of expectations.



#### Model NCS4B: Defense to Overall ratio
The higher the ratio of defense obligations to reciepts in the overall economy, the DoD holds a monosopy over a sector. Given the challenges of monosopy, the a higher ratio estimates a greater  risk of ceiling breaches.
```{r ModelNCS4cl_Offr}
#Frequency Plot for unlogged ceiling


summary_continuous_plot(metric="comp",smp,"capped_def4_ratio_lag1")
summary_continuous_plot(metric="comp",smp,"l_def4_ratio_lag1")

#Model
Comp_Cons_NCS4B <- glm (data=smp,
                 cl_Offr ~cl_def4_HHI_lag1+cl_def4_ratio_lag1, 
                 )
glmer_examine(Comp_Cons_NCS4B)



#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6C,Comp_Cons_NCS5B,Comp_Cons_NCS4A,Comp_Cons_NCS4B,
                       type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS4A,Comp_Cons_NCS4B)
summary_regression_compare(Comp_Cons_NCS5B,Comp_Cons_NCS4B)




```
The results align with the hypothesis, although the magnitude is small, if larger in magnitude than the level 5 or level 6 version.



#### Model NCS4C: cl_def4_obl_lag1
Defense sector obligations are added to better adjust for the fact that larger sectors tend to have lower HHI indices if only because they include a broader range of activities. In addition, Acting somewhat as a proxy for MDAP status, larger sectors may also have a greater risk of cascading problems. Thus greater defense obligations in a given sector are expected to estimate a greater likelihood over ceiling breaches,
Expectations are  unchanged.
```{r ModelNCS4C_Comp}


#Model
Comp_Cons_NCS4C <- glm (data=smp,
                 cl_Offr ~cl_def4_HHI_lag1+cl_def4_ratio_lag1+cl_def4_obl_lag1)
glmer_examine(Comp_Cons_NCS4C)


# 
# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")




#Plot residuals versus fitted
stargazer::stargazer(Comp_Cons_NCS6D,Comp_Cons_NCS5C,Comp_Cons_NCS4B,Comp_Cons_NCS4C,
                       type="text",
                       digits=2)



  #Compare to prior at same level
summary_regression_compare(Comp_Cons_NCS4B,Comp_Cons_NCS4C)
#Compare to prior at lower level
summary_regression_compare(Comp_Cons_NCS6D,Comp_Cons_NCS4C)
```
Size seems to add only a little less to the model at level 4 than level 6. In  general, magnitudes are  greater, though for HHI in an unexpected direction.

#### Model NCS4D: Average Salary
Average salary can be an proxy for unobserved skill requirements and thus complexity. We expect that a greater skill requirement will estimate fewer available competitors and thus fewer offers. The descriptive statistics appear to contradict this belief.
```{r ModelNCS4D_Comp}
#Frequency Plot for unlogged ceiling



summary_continuous_plot(metric="comp",smp,"US4_avg_sal_lag1")

#Model
#cl_def4_obl_lag1

Comp_Cons_NCS4D <- glm (data=smp,
                 cl_Offr ~cl_def4_HHI_lag1+cl_def4_ratio_lag1+cl_def4_obl_lag1+
                  cl_US4_avg_sal_lag1 )
glmer_examine(Comp_Cons_NCS4D)



# 
# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")




#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6E,Comp_Cons_NCS5D,Comp_Cons_NCS4A,Comp_Cons_NCS4B,Comp_Cons_NCS4C,Comp_Cons_NCS4D,
                       type="text",
                       digits=2)




summary_regression_compare(Comp_Cons_NCS4C,Comp_Cons_NCS4D)




```
The results were significant but in the opposite direction expected. Nothing flipps signs in this iteration. The AIC however, is notably higher than for level 5 and 6 results.
### Level 3
#### Model NCS3A: cl_def3_HHI
```{r ModelNCS3A_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"l_def3_HHI_lag1")


#Model
Comp_Cons_NCS3A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1)
display(Comp_Cons_NCS3A)


# #Plot the fitted model plot
# CBre_Comp_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(CBre_Comp_02A))}
# 
# #Competition curves
# fitted_cbre_model(smp,"cl_Ceil") + stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = CBre_Comp_02A_curve, 
#                              args=list(Comp=2),color="blue")
# 


#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6B,Comp_Cons_NCS6E,Comp_Cons_NCS5A,Comp_Cons_NCS4A,Comp_Cons_NCS3A,type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS6B,Comp_Cons_NCS3A)


```

HHI becomes a more powerful predictor at each level, but never in the expecteddirection.


#### Model NCS3B: Defense to Overall ratio
The higher the ratio of defense obligations to reciepts in the overall economy, the DoD holds a monosopy over a sector. Given the challenges of monosopy, the a higher ratio estimates a greater  risk of ceiling breaches.
```{r ModelNCS3cl_Offr}
#Frequency Plot for unlogged ceiling




summary_continuous_plot(metric="comp",smp,"capped_def3_ratio_lag1")
summary_continuous_plot(metric="comp",smp,"l_def3_ratio_lag1")

#Model
Comp_Cons_NCS3B <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1, 
                 )
glmer_examine(Comp_Cons_NCS3B)


#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6C,Comp_Cons_NCS5B,Comp_Cons_NCS4B,Comp_Cons_NCS3A,Comp_Cons_NCS3B,
                       type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS3A,Comp_Cons_NCS3B)
summary_regression_compare(Comp_Cons_NCS4B,Comp_Cons_NCS3B)


```
The results align with the hypothesis, although the magnitude is small, if larger in magnitude than the level 4 version. Although the residuals also notably increase in magnitude with the introduction of this variable.


#### Model NCS3C: cl_def3_obl_lag1
Defense sector obligations are added to better adjust for the fact that larger sectors tend to have lower HHI indices if only because they include a broader range of activities. In addition, Acting somewhat as a proxy for MDAP status, larger sectors may also have a greater risk of cascading problems. Thus greater defense obligations in a given sector are expected to estimate a greater likelihood over ceiling breaches,
Expectations are  unchanged.
```{r ModelNCS3C_Comp}


#Model
Comp_Cons_NCS3C <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+cl_def3_obl_lag1)
glmer_examine(Comp_Cons_NCS3C)

Comp_Cons_NCS3C2 <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_obl_lag1)
glmer_examine(Comp_Cons_NCS3C2)


#Plot residuals versus fitted
stargazer::stargazer(Comp_Cons_NCS6D,Comp_Cons_NCS5C,Comp_Cons_NCS4C,
                       Comp_Cons_NCS3C2,type="text",
                       digits=2)



  #Compare to prior at same level
summary_regression_compare(Comp_Cons_NCS3B,Comp_Cons_NCS3C2)
#Compare to prior at lower level
summary_regression_compare(Comp_Cons_NCS6D,Comp_Cons_NCS3C2)
```
Size and ratio have a VIF challenge. Keeping ratio as it has more predictive power.


#### Model NCS3D: Average Salary
Average salary can be an proxy for unobserved skill requirements. We expect that a greater skill requirement will estimate a greater risk of ceiling breaches.
```{r ModelNCS3D_Comp}
#Frequency Plot for unlogged ceiling


summary_continuous_plot(metric="comp",smp,"US3_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"l_US3_avg_sal_lag1")

summary_continuous_plot(metric="comp",smp,"US5_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US4_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US3_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US2_avg_sal_lag1")

#Model

Comp_Cons_NCS3D <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  cl_US3_avg_sal_lag1)
glmer_examine(Comp_Cons_NCS3D)






#Plot residuals versus fitted
 stargazer::stargazer(Comp_Cons_NCS6E,Comp_Cons_NCS5D,Comp_Cons_NCS4D,Comp_Cons_NCS3B,Comp_Cons_NCS3C2,Comp_Cons_NCS3D,
                       
                       type="text",digits=2)


summary_regression_compare(Comp_Cons_NCS3B,Comp_Cons_NCS3D)
summary_regression_compare(Comp_Cons_NCS3C2,Comp_Cons_NCS3D)


```
Average salary continues to surprise, but even without defense obligations this model has the lowest AIC.


#### Model NCS3E: NAICS 6 and NAICS 3
Consolidation at lessa nd more granular levels may have different effects. Efficiencies are often used to describe sectors, like utilities, with high barriers to entry. Many of these aspects seem like they would already be captured at less granular NAICS levels, e.g. power plants, rather than more specific NAICS levels, like solar vs. coal. As a result, consolidation for more granular NAICS codes should estimate higher rates of ceiling breaches compared to less granular NAICS code.

We'll start by adding in everything from both models and seeing what violates VIF.
```{r ModelNCS3E_Comp}
#Frequency Plot for unlogged ceiling


#Model
Comp_Cons_NCS3E <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1  )
glmer_examine(Comp_Cons_NCS3E,display=TRUE)
#Average salary 6 has the highest VIF though but both average salaries are over 2.0 and 3 is more contrary to expectations. Taking it out.
Comp_Cons_NCS3E2 <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1  )
glmer_examine(Comp_Cons_NCS3E2,display=TRUE)



#Plot residuals versus fitted
#Plot residuals versus fitted
 stargazer::stargazer(Comp_Cons_NCS6E,Comp_Cons_NCS5D,Comp_Cons_NCS4D,Comp_Cons_NCS3B,Comp_Cons_NCS3C2,Comp_Cons_NCS3D,Comp_Cons_NCS3E2,
                       
                       type="text",digits=2)


summary_regression_compare(Comp_Cons_NCS3D,Comp_Cons_NCS3E2)
summary_regression_compare(Comp_Cons_NCS6E,Comp_Cons_NCS3E2)


```
The expectation is upheld. Avereage Salary 3 was removed from the model for VIF reasons and because it is less precise than average salary 3.


### Level 2
#### Model NCS2A: cl_def2_HHI
```{r ModelNCS2A_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"l_def2_HHI_lag1")


#Model
Comp_Cons_NCS2A <- glm (data=smp,
                 cl_Offr ~cl_def2_HHI_lag1)
display(Comp_Cons_NCS2A)



#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6B,Comp_Cons_NCS5A,Comp_Cons_NCS4A,Comp_Cons_NCS3A,Comp_Cons_NCS2A,type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS6B,Comp_Cons_NCS2A)


```

Expectations not met. Level 2 HHI seems to slightly out perform level 6, but underperform level 3.

#### Model NCS2B: Defense to Overall ratio
The higher the ratio of defense obligations to reciepts in the overall economy, the DoD holds a monosopy over a sector. Given the challenges of monosopy, the a higher ratio estimates a greater  risk of ceiling breaches.
```{r ModelNCS2cl_Offr}
#Frequency Plot for unlogged ceiling




summary_continuous_plot(metric="comp",smp,"capped_def2_ratio_lag1")
summary_continuous_plot(metric="comp",smp,"l_def2_ratio_lag1")

#Model
Comp_Cons_NCS2B <- glm (data=smp,
                 cl_Offr ~cl_def2_HHI_lag1+cl_def2_ratio_lag1
                 )
glmer_examine(Comp_Cons_NCS2B)


#Plot residuals versus fitted
#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS6C,Comp_Cons_NCS5B,Comp_Cons_NCS4B,Comp_Cons_NCS3B,Comp_Cons_NCS2A,Comp_Cons_NCS2B,
                       type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS2A,Comp_Cons_NCS2B)
summary_regression_compare(Comp_Cons_NCS3B,Comp_Cons_NCS2B)

```
The results do align with the expectation, but with a minimal magnitude




#### Model NCS2C: cl_def2_obl_lag1
Defense sector obligations are added to better adjust for the fact that larger sectors tend to have lower HHI indices if only because they include a broader range of activities. In addition, Acting somewhat as a proxy for MDAP status, larger sectors may also have a greater risk of cascading problems. Thus greater defense obligations in a given sector are expected to estimate a greater likelihood over ceiling breaches,
Expectations are  unchanged.
```{r ModelNCS2C_Comp}


#Model
Comp_Cons_NCS2C <- glm (data=smp,
                 cl_Offr ~cl_def2_HHI_lag1+cl_def2_ratio_lag1+cl_def2_obl_lag1)
glmer_examine(Comp_Cons_NCS2C,display=TRUE)

Comp_Cons_NCS2C2 <- glm (data=smp,
                 cl_Offr ~cl_def2_HHI_lag1+cl_def2_obl_lag1)
glmer_examine(Comp_Cons_NCS2C,display=TRUE)




#Plot residuals versus fitted
stargazer::stargazer(Comp_Cons_NCS6D,Comp_Cons_NCS5C,Comp_Cons_NCS4C,
                       Comp_Cons_NCS3B,Comp_Cons_NCS3C2,Comp_Cons_NCS2B,Comp_Cons_NCS2C2,type="text",
                       digits=2)



  #Compare to prior at same level
summary_regression_compare(Comp_Cons_NCS2B,Comp_Cons_NCS2C2)
#Compare to prior at lower level
summary_regression_compare(Comp_Cons_NCS6D,Comp_Cons_NCS2C2)


```
Size seems to add less to the model at level 2 than level 6. That said it still has greater magnitude and lower AIC than the model with ratio, so keeping this one.


#### Model NCS2D: Average Salary
Average salary can be an proxy for unobserved skill requirements. We expect that a greater skill requirement will estimate a greater risk of ceiling breaches.
```{r ModelNCS2D_Comp}
#Frequency Plot for unlogged ceiling


summary_continuous_plot(metric="comp",smp,"US2_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"l_US2_avg_sal_lag1")

summary_continuous_plot(metric="comp",smp,"US5_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US4_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US2_avg_sal_lag1")
summary_continuous_plot(metric="comp",smp,"US2_avg_sal_lag1")

#Model

Comp_Cons_NCS2D <- glm (data=smp,
                 cl_Offr ~cl_def2_HHI_lag1+cl_def2_obl_lag1+
                  cl_US2_avg_sal_lag1 )
glmer_examine(Comp_Cons_NCS2D)






#Plot residuals versus fitted
 stargazer::stargazer(Comp_Cons_NCS6E,Comp_Cons_NCS5D,Comp_Cons_NCS4D,Comp_Cons_NCS3D,
                      Comp_Cons_NCS2B,Comp_Cons_NCS2C2,Comp_Cons_NCS2D,
                       
                       type="text",digits=2)



summary_regression_compare(Comp_Cons_NCS2C2,Comp_Cons_NCS2D)
summary_regression_compare(Comp_Cons_NCS6E,Comp_Cons_NCS2D)
summary_regression_compare(Comp_Cons_NCS3D,Comp_Cons_NCS2D)


```
Contrary to expectation but significant.

#### Model NCS2E: NAICS 6 and NAICS 2
Consolidation at lessa nd more granular levels may have different effects. Efficiencies are often used to describe sectors, like utilities, with high barriers to entry. Many of these aspects seem like they would already be captured at less granular NAICS levels, e.g. power plants, rather than more specific NAICS levels, like solar vs. coal. As a result, consolidation for more granular NAICS codes should estimate higher rates of ceiling breaches compared to less granular NAICS code.

We'll start by adding in everything from both models and seeing what violates VIF.
```{r ModelNCS2E_Comp}
#Frequency Plot for unlogged ceiling


#Model
Comp_Cons_NCS2E <- glm (data=smp,
                 cl_Offr ~cl_def2_HHI_lag1+cl_def2_obl_lag1+
                  cl_US2_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1  )
glmer_examine(Comp_Cons_NCS2E)

#Average salary 6 has the highest VIF though but both average salaries are over 2.0 and 2 is more contrary to expectations and less deatiled. Taking it out.
Comp_Cons_NCS2E2 <- glm (data=smp,
                 cl_Offr ~cl_def2_HHI_lag1+cl_def2_obl_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1  )
glmer_examine(Comp_Cons_NCS2E2)


#Plot residuals versus fitted
 stargazer::stargazer(Comp_Cons_NCS3E2,Comp_Cons_NCS2D,Comp_Cons_NCS2E2,
                       type="text",digits=2)


summary_regression_compare(Comp_Cons_NCS3E2,Comp_Cons_NCS2E2)
summary_regression_compare(Comp_Cons_NCS2D,Comp_Cons_NCS2E2)
summary_regression_compare(Comp_Cons_NCS2D,Comp_Cons_NCS2E2)



```
The expectations is upheld. AIC is  lower for the level3/level 6 version, so sticking with that.


##Scope Variables
###Model 02A: Cost Ceiling
Contract size is one proxy for contract complexity, which raises barriers to entry and reduces the number of qualified vendors. Thus contract size is expected to estimate a smaller number of offers.

```{r Model02A_Comp}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(metric="comp",smp,"UnmodifiedContractBaseAndAllOptionsValue",
               bins=1000)
summary_continuous_plot(subset(smp,UnmodifiedContractBaseAndAllOptionsValue<100000000),
               "UnmodifiedContractBaseAndAllOptionsValue",
               metric="comp")

#Frequency Plot for logged ceiling
summary_continuous_plot(metric="comp",smp,"l_Ceil")


#Model
Comp_Cons_02A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + cl_Ceil )
glmer_examine(Comp_Cons_02A,display=TRUE)

#Plot residuals versus fitted
  stargazer::stargazer(Comp_Cons_NCS3E2, Comp_Cons_02A,type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_NCS3E2,Comp_Cons_02A)


```

Contract ceiling has a significant relationship in the expected direction.






###Model 02B: Maximum Duration
The study team did not have strong apriori expectation on the effect on contract duration. Past research has found that longer contracts offer stability and are often more appealing to vendors but may also indicate increased complexity. Examining the descriptive stats, the second logic seems to win out. We expect that initial duration contracts will have fewer offers.

```{r Model02B_Comp}
#Frequency Plot for max duration
summary_continuous_plot(metric="comp",smp,"UnmodifiedDays",
               bins=1000)

#Frequency Plot for logged max duration
summary_continuous_plot(metric="comp",smp,"l_Days")



#Model
Comp_Cons_02B <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days )
glmer_examine(Comp_Cons_02B,display=TRUE)


  stargazer::stargazer(Comp_Cons_02A,Comp_Cons_02B,type="text",
                       digits=2)

summary_regression_compare(Comp_Cons_02A,Comp_Cons_02B)

```
The descriptive stat based expectation was upheld.




##Contract Vehicle
### Model 03A: Contract Vehicles
Our dataset includes both stand alone contract awards and task orders that are under larger indefinite delivery vehilces (IDVs). We do not have clear expectations on single-award IDCs or BPA/BOA. The baseline form of definitive contracts are commonly used in industry and do not have an intrinsic requirement to compete to compete. Multi-award IDCs and FSS/GWACs do have such a requirements, but also have a structure intended to insure competition, so they may estimate a lower rate of offers than definitive contracts but a higher rate than other forms.


```{r Model03A_Comp}
#Frequency Plot
summary_discrete_plot(metric="comp",smp,"Veh")





#Model
Comp_Cons_03A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh)
glmer_examine(Comp_Cons_03A,display=TRUE)


#Plot the fitted values vs actual results
stargazer::stargazer(Comp_Cons_02B,Comp_Cons_03A,type="text",
                       digits=2)


summary_regression_compare(Comp_Cons_02B,Comp_Cons_03A)

```

The greater numbmer of offers for definitive contracts is confirmed. Somewhat surprisingly, single-award IDCs receive a high number of offers, though this reflects competition for tha overall vehicle and not each specific task order like for Multiple Award IDCs.




##Type of Contract

The next step adds a measure for whether the contract was cost-based or fixed-price. Prior CSIS research has found that fixed-price contracts do face a higher risk of termination across the board.



###Model 04A: Fixed-Price Numerical
While fixed-price contracts can be higher risk, they are also standard in industry and do not require cost accounting standards. Closer to fixed-price contracts are expected to estimate  higher number of offers.
```{r Model04A}

#Frequency Plot
summary_discrete_plot(metric="comp",smp,"FxCb")


#Create the model
Comp_Cons_04A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   n_Fixed)
glmer_examine(Comp_Cons_04A,display=TRUE)



stargazer::stargazer(Comp_Cons_03A,Comp_Cons_04A,type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_03A,Comp_Cons_04A)

```

And fixed price contracts do indeed have a significant coefficient that correlates with a greater number of offer.


###Model 04B: Fixed-Price Bins
This appraoch treats combination as a seperate category of contracts rather than a mid point between fixed-price and cost base. The expectation is that it will still fall in the middle between the two when estimating the number of offers, since fixed-price is the base, this means that both it and cost-based would have a negative coefficient. 
```{r Model04B}

#Frequency Plot
summary_discrete_plot(metric="comp",smp,"FxCb")


#Create the model

Comp_Cons_04B <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   FxCb)
glmer_examine(Comp_Cons_04B,display=TRUE)

stargazer::stargazer(Comp_Cons_04A,Comp_Cons_04B,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_04A,Comp_Cons_04B)

```

Combo/Other contracts do not end up in the middle and are instead not significant, otherwise the results are as expcted.


###Model 04C: Pricing Detail


The more commercial like models, firm-fixed price and time & materials/labor hours/ fixed price;level of effort have fewer requirements for cost accounting and other standards not common in the commercial sector. The baseline condition of firm fixed price wwill estimate greater number of offers aswill T&M/LH/FP:LoE. 
```{r Model04C}

#Frequency Plot
summary_discrete_plot(metric="comp",smp,"FxCb")
summary_discrete_plot(metric="comp",smp,"Fee")
summary_discrete_plot(metric="comp",smp,"FxCb","Fee")



summary_discrete_plot(metric="comp",smp,"Pricing",rotate=FALSE)

#Create the model
Comp_Cons_04C <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   Pricing)
glmer_examine(Comp_Cons_04C,display=TRUE)


stargazer::stargazer(Comp_Cons_04A,Comp_Cons_04B,Comp_Cons_04C,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_04A,Comp_Cons_04B)

```
Labor Hours/T&M/FFP:LoE proved associated with even more offers than FFP, but Fixed-PRice other is the clear winner. Oddly including this breakout resulted in larger ceilings now predicting more offers.

###Model 04D: Incentive Fees

In the performance of the defense acquisition system report, the benefits found were reduced cost overruns. Their cost sharing might  be more popular than other forms of cost-based contracts, but the cost-accounting is likely to be a barrier to entry and  the  coefficient for other fixed price is  already quite high. Thus the expectation is that incentive fees will estimate a slightly lower rate of offers than firm fixed price contracts.

```{r Model04D_Comp}

#Frequency Plot
summary_discrete_plot(metric="comp",smp,"Fee")
summary_discrete_plot(metric="comp",smp,"PricingFee")


summary(factor(smp$PricingFee))

#Create the model
Comp_Cons_04D <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee)
glmer_examine(Comp_Cons_04D)


stargazer::stargazer(Comp_Cons_04A,Comp_Cons_04B,Comp_Cons_04C,Comp_Cons_04D,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_04C,Comp_Cons_04D)

```

Oddly the number of offers for incentive fee contracts is notably lower than cost-based contracts.

###Model 04E: Undefinitized Contract Awards
Undefinitized Contract Awards allow for quick action in situations where there is not time or information to establish all of a contracts properties at the time of signing. These circumstances are often not conducive to competing or receiving multiple offers and thus UCA is expected to estimate fewer offers.


```{r Model04E_Comp}

#Frequency Plot
summary_discrete_plot(metric="comp",smp,"UCA")



#Create the model
Comp_Cons_04E <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+UCA)

glmer_examine(Comp_Cons_04E)


stargazer::stargazer(Comp_Cons_04D,Comp_Cons_04E,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_04D,Comp_Cons_04E)


```
Expectations hold.


##Place of Performance
###Model 05A: Any International

International contracts may often offer fewer known options to DoD customer and a more challenging operating environment. And thus international place of performance contracts are expected to estimate fewer offers. Interestingly, in the descriptive stats, they are more competed but still receive fewer offers, which is not inconsistent with this expectation.
```{r Model05A_Comp}

#Frequency Plot
summary_discrete_plot(metric="comp",smp,"Intl")



#Create the model
Comp_Cons_05A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl)

glmer_examine(Comp_Cons_05A)


stargazer::stargazer(Comp_Cons_04E,Comp_Cons_05A,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_04E,Comp_Cons_05A)



```

International performance of contract had a positive  coefficent as expected.

##Who
Adding agency is a computationally light way of considering the eventual inclusion of agency and office.


###Model 06A: Agency
This inclusion is not intended to study agenc directly, but to see a blunt version of effect inclusion on other variables.
```{r Model06A}
    #Frequency Plot
  summary_discrete_plot(def,"Agency",rotate_text=TRUE)


#Create the model
Comp_Cons_06A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   Agency)

glmer_examine(Comp_Cons_06A)


  stargazer::stargazer(Comp_Cons_05A,Comp_Cons_06A,type="text",
                       digits=2)
  
summary_regression_compare(Comp_Cons_05A,Comp_Cons_06A)

rm(Comp_Cons_06A,Comp_Cons_06A2)
```



##What
### Model 07A: NAICS2
```{r Model07A}
corrdisp<-Hmisc::rcorr(
  as.matrix(cbind(subset(crisis_smp, select=c(b_UCA,c_OffCri,cl_Ceil,
                                              cl_Days,n_Fixed,b_Intl)),
                  dummies::dummy(crisis_smp$Crisis),
                  dummies::dummy(crisis_smp$NoComp),
                  dummies::dummy(crisis_smp$Reach),
                  dummies::dummy(crisis_smp$Veh),
                  dummies::dummy(crisis_smp$Is.Defense),
                  dummies::dummy(crisis_smp$Simple))))
corrdisp[[1]]

#Sumamry plot
summary_discrete_plot(metric="comp",smp,"NAICS2",rotate_text=TRUE)




#Create the model
Comp_Cons_07A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   Agency+
                   NAICS2)

glmer_examine(Comp_Cons_07A)



  stargazer::stargazer(Comp_Cons_06A,Comp_Cons_07A,type="text",
                       digits=2)
  
summary_regression_compare(Comp_Cons_06A,Comp_Cons_07A)


```


Unfortunately introduction of the NAICS variables significantly increases the magnitude of outlier residuals.

# Interactions
## Consolidation Level 6
### Model 10A: Cons:UCA
Starting with Consolidation and UCA. Time pressure is often in place for UCAs so in consolidated sectors, offers may be particularly hard to come by. Thus the interaction of consolidation and UCA estimates fewer offers.
```{r Model10A}
#Sumamry plot
summary_continuous_plot(metric="comp",smp,"cl_def6_HHI_lag1","UCA")



#Create the model
Comp_Cons_10A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   
                   b_UCA:cl_def6_HHI_lag1 +
                   
                   Agency+
                   NAICS2)

glmer_examine(Comp_Cons_10A)

  stargazer::stargazer(Comp_Cons_07A,Comp_Cons_10A,type="text",
                       digits=2)
  
  

summary_regression_compare(Comp_Cons_07A,Comp_Cons_10A)


```
The interaction is significant and UCA / high levels of consolidation estimates fewer offers.


### Model 10B: Cons:Veh
In consolidated markets, definitive contracts, single-award IDCs, and multi award IDCs may all prove less likely to receive multiple offers. The descriptive statistics seem to show more that definitive contracts may get fewer offers with size, but for IDCs, the opposite trend may occur, perhaps because they have already been gated to only viable competitors.

```{r Model10B}


#Sumamry plot
summary_continuous_plot(metric="comp",smp,"cl_def6_HHI_lag1","Veh")
summary_continuous_plot(metric="comp",smp,"cl_def3_HHI_lag1","Veh")

#Create the model
Comp_Cons_10B <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   
                   b_UCA:cl_def6_HHI_lag1 +
                   Veh:cl_def6_HHI_lag1 +
                   Agency+
                   NAICS2)
glmer_examine(Comp_Cons_10B)





  stargazer::stargazer(Comp_Cons_10A,Comp_Cons_10B,type="text",
                       digits=2)
  
  

summary_regression_compare(Comp_Cons_10A,Comp_Cons_10B)


```
Theory beat out descriptive stats. Single-Award IDCs had significantly fewer offers in consolidated sectors. Multi-award slightly fewer, and FSS-GWAC proved most effective at getting offers in that setting. HHi6 does approach the VIF threshold, so we may not be able to keep this one.


### Model 10C: Interaction Defense to Overall ratio
When there is a larger market available, consolidation may matter less, for better or worse, due to the existance of a larger market. Thus, consolidation and a high defense to overall ratio is expected to negatively estimate number of offers.

```{r Model10C_Comp}
#Frequency Plot for unlogged ceiling


#Model
#Create the model
Comp_Cons_10C <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   
                   b_UCA:cl_def6_HHI_lag1 +
                   Veh:cl_def6_HHI_lag1+
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1 +
                   Agency+
                   NAICS2)

glmer_examine(Comp_Cons_10C)

  stargazer::stargazer(Comp_Cons_10A,Comp_Cons_10B,Comp_Cons_10C,type="text",
                       digits=2)
  
  

summary_regression_compare(Comp_Cons_10B,Comp_Cons_10C)


```
Expectations are upheld.


### Model 10D: Interaction of HHI and size
Whether consolidation has positive or negative effets, these should be stronger for larger sectors, as size tends to dilute HHI. If a sector has substantial dollars and is still consolidated, that should mean that the HHI is given more weight. Thus the interactive of HHI and size should estimate fewer offers.
```{r ModelNCS6F_Comp}
#Frequency Plot for unlogged ceiling


#Model
Comp_Cons_10D <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   
                   b_UCA:cl_def6_HHI_lag1 +
                   Veh:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   Agency+
                   NAICS2)


glmer_examine(Comp_Cons_10D)
#First checking if removal of UCA resolves the situation, as that reduces th AIC by the least.

Comp_Cons_10D2 <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   
                   # b_UCA:cl_def6_HHI_lag1 +
                   Veh:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   Agency+
                   NAICS2)
glmer_examine(Comp_Cons_10D2)

# Removing UCA makes almost no difference to the VIF. It's probably Vehicle that has to go  sadly.

Comp_Cons_10D3 <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   
                   b_UCA:cl_def6_HHI_lag1 +
                   # Veh:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   Agency+
                   NAICS2)
glmer_examine(Comp_Cons_10D3)

stargazer::stargazer(Comp_Cons_07A,Comp_Cons_10A,Comp_Cons_10B,Comp_Cons_10C,Comp_Cons_10D3,type="text",
                       digits=2)
  
  

summary_regression_compare(Comp_Cons_10C,Comp_Cons_10D3)

```
Expectations were upheld, but Veh:Consolidation had to be removed. Other alternatives may be available, but adding the interaction took the VIF to 1.94 in its own right, so keeping it was always a challenge.

## Consolidation Level 3


#### Model 11A: Defense to Overall ratio
Applying the same logic as in model 10C, a greater ratio of def to civilian combined with consolidation is expected to estimate a lower number of offers.

```{r Model11A_Comp}
#Frequency Plot for unlogged ceiling


#Model

Comp_Cons_11A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   
                   # b_UCA:cl_def6_HHI_lag1 +
                   Veh:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   cl_def3_HHI_lag1:cl_def3_ratio_lag1+
                   Agency+
                   NAICS2)
glmer_examine(Comp_Cons_11A)

Comp_Cons_11A2 <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   
                   # b_UCA:cl_def6_HHI_lag1 +
                   Veh:cl_def6_HHI_lag1 +
                   # cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   cl_def3_HHI_lag1:cl_def3_ratio_lag1+
                   Agency+
                   NAICS2)
glmer_examine(Comp_Cons_11A2)



```
Both exceed VIF of 2.


## Vehicle

###Model 12A: Vehicle and Any International
Multi-award IDCs are used in part in cases like crisis situations where a pre-approved group of contractors could make a big difference. Multi-award international task orders are expected to have  more offers relative to definitive.


```{r Model12A}

#Frequency Plot
summary_discrete_plot(metric="comp",smp,"Intl","Veh")



#Create the model
Comp_Cons_12A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   Agency+
                   NAICS2)
glmer_examine(Comp_Cons_12A)

stargazer::stargazer(Comp_Cons_10D3,Comp_Cons_12A,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_10D3,Comp_Cons_12A)

```
Expectations were upheld for multi-award, and indeed all forms of indefinite delivery vehicles have higher offers for international. This also increased the significe of the base indefinitive delivery vehicles.


## Pricing
###Model 13A: Pricing and Average Wage
Firm Fixed Price is less  appropriate as an approach when there is greater uncertainty and thus should estimate fewer offers. A phenomenon likely to extend to time and materials / labor hours contracts. By comparison, fixed price incentive and cost based should estimate more offers.

```{r Model13A_Wage}


#Frequency Plot
summary_continuous_plot(metric="comp",smp,"cl_US6_avg_sal_lag1","PricingFee")


#Create the model
Comp_Cons_13A <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   Agency+
                   cl_US6_avg_sal_lag1:PricingFee+
                   NAICS2)
glmer_examine(Comp_Cons_13A)


stargazer::stargazer(Comp_Cons_12A,Comp_Cons_13A,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_12A,Comp_Cons_13A)



```


Results old for fixed-price incentive and t&mlh/fploe, but not for cost-based. The reduction in AIC is considerable, over 30k.


###Model 13B: Fixed-Price and Ceiling
Using size as  an alternate measure for complexity, firm fixed price and T&M/LH/FP:LoE contracts may be at greater risk for large contracts and thus attract fewer offers. Conversely, Cost-based and fixed-price level of effort may receive more.
```{r Model13B_Comp}

#Frequency Plot
summary_continuous_plot(metric="comp",smp,"l_Ceil","PricingFee")

#Create the model
Comp_Cons_13B <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   cl_Ceil:PricingFee+
                   cl_US6_avg_sal_lag1:PricingFee+
                   Agency+
                   NAICS2)
glmer_examine(Comp_Cons_13B)




stargazer::stargazer(Comp_Cons_12A,Comp_Cons_13A,Comp_Cons_13B,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_13C,Comp_Cons_13B)

```
While the AIC reduction is considerable, the results are entirely contrary to expectations, leaving it out.

###Model 13C: UCA and Duration
Longer direction UCAs may reflect an environment in which fewer options are available. Thus UCAs with long directions are expected to estimate fewer offers.


```{r Model13C_Term}


#Frequency Plot
summary_continuous_plot(metric="comp",smp,"l_Days","UCA")

Comp_Cons_13C <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   # cl_Ceil:PricingFee+
                   cl_US6_avg_sal_lag1:PricingFee+
                   b_UCA:cl_Days+
                   Agency+
                   
                   NAICS2)
glmer_examine(Comp_Cons_13C)
stargazer::stargazer(Comp_Cons_13A,Comp_Cons_13B,Comp_Cons_13C,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_13B,Comp_Cons_13C)


```
The results are in line with expectation, but not significant and barely add anything to the model. Leaving it in, but can drop it if any challenges are encountered.

###Model 13D: UCA and Ceiling

Here the possible risk is similar to days, that larger, and thus possibly more complex projects, are at greater risk with UCA and that UCA and high ceiling estimate a higher chance of breaches.
```{r Model13D_Term}


#Frequency Plot
summary_continuous_plot(metric="comp",smp,"l_Ceil","UCA")


Comp_Cons_13D <- glm (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   # cl_Ceil:PricingFee+
                   cl_US6_avg_sal_lag1:PricingFee+
                   b_UCA:cl_Days+
                   b_UCA:cl_Ceil+
                   Agency+
                   
                   NAICS2)



glmer_examine(Comp_Cons_13D)


stargazer::stargazer(Comp_Cons_13A,Comp_Cons_13B,Comp_Cons_13C,Comp_Cons_13D,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_13C,Comp_Cons_13D)




```
Ceiling is contrary to expectation and has a minimal coefficient. Leaving  it out.





#Multi-Level Model
##   NAICS3/6 & Agency/Office

###Model 15A: Agency/Office+NAICS6/NAICS3 
```{r Model15A}

Comp_Cons_15A <- lmer (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   # cl_Ceil:PricingFee+
                   cl_US6_avg_sal_lag1:PricingFee+
                   b_UCA:cl_Days+
                   # b_UCA:cl_Ceil+
                   (1 | NAICS3/NAICS) + (1 | Agency/Office),
                        verbose=1)

glmer_examine(Comp_Cons_15A,display=TRUE)

save(Comp_Cons_15A,file="Output//Comp_Cons_15A.rdata")

stargazer::stargazer( Comp_Cons_15A,
                     type="text",
                       digits=2)


stargazer::stargazer(Comp_Cons_13A,Comp_Cons_13B,Comp_Cons_13C,Comp_Cons_13D,Comp_Cons_15A,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_13D,Comp_Cons_15A)


```

###Model 15B: Agency/Office+NAICS6/NAICS3 trimmed

```{r Model15B}

Comp_Cons_15B <- lmer (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   # cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   # cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   # cl_Ceil:PricingFee+
                   cl_US6_avg_sal_lag1:PricingFee+
                   # b_UCA:cl_Days+
                   # b_UCA:cl_Ceil+
                   (1 | NAICS3/NAICS) + (1 | Agency/Office),
                        verbose=1)

glmer_examine(Comp_Cons_15B,display=TRUE)

save(Comp_Cons_15B,file="Output//Comp_Cons_15B.rdata")

stargazer::stargazer( Comp_Cons_15A,Comp_Cons_15B,
                     type="text",
                       digits=2)


stargazer::stargazer(Comp_Cons_13A,Comp_Cons_13B,Comp_Cons_13C,Comp_Cons_13D,Comp_Cons_15A,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_13D,Comp_Cons_15A)


```

###Model 15C: Adding Start Calendar Year
```{r Model15C}

Comp_Cons_15C <- lmer (data=smp,
                 cl_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   # cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   # cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   # cl_Ceil:PricingFee+
                   cl_US6_avg_sal_lag1:PricingFee+
                   # b_UCA:cl_Days+
                   # b_UCA:cl_Ceil+
                   (1 | NAICS3/NAICS) + (1 | Agency/Office)+
                   (1 | StartCY),
                        verbose=1)

glmer_examine(Comp_Cons_15C,display=TRUE)
get_icc(Comp_Cons_15C)
save(Comp_Cons_15C,file="Output//Comp_Cons_15C.rdata")

stargazer::stargazer( Comp_Cons_15A,Comp_Cons_15B,Comp_Cons_15C,
                     type="text",
                       digits=2)


stargazer::stargazer(Comp_Cons_13A,Comp_Cons_13B,Comp_Cons_13C,Comp_Cons_13D,Comp_Cons_15A,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_13D,Comp_Cons_15A)


```

###Model 16A: Agency/Office+NAICS6/NAICS3 trimmed
```{r Model16A}

Comp_Cons_16A <- lmer (data=smp,
                 cl_Offr ~#cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                  # cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1 + 
                   cl_Ceil+cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl+
                   b_UCA:cl_def6_HHI_lag1 +
                   cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                   cl_def6_HHI_lag1:cl_def6_obl_lag1+
                   b_Intl:Veh+
                   # cl_Ceil:PricingFee+
                   cl_US6_avg_sal_lag1:PricingFee+
                   b_UCA:cl_Days+
                   # b_UCA:cl_Ceil+
                   (1 | NAICS3/NAICS) + (1 | Agency/Office),
                        verbose=1)

glmer_examine(Comp_Cons_16A,display=TRUE)

save(Comp_Cons_16A,file="Output//Comp_Cons_16A.rdata")

stargazer::stargazer(Comp_Cons_15A, Comp_Cons_16A,
                     type="text",
                       digits=2)


stargazer::stargazer(Comp_Cons_15A,Comp_Cons_16A,
                     type="text",
                       digits=2)
summary_regression_compare(Comp_Cons_15A,Comp_Cons_16A)


```