---
title: "Monopoly Results Summary"
date: "Wednesday, February 8, 2017"
output: 
  html_document: 
    keep_md: yes
    toc: yes

---

#Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
source("DIIGstat.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```


Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations

Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  


##Prepare Data
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.


###Data Transformations and Summary



```{r ReadInData, echo = TRUE}
  load(file="Data/defense_contract_CSIScontractID_detail.Rdata")
  

head(DefenseModelAndDetail)
# undebug(transform_contract)
# debug(transform_contract)
# debug(transform_contract)
DefenseModelAndDetail<-transform_contract(DefenseModelAndDetail)


```


DefenseModelAndDetails$


NA_stats(DefenseModelAndDetail,"b_Crai")

* b_Crai is a binary variable that has a value of 1 for any contracts that have experienced a partial or complete termination, 0 otherwise. ('r summary(DefenseModelAndDetail$b_Crai)
NA_stats(DefenseModelAndDetail,"b_Crai"))
* b_Comp is a binary variable based on competition. It has a value of 0 for uncompeted contracts and a value of 1 for competition, regardless of number of offers. 'r  summary(DefenseModelAndDetail$b_Comp);
NA_stats(DefenseModelAndDetail,"b_Comp")'
* c_hh_index_lag1 is a numeric variable based on competition and number of offers. It has a value of 0 for uncompeted contracts and a value of 1 for single-offer competition, and a value of 2 for multi-offer competition. 'r summary(DefenseModelAndDetail$c_hh_index_lag1);
NA_stats(DefenseModelAndDetail,"c_hh_index_lag1")'
* n_Offr is a numeric variable based on competition and with more granularity on number offers. It has a value of 0 for uncompeted contracts and a value of 1 for single-offer competition, and a value of 2 for 2-offers, 3 for 3-4 offers, and 4 for 5+ offers. 'r summary(DefenseModelAndDetail$n_Offr);
NA_stats(DefenseModelAndDetail,"n_Offr")'
* hh_index_lag1 is the natural log of the number of offers received. Uncompeted contracts are classified as having received one offer. 'r summary(DefenseModelAndDetail$hh_index_lag1);
NA_stats(DefenseModelAndDetail,"hh_index_lag1")'
* cl_Ceil is the natural log of the initial contract cost ceiling, in then-year dollars. 'r centered_log_description(DefenseModelAndDetail$l_Ceil,"dollars");
NA_stats(DefenseModelAndDetail,"l_Ceil")'
* cl_Days is the natural log of the initial maximum duration of the contract, in days. The variable is centered, by subtracting its mean ('r centered_log_description(DefenseModelAndDetail$l_Days,"days");
NA_stats(DefenseModelAndDetail,"l_Days")' 
* SIDV, MIDV, and OIDV are dummy variables based on the contract vehicle. They correspond to Single-Award IDVs, Multi-Award IDVs, and Other IDVs, respectively, having a value of 1 when the task order has that vehicle type, and having a 0 other. The remaining types, definitive contracts and purchase orders, are intentionally left out. ('r summary(DefenseModelAndDetail$SIDV);
summary(DefenseModelAndDetail$MIDV);
summary(DefenseModelAndDetail$OIDV);
NA_stats(DefenseModelAndDetail,"Veh")'
* n_Fixed is a numeric variable based on contract pricing. It has a value of 0 for cost-based, 0.5 or "combination or other", 1 for any fixed price (excluding fixed-price level of effort which is classified as cost-based). ('r summary(DefenseModelAndDetail$n_Fixed);
NA_stats(DefenseModelAndDetail,"n_Fixed")')
* n_Incent is a numeric variable based on fee type. Ig has a value. 1 for incentive fee or cost sharing, 0.5 or "combination or other", 0 for all remaining types. ('r summary(DefenseModelAndDetail$n_Incent);
NA_stats(DefenseModelAndDetail,"n_Incent")')
* b_UCA is a binary variable with a value of 1 for contracts/task orders that begin as letter contracts or undefinitized contract awards (UCA) and a value of 0 otherwise. 'r
summary(DefenseModelAndDetail$b_UCA);
NA_stats(DefenseModelAndDetail,"b_UCA")'
* b_Intl is a binary variable with a value of 1 for contracts/task orders with any transactions performed internationally and a value of 0 otherwise. 'r
summary(DefenseModelAndDetail$b_Intl);
NA_stats(DefenseModelAndDetail,"b_Intl")'
* PSR is a factor reporting whether a contract is primarily for products/services/R&D. 'r
summary(DefenseModelAndDetail$PSR);
NA_stats(DefenseModelAndDetail,"PSR")'
* ProdServ is a factor reporting the top Product or Service Code of each contract. 'r
summary(DefenseModelAndDetail$ProdServ);
NA_stats(DefenseModelAndDetail,"ProdServ")'
* NAICS is a factor reporting the top North American Industrial Classification Code of each contract. 'r
summary(DefenseModelAndDetail$NAICS);
NA_stats(DefenseModelAndDetail,"NAICS")'
* Agency is a factor reporting the top Contracting Agency of each contract. 'r
summary(DefenseModelAndDetail$Agency);
NA_stats(DefenseModelAndDetail,"Agency")'
* Office is a factor reporting the top Contracting office of each contract. 'r
summary(DefenseModelAndDetail$Office);
NA_stats(DefenseModelAndDetail,"Office")'

