---
title: "ContractTermination"
author: "Greg Sanders"
date: "Wednesday, February 8, 2017"
output:
  html_document:
    keep_md: yes
--- 

Is Terminated exploration
============================================================================

#Setup
```{r InputFiles, echo = TRUE}
source("https://raw.githubusercontent.com/CSISdefense/R-scripts-and-data/master/helper.r")
source("https://raw.githubusercontent.com/CSISdefense/R-scripts-and-data/master/lookups.r")
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/DIIGstat.r")
source("ContractCleanup.r")

library(csis360)
library(ggplot2)
library(scales)
library(Hmisc)
library(dplyr)
# Coloration<-read.csv(
#     paste(Path,"Lookups\\","lookup_coloration.csv",sep=""),
#     header=TRUE, sep=",", na.strings="", dec=".", strip.white=TRUE, 
#     stringsAsFactors=FALSE
#     )
# 
# Coloration<-ddply(Coloration
#                   , c(.(R), .(G), .(B))
#                   , mutate
#                   , ColorRGB=as.character(
#                       if(min(is.na(c(R,G,B)))) {NA} 
#                       else {rgb(max(R),max(G),max(B),max=255)}
#                       )
#                   )

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations


Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  


##Prepare Data

```{r ReadInData, echo = TRUE}
  load(file="Data/Federal_contract_CSIScontractID_detail.Rdata")
debug(transform_contract)
def_full<-transform_contract(def_full)
#Unknown or uninitialised column: 'Comp'
head(def_full)

```

```{r PrepareData}

#ContractWeighted <- apply_lookups(Path,ContractWeighted)
#Is.Defense left out
def_full<-decision_tree(def_full)

summary(def_full$DecisionTreeDisplay)
# def_full<-subset(def_full,DecisionTreeDisplay != "Not in Sample")
# save(complete_def_full,def_full,file="data//def_full.Rdata")


View(def_full[is.na(def_full$DecisionTreeDisplay),])


summary(def_full$DecisionTree)
summary(def_full$DecisionTreeDisplay)
write.csv(subset(def_full,Term=="Terminated"),"LargeDataSets//Terminated.csv")

save(def_full,file="LargeDataSets//FederalModelForTerminations.RData")


```


#Analysis

##Data preparation
```{r SDurSCeilCount, fig.width=6.5,fig.height=5, dpi=600}
# load(file="LargeDataSets//FederalModelForTerminations.RData")
TerminatedSDurSCeilStatCount<-subset(def_full,
         !is.na(Dur.Simple) & 
           !is.na(Ceil.Simple) &
           !is.na(Term)) %>% group_by(Dur.Simple,
      Ceil.Simple,
      # StartFY,
      Term,
      # DecisionTreeDisplay,
      # Is.Defense,
      # Intl,
      # SingleOffer,
      # UCA
    ) %>%
      # DecisionTreeDisplay != "Not in Sample" &
           # StartFY>=2007 & 
           # StartFY<=2015 
           # (DecisionTreeDisplay != "Not in Sample")
  # &                
           #     (LastCurrentCompletionDate<=as.Date("2015-09-30") |
           #          IsClosed==1) &
           #     UnmodifiedCurrentCompletionDate<as.Date("2015-09-30")),
    dplyr::summarise(
    Action.Obligation=sum(Action.Obligation),
    Count=length(CSIScontractID),
    metric="Contracts within Period"
)


save(TerminatedSDurSCeilStatCount,file="TerminatedSDurSCeilStatCount.Rdata")
load(file="TerminatedSDurSCeilStatCount.Rdata")

TerminatedSDurSCeilStatCount$Term<-factor(TerminatedSDurSCeilStatCount$Term,
                                          levels=c("Unterminated",
                                                   "Terminated"),
                                          labels=c("Unterminated",
                                                   "Complete or Partial Termination"),
                                            ordered=TRUE)


TerminatedSDurSCeilLabels<-TerminatedSDurSCeilStatCount %>%
    group_by(Dur.Simple,Ceil.Simple) %>%
    dplyr::summarise(
    FacetCount=paste("Count:",prettyNum(sum(Count),big.mark=",")),
    FacetValue=paste(FacetCount,"\nObligated: $",round(sum(Action.Obligation)/1000000000,1),"B",sep="")
    )




# debug(LatticePlotWrapper)
# top_line_term<-LatticePlotWrapper(
#   VAR.color.legend.label="Classification",
#   VAR.main.label="",
#   VAR.X.label="Fiscal Year",
#   VAR.Y.label="Constant ($ Billions)",
#   VAR.Coloration=Coloration,
#   VAR.long.DF=TerminatedSDurSCeilStatCount,
#   # NA, #VAR.ncol
#   VAR.x.variable="StartFY", #VAR.x.variable
#   VAR.y.variable="Count", #VAR.y.variable
#   VAR.y.series="Term", #VAR.y.series
#   VAR.facet.primary="Dur.Simple", #VAR.facet.primary
#   VAR.facet.secondary= "Ceil.Simple", # VAR.facet.secondary=NA
#   # ,MovingAverage=0
#   # ,MovingSides=1
#   DataLabels=FALSE
#   #                       ,VAR.override.coloration=NA
# )+geom_text(data=TerminatedSDurSCeilLabels,
#               aes(x=2007,y=Ypos,label=FacetValue),
#               # parse=TRUE,
#               hjust=0,
#               vjust=1,
#               color="black")
```


