---
title: "Defense Acquisition Trends"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, October 6, 2021"
---

# Setup
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)
library(openxlsx)
axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40
if(!exists("platpscintldef"))
  load(file="../data/clean/platpscplatpscintldef.Rda")


if(!exists("platpscdefcd"))
  load(file="../data/clean/platpscdefcd.Rda")
# save.image("../.RData")
```

# Preprocessing 
## Group By PlatformPortfolio
### Project
```{r PreprocessProject}

# summary(factor(platpscintldef$ProjectPlatform))
# 
# colnames(platpscintldef)[colnames(platpscintldef)=="Action_Obligation_Then_Year_Then_Year"]<-
#   "Action_Obligation_Then_Year"
# 
# topplat<-platpscintldef %>% group_by (Project.Name,PlatformPortfolio) %>%
#   #Exclude NA from ranking and then create a recent only dollar amount
#   mutate(Action_Obligation_2023=if_else(is.na(Project.Name),Action_Obligation_OMB25_GDP23,NA),
#     Action_Obligation_2023=if_else(Fiscal_Year>=2023,Action_Obligation_OMB25_GDP23,NA))%>%
#   summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23,na.rm = TRUE),
#             Action_Obligation_2023=sum(Action_Obligation_2023,na.rm = TRUE))%>%
#               group_by (PlatformPortfolio) %>%
#     mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
#                         rank_2023=rank(desc(Action_Obligation_2023)))
# topplat %>% arrange(desc(Action_Obligation_OMB25_GDP23))
# 
# 
# topplat$TopProject<-
#   ifelse(topplat$rank_2023<=7 | topplat$rank_total<=7,topplat$Project.Name,NA)
# 
# platpscintldef<-left_join(platpscintldef,topplat %>% dplyr::select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2023),
#                           by=c("Project.Name","PlatformPortfolio"))
# 
# platpscintldef$TopProject[is.na(platpscintldef$TopProject) & !is.na(platpscintldef$Project.Name)]<-
#   "Other Labeled Project"
# 
# 
# summary(factor(platpscintldef$TopProject))
# 
# 
# colnames(platpscintldef)
# platpscintldef
# 
# write.csv(topplat,file=file.path("..","Output","AcqTrends","Topplat.csv"),row.names=FALSE)
# debug(label_top)
platpscintldef<-label_top(platpscintldef,
                    col="Project.Name",
                    n=7,
                    top_name="TopProject",
                    group_list="PlatformPortfolio",
                    recent=2023
                    #retain_rank=TRUE,
                    #write_file=file.path("..","Output","AcqTrends","TopProjectTest.csv")
                    )




```
### PSC
```{r PreprocessPSC}


# platpscintldef<-label_top(platpscintldef,
#                     col="ProductOrServiceCode",
#                     n=7,
#                     top_name="TopPScode",
#                     group_list="PlatformPortfolio",
#                     recent=2023
#                     #retain_rank=TRUE,
#                     #write_file=file.path("..","Output","AcqTrends","TopProjectTest.csv")
#                     )



summary(factor(platpscintldef$ProjectPlatform))

topPSC<-platpscintldef %>% group_by (ProductOrServiceCode,ProductOrServiceCodeText,PlatformPortfolio) %>%
  mutate(Action_Obligation_2023=ifelse(Fiscal_Year>=2023,Action_Obligation_OMB25_GDP23,NA))
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23,na.rm=TRUE),
            Action_Obligation_2023=sum(Action_Obligation_2023,na.rm=TRUE))%>%
              group_by (PlatformPortfolio) %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
                        rank_2023=rank(desc(Action_Obligation_2023)))
topPSC %>% arrange(desc(Action_Obligation_OMB25_GDP23))

topPSC$TopPScode<-
  ifelse(topPSC$rank_2023<=7 | topPSC$rank_total<=7,topPSC$ProductOrServiceCode,NA)
topPSC$TopPStext<-
  ifelse(topPSC$rank_2023<=7 | topPSC$rank_total<=7,topPSC$ProductOrServiceCodeText,NA)


platpscintldef<-left_join(platpscintldef,topPSC %>% select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2023),
          by=c("ProductOrServiceCode","PlatformPortfolio"))

platpscintldef$TopPScode[is.na(platpscintldef$TopPScode) & !is.na(platpscintldef$ProductOrServiceCode)]<-
  "Other Labeled PSC"
platpscintldef$TopPStext[is.na(platpscintldef$TopPStext) & !is.na(platpscintldef$ProductOrServiceCode)]<-
  "Other Labeled PSC"

platpscintldef$TopPStext<-factor_wrap(platpscintldef$TopPStext)

summary(factor(platpscintldef$TopPStext))


```

## Group By ProductOrServiceArea
### Place State
```{r PreprocessState}

# platpscintldef$pop_isna<-is.na(platpscintldef$pop_state_code)
# platpscintldef$sc_isna<-is.na(platpscintldef$PlaceStateCode)
# platpscintldef %>% group_by(Fiscal_Year,pop_isna,sc_isna) %>%
#   summarise(n=length(Fiscal_Year))

# summary(factor(platpscintldef$ProductOrServiceArea))


platpscintldef<-label_top(platpscintldef,
                    col="pop_state_code",
                    n=25,
                    top_name="TopStateAbbr",
                    group_list="ProductOrServiceArea",
                    recent=2023
                    #retain_rank=TRUE,
                    #write_file=file.path("..","Output","AcqTrends","TopProjectTest.csv")
                    )


# topState<-platpscintldef %>% group_by (pop_state_code,ProductOrServiceArea) %>%
#   summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
#             Action_Obligation_2023=sum(ifelse(Fiscal_Year==2023,Action_Obligation_OMB25_GDP23,0)))%>%
#               group_by (ProductOrServiceArea) %>%
#     mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
#                         rank_2023=rank(desc(Action_Obligation_2023)))
# topState %>% arrange(desc(Action_Obligation_OMB25_GDP23))
# 
# topState$TopStateAbbr<-
#   ifelse(topState$rank_2023<=25 | topState$rank_total<=25,topState$pop_state_code,NA)
# # topState$TopStateName<-
# #   ifelse(topState$rank_2023<=7 | topState$rank_total<=7,topState$PlaceStateCodeText,NA)
# platpscintldef<-platpscintldef[,!colnames(platpscintldef) %in% c("Action_Obligation_OMB25_GDP23.x","Action_Obligation_OMB25_GDP23.y",
#                                    "Action_Obligation_2023.x","Action_Obligation_2023.y",
#   "rank_total.y","rank_total.x","rank_2023.y","rank_2023.x","TopStateAbbr.x","TopStateAbbr.y")]
# 
# platpscintldef<-left_join(platpscintldef,topState %>% select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2023),
#           by=c("pop_state_code","ProductOrServiceArea"))
# 
# platpscintldef$TopStateAbbr[is.na(platpscintldef$TopStateAbbr) & !is.na(platpscintldef$pop_state_code)]<-
#   "Other Labeled State"
# platpscintldef$TopStateName[is.na(platpscintldef$TopStateName) & !is.na(platpscintldef$pop_state_code)]<-
#   "Other Labeled State"


# summary(factor(platpscintldef$TopStateName))


```

### Place Country
```{r PreprocessCountry}



platpscintldef<-label_top(platpscintldef,
                    col="PlaceISOalpha3",
                    n=7,
                    top_name="TopCountryISO",
                    group_list="ProductOrServiceArea",
                    recent=2023
                    #retain_rank=TRUE,
                    #write_file=file.path("..","Output","AcqTrends","TopProjectTest.csv")
                    )

# 
# # summary(factor(platpscintldef$ProductOrServiceArea))
# colnames(platpscintldef)[colnames(platpscintldef)=="Fiscal_Year"]<-"Fiscal_Year"
# topCountry<-platpscintldef %>% group_by (PlaceISOalpha3,ProductOrServiceArea) %>%
#   summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
#             Action_Obligation_2023=sum(ifelse(Fiscal_Year==2023,Action_Obligation_OMB25_GDP23,0)))%>%
#               group_by (ProductOrServiceArea) %>%
#     mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
#                         rank_2023=rank(desc(Action_Obligation_2023)))
# topCountry %>% arrange(desc(Action_Obligation_OMB25_GDP23))
# 
# topCountry$TopCountryISO<-
#   ifelse(topCountry$rank_2023<=7 | topCountry$rank_total<=7,topCountry$PlaceISOalpha3,NA)
# # topCountry$TopCountryName<-
# #   ifelse(topCountry$rank_2023<=7 | topCountry$rank_total<=7,topCountry$PlaceCountryCodeText,NA)
# 
# 
# platpscintldef<-left_join(platpscintldef,topCountry %>% select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2023),
#           by=c("PlaceISOalpha3","ProductOrServiceArea"))
# 
# platpscintldef$TopCountryISO[is.na(platpscintldef$TopCountryISO) & !is.na(platpscintldef$PlaceISOalpha3)]<-
#   "Other Labeled Country"
# # platpscintldef$TopCountryName[is.na(platpscintldef$TopCountryName) & !is.na(platpscintldef$PlaceISOalpha3)]<-
# #   "Other Labeled Country"
# 
# 
# # summary(factor(platpscintldef$TopCountryName))


```



# Inflation
## Fuel
```{r Fuel}

# PlaceIsForeign
# full_data$PlaceStateRegion
# replace_nas_with_unlabeled(factor(full_data$PlaceIsForeign,levels=c(1,0),labels=c("Performed Abroad","Performed in the U.S."))

full_data$SimpleArea.fuels<- as.character( full_data$SimpleArea)
full_data$SimpleArea.fuels[full_data$ProductServiceOrRnDarea=="Fuels"]<-"Fuels"
summary(factor(full_data$SimpleArea.fuels))
full_data$SimpleArea.fuels<-factor(full_data$SimpleArea.fuels,
                                           levels=c("Services (Non-R&D)" ,
                                                   "R&D",
                                                   "Products (All)",
                                                   "Fuels",
                                                   "Unlabeled" ),
                                           labels=c("Services (Non-R&D)" ,
                                                   "R&D",
                                                   "Products (Non-Fuels)",
                                                   "Fuels",
                                                   "Unlabeled" ))
summary(factor(full_data$SimpleArea.fuels))
labels_and_colors<-prepare_labels_and_colors(full_data,path="C:\\Users\\gsand\\Repositories\\Lookup-Tables\\style\\")
column_key<-get_column_key(full_data,path="C:\\Users\\gsand\\Repositories\\Lookup-Tables\\style\\")


(
psrfuel<-build_plot(
  data=full_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SimpleArea.fuels", #color_var
  # facet_var="TopPStext", #facet_var
  column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  # theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)",
              caption = "Source: FPDS, CSIS Analysis, OMB GDP deflators.")
)

  ggsave600dpi(filename = "..//Output//PSRfuels.png", psrfuel,  
               width=12, height= 5.6, units="in",size=18, lineheight=1.2,
               bg="transparent"
               )

write.csv(file="..//Output//PSRfuels.csv",row.names = FALSE, na = "",
  pivot_wider(psrfuel$data %>% 
                        arrange(dFYear) %>% mutate(Fiscal_Year=lubridate::year(dFYear)),
                      id_cols=c(SimpleArea.fuels),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>%
    arrange(SimpleArea.fuels))


(
fuel<-build_plot(
  data=full_data %>% filter(ProductOrServiceArea=="Fuels")%>% 
    mutate(PlaceIsForeign=factor(PlaceIsForeign,levels=c(1,0),labels=c("Performed Abroad","Performed in the U.S."))),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PlaceStateRegion", #color_var
  # facet_var="TopPStext", #facet_var
  # column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  # theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)",
       caption = "Source: FPDS, CSIS Analysis, OMB GDP deflators.")
)


(
fuel<-build_plot(
  data=full_data %>% filter(ProductOrServiceArea=="Fuels")%>% 
    mutate(PlaceIsForeign=factor(PlaceIsForeign,levels=c(1,0),labels=c("Performed Abroad","Performed in the U.S."))),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PlaceIsForeign", #color_var
  # facet_var="TopPStext", #facet_var
  # column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  # theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)")
)

ggsave600dpi("..//Output//Deep_Dives/Inflation/defense_fuel_place.png", fuel+labs(title="DoD Contract Obligations for Fuels", caption="Source: FPDS and CSIS analysis."), 
             width=6.5, height= 3.5, units="in",size=12,lineheight = 1
             )


write.csv(file="..//Output//Deep_Dives/Inflation/defense_fuel_place.csv",row.names = FALSE,na = "",
          fuel$data%>% mutate(Fiscal_Year=lubridate::year(dFYear))%>%
          pivot_wider(id_cols=c(PlaceIsForeign),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23))



(
fuel_psc<-build_plot(
  data=platpscintldef %>% filter(ProductOrServiceArea=="Fuels")%>% 
    mutate(PlaceIsForeign=factor(PlaceIsForeign,levels=c(1,0),labels=c("Performed Abroad","Performed in the U.S."))),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="ProductOrServiceCodeText", #color_var
  # facet_var="TopPStext", #facet_var
  # column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  # theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)")
)

```

# Construction
```{r FRSnC}
summary(factor(platpscintldef$ProductOrServiceArea))
# platpscintldef$Fiscal_Year
# 
# topplat<-platpscintldef %>% filter(PlatformPortfolio=="Ships & Submarines") %>% group_by (Project.Name) %>%
#   summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
#             )
#             )%>% mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
#                         rank_2023=rank(desc(Action_Obligation_2023)))
# topplat %>% arrange(desc(Action_Obligation_OMB25_GDP23))
# 
# platpscintldef$TopShipProject<-
#   ifelse(platpscintldef$Project.Name %in% topplat$Project.Name[topplat$rank_2023<=7 | topplat$rank_total<=7],
#          platpscintldef$Project.Name,NA)
# platpscintldef$TopShipProject[is.na(platpscintldef$TopShipProject) & !is.na(platpscintldef$Project.Name)]<-
#   "Other Labeled Project"
# summary(factor(platpscintldef$TopShipProject))

(
State<-build_plot(
  data=platpscintldef %>% filter(ProductOrServiceArea=="Construction"),
  chart_geom = "Line Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="TopStateAbbr", #color_var
  facet_var="TopStateAbbr", #facet_var
  # column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)")
)
ggsave(State,file="construction_state.png")
(
State<-build_plot(
  data=platpscintldef %>% filter(ProductOrServiceArea=="Construction"),
  chart_geom = "Line Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="TopStateAbbr", #color_var
  facet_var="TopStateAbbr", #facet_var
  second_var="SubCustomer",
  # column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)")
)


(
Country<-build_plot(
  data=platpscintldef %>% filter(ProductOrServiceArea=="Construction"),
  chart_geom = "Line Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="TopCountryISO", #color_var
  facet_var="TopCountryISO", #facet_var
  # column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)")
)


(
PSC<-build_plot(
  data=platpscintldef %>% filter(PlatformPortfolio=="Construction"),
  chart_geom = "Line Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="TopPStext", #color_var
  facet_var="TopPStext", #facet_var
  # column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)")
)

```

#FMS 
## Topline FMS





###FMS identification
```{r contract_identification}



# undebug(build_plot)

(contract_identification <-  build_plot(data=platpscintldef %>% filter(ContractingCustomer=="Defense"),
                            chart_geom="Bar Chart",
                            share=FALSE,
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="foreign_funding_description",
                            facet_var="IsFMS",
                            # second_var="StateRegion",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                        format=TRUE)+
    # facet_grid(  IsFMS~., scales="free_y")+
  labs(#x="Year of Delivery (Calendar or Fiscal Varies by Source)",
       y="Constant 2022 $ Obligated",
       caption="Source: FPDS; CSIS analysis.")+
    guides(fill=guide_legend(ncol=3)))

ggsave600dpi(contract_identification,file="../output/figure_03_contract_identification.png",size=12,lineheight=1, height =5, width=9)



```

# FMS or International

## Service Category
```{r FPDS_vendor_Intl}

summary(factor(platpscintldef$SimpleArea))
# undebug(format_data_for_plot)
(fmsintl_service <-  build_plot(data=platpscintldef%>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign) &
                                                                            Fiscal_Year>2011 & !is.na(IsFMS)&
                                                                  SimpleArea=="Services"),#IsFMS==TRUE                             
                                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="ProductOrServiceArea",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )+labs(title="Services FMS or Performed Internationally")#, scales="free_y"#, scales="free_y"
  )
summary(platpscintldef$dFYear)

write.csv(file="..//Output//fmsintl_service.csv",row.names = FALSE,na = "",
          fmsintl_service$data%>%# mutate(Fiscal_Year=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PlaceIsForeign,IsFMS,ProductOrServiceArea),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,ProductOrServiceArea))

ggsave600dpi(fmsintl_service,file="../output/fmsintl_service.png",
             size = 12, lineheight=1, height =6, width=9)


(fmsintl_service_vendor <-  build_plot(data=platpscintldef%>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign) &
                                                                            Fiscal_Year>2011 & !is.na(IsFMS)&
                                                                  SimpleArea=="Services"),#IsFMS==TRUE                             
                                            chart_geom="Bar Chart",
                            x_var="dFYear",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="ProductOrServiceArea",
                            facet_var="IsFMSplaceIntl",
                            second_var="VendorSize_Intl",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( IsFMSplaceIntl~VendorSize_Intl , scales="free_y", space="free_y")+labs(title="Services FMS or Performed Internationally")+
    theme(  strip.text.y=element_text(angle=0))
  )


write.csv(file="..//Output//fmsintl_service_vendor.csv",row.names = FALSE,na = "",
          fmsintl_service_vendor$data%>% mutate(Fiscal_Year=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(IsFMSplaceIntl,VendorSize_Intl,ProductOrServiceArea),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(IsFMSplaceIntl,VendorSize_Intl,ProductOrServiceArea))

ggsave600dpi(fmsintl_service_vendor,file="../output/fmsintl_service_vendor.png",
             size = 12, lineheight=1, height =6, width=9)

```



# JSF 

### JSF-MDAP-FMS
```{r FPDS_JSF}

summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$IsFMS)
summary(factor(platpscintldef$IsJSF))

platpscintldef<-platpscintldef %>% mutate(
  FMSJSF=case_when(
    IsFMS==1 & IsJSF =="JSF (F-35)" ~ "Includes FMS (JSF)",
    IsFMS==1 & IsJSF =="JSF (F-35)" ~ "Includes FMS (JSF)"
  )
)

# undebug(format_data_for_plot)
(fms_jsf <-  build_plot(data=platpscintldef %>% filter(Fiscal_Year>2011),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="IsFMS",
                            facet_var="IsJSF",
                            # second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsJSF)#, scales="free_y"
  )



ggsave600dpi(fms_jsf,file="../output/jsf_vendor_intl_place.png",
             size = 12, lineheight=1, height =4.5, width=9)




```
### JSF National Origin
```{r FPDS_JSF}

summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$VendorSize_Intl)

# undebug(format_data_for_plot)
(jsf_vendor_intl_place <-  build_plot(data=platpscintldef %>% filter(IsJSF=="JSF (F-35)"& Fiscal_Year>2011),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="VendorSize_Intl",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )#, scales="free_y"
  )


write.csv(file="..//Output//jsf_vendor_intl_place.csv",row.names = FALSE,na = "",
          jsf_vendor_intl_place$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(VendorSize_Intl,IsFMS, PlaceIsForeign),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,VendorSize_Intl))

ggsave600dpi(jsf_vendor_intl_place,file="../output/jsf_vendor_intl_place.png",
             size = 12, lineheight=1, height =4.5, width=9)


# platpscintldef$Shiny.VendorSize
# undebug(format_data_for_plot)
(jsf_manufacture_intl_place <-  build_plot(data=platpscintldef%>% filter(IsJSF=="JSF (F-35)"& Fiscal_Year>2011),              
                                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="PlaceOfManufacture_Sum",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )#, scales="free_y"
  )


write.csv(file="..//Output//jsf_manufacture_intl_place.csv",row.names = FALSE,na = "",
          jsf_manufacture_intl_place$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PlaceIsForeign,IsFMS, PlaceOfManufacture_Sum),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,PlaceOfManufacture_Sum))

ggsave600dpi(jsf_manufacture_intl_place,file="../output/jsf_manufacture_intl_place.png",
             size = 12, lineheight=1, height =4.5, width=9)

platpscintldef$OriginISOalpha3
(jsf_manufacture_intl_place <-  build_plot(data=platpscintldef%>% filter(IsJSF=="JSF (F-35)"& Fiscal_Year>2011),              
                                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="OriginISOalpha3",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            # labels_and_colors=intl_lc,
                            # column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )#, scales="free_y"
  )



```


### JSF Place
```{r FPDS_vendor_Intl}


# undebug(format_data_for_plot)
(fpds_manufacture_intl_place <-  build_plot(data=platpscintldef%>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign) &
                                                                            Fiscal_Year>2011 & !is.na(IsFMS)),#IsFMS==TRUE                             
                                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="PlaceOfManufacture_Sum",
                            facet_var="IsFMSplaceIntl",
                            second_var="IsJSF",
                            # labels_and_colors=intl_lc,
                            # column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")#+
    # facet_grid( IsJSF+PlaceIsForeign )#, scales="free_y"
  )


```

### FMS Vendor Size/Intl and Place No JSF
```{r FPDS_vendor_Intl}


summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$VendorSize_Intl)

# undebug(format_data_for_plot)
(fpds_vendor_intl_place <-  build_plot(data=platpscintldef %>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign)&
                                                                      !is.na(IsFMS)& Fiscal_Year>2011),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="VendorSize_Intl",
                            facet_var="IsJSF",
                            second_var="IsFMSplaceIntl",
                            # labels_and_colors=intl_lc,
                            # column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid(IsFMSplaceIntl~IsJSF, scales="free_y", space="free_y")
  )


summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$VendorSize_Intl)

# undebug(format_data_for_plot)
(fpds_vendor_intl_place_noJSF <-  build_plot(data=platpscintldef %>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign)&
                                                                      !is.na(IsFMS)& Fiscal_Year>2011&
                                                                            IsJSF %in% c("Other Project","Unknown Project")),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="VendorSize_Intl",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )+labs(title="FMS or Performed Internationally, No JSF")#, scales="free_y"
  )


write.csv(file="..//Output//FMS_vendorplaceintl_noJSF.csv",row.names = FALSE,na = "",
          fpds_vendor_intl_place_noJSF$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(VendorSize_Intl,IsFMS, PlaceIsForeign),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,VendorSize_Intl))

ggsave600dpi(fpds_vendor_intl_place_noJSF,file="../output/FMS_vendorplaceintl_noJSF.png",
             size = 12, lineheight=1, height =4.5, width=9)


# platpscintldef$Shiny.VendorSize
(fpds_vendor_place_noJSF <-  build_plot(data=platpscintldef %>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign)&
                                                                      !is.na(IsFMS)&Fiscal_Year>2011&
                                                                            IsJSF %in% c("Other Project","Unknown Project") ),#IsFMS==TRUE  
                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="Shiny.VendorSize",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )+labs(title="FMS or Performed Internationally, No JSF")#, scales="free_y"#, scales="free_y"
  )

ggsave600dpi(fpds_vendor_place_noJSF,file="../output/FMS_vendorplace_noJSF.png",
             size = 12, lineheight=1, height =4.5, width=9)


write.csv(file="..//Output//FMS_vendorplace_noJSF.csv",row.names = FALSE,na = "",
          fpds_vendor_place_noJSF$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(Shiny.VendorSize,PlaceIsForeign,IsFMS),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,Shiny.VendorSize,IsFMS))


```


