---
title: "Defense Acquisition Trends"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, October 6, 2021"
---

# Setup
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)
library(openxlsx)
axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40
if(!exists("platpscintldef"))
  load(file="../data/clean/platpscintl_FPDS.Rda")


if(!exists("platpscdefcd"))
  load(file="../data/clean/platpscdefcd.Rda")
# save.image("../.RData")
```

# Preprocessing 

## Project
```{r PreprocessProject}

summary(factor(platpscintldef$ProjectPlatform))

colnames(platpscintldef)[colnames(platpscintldef)=="Action_Obligation_Then_Year_Then_Year"]<-
  "Action_Obligation_Then_Year"

colnames(platpscintldef)[colnames(platpscintldef)=="Action_Obligation_Then_Year_OMB23_GDP21"]<-
  "Action_Obligation_OMB25_GDP23"

topplat<-platpscintldef %>% group_by (Project.Name,PlatformPortfolio) %>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
            Action_Obligation_2020=sum(ifelse(Fiscal_Year==2020,Action_Obligation_OMB25_GDP23,0)))%>%
              group_by (PlatformPortfolio) %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
                        rank_2020=rank(desc(Action_Obligation_2020)))
topplat %>% arrange(desc(Action_Obligation_OMB25_GDP23))


topplat$TopProject<-
  ifelse(topplat$rank_2020<=7 | topplat$rank_total<=7,topplat$Project.Name,NA)

platpscintldef<-left_join(platpscintldef,topplat %>% select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2020),
          by=c("Project.Name","PlatformPortfolio"))

platpscintldef$TopProject[is.na(platpscintldef$TopProject) & !is.na(platpscintldef$Project.Name)]<-
  "Other Labeled Project"


summary(factor(platpscintldef$TopProject))


```
## PSC
```{r PreprocessPSC}

summary(factor(platpscintldef$ProjectPlatform))

topPSC<-platpscintldef %>% group_by (ProductOrServiceCode,ProductOrServiceCodeText,PlatformPortfolio) %>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
            Action_Obligation_2020=sum(ifelse(Fiscal_Year==2020,Action_Obligation_OMB25_GDP23,0)))%>%
              group_by (PlatformPortfolio) %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
                        rank_2020=rank(desc(Action_Obligation_2020)))
topPSC %>% arrange(desc(Action_Obligation_OMB25_GDP23))

topPSC$TopPScode<-
  ifelse(topPSC$rank_2020<=7 | topPSC$rank_total<=7,topPSC$ProductOrServiceCode,NA)
topPSC$TopPStext<-
  ifelse(topPSC$rank_2020<=7 | topPSC$rank_total<=7,topPSC$ProductOrServiceCodeText,NA)


platpscintldef<-left_join(platpscintldef,topPSC %>% select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2020),
          by=c("ProductOrServiceCode","PlatformPortfolio"))

platpscintldef$TopPScode[is.na(platpscintldef$TopPScode) & !is.na(platpscintldef$ProductOrServiceCode)]<-
  "Other Labeled PSC"
platpscintldef$TopPStext[is.na(platpscintldef$TopPStext) & !is.na(platpscintldef$ProductOrServiceCode)]<-
  "Other Labeled PSC"

platpscintldef$TopPStext<-factor_wrap(platpscintldef$TopPStext)

summary(factor(platpscintldef$TopPStext))


```

## Place State
```{r PreprocessState}

# platpscintldef$pop_isna<-is.na(platpscintldef$pop_state_code)
# platpscintldef$sc_isna<-is.na(platpscintldef$PlaceStateCode)
# platpscintldef %>% group_by(Fiscal_Year,pop_isna,sc_isna) %>%
#   summarise(n=length(Fiscal_Year))

# summary(factor(platpscintldef$CrisisProductOrServiceArea))

topState<-platpscintldef %>% group_by (pop_state_code,CrisisProductOrServiceArea) %>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
            Action_Obligation_2020=sum(ifelse(Fiscal_Year==2020,Action_Obligation_OMB25_GDP23,0)))%>%
              group_by (CrisisProductOrServiceArea) %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
                        rank_2020=rank(desc(Action_Obligation_2020)))
topState %>% arrange(desc(Action_Obligation_OMB25_GDP23))

topState$TopStateAbbr<-
  ifelse(topState$rank_2020<=25 | topState$rank_total<=25,topState$pop_state_code,NA)
# topState$TopStateName<-
#   ifelse(topState$rank_2020<=7 | topState$rank_total<=7,topState$PlaceStateCodeText,NA)
platpscintldef<-platpscintldef[,!colnames(platpscintldef) %in% c("Action_Obligation_OMB25_GDP23.x","Action_Obligation_OMB25_GDP23.y",
                                   "Action_Obligation_2020.x","Action_Obligation_2020.y",
  "rank_total.y","rank_total.x","rank_2020.y","rank_2020.x","TopStateAbbr.x","TopStateAbbr.y")]

platpscintldef<-left_join(platpscintldef,topState %>% select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2020),
          by=c("pop_state_code","CrisisProductOrServiceArea"))

platpscintldef$TopStateAbbr[is.na(platpscintldef$TopStateAbbr) & !is.na(platpscintldef$pop_state_code)]<-
  "Other Labeled State"
# platpscintldef$TopStateName[is.na(platpscintldef$TopStateName) & !is.na(platpscintldef$pop_state_code)]<-
#   "Other Labeled State"


# summary(factor(platpscintldef$TopStateName))


```

## Place Country
```{r PreprocessCountry}

# summary(factor(platpscintldef$CrisisProductOrServiceArea))
colnames(platpscintldef)[colnames(platpscintldef)=="Fiscal_Year"]<-"Fiscal_Year"
topCountry<-platpscintldef %>% group_by (PlaceISOalpha3,CrisisProductOrServiceArea) %>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
            Action_Obligation_2020=sum(ifelse(Fiscal_Year==2020,Action_Obligation_OMB25_GDP23,0)))%>%
              group_by (CrisisProductOrServiceArea) %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB25_GDP23)),
                        rank_2020=rank(desc(Action_Obligation_2020)))
topCountry %>% arrange(desc(Action_Obligation_OMB25_GDP23))

topCountry$TopCountryISO<-
  ifelse(topCountry$rank_2020<=7 | topCountry$rank_total<=7,topCountry$PlaceISOalpha3,NA)
# topCountry$TopCountryName<-
#   ifelse(topCountry$rank_2020<=7 | topCountry$rank_total<=7,topCountry$PlaceCountryCodeText,NA)


platpscintldef<-left_join(platpscintldef,topCountry %>% select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2020),
          by=c("PlaceISOalpha3","CrisisProductOrServiceArea"))

platpscintldef$TopCountryISO[is.na(platpscintldef$TopCountryISO) & !is.na(platpscintldef$PlaceISOalpha3)]<-
  "Other Labeled Country"
# platpscintldef$TopCountryName[is.na(platpscintldef$TopCountryName) & !is.na(platpscintldef$PlaceISOalpha3)]<-
#   "Other Labeled Country"


# summary(factor(platpscintldef$TopCountryName))


```

# Top Projects Annual

```{r TopProject}
summary(platpscintldef$PlatformPortfolio[platpscintldef$ProductOrServiceCode=='AC11'])

topoverall<-platpscintldef %>% group_by (Project.Name,Fiscal_Year) %>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))%>%
              group_by (Fiscal_Year) %>%
    mutate(rank_annual=rank(desc(Action_Obligation_OMB25_GDP23))) %>%
  arrange(desc(Fiscal_Year) ,desc(Action_Obligation_OMB25_GDP23))


topoverall$TopProject<-
  ifelse(topoverall$rank_annual<=11,topoverall$Project.Name,NA)
#11 because NA counts as one.


topoverall$TopProject[is.na(topoverall$TopProject) & !is.na(topoverall$Project.Name)]<-
  "Other Labeled Project"


write.csv(topoverall %>% group_by(TopProject,Fiscal_Year) %>%
            summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))%>%
            arrange(desc(Fiscal_Year) ,desc(Action_Obligation_OMB25_GDP23))
          
          ,file="TopAnnualDoDproject.csv",row.names = FALSE)


# platpscintldef<-left_join(platpscintldef,topplat %>% select(-Action_Obligation_OMB25_GDP23,Action_Obligation_2020),
#           by=c("Project.Name","PlatformPortfolio"))


```


# International
##FMS 
### Topline FMS





####FMS identification
```{r contract_identification}



# undebug(build_plot)

(contract_identification <-  build_plot(data=platpscintldef %>% filter(ContractingCustomer=="Defense"),
                            chart_geom="Bar Chart",
                            share=FALSE,
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="foreign_funding_description",
                            facet_var="IsFMS",
                            # second_var="StateRegion",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                        format=TRUE)+
    # facet_grid(  IsFMS~., scales="free_y")+
  labs(#x="Year of Delivery (Calendar or Fiscal Varies by Source)",
       y="Constant 2022 $ Obligated",
       caption="Source: FPDS; CSIS analysis.")+
    guides(fill=guide_legend(ncol=3)))

ggsave600dpi(contract_identification,file="../output/figure_03_contract_identification.png",size=12,lineheight=1, height =5, width=9)



```

### FMS or International

#### Service Category
```{r FPDS_vendor_Intl}

summary(factor(platpscintldef$SimpleArea))
# undebug(format_data_for_plot)
(fmsintl_service <-  build_plot(data=platpscintldef%>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign) &
                                                                            Fiscal_Year>2011 & !is.na(IsFMS)&
                                                                  SimpleArea=="Services"),#IsFMS==TRUE                             
                                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="ProductOrServiceArea",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )+labs(title="Services FMS or Performed Internationally")#, scales="free_y"#, scales="free_y"
  )
summary(platpscintldef$dFYear)

write.csv(file="..//Output//fmsintl_service.csv",row.names = FALSE,na = "",
          fmsintl_service$data%>%# mutate(Fiscal_Year=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PlaceIsForeign,IsFMS,ProductOrServiceArea),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,ProductOrServiceArea))

ggsave600dpi(fmsintl_service,file="../output/fmsintl_service.png",
             size = 12, lineheight=1, height =6, width=9)


(fmsintl_service_vendor <-  build_plot(data=platpscintldef%>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign) &
                                                                            Fiscal_Year>2011 & !is.na(IsFMS)&
                                                                  SimpleArea=="Services"),#IsFMS==TRUE                             
                                            chart_geom="Bar Chart",
                            x_var="dFYear",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="ProductOrServiceArea",
                            facet_var="IsFMSplaceIntl",
                            second_var="VendorSize_Intl",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( IsFMSplaceIntl~VendorSize_Intl , scales="free_y", space="free_y")+labs(title="Services FMS or Performed Internationally")+
    theme(  strip.text.y=element_text(angle=0))
  )


write.csv(file="..//Output//fmsintl_service_vendor.csv",row.names = FALSE,na = "",
          fmsintl_service_vendor$data%>% mutate(Fiscal_Year=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(IsFMSplaceIntl,VendorSize_Intl,ProductOrServiceArea),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(IsFMSplaceIntl,VendorSize_Intl,ProductOrServiceArea))

ggsave600dpi(fmsintl_service_vendor,file="../output/fmsintl_service_vendor.png",
             size = 12, lineheight=1, height =6, width=9)

```

## Any International 
### ** Setup **
```{r vendor_label}


aus_fpds %>% group_by(ausorgtype,ParentID,parentheadquarterscountrycode)%>%
  filter(!is.na(parentheadquarterscountrycode))%>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))%>%
  arrange(ausorgtype,-Action_Obligation_OMB25_GDP23)
# "U.S. Owned Business"='A',
#   "Other U.S. Entity (e.g. Government)"='B',
  #   "Foreign-Owned Business Incorporated in the U.S."='C',
#   "Foreign-Owned Business Not Incorporated in the U.S."='D',
#   "Other Foreign Entity (e.g. Foreign Government)"='O'

aus_fpds$ausorgtype[
  aus_fpds$manufacturingorganizationtext=="U.S. Owned Business"&
           !is.na(aus_fpds$manufacturingorganizationtext)&
           aus_fpds$OriginIsoAlpha3=="AUS"&
           !is.na(aus_fpds$OriginIsoAlpha3)&
    is.na(aus_fpds$parentheadquarterscountrycode)]<-
  "U.S. Owned Business (Good/Service has Australian Origin)"


aus_fpds$ausorgtype[
  aus_fpds$manufacturingorganizationtext %in%
    c("U.S. Owned Business",
      "Foreign-Owned Business Incorporated in the U.S.",
      "Other Entities (e.g. Governments")&
           !is.na(aus_fpds$manufacturingorganizationtext)&
           aus_fpds$parentheadquarterscountrycode=="AUS"&
           !is.na(aus_fpds$parentheadquarterscountrycode)]<-
  "Australian-Owned Business Incorporated in the U.S."


aus_fpds$ausorgtype[
  aus_fpds$manufacturingorganizationtext %in%
    c("Foreign-Owned Business Not Incorporated in the U.S.")&
    !is.na(aus_fpds$ausorgtype)&
    aus_fpds$VendorIsoAlpha3=="AUS"&
    !is.na(aus_fpds$VendorIsoAlpha3)]<-
  "Australian-Owned Business (Including Global Subsidiaries)"


aus_fpds$PlaceIsForeignText<-factor(aus_fpds$PlaceIsForeign)
levels(aus_fpds$PlaceIsForeignText)<-list(
  "International\nLocation"=1,
  "U.S.\nLocation"=0
)

write.csv(file="aus_list.csv",row.names = FALSE,
          aus_fpds %>% filter(Fiscal_Year>=2011 & Customer=="Defense") %>%
            group_by(ausorgtype,ParentID,VendorIsoAlpha3)%>%
            summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))%>%
            arrange(ausorgtype,-Action_Obligation_OMB25_GDP23)
)
```

### FMS Vendor Size/Intl and Place
```{r FPDS_vendor_Intl}

summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$VendorSize_Intl)

# undebug(format_data_for_plot)
(fpds_vendor_intl_place <-  build_plot(data=platpscintldef %>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign)&
                                                                      !is.na(IsFMS)& Fiscal_Year>2011),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="VendorSize_Intl",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )+labs(title="FMS or Performed Internationally, Including JSF")#, scales="free_y"
  )


write.csv(file="..//Output//FMS_vendorplaceintl_all.csv",row.names = FALSE,na = "",
          fpds_vendor_intl_place$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(VendorSize_Intl,IsFMS, PlaceIsForeign),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,VendorSize_Intl))

ggsave600dpi(fpds_vendor_intl_place,file="../output/FMS_vendorplaceintl_all.png",
             size = 12, lineheight=1, height =4.5, width=9)


# platpscintldef$Shiny.VendorSize
(fpds_vendor_place <-  build_plot(data=platpscintldef %>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign)&
                                                                      !is.na(IsFMS)&Fiscal_Year>2011 ),#IsFMS==TRUE  
                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="Shiny.VendorSize",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )+labs(title="FMS or Performed Internationally, Including JSF")#, scales="free_y"#, scales="free_y"
  )

ggsave600dpi(fpds_vendor_place,file="../output/FMS_vendorplace_all.png",
             size = 12, lineheight=1, height =4.5, width=9)


write.csv(file="..//Output//FMS_vendorplace_all.csv",row.names = FALSE,na = "",
          fpds_vendor_place$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(Shiny.VendorSize,PlaceIsForeign,IsFMS),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,Shiny.VendorSize,IsFMS))


```





### FMS Vendor Size/Intl and Place
```{r FPDS_vendor_Intl}

summary(factor(aus_fpds$Shiny.VendorSize[aus_fpds$VendorIsForeign==1]))

#(PlaceIsForeign==1|IsFMS==TRUE)&
# undebug(format_data_for_plot)

(fpds_aus_vendor_intl_place <-  build_plot(data=aus_fpds %>% filter(!is.na(PlaceIsForeignText)&
                                                                      !is.na(isFMS)&
                                                                      Customer=="Defense"&
                                                                      Fiscal_Year>2011),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="dFYear",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="ausorgtype",
                            facet_var="PlaceIsForeignText",
                            # alpha_var="YTD",
                            second_var="isFMS",
                            labels_and_colors=aus_lc,
                            column_key=aus_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( isFMS~PlaceIsForeignText )+labs(title="U.S. DoD Prime Contracts with Australian\nLocation, Origin, or Vendor")+
    date_x_year_breaks(2012,2022,3,partial_year=2024,partial_label="\nQ1")#, scales="free_y"
  )





ggsave600dpi(fpds_aus_vendor_intl_place+
               theme(legend.position="bottom")+
    guides(fill=guide_legend(ncol=1)),file="../output/ntib/fpds_aus_vendor_intl_place.png",
             size = 12, lineheight=1, height =5.75, width=5.5)





```





## JSF 

#### JSF-MDAP-FMS
```{r FPDS_JSF}

summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$IsFMS)
summary(factor(platpscintldef$IsJSF))

platpscintldef<-platpscintldef %>% mutate(
  FMSJSF=case_when(
    IsFMS==1 & IsJSF =="JSF (F-35)" ~ "Includes FMS (JSF)",
    IsFMS==1 & IsJSF =="JSF (F-35)" ~ "Includes FMS (JSF)"
  )
)

# undebug(format_data_for_plot)
(fms_jsf <-  build_plot(data=platpscintldef %>% filter(Fiscal_Year>2011),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="IsFMS",
                            facet_var="IsJSF",
                            # second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsJSF)#, scales="free_y"
  )



ggsave600dpi(fms_jsf,file="../output/jsf_vendor_intl_place.png",
             size = 12, lineheight=1, height =4.5, width=9)




```
#### JSF National Origin
```{r FPDS_JSF}

summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$VendorSize_Intl)

# undebug(format_data_for_plot)
(jsf_vendor_intl_place <-  build_plot(data=platpscintldef %>% filter(IsJSF=="JSF (F-35)"& Fiscal_Year>2011),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="VendorSize_Intl",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )#, scales="free_y"
  )


write.csv(file="..//Output//jsf_vendor_intl_place.csv",row.names = FALSE,na = "",
          jsf_vendor_intl_place$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(VendorSize_Intl,IsFMS, PlaceIsForeign),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,VendorSize_Intl))

ggsave600dpi(jsf_vendor_intl_place,file="../output/jsf_vendor_intl_place.png",
             size = 12, lineheight=1, height =4.5, width=9)


# platpscintldef$Shiny.VendorSize
# undebug(format_data_for_plot)
(jsf_manufacture_intl_place <-  build_plot(data=platpscintldef%>% filter(IsJSF=="JSF (F-35)"& Fiscal_Year>2011),              
                                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="PlaceOfManufacture_Sum",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )#, scales="free_y"
  )


write.csv(file="..//Output//jsf_manufacture_intl_place.csv",row.names = FALSE,na = "",
          jsf_manufacture_intl_place$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PlaceIsForeign,IsFMS, PlaceOfManufacture_Sum),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,PlaceOfManufacture_Sum))

ggsave600dpi(jsf_manufacture_intl_place,file="../output/jsf_manufacture_intl_place.png",
             size = 12, lineheight=1, height =4.5, width=9)

platpscintldef$OriginISOalpha3
(jsf_manufacture_intl_place <-  build_plot(data=platpscintldef%>% filter(IsJSF=="JSF (F-35)"& Fiscal_Year>2011),              
                                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="OriginISOalpha3",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            # labels_and_colors=intl_lc,
                            # column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )#, scales="free_y"
  )



```


#### JSF Place
```{r FPDS_vendor_Intl}


# undebug(format_data_for_plot)
(fpds_manufacture_intl_place <-  build_plot(data=platpscintldef%>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign) &
                                                                            Fiscal_Year>2011 & !is.na(IsFMS)),#IsFMS==TRUE                             
                                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="PlaceOfManufacture_Sum",
                            facet_var="IsFMSplaceIntl",
                            second_var="IsJSF",
                            # labels_and_colors=intl_lc,
                            # column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")#+
    # facet_grid( IsJSF+PlaceIsForeign )#, scales="free_y"
  )


```

#### FMS Vendor Size/Intl and Place No JSF
```{r FPDS_vendor_Intl}


summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$VendorSize_Intl)

# undebug(format_data_for_plot)
(fpds_vendor_intl_place <-  build_plot(data=platpscintldef %>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign)&
                                                                      !is.na(IsFMS)& Fiscal_Year>2011),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="VendorSize_Intl",
                            facet_var="IsJSF",
                            second_var="IsFMSplaceIntl",
                            # labels_and_colors=intl_lc,
                            # column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid(IsFMSplaceIntl~IsJSF, scales="free_y", space="free_y")
  )


summary(factor(platpscintldef$Shiny.VendorSize[platpscintldef$VendorIsForeign==1]))
summary(platpscintldef$VendorSize_Intl)

# undebug(format_data_for_plot)
(fpds_vendor_intl_place_noJSF <-  build_plot(data=platpscintldef %>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign)&
                                                                      !is.na(IsFMS)& Fiscal_Year>2011&
                                                                            IsJSF %in% c("Other Project","Unknown Project")),
                                       #IsFMS==TRUE 
                                       chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="VendorSize_Intl",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )+labs(title="FMS or Performed Internationally, No JSF")#, scales="free_y"
  )


write.csv(file="..//Output//FMS_vendorplaceintl_noJSF.csv",row.names = FALSE,na = "",
          fpds_vendor_intl_place_noJSF$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(VendorSize_Intl,IsFMS, PlaceIsForeign),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,IsFMS,VendorSize_Intl))

ggsave600dpi(fpds_vendor_intl_place_noJSF,file="../output/FMS_vendorplaceintl_noJSF.png",
             size = 12, lineheight=1, height =4.5, width=9)


# platpscintldef$Shiny.VendorSize
(fpds_vendor_place_noJSF <-  build_plot(data=platpscintldef %>% filter((PlaceIsForeign==1|IsFMS==TRUE)&!is.na(PlaceIsForeign)&
                                                                      !is.na(IsFMS)&Fiscal_Year>2011&
                                                                            IsJSF %in% c("Other Project","Unknown Project") ),#IsFMS==TRUE  
                            chart_geom="Bar Chart",
                            x_var="Fiscal_Year",
                            y_var="Action_Obligation_OMB25_GDP23",
                            color_var="Shiny.VendorSize",
                            facet_var="PlaceIsForeign",
                            second_var="IsFMS",
                            labels_and_colors=intl_lc,
                            column_key=intl_ck,
                            legend=TRUE,
                            caption=FALSE,
                            format=TRUE)+theme(legend.position = "right")+
    facet_grid( .~IsFMS+PlaceIsForeign )+labs(title="FMS or Performed Internationally, No JSF")#, scales="free_y"#, scales="free_y"
  )

ggsave600dpi(fpds_vendor_place_noJSF,file="../output/FMS_vendorplace_noJSF.png",
             size = 12, lineheight=1, height =4.5, width=9)


write.csv(file="..//Output//FMS_vendorplace_noJSF.csv",row.names = FALSE,na = "",
          fpds_vendor_place_noJSF$data%>%# mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(Shiny.VendorSize,PlaceIsForeign,IsFMS),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)%>% arrange(PlaceIsForeign,Shiny.VendorSize,IsFMS))


```


