---
title: "Contract Termination"
author: "Greg Sanders"
date: "Wednesday, February 8, 2017"
output:
  html_document:
    keep_md: yes
--- 

Modeling Size f  Contract Breaches for those Contracts that Breached
============================================================================

#Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(Hmisc)
library(sjstats)
source("..\\scripts\\DIIGstat.r")
source("..\\scripts\\NAICS.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start.

##Prepare Data

First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from FPDS.

The final sample uses 1 million rows of data, but as a computation shortcut, only a subset of the data is needed to allow for processing of models in minutes rather than hours.

```{r ReadInData, echo = TRUE}
if(!exists("def")) load(file="..//Data//clean//transformed_def.Rdata")
load(file="..//data//clean//def_sample.Rdata")
```

### Contract Ceiling Breaches

Contract Ceiling Breaches and the number of change orders can be calculated for the entire sample.  Change orders are determined using the *Reason for Modification* field in FPDS. 

#Level-1 Regression Model

##Study Variable: Competition
Competition has the potential to reduce terminations by giving the government more options in vendors and encouraging better behavior from the contractor that was chosen. 

###Model 01A: No Competition / Number of Offer Categories 

```{r Model01A}

#Frequency Plot
summary_discrete_plot(def_breach,"CompOffr",metric="cbre")

#Model
ln_CBre_Comp_01A <- glm (data=def_breach,
                 ln_CBre_Then_Year ~ CompOffr)
summary(ln_CBre_Comp_01A)
summary_residual_compare(ln_CBre_Comp_01A,bins=2, skip_vif=TRUE)

```

For ceiling breaches, no competition is associated with larger magnitude breaches in line with expectations. Contrary to expectations, so competition with 5+ offers is only a bit below that. The other results are in line with expectations, with 3-4 offers is associated with the smallest size of breaches and perhaps surprisingly single offer competition having similar results as competition with two offers.

## Study Variable Consolidation

### Level 6
#### Model NCS6A: l_def6_HHI_lag1

Expectations is that more consolidation is assoiated a change in occurance of breaches.
```{r ModelNCS6A}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(def_breach,"def6_HHI_lag1",metric="cbre")
summary_continuous_plot(def_breach,"def6_HHI_lag1",metric="cbre",log=TRUE)
summary_continuous_plot(def_breach,"def3_HHI_lag1",metric="cbre")
summary_continuous_plot(def_breach,"def3_HHI_lag1",metric="cbre",log=TRUE)


#Model
ln_CBre_Cons_NCS6A <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1)
summary(ln_CBre_Cons_NCS6A)


#Plot residuals versus fitted
  stargazer::stargazer(ln_CBre_Comp_01A,ln_CBre_Cons_NCS6A,type="text",
                       digits=2)
  
#For first model in category, include only the new model(s), skip_vif=true
summary_residual_compare(ln_CBre_Cons_NCS6A,bins=20,skip_vif = TRUE)


```

Expectation is are upheld with a negative sign.

#### Model NCS6B: Defense to Overall ratio
The higher the ratio of defense obligations to reciepts in the overall economy, the DoD holds a monosopy over a sector. Given the challenges of monosopy, the a higher ratio estimates a greater  risk of ceiling breaches.
```{r ModelNCS6B}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(def_breach,"capped_def6_ratio_lag1",metric="cbre")
      summary_continuous_plot(def_breach,"capped_def6_ratio_lag1",metric="cbre",log=TRUE)

      summary_continuous_plot(def_breach,"capped_def3_ratio_lag1",metric="cbre")
      summary_continuous_plot(def_breach,"capped_def3_ratio_lag1",metric="cbre",log=TRUE)



#Model
ln_CBre_NCS6B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_ratio_lag1)
summary(ln_CBre_NCS6B)

# 
# #Plot the fitted model plot
# ln_CBre_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(ln_CBre_02A))}
# 
# #Competition curves
# fitted_ln_CBre_model(def_breach,"cl_Ceil_Then_Year") + stat_function(fun = ln_CBre_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = ln_CBre_02A_curve, 
#                              args=list(Comp=2),color="blue")



#Plot residuals versus fitted
  stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_NCS6B,
                       ln_CBre_Comp_01A,type="text",
                       digits=2)


#For first model in category, include only the new model(s), skip_vif=true
summary_residual_compare(ln_CBre_NCS6B,skip_vif=TRUE,bins=10)


```
The results align with expectations, when ratio is  logged.


#### Model NCS6C: cl_def6_obl_lag1
Defense sector obligations are added to better adjust for the fact that larger sectors tend to have lower HHI indices if only because they include a broader range of activities. In addition, Acting somewhat as a proxy for MDAP status, larger sectors may also have a greater risk of cascading problems. Thus greater defense obligations in a given sector are expected to estimate a greater likelihood over ceiling breaches,
Expectations are  unchanged.
```{r ModelNCS6C}

summary_continuous_plot(def_breach,"cl_def6_obl_lag1",metric="cbre")
      summary_continuous_plot(def_breach,"cl_def6_obl_lag1",metric="cbre",log=TRUE)


#Model
ln_CBre_NCS6C <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_obl_lag1)
summary(ln_CBre_NCS6C)

#Plot residuals versus fitted
stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_NCS6B,ln_CBre_NCS6C,
                       type="text",
                       digits=2)


#For first model in category, include only the new model(s), skip_vif=true
summary_residual_compare(ln_CBre_NCS6C,bins=10,skip_vif = TRUE)


```
The result runs contrary to expectation. 

#### Model NCS6D: Average Salary
Average salary can be an proxy for unobserved skill requirements. We expect that a greater skill requirement will estimate a greater risk of ceiling breaches.
```{r ModelNCS6D}
#Frequency Plot for unlogged ceiling

summary_continuous_plot(def_breach,"US6_avg_sal_lag1",metric="cbre")
summary_continuous_plot(def_breach,"US6_avg_sal_lag1",metric="cbre" ,log=TRUE)

#Model

ln_CBre_NCS6D <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_US6_avg_sal_lag1 )
summary(ln_CBre_NCS6D)



#Plot residuals versus fitted
stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_NCS6B,ln_CBre_NCS6C,ln_CBre_NCS6D,
                       type="text",
                       digits=2)


# For individual models, only the new model(s) unless they have a clear counterpart or alternate, skip_vif=true
summary_residual_compare(ln_CBre_NCS6D,bins=10,skip_vif = TRUE)

```
Results align with expectations. Interestingly, this had not been true in the logit model, suggesting that larger salary may be associated with less frequent but greater magnitude breaches.

#### Model NCS6E: Cumulative
```{r ModelNCS6l}
#Model
ln_CBre_Cons_NCS6E <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+cl_US6_avg_sal_lag1)
glmer_examine(ln_CBre_Cons_NCS6E)

ln_CBre_Comp_NCS6E <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_ratio_lag1+cl_def6_obl_lag1+cl_US6_avg_sal_lag1)
glmer_examine(ln_CBre_Comp_NCS6E)
# 


#Plot residuals versus fitted
  stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_NCS6B,ln_CBre_NCS6C,ln_CBre_NCS6D,ln_CBre_Cons_NCS6E,
                       ln_CBre_Comp_01A,ln_CBre_Comp_NCS6E,type="text",
                       digits=2)

#For the first cumulative model(s) compare to compnent study variables, skip_vif =false
summary_residual_compare(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS6E,bins=10)
summary_residual_compare(ln_CBre_Comp_01A,ln_CBre_Comp_NCS6E,bins=2)


```
With the ceiling breach model, when combined magnitudes are reduced but the signs are unchanged.

With competition, the sign flips for ratio and average salary, in both cases turning it contrary to expectation.

### Level 3
#### Model NCS3A: cl_def3_HHI
As with NAICS6, consolidation is expected to influence ceiling breach occurance/size, but the direction is not predicted.
```{r ModelNCS3A}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(def_breach,"def3_HHI_lag1",metric="cbre")
summary_continuous_plot(def_breach,"def3_HHI_lag1",metric="cbre",log=TRUE)

#Model
ln_CBre_Cons_NCS3A <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1)
summary(ln_CBre_Cons_NCS3A)


#Plot residuals versus fitted
stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS6E,ln_CBre_Cons_NCS3A,
                       ln_CBre_Comp_01A,ln_CBre_Comp_NCS6E,type="text",
                       digits=2)


#For subsequent models in category, compare to prior in category or prior highly relevant, skip_vif=true
summary_residual_compare(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,bins=20,skip_vif=TRUE)


```

Expectations are upheld with a negative sign. That said, this seems to turn around some at the high end of the scale.

#### Model NCS3B: Defense to Overall ratio
The higher the ratio of defense obligations to reciepts in the overall economy, the DoD holds a monosopy over a sector. Given the challenges of monosopy, the a higher ratio estimates a greater  risk of ceiling breaches.
```{r ModelNCS3l}
#Frequency Plot for unlogged ceiling


summary_continuous_plot(def_breach,"capped_def3_ratio_lag1",metric="cbre")
summary_continuous_plot(def_breach,"capped_def3_ratio_lag1",metric="cbre",log=TRUE)

#Model
ln_CBre_NCS3B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~ cl_def3_ratio_lag1)
summary(ln_CBre_NCS3B)
# 
stargazer::stargazer(ln_CBre_Cons_NCS3A,ln_CBre_NCS3B,ln_CBre_NCS6B,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS6E,
                       ln_CBre_Comp_01A,ln_CBre_Comp_NCS6E,
                     type="text",
                       digits=2)

#For subsequent models in category, compare to prior in category or prior highly relevant, skip_vif=true
summary_residual_compare(ln_CBre_NCS6B,ln_CBre_NCS3B,bins=5,skip_vif = TRUE)



```
The results align with the hypothesis and the magnitude is larger than the level 6 version.

#### Model NCS3C: Cumulative Model
Consolidation at lessa nd more granular levels may have different effects. Efficiencies are often used to describe sectors, like utilities, with high barriers to entry. Many of these aspects seem like they would already be captured at less granular NAICS levels, e.g. power plants, rather than more specific NAICS levels, like solar vs. coal. As a result, consolidation for more granular NAICS codes should estimate higher rates of ceiling breaches compared to less granular NAICS code.

We'll start by adding in everything from both models and seeing what violates VIF.
```{r ModelNCS3C}
#Frequency Plot for unlogged ceiling



#Model
ln_CBre_Cons_NCS3C <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1)
glmer_examine(ln_CBre_Cons_NCS3C)


ln_CBre_Cons_NCS3C2 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1)
glmer_examine(ln_CBre_Cons_NCS3C2)

ln_CBre_Cons_NCS3C3 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1)
glmer_examine(ln_CBre_Cons_NCS3C3)

ln_CBre_Comp_NCS3C <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_def6_obl_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1)
glmer_examine(ln_CBre_Comp_NCS3C)
# 
ln_CBre_Comp_NCS3C2 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1)
glmer_examine(ln_CBre_Comp_NCS3C2)

#Plot residuals versus fitted
  stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS6E,
                       ln_CBre_Cons_NCS3A,ln_CBre_NCS3B,ln_CBre_Cons_NCS3C3,
                       ln_CBre_Comp_01A,ln_CBre_Comp_NCS6E,ln_CBre_Comp_NCS3C2,type="text",
                       digits=2)



# 
# #Plot the fitted model plot
# ln_CBre_02A_curve<-function(x, Comp){invlogit(cbind(1,Comp,x) %*%  coef(ln_CBre_02A))}
# 
# #Competition curves
# fitted_ln_CBre_model(def_breach,"cl_Ceil_Then_Year") + stat_function(fun = ln_CBre_02A_curve, 
#                              args=list(Comp=0),color="blue")+
#   stat_function(fun = ln_CBre_02A_curve, 
#                              args=list(Comp=2),color="blue")


#ompare with cumulative consolidation and competition
summary_residual_compare(ln_CBre_Cons_NCS6E,ln_CBre_Cons_NCS3C3,ln_CBre_Comp_NCS6E,ln_CBre_Comp_NCS3C2,bins=10)

```
Dropping defense obligations in both models due to VIF challenges in the consolidation model and a desire to maintain consistency between the models.

Def 6 HHI grows  in magnitude. Def 3 ratio greatly reduces in magnitude for competition, though retains signficance. Also in the competition model, average salary and def 6 ratio reverses itself,  resuming the expected direction.
Otherwise some reduction in magnitude, e.g. for 5 offers in the competition model and def3 hhi in the consolidation model.

In the residuals, the high end fitted values appear to overestimate the size of breach. Also worth watching the vif for the two HHI variables remains high in the consolidation model.

##Scope Variables
###Model 02A: Cost Ceiling


```{r Model02A}
#Frequency Plot for unlogged ceiling
summary_continuous_plot(def_breach,"UnmodifiedCeiling_Then_Year",metric="cbre",
               bins=1000)
#Frequency Plot for logged ceiling
summary_continuous_plot(def_breach,"UnmodifiedCeiling_Then_Year",metric="cbre",
               log=TRUE)


#Model
ln_CBre_02A <- glm (data=def_breach,
                 ln_CBre_Then_Year ~ cl_Ceil_Then_Year)
summary(ln_CBre_02A)

#Plot residuals versus fitted
stargazer::stargazer(ln_CBre_02A,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_NCS3C3,
                       ln_CBre_Comp_01A,ln_CBre_Comp_NCS3C2,type="text",
                       digits=2)


#For first model in category, include only the new model(s), skip_vif=true
summary_residual_compare(ln_CBre_02A,bins=20,skip_vif = TRUE)

```

Contract ceiling has a significant relationship, the largest magnitude of the models yet included, and more explanatory power than the previous cumulative model. That said, while the relationship  with contract size for the sample that overruns appears to be linear (once both are logged), the relatonship with frequency appears to follow an exponential pattern. Likewise the residuals are parabolic. Perhaps l_ceil^2 should be introduced.

###Model 02B: Maximum Duration


```{r Model02B}
#Frequency Plot for max duration
summary_continuous_plot(def_breach,"UnmodifiedDays",
               bins=1000,metric="cbre")

#Frequency Plot for logged max duration
summary_continuous_plot(def_breach,"UnmodifiedDays", metric="cbre",log=TRUE)

#Model
ln_CBre_02B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~ cl_Days )
summary(ln_CBre_02B)


stargazer::stargazer(ln_CBre_02A,ln_CBre_02B,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_NCS3C3,
                       ln_CBre_Comp_01A,ln_CBre_Comp_NCS3C2,type="text",
                       digits=2)



#Compare with prior in category
summary_residual_compare(ln_CBre_02B,bins=10,skip_vif = TRUE)

```
Initial duration has the expected relationship, though not as strongly as ceiling. and a stronger one than for ceiling. The frequency relationship looks exponential, if  perhaps not as clearly as for ceiling, and the breach size relationship, when breaches occur, is slightly parabolic, with short duration contracts and long durations contracts both associated with some of the larger breaches.

###Model 02C: Both Scope


```{r Model02C}
#Model
ln_CBre_02C <- glm (data=def_breach,
                 ln_CBre_Then_Year ~ cl_Ceil_Then_Year+ cl_Days )
summary(ln_CBre_02C)


stargazer::stargazer(ln_CBre_02A,ln_CBre_02B,ln_CBre_02C,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_NCS3C3,
                       ln_CBre_Comp_01A,ln_CBre_Comp_NCS3C2,type="text",
                       digits=2)

#ompare with cumulative consolidation and competition
summary_residual_compare(ln_CBre_Cons_NCS3C3,ln_CBre_02C,ln_CBre_Comp_NCS6E,ln_CBre_02C,bins=10,skip_vif = FALSE)



```
Including both moderates both of their influence. 

###Model 02D: Cumulative 


```{r Model02D}
#Model
ln_CBre_02C <- glm (data=def_breach,
                 ln_CBre_Then_Year ~ cl_Ceil_Then_Year+ cl_Days )
summary(ln_CBre_02C)



#Model
ln_CBre_Cons_02D <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days)
glmer_examine(ln_CBre_Cons_02D)

ln_CBre_Comp_02D <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days)
glmer_examine(ln_CBre_Comp_02D)




stargazer::stargazer(ln_CBre_02A,ln_CBre_02B,ln_CBre_02C,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_NCS3C3,ln_CBre_Cons_02D,
                       ln_CBre_Comp_01A,ln_CBre_Comp_NCS3C2,ln_CBre_Comp_02D,type="text",
                       digits=2)

#ompare with cumulative consolidation and competition
summary_residual_compare(ln_CBre_Cons_NCS3C3,ln_CBre_Cons_02D,ln_CBre_Comp_NCS6E,ln_CBre_Comp_02D,bins=10)


if(exists("ln_CBre_NCS6C")){
  #Drop models  not used in NAICS3 comparisons
  rm(ln_CBre_NCS6C,ln_CBre_NCS6D)
  #Drop individual models that  aren't study  variables.
  rm(ln_CBre_NCS3B)
  #Drop NAICS6 models used in NAICS3 comparisons, execept original HHI
  rm(ln_CBre_NCS6B)
}

```
Adding ceiling and duration strengthens the significance of HHI6 but weakens def3_ratio in the consolidation model. Likewise def3_ratio loses significance for the competition model.

##Contract Vehicle
Our dataset includes both stand alone contract awards and task orders that are under larger indefinite delivery vehilces (IDVs). 

###Model 03A: Single-Award, Multi-Award, and Other Indefinite Delivery Vehicles
Expectations, lower ceiling breaches for IDVs in general, in particular for FSS/GWAC

```{r Model03A}
#Frequency Plot
summary_discrete_plot(def_breach,"Veh")


#Create the model
ln_CBre_03A <- glm (data=def_breach,
                 ln_CBre_Then_Year ~ Veh)
summary(ln_CBre_03A)



stargazer::stargazer(ln_CBre_03A,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_02D,
                       ln_CBre_Comp_01A,ln_CBre_Comp_02D,type="text",
                       digits=2)

#For first model in category, include only the new model(s), skip_vif=true
summary_residual_compare(ln_CBre_03A,bins=3,skip_vif = TRUE)

```

Expetation doesn't really hold, both Multiaward and BPA/BOA show higher more/larger ceiling breaches.


###Model 03B: Cumulative

```{r Model03B}
#Model
ln_CBre_Cons_03B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh)
glmer_examine(ln_CBre_Cons_03B)

ln_CBre_Comp_03B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh)
glmer_examine(ln_CBre_Comp_03B)




stargazer::stargazer(ln_CBre_03A,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_02D,ln_CBre_Cons_03B,
                       ln_CBre_Comp_01A,ln_CBre_Comp_02D,ln_CBre_Comp_03B,type="text",
                       digits=2)



#Compare to prior cumulative model(s), skip_vif =false
summary_residual_compare(ln_CBre_Cons_02D,ln_CBre_Cons_03B,ln_CBre_Comp_02D,ln_CBre_Comp_03B,bins=10,skip_vif = FALSE)
#Remove all but cumulative model
if(exists("ln_CBre_02A"))  rm(ln_CBre_02A,ln_CBre_02B,ln_CBre_02C)


```
Intriguingly,  the sign on single award IDVs flips after the introduction of the full model.

##Type of Contract

The next step adds a measure for whether the contract was cost-based or fixed-price. Prior CSIS research has found that fixed-price contracts do face a higher risk of termination across the board.

###Model 04A: Incentive Fees

Fixed-price contracts are generally thought to be at greater risk of overruns, as they are less flexible, although prior CSIS work complicates this finding.

In the performance of the defense acquisition system report, the benefits found were reduced cost overruns. That could help avoid terminations, but it's an indirect connection at best. Unfortunately, incentive fees are incredibly rare, which makes them challenging to examine directly.


```{r Model04A}

#Frequency Plot
summary_discrete_plot(def_breach,"PricingFee")




#Create the model
ln_CBre_04A <- glm (data=def_breach,
                 ln_CBre_Then_Year ~PricingFee)
summary(ln_CBre_04A)



stargazer::stargazer(ln_CBre_04A,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_03B,
                       ln_CBre_Comp_01A,ln_CBre_Comp_03B,type="text",
                       digits=2)





#For first model in category, include only the new model(s), skip_vif=true
summary_residual_compare(ln_CBre_04A,bins=2,skip_vif = TRUE)


```
Expectations are not particularly met, incentive fees have a lower coefficient than cost based, other fixed price is lowest.



###Model 04B: Undefinitized Contract Awards
Undefinitized Contract Awards allow for quick action in situations where there is not time or information to establish all of a contracts properties at the time of signing. They have been found by the GAO and the Performance of the Defense Acquisition studies to contain notable risks, primarily relating to cost overruns and thus ceiling breaches. Will these risks also carry into terminations and ceiling breaches?


```{r Model04B}

#Frequency Plot
summary_discrete_plot(def_breach,"UCA")



#Create the model
ln_CBre_04B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~ b_UCA )
summary(ln_CBre_04B)


stargazer::stargazer(ln_CBre_04A,ln_CBre_04B,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_03B,
                       ln_CBre_Comp_01A,ln_CBre_Comp_03B,type="text",
                       digits=2)


#Compare to earlier contract types
summary_residual_compare(ln_CBre_04A,ln_CBre_04B,bins=2,skip_vif = TRUE)


```
UCAs are associated with more/larger ceiling breaches ,as expected.

###Model 04C: Cumulative

```{r Model04C}
#Create the model
ln_CBre_Cons_04C <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA)
glmer_examine(ln_CBre_Cons_04C)

ln_CBre_Comp_04C <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA)
glmer_examine(ln_CBre_Comp_04C)



stargazer::stargazer(ln_CBre_04A,ln_CBre_04B,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_03B,ln_CBre_Cons_04C,
                       ln_CBre_Comp_01A,ln_CBre_Comp_03B,ln_CBre_Comp_04C,type="text",
                       digits=2)


#Compare with cumulative consolidation and competition
summary_residual_compare(ln_CBre_Cons_03B,ln_CBre_Comp_04C,ln_CBre_Comp_03B,ln_CBre_Comp_04C,bins=20,skip_vif = TRUE)
rm(ln_CBre_04A,ln_CBre_04B)

if(exists("ln_CBre_03A")) rm(ln_CBre_03A)

```

The pricing variables reduce significance for HHI and magnitude for Comp. Changes for vehicle are more sporatic.  Def3_ratio and ceiling also face decreasing/loss of significance. UCA and Combination/Fee have perhaps the largest coefficients.

##Place of Performance
###Model 05A: Any International

International contracts may often be in conflict zones and thus experience greater risk. International contracts are exepected to estimate a higher probability of ceiling breaches.
```{r Model05A_Intl}

#Frequency Plot
summary_discrete_plot(def_breach,"Intl")



#Create the model
ln_CBre_05A <- glm(data=def_breach,
  ln_CBre_Then_Year ~b_Intl
)
summary(ln_CBre_05A)



stargazer::stargazer(ln_CBre_05A,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_04C,
                       ln_CBre_Comp_01A,ln_CBre_Comp_04C,type="text",
                       digits=2)


#For first model in category, include only the new model(s), skip_vif=true
summary_residual_compare(ln_CBre_05A,bins=2,skip_vif = TRUE)

```

International performance of contract had a positive  coefficent as expected.

###Model 05B: Cumulative

```{r Model05B_Comp}

#Create the model
ln_CBre_Cons_05B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl)
glmer_examine(ln_CBre_Cons_05B)

ln_CBre_Comp_05B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl)
glmer_examine(ln_CBre_Comp_05B)




stargazer::stargazer(ln_CBre_05A,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_04C,ln_CBre_Cons_05B,
                       ln_CBre_Comp_01A,ln_CBre_Comp_04C,ln_CBre_Comp_05B,type="text",
                       digits=2)

#ompare with cumulative consolidation and competition
summary_residual_compare(ln_CBre_Cons_04C,ln_CBre_Cons_05B,ln_CBre_Comp_04C,ln_CBre_Comp_05B,bins=20,skip_vif = FALSE)

rm(ln_CBre_05A)

if(exists("ln_CBre_04A")) rm(ln_CBre_04A,ln_CBre_04B)

```
Not much in the way of big changes, though reduction in significance for ceiling for competition.


## Competition and Consolidation together
### Model 09A: Combination
```{r Model09A}


#Sumamry plot

ln_CBre_Cons_Comp_09A <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl)
glmer_examine(ln_CBre_Cons_Comp_09A)



stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Cons_05B,
                       ln_CBre_Comp_01A,ln_CBre_Comp_05B,ln_CBre_Cons_Comp_09A,type="text",
                       digits=2)

#Compare with cumulative consolidation and competition
summary_residual_compare(ln_CBre_Cons_05B,ln_CBre_Cons_Comp_09A,ln_CBre_Comp_05B,ln_CBre_Cons_Comp_09A,bins=20,skip_vif = TRUE)


if(exists("ln_CBre_05A")) rm(ln_CBre_05A)
```
There is no real hange in the study variables. Instead, those controls that were significant in only one of the two models, 
cl_Ceil_Then_Year, FSS/GWAC, and BPA/BOA lost significance. b_Intl also increased in magnitude. The patterns in the residuals show no signs of abating, suggesting that ceiling breaches may simply be too rare for this approach. 
## Interactions

### Interactions with Study Variables

#### Model 10A: Comp:UCA
Starting with Competition and UCA. It's strong in both models and thus a natural starting point.Competition is expected to mitigate the risks of UCA.
```{r Model10A}
#Sumamry plot
summary_discrete_plot(def_breach,"CompOffr","UCA")


#Create the model
ln_CBre_Comp_10A_no_interact <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+b_UCA)
glmer_examine(ln_CBre_Comp_10A)



ln_CBre_Comp_10A <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+b_UCA+
                        b_UCA:CompOffr)
glmer_examine(ln_CBre_Comp_10A)


stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_04B,
                       ln_CBre_Comp_01A,ln_CBre_Comp_10A_no_interact,ln_CBre_Comp_10A,type="text",
                       digits=2)

  

summary_residual_compare(ln_CBre_Comp_10A_no_interact,ln_CBre_Comp_10A,bins=5)


```
The results are in line with expectations and improve the VIF.


#### Model 10B: Cumulative
Starting with Competition and UCA. It's strong in both models and thus a natural starting point.
```{r Model10B}
#Sumamry plot


#Create the model
ln_CBre_Comp_10B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr)
glmer_examine(ln_CBre_Comp_10B)



ln_CBre_Cons_Comp_10B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr )
glmer_examine(ln_CBre_Cons_Comp_10B)



stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_04B,
                       ln_CBre_Comp_01A,ln_CBre_Comp_10A_no_interact,ln_CBre_Comp_10A,
                     ln_CBre_Comp_05B,ln_CBre_Comp_10B,ln_CBre_Cons_Comp_09A,ln_CBre_Cons_Comp_10B,type="text",
                       digits=2)



summary_residual_compare(ln_CBre_Comp_10A,ln_CBre_Comp_10B,bins=5)

summary_residual_compare(ln_CBre_Comp_05B,ln_CBre_Comp_10B,ln_CBre_Cons_Comp_09A,ln_CBre_Cons_Comp_10B,bins=50)


```
The interaction is significant and multi-offer competion estimates lower risks associated with UCAs.

In diagnostic terms, the residuals for ceiling breaches get a little worse, but the change is marginal and the interaction is relevant to study questions. Keeping it.

#### Model 11C: Cons:UCA
Next Consolidation and UCA. Testing at both levels. Right now 3 HHI is negative, and 6 HHI is positive, but in both case expect a less consolidated market is riskier for UCA.
```{r Model10C}
#Sumamry plot
summary_continuous_plot(def_breach,"cl_def6_HHI_lag1","UCA")



#Create the model
ln_CBre_Cons_10C_NCS6_no_interact <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+b_UCA)
glmer_examine(ln_CBre_Cons_10C_NCS6_no_interact)

ln_CBre_Cons_10C_NCS6 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+b_UCA+
                        b_UCA:cl_def6_HHI_lag1 )
glmer_examine(ln_CBre_Cons_10C_NCS6)

ln_CBre_Cons_10C_NCS3_no_interact <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+b_UCA )
glmer_examine(ln_CBre_Cons_10C_NCS3_no_interact)


ln_CBre_Cons_10C_NCS3 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+b_UCA+
                        b_UCA:cl_def3_HHI_lag1 )
glmer_examine(ln_CBre_Cons_10C_NCS3)


stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_04B,ln_CBre_Cons_10C_NCS6_no_interact,
                     ln_CBre_Cons_10C_NCS6,ln_CBre_Cons_10C_NCS3_no_interact,ln_CBre_Cons_10C_NCS3,type="text",
                       digits=2)

  

summary_residual_compare(ln_CBre_Cons_10C_NCS6_no_interact,ln_CBre_Cons_10C_NCS6,
                         ln_CBre_Cons_10C_NCS3_no_interact,ln_CBre_Cons_10C_NCS3,bins=20)


```
Expectations hold. Both improve the AIC, the jump for HHI3 is larger than for HHi6

#### Model 10D: Cumulative
```{r Model10D}
#Sumamry plot
summary_continuous_plot(def_breach,"cl_def6_HHI_lag1","UCA")
summary_discrete_plot(def_breach,"CompOffr","UCA")


#Create the model
ln_CBre_Cons_10D_NCS6 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:cl_def6_HHI_lag1 )
glmer_examine(ln_CBre_Cons_10D_NCS6)

ln_CBre_Cons_10D_NCS3 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:cl_def3_HHI_lag1 )
glmer_examine(ln_CBre_Cons_10D_NCS3)


ln_CBre_Cons_Comp_10D_NCS6 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+b_UCA:cl_def6_HHI_lag1 )
glmer_examine(ln_CBre_Cons_Comp_10D_NCS6)


ln_CBre_Cons_Comp_10D_NCS3 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+b_UCA:cl_def3_HHI_lag1 )
glmer_examine(ln_CBre_Cons_Comp_10D_NCS3)




stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_04B,ln_CBre_Cons_10C_NCS6_no_interact,
                     ln_CBre_Cons_10C_NCS6,ln_CBre_Cons_10C_NCS3_no_interact,ln_CBre_Cons_10C_NCS3,ln_CBre_Cons_05B,ln_CBre_Cons_10D_NCS6,ln_CBre_Cons_10D_NCS3,type="text",
                       digits=2)




summary_residual_compare(ln_CBre_Cons_10C_NCS3_no_interact,ln_CBre_Cons_10D_NCS3,
                         ln_CBre_Cons_10C_NCS6_no_interact,ln_CBre_Cons_10D_NCS6,bins=20)


summary_residual_compare(ln_CBre_Cons_10C_NCS3_no_interact,ln_CBre_Cons_Comp_10D_NCS3,
                         ln_CBre_Cons_10C_NCS6_no_interact,ln_CBre_Cons_Comp_10D_NCS6,bins=20)


summary_residual_compare(ln_CBre_Cons_05B,ln_CBre_Cons_10D_NCS3,
                         ln_CBre_Cons_05B,ln_CBre_Cons_10D_NCS6,bins=50)

summary_residual_compare(ln_CBre_Cons_Comp_10B,ln_CBre_Cons_Comp_10D_NCS3,
                         ln_CBre_Cons_Comp_10B,ln_CBre_Cons_Comp_10D_NCS6,bins=50)


```
Adds a bit to the model and doesn't make the residuals worse. Going with the NAICS 6 version, although NAIC6 HHI does lose signifiance, it is the stronger of the two interactions by magniutude and has the higher AIC by a fair margin.

#### Model 10E: Comp:Days
The next reintroduction is competition and days. The benefits of competition may reduce over time. We don't have firm expectations for consolidation, so leaving that out.
```{r Model10E}


#Sumamry plot
summary_continuous_plot(def_breach,"cl_Days","EffComp")



ln_CBre_Comp_10E_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year~CompOffr+ cl_Days
                      )
glmer_examine(ln_CBre_Comp_10E_no_interact)


ln_CBre_Comp_10E <- glm (data=def_breach,
                      ln_CBre_Then_Year~CompOffr+ cl_Days+
                        cl_Days:CompOffr
                      )
glmer_examine(ln_CBre_Comp_10E)


```

This combination encounters VIF problems for competition Leaving it out.

#### Model 10F: Comp:Ceiling
The next reintroduction is competition and size. Large contracts may inspire aggressive biddng, which may in turn lead to cost growth as true costs are discovered. We don't have firm expectations for consolidation, so leaving that out.
```{r Model10F}


#Sumamry plot
summary_continuous_plot(def_breach,"cl_Ceil_Then_Year","EffComp")



ln_CBre_Comp_10F_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year~CompOffr+ cl_Ceil_Then_Year
                      )
glmer_examine(ln_CBre_Comp_10F_no_interact)


ln_CBre_Comp_10F <- glm (data=def_breach,
                      ln_CBre_Then_Year~CompOffr+ cl_Ceil_Then_Year+
                        cl_Ceil_Then_Year:CompOffr
                      )
glmer_examine(ln_CBre_Comp_10F)


```
VIF challenges. Leaving out.

#### Model 10G: Comp:Veh
Competition works differently for single award vehicles, it represents  the initial competition, not the ongoing competition. As a result, single-award IDCs and BPA/BOAs are expected to be associated with more growth, than for other contracting forms where contracting occurs with every iteration.
```{r Model10G}


#Sumamry plot
summary_continuous_plot(def_breach,"cl_Ceil_Then_Year","EffComp")



ln_CBre_Comp_10G_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year~CompOffr+ Veh
                      )
glmer_examine(ln_CBre_Comp_10G_no_interact)


ln_CBre_Comp_10G <- glm (data=def_breach,
                      ln_CBre_Then_Year~CompOffr+ Veh+
                        Veh:CompOffr
                      )
glmer_examine(ln_CBre_Comp_10G)


stargazer::stargazer(ln_CBre_Comp_10G,ln_CBre_Comp_10G_no_interact,type="text",
                       digits=2)


```
There's a lot of combinations, which makes it a bit tricky to include and probably helps drive up the VIF (1.7 even w/ only two variables.


#### Model 10H: Cumulative
Starting with Competition and UCA. It's strong in both models and thus a natural starting point.
```{r Model10H}
#Sumamry plot


#Create the model
ln_CBre_Comp_10H <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+
                   CompOffr:Veh)
glmer_examine(ln_CBre_Comp_10H)

```

VIF precludes this combination.


#### Model 10K: Ratio:HHI
Because HHI in smaller sectors tends to be larger, high readings from large sectors may deserve more weight. This interaction is expected to amplify HHI magnitudes.

```{r Model10K}


#Sumamry plot
summary_continuous_plot(def_breach,"cl_def6_ratio_lag1","cl_def6_HHI_lag1")

#Create the model
ln_CBre_Cons_10K_NCS6_no_interact <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1)
glmer_examine(ln_CBre_Cons_10K_NCS6_no_interact)

ln_CBre_Cons_10K_NCS6 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                        cl_def6_ratio_lag1:cl_def6_HHI_lag1 )
glmer_examine(ln_CBre_Cons_10K_NCS6)

ln_CBre_Cons_10K_NCS3_no_interact <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1 )
glmer_examine(ln_CBre_Cons_10K_NCS3_no_interact)


ln_CBre_Cons_10K_NCS3 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                        cl_def3_ratio_lag1:cl_def3_HHI_lag1 )
glmer_examine(ln_CBre_Cons_10K_NCS3)


  stargazer::stargazer(ln_CBre_Cons_10K_NCS6_no_interact,ln_CBre_Cons_10K_NCS6,
                       ln_CBre_Cons_10K_NCS3_no_interact,ln_CBre_Cons_10K_NCS3,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_Cons_10K_NCS6_no_interact,ln_CBre_Cons_10K_NCS6,
                       ln_CBre_Cons_10K_NCS3_no_interact,ln_CBre_Cons_10K_NCS3,bins=20)



```
Significant and in line with expectations for def 6 but contract for def 3, despite a larger AIC.

#### Model 10L: Cumulative
```{r Model10L}
#Sumamry plot
summary_continuous_plot(def_breach,"cl_def6_HHI_lag1","UCA")
summary_discrete_plot(def_breach,"CompOffr","UCA")


#Create the model
ln_CBre_Cons_10L_NCS6 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:cl_def6_HHI_lag1+
                   cl_def6_ratio_lag1:cl_def6_HHI_lag1)
glmer_examine(ln_CBre_Cons_10L_NCS6)

ln_CBre_Cons_10L_NCS3 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:cl_def6_HHI_lag1 +
                   cl_def3_ratio_lag1:cl_def3_HHI_lag1 )
glmer_examine(ln_CBre_Cons_10L_NCS3)


ln_CBre_Cons_Comp_10L_NCS6 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+b_UCA:cl_def6_HHI_lag1+
                   cl_def6_ratio_lag1:cl_def6_HHI_lag1)
glmer_examine(ln_CBre_Cons_Comp_10L_NCS6)


ln_CBre_Cons_Comp_10L_NCS3 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+b_UCA:cl_def6_HHI_lag1 +
                   cl_def3_ratio_lag1:cl_def3_HHI_lag1 )
glmer_examine(ln_CBre_Cons_Comp_10L_NCS3)




stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_NCS3B,ln_CBre_NCS6B,ln_CBre_Cons_10K_NCS6_no_interact,
                     ln_CBre_Cons_10K_NCS6,ln_CBre_Cons_10K_NCS3_no_interact,ln_CBre_Cons_10K_NCS3,ln_CBre_Cons_10D_NCS6,
                     ln_CBre_Cons_10L_NCS6,ln_CBre_Cons_10L_NCS3,type="text",
                       digits=2)


stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_Comp_01A,
                     ln_CBre_Cons_Comp_10D_NCS6,ln_CBre_Cons_Comp_10L_NCS6,ln_CBre_Cons_Comp_10L_NCS3,type="text",
                       digits=2)




summary_residual_compare(ln_CBre_Cons_10K_NCS3,ln_CBre_Cons_10L_NCS3,
                         ln_CBre_Cons_10K_NCS6,ln_CBre_Cons_10L_NCS6,bins=20)


summary_residual_compare(ln_CBre_Cons_10K_NCS3,ln_CBre_Cons_Comp_10L_NCS3,
                         ln_CBre_Cons_10K_NCS6,ln_CBre_Cons_Comp_10L_NCS6,bins=20)


summary_residual_compare(ln_CBre_Cons_10D_NCS6,ln_CBre_Cons_10L_NCS3,
                         ln_CBre_Cons_10D_NCS6,ln_CBre_Cons_10L_NCS6,bins=50)

summary_residual_compare(ln_CBre_Cons_Comp_10D_NCS6,ln_CBre_Cons_Comp_10L_NCS3,
                         ln_CBre_Cons_Comp_10D_NCS6,ln_CBre_Cons_Comp_10L_NCS6,bins=50)


```
NAICS6 has the  better AIC, restores significance to HHI6 and goes in the expected direction. Ther residuals get a bit more extreme but less patterned. The 6 version of the ratio seems worth adding
#### Model 10M: Ratio:Comp
Likewise, competition may be more effective in more commercial sectors where monosopy is not a problem.
```{r Model10M}
summary_continuous_plot(def_breach,"cl_def6_ratio_lag1","EffComp")
summary_continuous_plot(def_breach,"cl_def3_ratio_lag1","EffComp")

ln_CBre_Comp_10M_NCS3_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year ~
                        cl_def3_ratio_lag1+
                        CompOffr
                      )
glmer_examine(ln_CBre_Comp_10M_NCS3_no_interact)



ln_CBre_Comp_10M_NCS3 <- glm (data=def_breach,
                      ln_CBre_Then_Year ~
                        cl_def3_ratio_lag1+
                        CompOffr+
                        cl_def3_ratio_lag1:CompOffr
                      )
glmer_examine(ln_CBre_Comp_10M_NCS3)



ln_CBre_Comp_10M_NCS6_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year ~
                        cl_def6_ratio_lag1+
                        CompOffr
                      )
glmer_examine(ln_CBre_Comp_10M_NCS6_no_interact)



ln_CBre_Comp_10M_NCS6 <- glm (data=def_breach,
                      ln_CBre_Then_Year ~
                        cl_def6_ratio_lag1+
                        CompOffr+
                        cl_def6_ratio_lag1:CompOffr
                      )
glmer_examine(ln_CBre_Comp_10M_NCS6)




  stargazer::stargazer(ln_CBre_Comp_10M_NCS3_no_interact,ln_CBre_Comp_10M_NCS3,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_Comp_10M_NCS3_no_interact,ln_CBre_Comp_10M_NCS3,bins=10)

```
In line with expectation and significant for def3, but doesn't change the AIC much and the residuals get worse. VIF is exceed for Def6 and close for Def3. Leaving out.

#### Model 10O: HHI6 and competition
If competition is an instrument for consolidation, than it should be most effective when consolidation is lower.
```{r Model10O}


#Create the model
ln_CBre_Cons_Comp_10O_NCS6_no_interact <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+CompOffr)
glmer_examine(ln_CBre_Cons_Comp_10O_NCS6_no_interact)

ln_CBre_Cons_Comp_10O_NCS6 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+CompOffr+
                        CompOffr:cl_def6_HHI_lag1 )
glmer_examine(ln_CBre_Cons_Comp_10O_NCS6)

ln_CBre_Cons_Comp_10O_NCS3_no_interact <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+CompOffr )
glmer_examine(ln_CBre_Cons_Comp_10O_NCS3_no_interact)


ln_CBre_Cons_Comp_10O_NCS3 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+CompOffr+
                        CompOffr:cl_def3_HHI_lag1 )
glmer_examine(ln_CBre_Cons_Comp_10O_NCS3)




```
The interaction ran into VIF challenges. Leaving it out.


### Other Interactions

#### Model 11A: UCA and Ceiling
Larger ceiling UCAs may run into bigger problems. The interaction of UCA and ceiling estimates a higher risk of breaches. 

```{r Model11A}


#Sumamry plot
summary_continuous_plot(def_breach,"cl_Ceil_Then_Year","UCA")

#Create the model


ln_CBre_11A_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year ~cl_Ceil_Then_Year + b_UCA
                      )
glmer_examine(ln_CBre_11A_no_interact)


ln_CBre_11A <- glm (data=def_breach,
                      ln_CBre_Then_Year ~cl_Ceil_Then_Year + b_UCA+
                        b_UCA:cl_Ceil_Then_Year
                      )
glmer_examine(ln_CBre_11A)



  stargazer::stargazer(ln_CBre_02A,ln_CBre_04B,ln_CBre_11A_no_interact,ln_CBre_11A,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_11A_no_interact,ln_CBre_11A,bins=5)


```
The result runs contrary to expectation and only slightly reduces AIC and is largely a wash when it comes to residuals. One possible rationale is that small UCAs may raise risks because they are under less scrutiny.

#### Model 11B: Cumulative
```{r Model11B}

#Create the model
ln_CBre_Cons_11B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:cl_def6_HHI_lag1+
                   cl_def6_ratio_lag1:cl_def6_HHI_lag1+
                        b_UCA:cl_Ceil_Then_Year)
glmer_examine(ln_CBre_Cons_11B)


ln_CBre_Comp_11B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+
                        b_UCA:cl_Ceil_Then_Year)
glmer_examine(ln_CBre_Comp_10B)



ln_CBre_Cons_Comp_11B <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+b_UCA:cl_def6_HHI_lag1+
                   cl_def6_ratio_lag1:cl_def6_HHI_lag1+
                        b_UCA:cl_Ceil_Then_Year)
glmer_examine(ln_CBre_Cons_Comp_11B)





  
  
  stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_02A,ln_CBre_04B,ln_CBre_11A_no_interact,ln_CBre_11A,
                       ln_CBre_Cons_10L_NCS6,ln_CBre_Cons_11B,ln_CBre_Comp_10B,ln_CBre_Comp_11B,ln_CBre_Cons_Comp_10L_NCS6,ln_CBre_Cons_Comp_11B,type="text",
                         digits=2)


summary_residual_compare(ln_CBre_11A,ln_CBre_Cons_11B,
                         ln_CBre_11A,ln_CBre_Comp_11B,bins=20)
summary_residual_compare(ln_CBre_11A,ln_CBre_Cons_Comp_11B,bins=20)

summary_residual_compare(ln_CBre_Cons_10L_NCS6,ln_CBre_Cons_11B,
                         ln_CBre_Comp_10B,ln_CBre_Comp_11B,bins=20)


summary_residual_compare(ln_CBre_Cons_Comp_10L_NCS6,ln_CBre_Cons_Comp_11B,bins=50)


```


#### Model 11C: UCA and Duration
UCA is sometimes used for contracts that need to be executed fast and may be short. Definitizing a  contract isa form of change order, though not one that  necessarily leads to a ceiling breach. Thus the slope for UCAs across duration may be  gentler than it is for non-UCA contracts.

```{r Model11C}


#Sumamry plot
summary_continuous_plot(def_breach,"cl_Days","UCA")

#Create the model
ln_CBre_11C_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year ~cl_Days + b_UCA
                      )
glmer_examine(ln_CBre_11C_no_interact)


ln_CBre_11C <- glm (data=def_breach,
                      ln_CBre_Then_Year ~cl_Days + b_UCA+
                        b_UCA:cl_Days
                      )
glmer_examine(ln_CBre_11C)



  stargazer::stargazer(ln_CBre_02B,ln_CBre_04B,ln_CBre_11C_no_interact,ln_CBre_11C,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_11C_no_interact,ln_CBre_11C,bins=5)


```
The direction is as expected and highmagnitude, though adds little to the AIC.

#### Model 11D: Cumulative
```{r Model11D}
#Create the model
ln_CBre_NCS6D_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year ~cl_Days + b_UCA
                      )
glmer_examine(ln_CBre_NCS6D_no_interact)


ln_CBre_NCS6D <- glm (data=def_breach,
                      ln_CBre_Then_Year ~cl_Days + b_UCA+
                        b_UCA:cl_Days
                      )
glmer_examine(ln_CBre_NCS6D)

ln_CBre_Comp_11D2 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+
                   cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        # b_UCA:CompOffr+
                        b_UCA:cl_Days)
glmer_examine(ln_CBre_Comp_11D2)



ln_CBre_Cons_Comp_11D <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+b_UCA:cl_def6_HHI_lag1+
                   cl_def6_ratio_lag1:cl_def6_HHI_lag1+
                        b_UCA:cl_Days)
glmer_examine(ln_CBre_Cons_Comp_11D)


ln_CBre_Cons_Comp_11D2 <- glm (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        # b_UCA:CompOffr+
                   b_UCA:cl_def6_HHI_lag1+
                   cl_def6_ratio_lag1:cl_def6_HHI_lag1+
                        b_UCA:cl_Days)
glmer_examine(ln_CBre_Cons_Comp_11D2)

  stargazer::stargazer(ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,ln_CBre_02A,ln_CBre_04B,ln_CBre_11C_no_interact,ln_CBre_11C,
                       ln_CBre_Cons_10L_NCS6,ln_CBre_Cons_11D,ln_CBre_Comp_10B,ln_CBre_Comp_11D2,ln_CBre_Cons_Comp_10L_NCS6,ln_CBre_Cons_Comp_11D2,type="text",
                         digits=2)

```

Adding days require removing UCA:Comp and substantially reduces AIC as a result.

#### Model 11E: Pricing and Average Wage

Average wage is a proxy for unobserved skill requirements, which in turn is a proxy for complexity. Fixed price contracting may run afoul of in these sectors, due to the greater difficulties of prediction. Labor hours/t&M, will likely are expected to estimate lower risk of problems, but not as low as cost-based. Incentive fee and cost-based are both expected to lower the estimated risk fo breaches.

```{r Model11E}


#Sumamry plot
summary_continuous_plot(def_breach,"cl_US6_avg_sal_lag1","PricingFee",log=TRUE)


#Create the model
ln_CBre_NCS6D_no_interact <- glm (data=def_breach,
                      ln_CBre_Then_Year ~cl_US6_avg_sal_lag1 + PricingFee
                      )
glmer_examine(ln_CBre_NCS6D_no_interact)

ln_CBre_NCS6D <- glm (data=def_breach,
                      ln_CBre_Then_Year ~cl_US6_avg_sal_lag1 + PricingFee+
                        cl_US6_avg_sal_lag1:PricingFee
                      )
glmer_examine(ln_CBre_NCS6D)


  stargazer::stargazer(ln_CBre_NCS6D,ln_CBre_04A,ln_CBre_NCS6D_no_interact,ln_CBre_NCS6D,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_Cons_10D,ln_CBre_Cons_11E,ln_CBre_Comp_10H,ln_CBre_Comp_11E,bins=20)


```
The results run contrary to for incentive, with expectaion for cost based, only minor influence on AIC. Leaving this out.


## Agency/Office & NAICS6
###Model 12A: 2019-06-08 1st ln_CBre_Then_Year multilevel 
This initial run proved a bit premature, as incorporation of Agency as a dummy variable showed that many of the interactions included.
```{r Model12A}
if(file.exists("..//Output//ln_CBre_Cons_12A.rdata")) load(file="..//Output//ln_CBre_Cons_12A.rdata")

if(!exists("ln_CBre_Cons_12A_1m"))
ln_CBre_Cons_12A_1m <- lmer (data=def_breach,
                 ln_CBre_Then_Year ~cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:cl_def6_HHI_lag1+
                   cl_def6_ratio_lag1:cl_def6_HHI_lag1+
                          
                          (1 | NAICS3/NAICS) + 
                          (1 | Agency/Office)
                        ,
                        verbose=1,
verbose=TRUE)
glmer_examine(ln_CBre_Cons_12A_1m)


if(!exists("ln_CBre_Comp_12A_1m"))
ln_CBre_Comp_12A_1m <- lmer (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+
                          
                          (1 | NAICS3/NAICS) + 
                          (1 | Agency/Office))
glmer_examine(ln_CBre_Comp_12A_1m)

if(!exists("ln_CBre_Cons_Comp_12A_1m"))
ln_CBre_Cons_Comp_12A_1m <- lmer (data=def_breach,
                 ln_CBre_Then_Year ~CompOffr+cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   cl_Ceil_Then_Year+ cl_Days+
                   Veh+
                   PricingFee+b_UCA+
                   b_Intl +
                        b_UCA:CompOffr+b_UCA:cl_def6_HHI_lag1+
                   cl_def6_ratio_lag1:cl_def6_HHI_lag1+
                          
                          (1 | NAICS3/NAICS) + 
                          (1 | Agency/Office))
glmer_examine(ln_CBre_Cons_Comp_12A_1m)

summary(def_breach$n_CBre)

stargazer::stargazer(ln_CBre_Comp_01A,ln_CBre_Cons_NCS6A,ln_CBre_Cons_NCS3A,
                     ln_CBre_Cons_10L_NCS6,ln_CBre_Cons_12A_1m,
                     ln_CBre_Comp_10B,ln_CBre_Comp_12A_1m,
                     ln_CBre_Cons_Comp_10L_NCS6,ln_CBre_Cons_Comp_12A_1m,type="text",
                       digits=2)


debug(binned_fitted_versus_residuals)
summary_residual_compare(ln_CBre_Cons_10L_NCS6,ln_CBre_Cons_12A_1m,
                         ln_CBre_Comp_10B,ln_CBre_Comp_12A_1m,bins=50)

summary_residual_compare(ln_CBre_Cons_Comp_10L_NCS6,ln_CBre_Cons_Comp_12A_1m,bins=50)



summary_residual_compare(ln_CBre_Cons_07B2,ln_CBre_Cons_12A,ln_CBre_Comp_07B2,ln_CBre_Comp_06A3,bins=20)
save(ln_CBre_Cons_12A_1m,ln_CBre_Comp_12A_1m,ln_CBre_Cons_Comp_12A_1m,file="..//Output//ln_CBre_12A.rdata")
```

The initial attempt to include the pre-existing intercepts and all inputs resulted in a model that initially failed to converge. Conservatively the intercepts have been temporarily removed to be added back in a subsequent step.

### Model 12B: Trimmed 
```{r Model12B}
#Frequency Plot
summary_discrete_plot(def_breach,"NAICS")

#This is currently running at home

ln_CBre_Cons_12B <- glmer (data=def_breach,
                        ln_CBre_Then_Year ~cl_def6_HHI_lag1 +cl_def6_ratio_lag1+cl_def6_obl_lag1+
                          cl_US6_avg_sal_lag1+
                          cl_Ceil_Then_Year + cl_Days+ 
                          Veh +
                          PricingFee + b_UCA +
                          b_Intl+
                          
                         
                          
                          cl_def6_HHI_lag1:cl_def6_obl_lag1+ 
                          b_UCA:cl_def6_HHI_lag1 + 
                          b_UCA:cl_Ceil_Then_Year+

                          (1 | NAICS) + (1 | Agency/Office)
                        
                        ,
                        verbose=1)

glmer_examine(ln_CBre_Cons_12B)

ln_CBre_Comp_12B <-  glmer (data=def_breach,
                      ln_CBre_Then_Year ~CompOffr +
                        cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                        cl_Ceil_Then_Year + cl_Days+
                        Veh  +
                        PricingFee+ b_UCA +
                        b_Intl+
                    
                        b_UCA:CompOffr +
                        b_UCA:cl_Ceil_Then_Year+

                   (1 | NAICS) + (1 | Agency/Office)

                   ,
                  verbose=1)

glmer_examine(ln_CBre_Comp_12B)
save(ln_CBre_Comp_12B,file="ln_CBre_Comp_12B.rdata")
summary_residual_compare(ln_CBre_Cons_07B2,ln_CBre_Cons_12B,ln_CBre_Comp_07B2,ln_CBre_Comp_06A3,bins=20)
```

## Agency/Office & NAICS3/6
###Model 13A: Agency/Office+NAICS6/NAICS3
The North American Industrial Classification system captures the sector of each contract, which are each given a seperate intercept in the model.
```{r Model13A}
load(file="Output//ln_CBre_Cons_13A.rdata")

if(!exists("ln_CBre_Cons_13A"))
  ln_CBre_Cons_13A <- glmer (data=def_breach,
                          ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                            #cl_US3_avg_sal_lag1+
                            cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                            cl_US6_avg_sal_lag1+
                            cl_Ceil_Then_Year + cl_Days+ 
                            Veh +
                            PricingFee + b_UCA +
                            b_Intl+
                            # Who+
                           
                            Veh:cl_Days+
                            
                            Veh:cl_Ceil_Then_Year+
                            cl_Ceil_Then_Year:PricingFee+
                            cl_def6_HHI_lag1:cl_def6_obl_lag1+
                            b_UCA:cl_def6_HHI_lag1 + 
                            b_UCA:cl_Ceil_Then_Year+
                            # 6
                            b_Intl:Veh+ 
                            (1 | NAICS3/NAICS) + 
                            (1 | Agency/Office) 
                          # Who:b_Intl+
                          # NAICS2
                          ,
                          verbose=1)


glmer_examine(ln_CBre_Cons_13A,display=TRUE)

save(ln_CBre_Cons_13A,file="Output//ln_CBre_Cons_13A.rdata")
```

###Model 13B: Agency/Office+NAICS6/NAICS3 trimmed
```{r Model13B}
load("Output//ln_CBre_Cons_13B.rdata")

ln_CBre_Cons_13B <- glmer (data=def_breach,
                        ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                          #cl_US3_avg_sal_lag1+
                          cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                          cl_US6_avg_sal_lag1+
                          cl_Ceil_Then_Year + cl_Days+ 
                          Veh +
                          PricingFee + b_UCA +
                          b_Intl+
                          
                          
                          
                          
                          b_UCA:cl_def6_HHI_lag1 + 
                          b_UCA:cl_Ceil_Then_Year+
                          cl_def6_HHI_lag1:cl_def6_obl_lag1+
                          
                          (1 | NAICS3/NAICS) + 
                          (1 | Agency/Office) 
                        
                        ,
                        verbose=1)

glmer_examine(ln_CBre_Cons_13B,display=TRUE)


  ln_CBre_Cons_13B_1m <- glmer (data=def_breach,
                          ln_CBre_Then_Year ~cl_def3_HHI_lag1+
                            cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                            #cl_US3_avg_sal_lag1+
                            cl_def6_HHI_lag1+
                            cl_def6_ratio_lag1+
                            cl_US6_avg_sal_lag1+
                            cl_Ceil_Then_Year + cl_Days+ 
                            Veh +
                            PricingFee + b_UCA +
                            b_Intl+
                            
                            b_UCA:cl_def6_HHI_lag1 + 
                            b_UCA:cl_Ceil_Then_Year+
                            cl_def6_HHI_lag1:cl_def6_obl_lag1+
                            
                            (1 | NAICS3/NAICS) + 
                            (1 | Agency/Office), 
                          
                          family=binomial(link="logit"),
                          verbose=1)
glmer_examine(ln_CBre_Cons_13B_1m,display=TRUE)

save(ln_CBre_Cons_13B,file="Output//ln_CBre_Cons_13B.rdata")
ln_CBre_Comp_13B <- glmer (data=def_breach,
                        ln_CBre_Then_Year~CompOffr+
                          cl_def3_ratio_lag1+
                          #cl_US3_avg_sal_lag1+#cl_def3_obl_lag1+
                          CompOffr+
                          cl_def6_ratio_lag1+
                          cl_US6_avg_sal_lag1+
                          cl_Ceil_Then_Year + cl_Days+
                          Veh  +
                          PricingFee+
                          b_UCA +
                          b_Intl+
                          
                          b_UCA:CompOffr +
                          b_UCA:cl_Ceil_Then_Year+
                          
                          (1 | NAICS3/NAICS) + (1 | Agency/Office)
                        ,
                        verbose=1)
glmer_examine(ln_CBre_Comp_13B)

stargazer::stargazer(ln_CBre_Cons_14A,ln_CBre_Cons_13B,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13B,type="text",
                     digits=2)



summary_residual_compare(ln_CBre_Cons_14A,ln_CBre_Cons_13B,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13B,bins=20)



any(diag.vals<1e-6)

if(!exists("ln_CBre_Cons_13B.devfun"))
  ln_CBre_Cons_13B.devfun <- update(ln_CBre_Cons_13B, devFunOnly=TRUE)


pars<-get_pars(ln_CBre_Cons_13B)


if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Cons_13B.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Cons_13B.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(ln_CBre_Cons_13_scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Cons_13B@optinfo$derivs

if(!exists("ln_CBre_Cons_13B.restart"))
  ln_CBre_Cons_13B.restart <- update(ln_CBre_Cons_13B, start=pars)
glmer_examine(ln_CBre_Cons_13B.restart)

save(ln_CBre_Cons_13B,
     ln_CBre_Cons_13B.devfun,
     ln_CBre_Cons_13_scgrad,
     ln_CBre_Cons_13B.restart,
     ln_CBre_Comp_13B,
     ln_CBre_Comp_13B.devfun,
     ln_CBre_Comp_13B.restart,
     file="Output//ln_CBre_Cons_13B.rdata")

source(system.file("utils", "allFit.R", package="lme4"))
ln_CBre_Cons_13B.all <- allFit(ln_CBre_Cons_13B)
ln_CBre_Cons_13B_ss_cons <- summary(ln_CBre_Cons_13B.all)

ln_CBre_Comp_13C.all <- allFit(ln_CBre_Comp_13C)
ln_CBre_Comp_13C_ss_cons <- summary(ln_CBre_Cons_13C.all)


#CBre Comp
if(!exists("ln_CBre_Comp_13B.devfun"))
  ln_CBre_Comp_13B.devfun <- update(ln_CBre_Comp_13B, devFunOnly=TRUE)

pars<-get_pars(ln_CBre_Comp_13B)

if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Comp_13B.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Comp_13B.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Comp_13B@optinfo$derivs

if(!exists("ln_CBre_Comp_13B.restart"))
  ln_CBre_Comp_13B.restart <- update(ln_CBre_Comp_13B, start=pars)
glmer_examine(ln_CBre_Comp_13B.restart)


save(ln_CBre_Cons_13B,ln_CBre_Comp_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_13B.restart,
     file="Output//ln_CBre_Cons_13B.rdata")

stargazer::stargazer(ln_CBre_Cons_14A,ln_CBre_Cons_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13B,type="text",
                     digits=2)



if(!exists("ln_CBre_Cons_13B_1m_restart")){
   pars<-get_pars(ln_CBre_Cons_13B_1m)
   ln_CBre_Cons_13B_1m_restart <- update(ln_CBre_Cons_13B_1m, 
                                      start=pars,
                                      verbose=1)
   save(ln_CBre_Cons_13B,
        ln_CBre_Cons_13B.restart,
        ln_CBre_Cons_13B_1m,
        ln_CBre_Cons_13B_1m_restart,
        file="Output//ln_CBre_Cons_13B.rdata")
 }
stargazer::stargazer(ln_CBre_Cons_13B,ln_CBre_Cons_13B.restart,
                     ln_CBre_Cons_13B_1m_restart,
                     ln_CBre_Cons_13B_1m,type="text",
                     digits=2)
summary_residual_compare(ln_CBre_Cons_13B,ln_CBre_Cons_13B.restart,ln_CBre_Cons_13B_1m,ln_CBre_Cons_13B_1m_restart,bins=50)
glmer_examine(ln_CBre_Cons_13B_1m)
glmer_examine(ln_CBre_Cons_13B_1m_restart)
load("Output//ln_CBre_Comp_13B.rdata")

summary(ln_CBre_Cons_13B_1m_restart)
source(system.file("utils", "allFit.R", package="lme4"))
ln_CBre_Cons_13B_1m_all <- allFit(ln_CBre_Cons_13B_1m_restart)
ss_cons <- summary(ln_CBre_Cons_13B_1m_all)
   save(ln_CBre_Cons_13B,
        ln_CBre_Cons_13B.restart,
        ln_CBre_Cons_13B_1m,
        ln_CBre_Cons_13B_1m_restart,
        ln_CBre_Cons_13B_1m_all,
        file="Output//ln_CBre_Cons_13B.rdata")

summary_residual_compare(ln_CBre_Cons_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13B,bins=20)

summary(ln_CBre_Cons_13B.restart)
source(system.file("utils", "allFit.R", package="lme4"))
ln_CBre_Cons_13C.all <- allFit(ln_CBre_Cons_13B.restart)
ss_cons <- summary(ln_CBre_Cons_13C.all)

# str(ln_CBre_Cons_13C.all[[1]])
# stargazer::stargazer(ln_CBre_Cons_13C.all[[1]],
#                 ln_CBre_Cons_13C.all[[2]],
#                 ln_CBre_Cons_13C.all[[3]],
#                 ln_CBre_Cons_13C.all[[4]],
#                 ln_CBre_Cons_13C.all[[5]],
#                 ln_CBre_Cons_13C.all[[6]],
#                 ln_CBre_Cons_13C.all[[7]],type="text",
#                        digits=2)
# 
#               

save(ln_CBre_Cons_13B,ln_CBre_Comp_13B,ln_CBre_Cons_13B.restart,ln_CBre_Cons_13C.all,
     ln_CBre_Comp_13B.restart,
     file="Output//ln_CBre_Cons_13B.rdata")

# fm1.all <- allFit(ln_CBre_Comp_13C)
# ss_comp <- summary(ln_CBre_Comp_13C.all)
```


###Model 13C: Agency/Office+NAICS6/NAICS3 Binned Comp Offers
```{r Model13C}

ln_CBre_Comp_13C <- glmer (data=def_breach,
                        ln_CBre_Then_Year ~CompOffr+cl_def3_ratio_lag1+
                          #cl_US3_avg_sal_lag1+#cl_def3_obl_lag1+
                          cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                          cl_Ceil_Then_Year + cl_Days+
                          Veh  +
                          PricingFee+
                          b_UCA +
                          b_Intl+
                          
                          b_UCA:CompOffr +
                          b_UCA:cl_Ceil_Then_Year+
                          
                          (1 | NAICS3/NAICS) + (1 | Agency/Office)
                        ,
                        verbose=1)
glmer_examine(ln_CBre_Comp_13C)

ln_CBre_Comp_13C_1m <- glmer (data=def_breach,
                        ln_CBre_Then_Year ~CompOffr+cl_def3_ratio_lag1+
                          #cl_US3_avg_sal_lag1+#cl_def3_obl_lag1+
                          cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                          cl_Ceil_Then_Year + cl_Days+
                          Veh  +
                          PricingFee+
                          b_UCA +
                          b_Intl+
                          
                          b_UCA:CompOffr +
                          b_UCA:cl_Ceil_Then_Year+
                          
                          (1 | NAICS3/NAICS) + (1 | Agency/Office)
                        ,
                        verbose=1)
glmer_examine(ln_CBre_Comp_13C_1m)

save(ln_CBre_Comp_13C,file="Output//ln_CBre_Comp_13C.rdata")

  stargazer::stargazer(ln_CBre_Comp_13B,ln_CBre_Comp_13C,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_Cons_14A,ln_CBre_Cons_13C,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13C,bins=20)



any(diag.vals<1e-6)

if(!exists("ln_CBre_Cons_13C.devfun"))
  ln_CBre_Cons_13C.devfun <- update(ln_CBre_Cons_13C, devFunOnly=TRUE)


pars<-get_pars(ln_CBre_Cons_13C)
if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Cons_13C.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Cons_13C.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Cons_13C@optinfo$derivs

if(!exists("ln_CBre_Cons_13C.restart"))
  ln_CBre_Cons_13C.restart <- update(ln_CBre_Cons_13C, start=pars)
glmer_examine(ln_CBre_Cons_13C.restart)




#CBre Comp
if(!exists("ln_CBre_Comp_13C.devfun"))
  ln_CBre_Comp_13C.devfun <- update(ln_CBre_Comp_13C, devFunOnly=TRUE)

pars<-get_pars(ln_CBre_Comp_13C)
if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Comp_13C.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Comp_13C.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Comp_13C@optinfo$derivs

if(!exists("ln_CBre_Comp_13C.restart"))
  ln_CBre_Comp_13C.restart <- update(ln_CBre_Comp_13C, start=pars)
glmer_examine(ln_CBre_Comp_13C.restart)


  save(ln_CBre_Cons_13C,ln_CBre_Comp_13C,ln_CBre_Cons_13C.restart,ln_CBre_Comp_13C.restart,
       file="Output//ln_CBre_Cons_13C.rdata")
  
stargazer::stargazer(ln_CBre_Cons_14A,ln_CBre_Cons_13C,ln_CBre_Cons_13C.restart,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13C,type="text",
                       digits=2)





  
load("Output//ln_CBre_Comp_13C.rdata")

  summary_residual_compare(ln_CBre_Cons_13C,ln_CBre_Cons_13C.restart,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13C,bins=20)


  source(system.file("utils", "allFit.R", package="lme4"))
  ln_CBre_Cons_13C.all <- allFit(ln_CBre_Cons_13C.restart)
  ss_cons <- summary(ln_CBre_Cons_13C.all)
  save(ln_CBre_Cons_13C,ln_CBre_Comp_13C,ln_CBre_Cons_13C.restart,ln_CBre_Cons_13C.all,
       ln_CBre_Comp_13C.restart,
       file="Output//ln_CBre_Cons_13C.rdata")
  
  # fm1.all <- allFit(ln_CBre_Comp_13C)
  # ss_comp <- summary(ln_CBre_Comp_13C.all)
```

###Model 13D: Cluster Means
```{r Model13D}

load("Output//ln_CBre_Cons_13D.rdata")

ln_CBre_Cons_13D <- glmer (data=def_breach,
                        ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                          #cl_US3_avg_sal_lag1+
                          cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                          cl_US6_avg_sal_lag1+
                          c_office_l_Ceil + c_office_l_Days+ 
                          Veh +
                          PricingFee + b_UCA +
                          b_Intl+
                          
                          b_UCA:cl_def6_HHI_lag1 + 
                          b_UCA:c_office_l_Ceil+
                          cl_def6_HHI_lag1:cl_def6_obl_lag1+
                          
                          (1 | NAICS3/NAICS) + 
                          (1 | Agency/Office) 
                        
                        ,
                        verbose=1)



glmer_examine(ln_CBre_Cons_13D,display=TRUE)


ln_CBre_Comp_13D <- glmer (data=def_breach,
                        ln_CBre_Then_Year ~CompOffr+cl_def3_ratio_lag1+#cl_US3_avg_sal_lag1+#cl_def3_obl_lag1+
                   CompOffr+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                        c_office_l_Ceil + c_office_l_Days+
                        Veh  +
                        PricingFee+
                        b_UCA +
                        b_Intl+
                        
                        
                        
                        b_UCA:CompOffr +
                        b_UCA:c_office_l_Ceil+
                        
                        (1 | NAICS3/NAICS) + (1 | Agency/Office)
                      ,
                        verbose=1)
glmer_examine(ln_CBre_Comp_13D)


  stargazer::stargazer(ln_CBre_Cons_13C, ln_CBre_Cons_13D,ln_CBre_Comp_13C,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_Cons_13C,ln_CBre_Cons_13D,#ln_CBre_Comp_14A.restart,ln_CBre_Comp_13D,
                         bins=20)

ln_CBre_Cons_13C@devcomp$cmp[[8]]
ln_CBre_Cons_13C@devcomp$cmp

any(diag.vals<1e-6)

if(!exists("ln_CBre_Cons_13D.devfun"))
  ln_CBre_Cons_13D.devfun <- update(ln_CBre_Cons_13D, devFunOnly=TRUE)


pars<-get_pars(ln_CBre_Cons_13D)


if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Cons_13D.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Cons_13D.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Cons_13D@optinfo$derivs

if(!exists("ln_CBre_Cons_13D.restart"))
  ln_CBre_Cons_13D.restart <- update(ln_CBre_Cons_13D, start=pars)
glmer_examine(ln_CBre_Cons_13D.restart)




#CBre Comp
if(!exists("ln_CBre_Comp_13D.devfun"))
  ln_CBre_Comp_13D.devfun <- update(ln_CBre_Comp_13D, devFunOnly=TRUE)


pars<-get_pars(ln_CBre_Comp_13D)



if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Comp_13D.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Comp_13D.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Comp_13D@optinfo$derivs

if(!exists("ln_CBre_Comp_13D.restart"))
  ln_CBre_Comp_13D.restart <- update(ln_CBre_Comp_13D, start=pars)
glmer_examine(ln_CBre_Comp_13D.restart)


  save(ln_CBre_Cons_13D,ln_CBre_Comp_13D,ln_CBre_Cons_13D.restart,ln_CBre_Comp_13D.restart,
       file="Output//ln_CBre_Cons_13D.rdata")
  
stargazer::stargazer(ln_CBre_Cons_13C,ln_CBre_Cons_13D,ln_CBre_Cons_13D.restart,
                    ln_CBre_Comp_13C,ln_CBre_Comp_13D,ln_CBre_Comp_13D.restart,
                    type="text",
                       digits=2)





  save(ln_CBre_Cons_13D,ln_CBre_Comp_13D.devfun,ln_CBre_Cons_13D.restart,
       ln_CBre_Comp_13D,ln_CBre_Comp_13D.devfun,ln_CBre_Comp_13D.restart,
       file="Output//ln_CBre_Cons_13D.rdata")
load("Output//ln_CBre_Comp_13D.rdata")

  summary_residual_compare(ln_CBre_Cons_13D,ln_CBre_Cons_13D.restart,ln_CBre_Comp_13D,ln_CBre_Comp_13D.restart,bins=20)
  summary_residual_compare(ln_CBre_Cons_13C,ln_CBre_Cons_13D.restart,ln_CBre_Comp_13C,ln_CBre_Comp_13D.restart,bins=20)


```
###Model 13E: Interlevel Ceiling Slope
```{r Model13E}

load(file="Output//ln_CBre_Cons_13E.rdata")
ln_CBre_Cons_13E <- glmer (data=def_breach,
                        ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                          #cl_US3_avg_sal_lag1+
                          cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                          cl_US6_avg_sal_lag1+
                          c_office_l_Ceil + c_office_l_Days+ 
                          Veh +
                          PricingFee + b_UCA +
                          b_Intl+
                          
                          b_UCA:cl_def6_HHI_lag1 + 
                          b_UCA:c_office_l_Ceil+
                          cl_def6_HHI_lag1:cl_def6_obl_lag1+
                          
                          (1 | NAICS3/NAICS) + 
                          (1 | Agency) +
                          (1 + c_office_l_Ceil | Agency:Office) 
                        
                        ,
                        verbose=1)


glmer_examine(ln_CBre_Cons_13E,display=TRUE)
save(ln_CBre_Cons_13E,file="Output//ln_CBre_Cons_13E.rdata")

ln_CBre_Comp_13E <- glmer (data=def_breach,
                        ln_CBre_Then_Year ~CompOffr+cl_def3_ratio_lag1+#cl_US3_avg_sal_lag1+#cl_def3_obl_lag1+
                   CompOffr+cl_def6_ratio_lag1+cl_US6_avg_sal_lag1+
                        c_office_l_Ceil + c_office_l_Days+
                        Veh  +
                        PricingFee+
                        b_UCA +
                        b_Intl+
                        
                        
                        
                        b_UCA:CompOffr +
                        b_UCA:c_office_l_Ceil+
                        
                        (1 | NAICS3/NAICS) +
                                               (1 | Agency) +
                          (1 + c_office_l_Ceil | Agency:Office) 
                      ,
                        verbose=1)
glmer_examine(ln_CBre_Comp_13E,display=TRUE)

save(ln_CBre_Cons_13E,ln_CBre_Comp_13E,file="Output//ln_CBre_13E.rdata")
  stargazer::stargazer(ln_CBre_Cons_13B, ln_CBre_Cons_13D,ln_CBre_Cons_13E,ln_CBre_Comp_13B,type="text",
                       digits=2)
  
  
summary_residual_compare(ln_CBre_Cons_13D,ln_CBre_Cons_13E,#ln_CBre_Comp_14A.restart,ln_CBre_Comp_13E,
                         bins=100)
summary_residual_compare(ln_CBre_Cons_13B,ln_CBre_Cons_13E,#ln_CBre_Comp_14A.restart,ln_CBre_Comp_13E,
                         bins=100)



any(diag.vals<1e-6)

if(!exists("ln_CBre_Cons_13E.devfun"))
  ln_CBre_Cons_13E.devfun <- update(ln_CBre_Cons_13E, devFunOnly=TRUE)


pars<-get_pars(ln_CBre_Cons_13D)

if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Cons_13D.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Cons_13D.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Cons_13D@optinfo$derivs



if(!exists("ln_CBre_Cons_13D.restart"))
  ln_CBre_Cons_13D.restart <- update(ln_CBre_Cons_13D, start=pars)
glmer_examine(ln_CBre_Cons_13D.restart)


#CBre Comp
if(!exists("ln_CBre_Comp_13D.devfun"))
  ln_CBre_Comp_13D.devfun <- update(ln_CBre_Comp_13D, devFunOnly=TRUE)



if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Comp_13D.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Comp_13D.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Comp_13D@optinfo$derivs

if(!exists("ln_CBre_Comp_13D.restart"))
  ln_CBre_Comp_13D.restart <- update(ln_CBre_Comp_13D, start=pars)
glmer_examine(ln_CBre_Comp_13D.restart)


  save(ln_CBre_Cons_13D,ln_CBre_Comp_13D,ln_CBre_Cons_13D.restart,ln_CBre_Comp_13D.restart,
       file="Output//ln_CBre_Cons_13D.rdata")
  
stargazer::stargazer(ln_CBre_Cons_13B,ln_CBre_Cons_13D,ln_CBre_Cons_13D.restart,
                    ln_CBre_Comp_13B,ln_CBre_Comp_13D,ln_CBre_Comp_13D.restart,
                    type="text",
                       digits=2)





  save(ln_CBre_Cons_13D,ln_CBre_Comp_13D.devfun,ln_CBre_Cons_13D.restart,
       ln_CBre_Comp_13D,ln_CBre_Comp_13D.devfun,ln_CBre_Comp_13D.restart,
       file="Output//ln_CBre_Cons_13D.rdata")
load("Output//ln_CBre_Comp_13D.rdata")

  summary_residual_compare(ln_CBre_Cons_13D,ln_CBre_Cons_13D.restart,ln_CBre_Comp_13D,ln_CBre_Comp_13D.restart,bins=20)
  summary_residual_compare(ln_CBre_Cons_13B,ln_CBre_Cons_13D.restart,ln_CBre_Comp_13B,ln_CBre_Comp_13D.restart,bins=20)


```




###Model 13F: Agency/Office+NAICS6/NAICS3 Binned Comp Offers
```{r Model13F}

glmer_examine(ln_CBre_Comp_13F)
save(ln_CBre_Comp_13F,file="Output//ln_CBre_Comp_13F.rdata")

  stargazer::stargazer(ln_CBre_Comp_13B,ln_CBre_Comp_13C,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_Cons_14A,ln_CBre_Cons_13C,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13C,bins=20)



any(diag.vals<1e-6)

if(!exists("ln_CBre_Cons_13C.devfun"))
  ln_CBre_Cons_13C.devfun <- update(ln_CBre_Cons_13C, devFunOnly=TRUE)
pars<-get_pars(ln_CBre_Cons_13C)

if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Cons_13C.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Cons_13C.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Cons_13C@optinfo$derivs

if(!exists("ln_CBre_Cons_13C.restart"))
  ln_CBre_Cons_13C.restart <- update(ln_CBre_Cons_13C, start=pars)
glmer_examine(ln_CBre_Cons_13C.restart)



```


#Multi-Level Model Both Cons and Comp 
##Agency/Office & NaICS7
###Model 14A: Base
```{r Model14A}
load("Output//ln_CBre_Cons_Comp_14A.rdata")



ln_CBre_Cons_Comp_14A <- glmer (data=def_breach,
                      ln_CBre_Then_Year ~cl_def6_HHI_lag1 +cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1+
                    CompOffr+
                        cl_Ceil_Then_Year + cl_Days+ 
                        Veh +
                        PricingFee + b_UCA +
                        b_Intl+
                    
                       
                          +cl_def6_HHI_lag1:cl_def6_obl_lag1+ 
                        # Veh:cl_def6_HHI_lag1  +
                        b_UCA:cl_def6_HHI_lag1 + 
                            b_UCA:CompOffr + 
                        b_UCA:cl_Ceil_Then_Year+
                        
        (1 | NAICS) + 
                        (1 | Agency/Office) 

                      )
glmer_examine(ln_CBre_Cons_Comp_14A)
save(ln_CBre_Cons_Comp_14A,"Output//ln_CBre_Cons_Comp_14A.rdata")




  stargazer::stargazer(ln_CBre_Cons_13A,ln_CBre_Cons_13B,ln_CBre_Comp_13A.restart,ln_CBre_Comp_13B,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_Cons_13A,ln_CBre_Cons_13B,ln_CBre_Comp_13A.restart,ln_CBre_Comp_13B,bins=20)



any(diag.vals<1e-6)

if(!exists("ln_CBre_Cons_13B.devfun"))
  ln_CBre_Cons_13B.devfun <- update(ln_CBre_Cons_13B, devFunOnly=TRUE)
pars<-get_pars(ln_CBre_Cons_13B)

if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Cons_13B.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Cons_13B.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Cons_13B@optinfo$derivs

if(!exists("ln_CBre_Cons_13B.restart"))
  ln_CBre_Cons_13B.restart <- update(ln_CBre_Cons_13B, start=pars)
glmer_examine(ln_CBre_Cons_13B.restart)




#CBre Comp
if(!exists("ln_CBre_Comp_13B.devfun"))
  ln_CBre_Comp_13B.devfun <- update(ln_CBre_Comp_13B, devFunOnly=TRUE)
pars<-get_pars(ln_CBre_Comp_13B)

if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Comp_13B.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Comp_13B.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Comp_13B@optinfo$derivs

if(!exists("ln_CBre_Comp_13B.restart"))
  ln_CBre_Comp_13B.restart <- update(ln_CBre_Comp_13B, start=pars)
glmer_examine(ln_CBre_Comp_13B.restart)


  save(ln_CBre_Cons_13B,ln_CBre_Comp_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_13B.restart,
       file="Output//ln_CBre_Cons_13B.rdata")
  
stargazer::stargazer(ln_CBre_Cons_14A,ln_CBre_Cons_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13B,type="text",
                       digits=2)





  save(ln_CBre_Cons_13B,ln_CBre_Comp_13B,ln_CBre_Cons_13B.restart,
       file="Output//ln_CBre_Cons_13B.rdata")
load("Output//ln_CBre_Comp_13B.rdata")

  summary_residual_compare(ln_CBre_Cons_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13B,bins=20)


  source(system.file("utils", "allFit.R", package="lme4"))
  ln_CBre_Cons_13C.all <- allFit(ln_CBre_Cons_13C)
  ss_cons <- summary(ln_CBre_Cons_13C.all)

  fm1.all <- allFit(ln_CBre_Comp_13C)
  ss_comp <- summary(ln_CBre_Comp_13C.all)
```

###Model 14B: Switch fromCompOffr to CompOffr
```{r Model14B}
load("Output//ln_CBre_Cons_Comp_14B.rdata")



ln_CBre_Cons_Comp_14B <- glmer (data=def_breach,
                      ln_CBre_Then_Year ~cl_def6_HHI_lag1 +cl_def6_ratio_lag1+cl_def6_obl_lag1+
                  cl_US6_avg_sal_lag1+
                    CompOffr+
                        cl_Ceil_Then_Year + cl_Days+ 
                        Veh +
                        PricingFee + b_UCA +
                        b_Intl+
                    
                       
                          +cl_def6_HHI_lag1:cl_def6_obl_lag1+ 
                        # Veh:cl_def6_HHI_lag1  +
                        b_UCA:cl_def6_HHI_lag1 + 
                            b_UCA:CompOffr + 
                        b_UCA:cl_Ceil_Then_Year+
                        
        (1 | NAICS) + 
                        (1 | Agency/Office) 

                      )
glmer_examine(ln_CBre_Cons_Comp_14B)
save(ln_CBre_Cons_Comp_14B,"Output//ln_CBre_Cons_Comp_14B.rdata")




  stargazer::stargazer(ln_CBre_Cons_13A,ln_CBre_Cons_13B,ln_CBre_Comp_13A.restart,ln_CBre_Comp_13B,type="text",
                       digits=2)
  
  

summary_residual_compare(ln_CBre_Cons_13A,ln_CBre_Cons_13B,ln_CBre_Comp_13A.restart,ln_CBre_Comp_13B,bins=20)



any(diag.vals<1e-6)

if(!exists("ln_CBre_Cons_13B.devfun"))
  ln_CBre_Cons_13B.devfun <- update(ln_CBre_Cons_13B, devFunOnly=TRUE)

pars<-get_pars(ln_CBre_Cons_13B)
if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Cons_13B.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Cons_13B.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Cons_13B@optinfo$derivs

if(!exists("ln_CBre_Cons_13B.restart"))
  ln_CBre_Cons_13B.restart <- update(ln_CBre_Cons_13B, start=pars)
glmer_examine(ln_CBre_Cons_13B.restart)




#CBre Comp
if(!exists("ln_CBre_Comp_13B.devfun"))
  ln_CBre_Comp_13B.devfun <- update(ln_CBre_Comp_13B, devFunOnly=TRUE)

pars<-get_pars(ln_CBre_Comp_13B)
if (require("numDeriv")) {
  cat("hess:\n"); print(hess <- hessian(ln_CBre_Comp_13B.devfun, unlist(pars)))
  cat("grad:\n"); print(grad <- grad(ln_CBre_Comp_13B.devfun, unlist(pars)))
  cat("scaled gradient:\n")
  print(scgrad <- solve(chol(hess), grad))
}
## compare with internal calculations:
ln_CBre_Comp_13B@optinfo$derivs

if(!exists("ln_CBre_Comp_13B.restart"))
  ln_CBre_Comp_13B.restart <- update(ln_CBre_Comp_13B, start=pars)
glmer_examine(ln_CBre_Comp_13B.restart)


  save(ln_CBre_Cons_13B,ln_CBre_Comp_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_13B.restart,
       file="Output//ln_CBre_Cons_13B.rdata")
  
stargazer::stargazer(ln_CBre_Cons_14A,ln_CBre_Cons_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13B,type="text",
                       digits=2)





  save(ln_CBre_Cons_13B,ln_CBre_Comp_13B,ln_CBre_Cons_13B.restart,
       file="Output//ln_CBre_Cons_13B.rdata")
load("Output//ln_CBre_Comp_13B.rdata")

  summary_residual_compare(ln_CBre_Cons_13B,ln_CBre_Cons_13B.restart,ln_CBre_Comp_14A.restart,ln_CBre_Comp_13B,bins=20)


  source(system.file("utils", "allFit.R", package="lme4"))
  ln_CBre_Cons_13C.all <- allFit(ln_CBre_Cons_13C)
  ss_cons <- summary(ln_CBre_Cons_13C.all)

  fm1.all <- allFit(ln_CBre_Comp_13C)
  ss_comp <- summary(ln_CBre_Comp_13C.all)
```

## Agency/Office & NAICS3/6
###Model 15A: Models 13B Cons and 13C Comp combined
```{r Model15A}
load("Output//ln_CBre_Cons_Comp_15A.rdata")

ln_CBre_Cons_Comp_15A <- glmer (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                  #cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                  cl_US6_avg_sal_lag1+
                   CompOffr+
                                                cl_Ceil_Then_Year + cl_Days+ 
                        Veh +
                        PricingFee + b_UCA +
                        b_Intl+
                   
                       
                        
                        b_UCA:CompOffr +
                        b_UCA:cl_def6_HHI_lag1 + 
                        b_UCA:cl_Ceil_Then_Year+
                        cl_def6_HHI_lag1:cl_def6_obl_lag1+
                         
                        (1 | NAICS3/NAICS) + 
                        (1 | Agency/Office) 

                      ,
                        verbose=1)

save(ln_CBre_Cons_Comp_15A,ln_CBre_Cons_Comp_15A_1m,file="Output//ln_CBre_Cons_Comp_15A.rdata")
glmer_examine(ln_CBre_Cons_Comp_15A)


stargazer::stargazer(ln_CBre_Cons_Comp_15A,ln_CBre_Cons_Comp_15A_1m,type="text",
                       digits=2)
  stargazer::stargazer(ln_CBre_Cons_13B,ln_CBre_Comp_13C,ln_CBre_Cons_Comp_14B,ln_CBre_Cons_Comp_15A,ln_CBre_Cons_Comp_15A_1m,type="text",
                       digits=2)
  
```


###Model 15B: Ratio instead of obligations
```{r Model15B}
load("Output//ln_CBre_Cons_15B.rdata")

ln_CBre_Cons_15B <- glmer (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                  #cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                  cl_US6_avg_sal_lag1+
                                                cl_Ceil_Then_Year + cl_Days+ 
                        Veh +
                        PricingFee + b_UCA +
                        b_Intl+
                   
                       
                        
                        
                        b_UCA:cl_def6_HHI_lag1 + 
                        b_UCA:cl_Ceil_Then_Year+
                        cl_def6_ratio_lag1:cl_def6_HHI_lag1+
                         
                        (1 | NAICS3/NAICS) + 
                        (1 | Agency/Office) ,
                 
                 family=binomial(link="logit"),
                        verbose=1)

glmer_examine(ln_CBre_Cons_15B,display=TRUE)

ln_CBre_Cons_Comp_15B <- glmer (data=def_breach,
                 ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                  #cl_US3_avg_sal_lag1+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                  cl_US6_avg_sal_lag1+
                   CompOffr+
                                                cl_Ceil_Then_Year + cl_Days+ 
                        Veh +
                        PricingFee + b_UCA +
                        b_Intl+
                   
                       
                        
                        b_UCA:CompOffr +
                        b_UCA:cl_def6_HHI_lag1 + 
                        b_UCA:cl_Ceil_Then_Year+
                        cl_def6_ratio_lag1:cl_def6_HHI_lag1+
                         
                        (1 | NAICS3/NAICS) + 
                        (1 | Agency/Office) ,
                 
                 family=binomial(link="logit"),
                        verbose=1)



glmer_examine(ln_CBre_Cons_Comp_15B,display=TRUE)


  stargazer::stargazer(ln_CBre_Cons_13B,ln_CBre_Comp_13C,ln_CBre_Cons_Comp_14B,ln_CBre_Cons_15B,ln_CBre_Cons_Comp_15A,ln_CBre_Cons_Comp_15B,type="text",
                       digits=2)

save(ln_CBre_Cons_15B,ln_CBre_Cons_Comp_15B,file="Output//ln_CBre_15B.rdata")



```
The new variable proves to not be significant.

## Rare Events Logit
### Model 16A 1-level traditional
```{r Model16A}

# stargazer::stargazer(ln_CBre_Cons_Comp_16A,type="text",
#                        digits=2)
# if(!exists("ln_CBre_Cons_Comp_16A")){
  ln_CBre_Cons_Comp_16A <- glm (data=def_breach,
                               ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                                 #cl_US3_avg_sal_lag1+
                                 cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                                 cl_US6_avg_sal_lag1+
                                 CompOffr+
                                   cl_Ceil_Then_Year + cl_Days+ 
                                 Veh +
                                 PricingFee + b_UCA +
                                 b_Intl+
                                 
                                 
                                 
                                 b_UCA:CompOffr +
                                 b_UCA:cl_def6_HHI_lag1 + 
                                 b_UCA:cl_Ceil_Then_Year+
                                 cl_def6_HHI_lag1:cl_def6_obl_lag1+
                                 
                                 NAICS3 + 
                                 Agency ,
                               family=binomial(link="logit"))
  
  ln_CBre_Cons_Comp_16A_1m <- glm (data=def_breach,
                               ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                                 #cl_US3_avg_sal_lag1+
                                 cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                                 cl_US6_avg_sal_lag1+
                                 CompOffr+
                                 cl_Ceil_Then_Year + cl_Days+ 
                                 Veh +
                                 PricingFee + b_UCA +
                                 b_Intl+
                                 
                                 
                                 
                                 b_UCA:CompOffr +
                                 b_UCA:cl_def6_HHI_lag1 + 
                                 b_UCA:cl_Ceil_Then_Year+
                                 cl_def6_HHI_lag1:cl_def6_obl_lag1+
                                 
                                 NAICS3+
                                 Agency ,
                               family=binomial(link="logit"))
  
  # save(ln_CBre_Cons_Comp_16A,ln_CBre_Cons_Comp_16A_1m,file="..//Output//ln_CBre_Cons_Comp_16A.rdata")
# }


# source(system.file("utils", "allFit.R", package="lme4"))
# ln_CBre_Cons_Comp_16A_1m.all <- allFit(ln_CBre_Cons_Comp_16A_1m)
# ln_CBre_Cons_Comp_16A_1m_ss_cons <- summary(ln_CBre_Cons_Comp_16A_1m.all)
# 
# 
# glmer_examine(ln_CBre_Cons_Comp_16A,display=TRUE)
# ln_CBre_Cons_Comp_16A_odds_ratio<-odds_ratio(ln_CBre_Cons_Comp_16A,"ln_CBre_Cons_Comp_16A")
# get_icc(ln_CBre_Cons_Comp_16A)
```


### Model 16B 1-level rare events
```{r Model16B}

# stargazer::stargazer(ln_CBre_Cons_Comp_16B,type="text",
#                        digits=2)
# if(!exists("ln_CBre_Cons_Comp_16B")){
  ln_CBre_Cons_Comp_16B <- Zelig::zelig(data=as.data.frame(def_breach),
                               ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                                 #cl_US3_avg_sal_lag1+
                                 cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                                 cl_US6_avg_sal_lag1+
                                 CompOffr+
                                   cl_Ceil_Then_Year + cl_Days+ 
                                 Veh +
                                 PricingFee + b_UCA +
                                 b_Intl+
                                 
                                 
                                 
                                 b_UCA:CompOffr +
                                 b_UCA:cl_def6_HHI_lag1 + 
                                 b_UCA:cl_Ceil_Then_Year+
                                 cl_def6_HHI_lag1:cl_def6_obl_lag1+
                                 
                                 NAICS3 + 
                                 Agency ,
                               model="relogit")
  
  ln_CBre_Cons_Comp_16B_1m <- Zelig::zelig(data=as.data.frame(def_breach),
                               ln_CBre_Then_Year ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+
                                 #cl_US3_avg_sal_lag1+
                                 cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                                 cl_US6_avg_sal_lag1+
                                 CompOffr+
                                 cl_Ceil_Then_Year + cl_Days+ 
                                 Veh +
                                 PricingFee + b_UCA +
                                 b_Intl+
                                 
                                 
                                 
                                 b_UCA:CompOffr +
                                 b_UCA:cl_def6_HHI_lag1 + 
                                 b_UCA:cl_Ceil_Then_Year+
                                 cl_def6_HHI_lag1:cl_def6_obl_lag1+
                                 
                                 NAICS3+
                                 Agency ,
                                model="relogit")
  
  # save(ln_CBre_Cons_Comp_16B,ln_CBre_Cons_Comp_16B_1m,file="..//Output//ln_CBre_Cons_Comp_16B.rdata")
# }
load("..//Output//ln_CBre_Cons_Comp_15A.rdata")
screenreg(list(ln_CBre_Cons_Comp_15A, ln_CBre_Cons_Comp_16A,ln_CBre_Cons_Comp_16B,
               ln_CBre_Cons_Comp_15A_1m,ln_CBre_Cons_Comp_16A_1m,ln_CBre_Cons_Comp_16B_1m))


# source(system.file("utils", "allFit.R", package="lme4"))
# ln_CBre_Cons_Comp_16B_1m.all <- allFit(ln_CBre_Cons_Comp_16B_1m)
# ln_CBre_Cons_Comp_16B_1m_ss_cons <- summary(ln_CBre_Cons_Comp_16B_1m.all)
# 
# 
# glmer_examine(ln_CBre_Cons_Comp_16B,display=TRUE)
# ln_CBre_Cons_Comp_16B_odds_ratio<-odds_ratio(ln_CBre_Cons_Comp_16B,"ln_CBre_Cons_Comp_16B")
# get_icc(ln_CBre_Cons_Comp_16B)
```


