---
title: "Services Codebook"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Thursday, July 11, 2017"
---

# Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(knitr)
library(foreign)
library(stargazer)
library(texreg)
library(reshape2)
library(tidyverse)
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")


axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```


Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start.


## Load Data
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.


```{r ReadInData, echo = TRUE}

load("../data/clean/transformed_def_serv.Rdata")

```



# Dependent Variables

### Number of  Offers
summary(def$offer)
centered_description(def$UnmodifiedNumberOfOffersReceived,"number of offers")
centered_log_description(def$UnmodifiedNumberOfOffersReceived,"number of offers")
NA_stats(def,"cl_Offr")


```{r NumOffers}

statsummary_continuous(c("UnmodifiedNumberOfOffersReceived"), def)
grouped_barplot("Offr", def)

```



### Ceiling  Breaches
* b_CBre is a binary variable that has a value of 1 for any contracts that have experienced a partial or complete termination, 0 otherwise. (`r summary(def$b_CBre);
sum(def$Action_Obligation[def$b_CBre==1],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
NA_stats(def,"b_CBre")`)


```{r vargraphs: b_Term, b_CBre}
#The original variables for b_Term and b_CBre are Term and CBre
grouped_barplot("CBre", def_serv)
statsummary_discrete(c("CBre"), def_serv)
```


### Contract Terminations

Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four categories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  



NA_stats(def_serv,"b_Term")
* b_Term is a binary variable that has a value of 1 for any contracts that have experienced a partial or complete termination, 0 otherwise. (`r summary(def_serv$b_Term);
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$b_Term==1],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)`

```{r vargraphs: b_Term, b_CBre}
#The original variables for b_Term and b_CBre are Term and CBre
grouped_barplot("Term", def_serv)
statsummary_discrete(c("b_Term"), def_serv)
```






# Independent Variables

## Study Variables



### Competition
* b_Comp is a binary variable based on competition. It has a value of 0 for uncompeted contracts and a value of 1 for competition, regardless of number of offers. `r  summary(def_serv$Comp);
NA_stats(def_serv,"Comp") `
* n_Comp is a binary variable based on competition. It has a value of 0 for uncompeted contracts and a value of 1 for competition, regardless of number of offers. `r  summary(def_serv$EffComp);
NA_stats(def_serv,"EffComp")
sum(def$Action_Obligation[def$EffComp=="No Comp."],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
sum(def$Action_Obligation[def$EffComp=="1 Offer"],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
sum(def$Action_Obligation[def$EffComp=="2+ Offers"],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)`
)


* CompOffr is a dummy variable based on competition and the number of offers. It's baseline value is No Competition, sole-source contracts, which are intentionally not assigned a dummy to avoid multicollinearity. `r  summary(def$CompOffr);
debug(NA_stats)
NA_stats(def,"CompOffr")
sum(def$Action_Obligation[def$CompOffr=="No Competition"],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
sum(def$Action_Obligation[def$CompOffr=="1 offer"],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
sum(def$Action_Obligation[def$CompOffr=="2 offers"],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
sum(def$Action_Obligation[def$CompOffr=="3-4 offers"],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
sum(def$Action_Obligation[def$CompOffr=="5+ offers"],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)

length(def$CompOffr[def$CompOffr=="No Competition" & !is.na(def$CompOffr)])/nrow(def)
length(def$CompOffr[def$CompOffr=="1 offer"& !is.na(def$CompOffr)])/nrow(def)
length(def$CompOffr[def$CompOffr=="2 offers"& !is.na(def$CompOffr)])/nrow(def)
length(def$CompOffr[def$CompOffr=="3-4 offers"& !is.na(def$CompOffr)])/nrow(def)
length(def$CompOffr[def$CompOffr=="5+ offers"& !is.na(def$CompOffr)])/nrow(def)

`
)



```{r Competition}  
summary(def_serv$CompOffr);
debug(NA_stats)
NA_stats(def_serv,"CompOffr")
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$CompOffr=="No Competition"],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$CompOffr=="1 offer"],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$CompOffr=="2 offers"],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$CompOffr=="3-4 offers"],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$CompOffr=="5+ offers"],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)

length(def_serv$CompOffr[def_serv$CompOffr=="No Competition" & !is.na(def_serv$CompOffr)])/nrow(def_serv)
length(def_serv$CompOffr[def_serv$CompOffr=="1 offer"& !is.na(def_serv$CompOffr)])/nrow(def_serv)
length(def_serv$CompOffr[def_serv$CompOffr=="2 offers"& !is.na(def_serv$CompOffr)])/nrow(def_serv)
length(def_serv$CompOffr[def_serv$CompOffr=="3-4 offers"& !is.na(def_serv$CompOffr)])/nrow(def_serv)
length(def_serv$CompOffr[def_serv$CompOffr=="5+ offers"& !is.na(def_serv$CompOffr)])/nrow(def_serv)



summary(def_serv$offer)
centered_description(def_serv$UnmodifiedNumberOfOffersReceived,"number of offers")
centered_log_description(def_serv$UnmodifiedNumberOfOffersReceived,"number of offers")
NA_stats(def_serv,"cl_Offr")
# <!-- cl_def3_HHI_lag1+cl_def3_ratio_lag1+#cl_def3_obl_lag1+ -->
#                             <!-- #cl_US3_avg_sal_lag1+ -->
#                             <!-- cl_def6_HHI_lag1+cl_def6_obl_lag1+cl_def6_ratio_lag1+ -->
#                             <!-- cl_US6_avg_sal_lag1Const+ -->


centered_log_description(def_serv$l_def3_obl_lag1,"obligations")
centered_log_description(def_serv$l_def6_obl_lag1,"obligations")
NA_stats(def_serv,"l_def3_obl_lag1")

NA_stats(def_serv,"l_def6_obl_lag1")
def_serv$l_def6_ratio_lag1[is.nan(def_serv$l_def6_ratio_lag1) | is.infinite(def_serv$l_def6_ratio_lag1)]<-NA
def_serv$cl_def6_ratio_lag1[is.nan(def_serv$cl_def6_ratio_lag1) | is.infinite(def_serv$cl_def6_ratio_lag1)]<-NA

centered_log_description(def_serv$l_def3_ratio_lag1,"obligations")

centered_log_description(def_serv$l_def6_ratio_lag1,"obligations")
NA_stats(def_serv,"cl_def3_ratio_lag1")
NA_stats(def_serv,"cl_def6_ratio_lag1")


# Effplot<-freq_discrete_plot(subset(def_serv,"EffComp"))
# Effplot<-Effplot+labs(x="Effective Competition",y="Contract or Task Order Count")
# ggsave(Effplot,file="..\\Output//EffFreq.png",width=5.5,height=5.5,dpi=600)
```


```{r varGraphs: b_Comp, n_Comp, Comp, CompOffr, EffComp, offr}
# b_Comp
# n_Comp
# Comp
# EffComp
# CompOffr
# offr:


grouped_barplot("Comp",def)
grouped_barplot("EffComp",def)
grouped_barplot("CompOffr", def)

# def$n_Comp <- factor(def$n_Comp,c(0,1))
# grouped_barplot("Comp", def)
# #grouped_barplot("n_Comp")
# grouped_barplot("Comp", def)
# grouped_barplot("EffComp", def)
# grouped_barplot("CompOffr", def)
# grouped_barplot("Offr", def)

```




##### Subsector HHI
NA_stats(def_serv,"def3_HHI_lag1")
centered_description(def$def3_HHI_lag1,"HHI score")
centered_log_description(def$def3_HHI_lag1,"HHI score")

NA_stats(def,"def3_HHI_lag1")
NA_stats(def,"cl_def3_HHI_lag1")


##### Detailed Industry HHI                            

* cl_def6_HHI_lag1 is a numeric variable based on the HHI Index of a NAICS code for defense contracting. Index values of 1500 and below are considered unconsolidated. 1500-2000 is considered moderately consolidated. And 2,000 and above are considered highly consolidated. The scale runs from 0 to 10,000. `r summary(def$cl_def6_HHI_lag1);
summary(def$l_def6_HHI_lag1);
centered_description(def$def6_HHI_lag1,"HHI score")
centered_log_description(def$l_def6_HHI_lag1,"HHI score")

                            
NA_stats(def,"def6_HHI_lag1")


`
```{r statistic summary table for continuous variables: cl_def_HHI_lag1, cl_def_ratio_lag1, cl_US_avg_sal_lag1, cl_def_obl_lag1, all use original variables instead}

# !is.na(def_serv$cl_US6_avg_sal_lag1Const)&
#   !is.na(def_serv$pPBSC)&
# !is.na(def_serv$pOffPSC)&

HHI_category<-c("def3_HHI_lag1","def6_HHI_lag1")
complex_category <- c("US6_avg_sal_lag1","CFTE_Rate_1year")
capacity_category <- c("pPBSC", "pOffPSC")
pair_category <- c("office_entity_ca_inc")

# def_serv$CFTE_Rate_1year
statsummary_discrete("CompOffr",def_serv)

def_serv$office_entity_ca_inc<-def_serv$office_entity_numberofactions_1year+1
hhi<-statsummary_continuous(HHI_category, def_serv)
hhi
write.csv(hhi,file="..\\Output/hhi_summary.csv")
statsummary_continuous(complex_category, def_serv)
statsummary_continuous(capacity_category, def_serv,log=FALSE)
statsummary_continuous(pair_category, def_serv)



```

```{r statistic summary table for continuous variables: cl_def_HHI_lag1, cl_def_ratio_lag1, cl_US_avg_sal_lag1, cl_def_obl_lag1, all use original variables instead}
ratio_category <- c("capped_def6_ratio_lag1", "capped_def5_ratio_lag1", "capped_def4_ratio_lag1", "capped_def3_ratio_lag1", "capped_def2_ratio_lag1")
avg_category <- c("US6_avg_sal_lag1", "US5_avg_sal_lag1", "US4_avg_sal_lag1", "US3_avg_sal_lag1", "US2_avg_sal_lag1")
obl_category <- c("def6_obl_lag1", "def5_obl_lag1", "def4_obl_lag1", "def3_obl_lag1", "def2_obl_lag1" )

statsummary_discrete("CompOffr",def)



statsummary_continuous(ratio_category, def)
statsummary_continuous(avg_category, def)
statsummary_continuous(obl_category, def)

statsummary_discrete("CompOffr", def)

HHI_category <- c("def6_HHI_lag1", "def5_HHI_lag1", "def4_HHI_lag1","def3_HHI_lag1", "def2_HHI_lag1")

hhi<-statsummary_continuous(HHI_category, def)
hhi
write.csv(hhi,file="..//Output/hhi_summary.csv")
```


## Controls


### Initial Contract Scope

#### Ceiling
* cl_Ceil is the natural log of the initial contract cost ceiling, in then-year dollars. `r centered_log_description(def$UnmodifiedContractBaseAndAllOptionsValue,"dollars");
NA_stats(def,"cl_Ceil")`

* cl_Days is the natural log of the initial maximum duration of the contract, in days. The variable is centered, by subtracting its mean (`r centered_log_description(def$UnmodifiedDays,"days");
NA_stats(def,"cl_Days")` 


```{r statistic summary table for continuous variables: cl_Ceil, cl_Days}
#original variable for cl_Ceil: UnmodifiedContractBaseAndAllOptionsValue
#original variable for cl_Days: UnmodifiedDays


statsummary_continuous(c("UnmodifiedDays","UnmodifiedContractBaseAndAllOptionsValue"), def)



```


#### Duration
* cl_Days is the natural log of the initial maximum duration of the contract, in days. The variable is centered, by subtracting its mean (`r centered_log_description(def_serv$UnmodifiedDays,"days");
NA_stats(def_serv,"cl_Days")` 


```{r statistic summary table for continuous variables: cl_Ceil, cl_Days}
#original variable for cl_Ceil: UnmodifiedContractBaseAndAllOptionsValue.OMB20_GDP18
#original variable for cl_Days: UnmodifiedDays

statsummary_continuous(c("UnmodifiedDays","UnmodifiedContractBaseAndAllOptionsValue.OMB20_GDP18"), def_serv)



```


### Contract Vehicle
* SIDV, MIDV, and FSS/GWAC, BPA/BOA are dummy variables based on the contract vehicle. They correspond to Single-Award IDVs, Multi-Award IDVs, and Other IDVs, respectively, having a value of 1 when the task order has that vehicle type, and having a 0 other. The remaining types, definitive contracts and purchase orders, are intentionally left out. (`r 
summary(def_serv$Veh);
length(def_serv$Veh[def_serv$Veh =="def_serv/Pur"])/nrow(def_serv)

length(def_serv$Veh[def_serv$Veh =="S-IDC"& !is.na(def_serv$Veh)])/nrow(def_serv)
length(def_serv$Veh[def_serv$Veh =="M-IDC"& !is.na(def_serv$Veh)])/nrow(def_serv)
length(def_serv$Veh[def_serv$Veh =="FSS/GWAC"& !is.na(def_serv$Veh)])/nrow(def_serv)
length(def_serv$Veh[def_serv$Veh =="BPA/BOA"& !is.na(def_serv$Veh)])/nrow(def_serv)
NA_stats(def_serv,"Veh")`

```{r VehGraph}
grouped_barplot("Veh", def_serv)
statsummary_discrete("Veh", def_serv)
```


### Pricing Fee
* n_Fixed is a numeric variable based on contract pricing. It has a value of 0 for cost-based, 0.5 or "combination or other", 1 for any fixed price (excluding fixed-price level of effort which is classified as cost-based). (`r summary(def_serv$n_Fixed);
NA_stats(def_serv,"n_Fixed")
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$n_Fixed==0],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$n_Fixed==0.5],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$n_Fixed==1],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)
nrow(def_serv[def_serv$n_Fixed==0,])/nrow(def_serv)
nrow(def_serv[def_serv$n_Fixed==0.5,])/nrow(def_serv)
nrow(def_serv[def_serv$n_Fixed==1,])/nrow(def_serv)


summary(def_serv$PricingFee);
length(def_serv$PricingFee[def_serv$PricingFee =="FFP"])/nrow(def_serv)

length(def_serv$PricingFee[def_serv$PricingFee =="Other FP" & !is.na(def_serv$PricingFee)])/nrow(def_serv)
length(def_serv$PricingFee[def_serv$PricingFee =="Incentive" & !is.na(def_serv$PricingFee)])/nrow(def_serv)
length(def_serv$PricingFee[def_serv$PricingFee =="Combination or Other" & !is.na(def_serv$PricingFee)])/nrow(def_serv)
length(def_serv$PricingFee[def_serv$PricingFee =="Other CB" & !is.na(def_serv$PricingFee)])/nrow(def_serv)
length(def_serv$PricingFee[def_serv$PricingFee =="T&M/LH/FPLOE" & !is.na(def_serv$PricingFee)])/nrow(def_serv)
NA_stats(def_serv,"PricingFee")

`)

NA_stats(def_serv,"n_Incent")`)
* b_UCA is a binary variable with a value of 1 for contracts/task orders that begin as letter contracts or undefinitized contract awards (UCA) and a value of 0 otherwise. `r summary(def_serv$b_UCA);
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$b_UCA==1],na.rm=TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18,na.rm=TRUE)

### Pricing Fee
* n_Fixed is a numeric variable based on contract pricing. It has a value of 0 for cost-based, 0.5 or "combination or other", 1 for any fixed price (excluding fixed-price level of effort which is classified as cost-based). (`r summary(def$n_Fixed);
NA_stats(def,"n_Fixed")
sum(def$Action_Obligation[def$n_Fixed==0],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
sum(def$Action_Obligation[def$n_Fixed==0.5],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
sum(def$Action_Obligation[def$n_Fixed==1],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
nrow(def[def$n_Fixed==0,])/nrow(def)
nrow(def[def$n_Fixed==0.5,])/nrow(def)
nrow(def[def$n_Fixed==1,])/nrow(def)


summary(def$PricingFee);
length(def$PricingFee[def$PricingFee =="FFP"])/nrow(def)

length(def$PricingFee[def$PricingFee =="Other FP" & !is.na(def$PricingFee)])/nrow(def)
length(def$PricingFee[def$PricingFee =="Incentive" & !is.na(def$PricingFee)])/nrow(def)
length(def$PricingFee[def$PricingFee =="Combination or Other" & !is.na(def$PricingFee)])/nrow(def)
length(def$PricingFee[def$PricingFee =="Other CB" & !is.na(def$PricingFee)])/nrow(def)
length(def$PricingFee[def$PricingFee =="T&M/LH/FPLOE" & !is.na(def$PricingFee)])/nrow(def)
NA_stats(def,"PricingFee")

`)
NA_stats(def,"n_Incent")`)



```{r PricingFeeGraphs}
#n_Fixed(0,1), PricingFee, n_Incent, b_UCA(0,1), b_Intl
#original variable for b_UCA: UCA
#original variable for n_Fixed: FxCb
#original variable for n_Incent: Fee

grouped_barplot("FxCb", def)
grouped_barplot("Fee", def)
grouped_barplot("PricingFee", def)
statsummary_discrete("PricingFee", def)
```

### UCA

* b_UCA is a binary variable with a value of 1 for contracts/task orders that begin as letter contracts or undefinitized contract awards (UCA) and a value of 0 otherwise. `r summary(def$b_UCA);
sum(def$Action_Obligation[def$b_UCA==1],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
length(def$b_UCA[def$b_UCA==1 & !is.na(def$b_UCA)])/nrow(def)
NA_stats(def,"b_UCA")`


length(def_serv$b_UCA[def_serv$b_UCA==1 & !is.na(def_serv$b_UCA)])/nrow(def_serv)
NA_stats(def_serv,"b_UCA")`
* NAICS is a factor reporting the top North American Industrial Classification Code of each contract. 
`r summary(def_serv$NAICS);
NA_stats(def_serv,"NAICS")`
* Agency is a factor reporting the top Contracting Agency of each contract. 
`r summary(def_serv$Agency);
NA_stats(def_serv,"Agency")`
* Office is a factor reporting the top Contracting office of each contract. 
`r summary(def_serv$Office);
NA_stats(def_serv,"Office")`


```{r UCA}
# def$b_UCA <- factor(def$b_UCA, c(0,1))
def_serv$b_UCA <- factor(def_serv$b_UCA, c(0,1))
grouped_barplot("UCA", def)
statsummary_discrete("UCA", def)

```
### International



* b_Intl is a binary variable with a value of 1 for contracts/task orders with any transactions performed internationally and a value of 0 otherwise. `r summary(def$b_Intl);
sum(def$Action_Obligation[def$b_Intl==1],na.rm=TRUE)/sum(def$Action_Obligation,na.rm=TRUE)
NA_stats(def,"b_Intl")`


```{r International}
#n_Fixed(0,1), PricingFee, n_Incent, b_UCA(0,1), b_Intl
#original variable for b_UCA: UCA
#original variable for n_Fixed: FxCb
#original variable for n_Incent: Fee

grouped_barplot("Intl", def)
statsummary_discrete("Intl", def)
```

### Contracting Customer
#### Agency
* Agency is a factor reporting the top Contracting Agency of each contract. 
`r summary(def$Agency);
NA_stats(def,"Agency")`




### Agency


```{r frequancy bar plot for agency}
#Prepare the dataframe for plot
Agency_Freq <- as.data.frame(table(def_serv$Agency))
Agency_Freq$Percent_Freq <- round(Agency_Freq$Freq/sum(Agency_Freq$Freq),4)*100
colnames(Agency_Freq) <- c("Agency","Count_Freq","Percent_Freq")
Agency_Freq <- Agency_Freq[order(-Agency_Freq$Count_Freq),]
Agency_Freq <- Agency_Freq[1:10,]

#Add detail description to Agency code
Agency_Lookup <- read.csv("https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/Agency_AgencyID.csv")
Agency_Lookup <- Agency_Lookup[,1:2]
colnames(Agency_Lookup) <- c("Agency","Agency_Description")
Agency_Freq <- left_join(Agency_Freq, Agency_Lookup, by = "Agency")
Agency_Freq$Agency <- factor(Agency_Freq$Agency, levels = rev(Agency_Freq$Agency))
Agency_Freq <- Agency_Freq[order(-Agency_Freq$Percent_Freq),]
Agency_Freq$Agency_Description <- factor(Agency_Freq$Agency_Description, 
                                         levels=rev(Agency_Freq$Agency_Description))

#build the frequency bar plot
Frequency_Plot3 <- ggplot(data = Agency_Freq, aes(x=Agency_Description,        y=Percent_Freq)) +
                   geom_bar(stat = "identity", position = "dodge", width = 0.8) +
                   coord_flip() +
                   xlab("Agency") +
                   ylab("Percent of Frequency") +
                   theme_grey() +
                   scale_fill_grey() +
                   ggtitle("Top 10 of the most frequently appeared Agency") +
                   theme(text = element_text(size = 10))
Frequency_Plot3
```


```{r frequancy and obligation percent grouped bar plot for agency}

#Percent grouped bar plot for variable Agency
#Generate new data frame containing frequency information
Agency_Freq <- as.data.frame(table(def$Agency))
Agency_Freq$Percent_Freq <- round(Agency_Freq$Freq/sum(Agency_Freq$Freq),4)*100
colnames(Agency_Freq) <- c("Agency","Count_Freq","Percent_Freq")

#Add detail Agency description according to agency code
Agency_Lookup <- read.csv("https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/Agency_AgencyID.csv")
Agency_Lookup <- Agency_Lookup[,1:2]
colnames(Agency_Lookup) <- c("Agency","Agency_Description")
Agency_Freq <- left_join(Agency_Freq, Agency_Lookup, by = "Agency")
#Add obligation percent information to data frame
Percent_Obli <- c()
for (i in Agency_Freq$Agency) {
  Percent_Obligation <- round(sum(def$Action_Obligation[def$Agency == i], na.rm = TRUE)/sum(def$Action_Obligation, na.rm = TRUE),5)
  Percent_Obli <- c(Percent_Obli, Percent_Obligation)
}
Agency_Freq$Agency_Description <- as.character(Agency_Freq$Agency_Description)
Agency_Freq$Percent_Obli <- Percent_Obli*100

#Get top 5 Agencies that take largest percent obligation
Agency_Freq <- Agency_Freq[order(-Percent_Obli),]
Agency_Freq <- Agency_Freq[1:5,]
percent_freq_rest <- 100 - sum(Agency_Freq$Percent_Freq, na.rm = TRUE)
percent_obli_rest <- 100 - sum(Agency_Freq$Percent_Obli, na.rm = TRUE)

Agency_Freq[6,] <- c("All Other", "NA", percent_freq_rest, "All Other", percent_obli_rest)
Agency_Freq$Agency_Description <- factor(Agency_Freq$Agency_Description, levels = rev(Agency_Freq$Agency_Description))
Agency_Freq[,c(3,5)] <- lapply(Agency_Freq[,c(3,5)], function(x) as.numeric(x))
Agency_Freq <- melt(Agency_Freq, id = c("Agency","Count_Freq", "Agency_Description"))

#Build grouped bar plot
Agency_barplot <- ggplot(data = Agency_Freq, 
                         aes(x = Agency_Description, 
                             y=value, 
                             fill=factor(variable))) + 
                  geom_bar(stat = "identity", 
                           position= "dodge", 
                           width = 0.8) + 
                  xlab("") + 
                  ylab("") + 
                  coord_flip() + 
                  theme_grey() +
                  scale_fill_grey(labels = c("% of records", "% of obligation"),
                                  guide = guide_legend(reverse = TRUE)) +
                  theme(legend.title = element_blank(),
                        legend.position = "bottom",
                        legend.margin = margin(t=-0.8, r=0, b=0.5, l=0, unit = "cm"),
                        legend.text = element_text(margin = margin(r=0.5, unit = "cm")),
                        plot.margin = margin(t=0.3, r=0.5, b=0, l=0.5, unit = "cm")) +
                 ggtitle("Top 5 of the most frequently appeared Agency") 
Agency_barplot                  

```


#### Office 

* Office is a factor reporting the top Contracting office of each contract. 
`r summary(def$Office);
NA_stats(def,"Office")`
```{r grouped percent frequency/obligation barplot for all Office}
#grouped bar plot for variable Office
#Perpare data for plot
#get the detailed desceription for Office by AgencyID and OfficeID
# Office_Lookup <- read.delim("https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/office/Office.ContractingOfficeCode.txt")
# def_dup <- def_serv

memory.limit(56000)
Office_Freq <- def_serv %>% group_by(Office,ContractingOfficeName) %>% summarise(
  Count_Freq=length(CSIScontractID),
  Action_Obligation.OMB20_GDP18=sum(Action_Obligation.OMB20_GDP18)
)
  
  # Office_Freq <- Office_Freq[order(-Office_Freq$Freq),]
# Office_Freq_TOP20 <- Office_Freq[1:20,]   #Get top 20 NAICS has largest frequency count
Office_Freq$Percent_Freq <- round(Office_Freq$Count_Freq/
                                   sum(Office_Freq$Count_Freq),4)*100
Office_Freq$Percent_Obli <- round(Office_Freq$Action_Obligation.OMB20_GDP18/
                                         sum(Office_Freq$Action_Obligation.OMB20_GDP18),4)*100

colnames(Office_Freq)[colnames(Office_Freq)=="Office"] <- "OfficeID"
colnames(Office_Freq)[colnames(Office_Freq)=="ContractingOfficeName"] <- "OfficeName"

Office_Freq$Percent_Freq <- round(Office_Freq$Count_Freq/sum(Office_Freq$Count_Freq),4)*100
Office_Freq <- subset(Office_Freq, (Office_Freq$Count_Freq != 0)&(Office_Freq$Percent_Freq!=0))
Office_Freq[,1:2] <- lapply(Office_Freq[,1:2], function(x) as.character(x))

Office_Freq$Office_Full <- ifelse(is.na(Office_Freq$OfficeName), Office_Freq$OfficeID, Office_Freq$OfficeName)



Office_Freq_top10Freq <- Office_Freq[order(-Office_Freq$Percent_Freq),]
Office_Freq_top10Freq <- Office_Freq_top10Freq[1:10, ]  #including NULL category
Office_Freq_top10Obli <- Office_Freq[order(-Office_Freq$Percent_Obli),]
Office_Freq_top10Obli <- Office_Freq_top10Obli[1:10, ]  #including NULL category

Office_Freq_TOP <- rbind(Office_Freq_top10Obli, Office_Freq_top10Freq)
Office_Freq_TOP <- unique(Office_Freq_TOP)  #17 records in total

#Generate a new name column by Combining officeID and officeName
Office_Freq_TOP$Office_Full <- ifelse(Office_Freq_TOP$Office_Full == Office_Freq_TOP$OfficeID, 
                                      Office_Freq_TOP$OfficeID, 
                                      paste(Office_Freq_TOP$OfficeID, 
                                            " - ", 
                                            Office_Freq_TOP$OfficeName))

Office_Freq_TOP$Office_Full <- factor(Office_Freq_TOP$Office_Full, 
                                      levels = rev(Office_Freq_TOP$Office_Full))
Office_Freq_TOP <- melt(Office_Freq_TOP, 
                        id = c("OfficeID", "OfficeName", "Count_Freq", "Office_Full"))

Office_barplot <- ggplot(data = Office_Freq_TOP,
                         aes(x = Office_Full, 
                             y = value,
                             fill = factor(variable))) +
                  geom_bar(stat = "identity", 
                  position = "dodge", 
                  width = 0.8) + 
                  coord_flip() +
                  xlab("") + 
                  ylab("") + 
                  theme_grey() + 
                  scale_fill_grey(labels = c("% of records", "% of obligation"),
                                  guide = guide_legend(reverse = TRUE)) + 
                  ggtitle("Percent of Frequency and obligation for Office") +
                  theme(text = element_text(size = 10), 
                        legend.title = element_blank(),
                        legend.position = "bottom",
                        legend.margin = margin(t=-0.8, r=0, b=0.5, l=0, unit = "cm"),
                        legend.text = element_text(margin = margin(r=0.5, unit = "cm")), 
                        plot.margin = margin(t=0.3, r=0.5, b=0, l=0.5, unit = "cm"))
Office_barplot
```

```{r frequancy and obligation percent grouped bar plot for agency}

#Percent grouped bar plot for variable Agency
#Generate new data frame containing frequency information
Agency_Freq <- as.data.frame(table(def_serv$Agency))
Agency_Freq$Percent_Freq <- round(Agency_Freq$Freq/sum(Agency_Freq$Freq),4)*100
colnames(Agency_Freq) <- c("Agency","Count_Freq","Percent_Freq")

#Add detail Agency description according to agency code
Agency_Lookup <- read.csv("https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/Agency_AgencyID.csv")
Agency_Lookup <- Agency_Lookup[,1:2]
colnames(Agency_Lookup) <- c("Agency","Agency_Description")
Agency_Freq <- left_join(Agency_Freq, Agency_Lookup, by = "Agency")
#Add obligation percent information to data frame
Percent_Obli <- c()
for (i in Agency_Freq$Agency) {
  Percent_Obligation <- round(sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$Agency == i], na.rm = TRUE)/sum(def_serv$Action_Obligation.OMB20_GDP18, na.rm = TRUE),5)
  Percent_Obli <- c(Percent_Obli, Percent_Obligation)
}
Agency_Freq$Agency_Description <- as.character(Agency_Freq$Agency_Description)
Agency_Freq$Percent_Obli <- Percent_Obli*100

#Get top 5 Agencies that take largest percent obligation
Agency_Freq <- Agency_Freq[order(-Percent_Obli),]
Agency_Freq <- Agency_Freq[1:5,]
percent_freq_rest <- 100 - sum(Agency_Freq$Percent_Freq, na.rm = TRUE)
percent_obli_rest <- 100 - sum(Agency_Freq$Percent_Obli, na.rm = TRUE)

Agency_Freq[6,] <- c("All Other", "NA", percent_freq_rest, "All Other", percent_obli_rest)
Agency_Freq$Agency_Description <- factor(Agency_Freq$Agency_Description, levels = rev(Agency_Freq$Agency_Description))
Agency_Freq[,c(3,5)] <- lapply(Agency_Freq[,c(3,5)], function(x) as.numeric(x))
Agency_Freq <- melt(Agency_Freq, id = c("Agency","Count_Freq", "Agency_Description"))

#Build grouped bar plot
Agency_barplot <- ggplot(data = Agency_Freq, 
                         aes(x = Agency_Description, 
                             y=value, 
                             fill=factor(variable))) + 
                  geom_bar(stat = "identity", 
                           position= "dodge", 
                           width = 0.8) + 
                  xlab("") + 
                  ylab("") + 
                  coord_flip() + 
                  theme_grey() +
                  scale_fill_grey(labels = c("% of records", "% of obligation"),
                                  guide = guide_legend(reverse = TRUE)) +
                  theme(legend.title = element_blank(),
                        legend.position = "bottom",
                        legend.margin = margin(t=-0.8, r=0, b=0.5, l=0, unit = "cm"),
                        legend.text = element_text(margin = margin(r=0.5, unit = "cm")),
                        plot.margin = margin(t=0.3, r=0.5, b=0, l=0.5, unit = "cm")) +
                 ggtitle("Top 5 of the most frequently appeared Agency") 
Agency_barplot                  

```

### Economic Sector
* NAICS is a factor reporting the top North American Industrial Classification Code of each contract. 
`r summary(def$NAICS);
NA_stats(def,"NAICS")`

#### NAICS 2
```{r NAICS2_Summary, fig.width=7.5 , fig.height=3}

# Add NAICS title
#def$NAICS_Code<-create_naics2(def$NAICS)
def$NAICS_Code<-def$NAICS2


def<-csis360::read_and_join(def,
                            lookup_file = "Lookup_NAICS_code.csv",
                            path="",
                            dir="Lookup\\",
                            by="NAICS_Code",
                            skip_check_var="NAICS_DESCRIPTION"
)

def$NAICS2_label<-paste(def$NAICS_Code,
                             def$NAICS_DESCRIPTION)

def$NAICS2_label[
  def$NAICS2_label==
    "56 Administrative and Support and Waste Management and Remediation Services"
  ]<-"56 Admin./Support/Waste Management and Remediation"
def$NAICS2_label[def$NAICS2_label==
                                    "NA NA"]<-"Unlabeled"

def$NAICS2_label<-factor(def$NAICS2_label)
order<-  rev(levels(def$NAICS2_label))


NAICS2digit<-ggplot(def,
       aes(x=NAICS2_label))+
  geom_bar()+coord_flip()+
  scale_y_continuous(label=scales::comma)+scale_x_discrete(limits=order)+
  labs(x="2-Digit NAICS Code",y="Number of Contracts and Task Orders in Unfiltered Dataset")

NAICS2digit
ggsave(NAICS2digit,file="..//Output\\NAICS2digitCount.png",width=10,height=6,dpi=600)
ggsave(NAICS2digit,file="..//Output\\NAICS2digitCount.eps",width=10,height=6,dpi=600)
```



```{r barplot for all NAICS2, 21 in total}
#Prepare data for plot
NAICS2_Freq <- as.data.frame(table(def_serv$NAICS2))
NAICS2_Freq$Percent_Freq <- round(NAICS2_Freq$Freq/sum(NAICS2_Freq$Freq),4)*100
colnames(NAICS2_Freq) <- c("NAICS_Code", "Count_Freq", "Percent_Freq")

#Get detail description for NAICS2 code
NAICS_Lookup <- read.csv(file = "https://raw.githubusercontent.com/CSISdefense/Vendor/master/Data/Clean/NAICS/Lookup_NAICS_code.csv")
colnames(NAICS_Lookup) <- c("NAICS_Code", "NAICS_DESCRIPTION")
NAICS2_Freq <- left_join(NAICS2_Freq, NAICS_Lookup, by = "NAICS_Code")
NAICS2_Freq <- NAICS2_Freq[order(-NAICS2_Freq$Percent_Freq),]
NAICS2_Freq$NAICS_DESCRIPTION <- factor(NAICS2_Freq$NAICS_DESCRIPTION, levels = rev(NAICS2_Freq$NAICS_DESCRIPTION))

Frequency_Plot2 <- ggplot(data = NAICS2_Freq,
                          aes(x = NAICS2_Freq$NAICS_DESCRIPTION, 
                              y = NAICS2_Freq$Percent_Freq)) +
                   geom_bar(stat = "identity", position = "dodge", width = 0.8) + 
                   coord_flip() +
                   xlab("") + 
                   ylab("Percent of Frequency") + 
                   theme_grey() + 
                   scale_fill_grey() + 
                   ggtitle("Percent of Frequency for NAICS2") +
                   theme(text = element_text(size = 10))
Frequency_Plot2
```

```{r grouped percent frequency/obligation barplot for all NAICS2, 21 in total}
#Prepare data for plot
NAICS2_Freq <- as.data.frame(table(def_serv$NAICS2))
NAICS2_Freq$Percent_Freq <- round(NAICS2_Freq$Freq/sum(NAICS2_Freq$Freq),4)*100
colnames(NAICS2_Freq) <- c("NAICS_Code", "Count_Freq", "Percent_Freq")

#Get detail description for NAICS2 code
NAICS2_Freq <- left_join(NAICS2_Freq, NAICS_Lookup, by = "NAICS_Code")

Percent_Obli <- c()
Total_Obli <- sum(def_serv$Action_Obligation.OMB20_GDP18, na.rm = TRUE)
for (i in NAICS2_Freq$NAICS_Code) {
  Percent_Obligation <- round(sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$NAICS2 == i], na.rm = TRUE)/Total_Obli,5)
  Percent_Obli <- c(Percent_Obli, Percent_Obligation)
}

NAICS2_Freq$Percent_Obli <- Percent_Obli * 100
NAICS2_Freq <- NAICS2_Freq[order(-NAICS2_Freq$Percent_Obli),]
NAICS2_Freq[,c(1,3)] <- lapply(NAICS2_Freq[,c(1,3)], function(x) as.character(x))
NAICS2_Freq$NAICS_DESCRIPTION <- paste(NAICS2_Freq$NAICS_Code, " - ", NAICS2_Freq$NAICS_DESCRIPTION)
NAICS2_Freq$NAICS_DESCRIPTION <- factor(NAICS2_Freq$NAICS_DESCRIPTION, levels = rev(NAICS2_Freq$NAICS_DESCRIPTION))
NAICS2_Freq <- melt(NAICS2_Freq, id = c("NAICS_Code", "Count_Freq","NAICS_DESCRIPTION"))
NAICS2_Freq$value <- as.numeric(NAICS2_Freq$value)

NAICS2_barplot <- ggplot(data = NAICS2_Freq,
                          aes(x = NAICS_DESCRIPTION, 
                              y = value,
                              fill = factor(variable))) +
                   geom_bar(stat = "identity", 
                            position = "dodge", 
                            width = 0.8) + 
                   coord_flip() +
                   xlab("") + 
                   ylab("") + 
                   theme_grey() + 
                   scale_fill_grey(labels = c("% records", "% obligation"),
                                  guide = guide_legend(reverse = TRUE)) + 
                   ggtitle("Percent of Frequency and obligation for NAICS2") +
                   theme(text = element_text(size = 10), 
                         legend.title = element_blank(),
                         legend.position = "bottom",
                         legend.margin = margin(t=-0.8, r=0, b=0.5, l=0, unit = "cm"),
                         legend.text = element_text(margin = margin(r=0.5, unit = "cm")),
                         plot.margin = margin(t=0.3, r=0.5, b=0, l=0.5, unit = "cm"))
NAICS2_barplot
```


#### NAICS 3

centered_log_description(def$l_def3_obl_lag1,"obligations")
centered_log_description(def$l_def6_obl_lag1,"obligations")
NA_stats(def,"l_def3_obl_lag1")

centered_log_description(def$l_def3_ratio_lag1,"obligations")

NA_stats(def,"cl_def3_ratio_lag1")

```{r NAICS3_Summary, fig.width=7.5 , fig.height=3}
NAICS_summary<-def_serv %>% group_by(NAICS3,StartCY,def3_HHI_lag1,def3_obl_lag1,def3_ratio_lag1,US3_avg_sal_lag1) %>%
  dplyr::summarise(annual_action_obligation=sum(Action_Obligation.OMB20_GDP18),
                   annual_count=length(StartCY)) 

top_NAICS <- NAICS_summary %>% group_by(NAICS3) %>% 
  dplyr::summarise(naics_action_obligation=sum(annual_action_obligation),
                   naics_count=sum(annual_count)) 
top_NAICS$naics_dollar_rank<-rank(-top_NAICS$naics_action_obligation)
top_NAICS$naics_count_rank<-rank(-top_NAICS$naics_count)


NAICS_summary<-left_join(NAICS_summary,top_NAICS, by="NAICS3")

colnames(NAICS_summary)[colnames(NAICS_summary)=="NAICS3"]<-"principalnaicscode"

NAICS_summary$principalnaicscode<-as.character(NAICS_summary$principalnaicscode)
NAICS_summary<-as.data.frame(NAICS_summary)
NAICS_summary<-read_and_join_experiment(NAICS_summary,
                                                 lookup_file = "Lookup_PrincipalNAICScode.csv",
                                                 path="https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/",
                                                 dir="economic/",
                                                 by="principalnaicscode",
                                                 skip_check_var=c("principalnaicscodeText",
                                                                  "NAICS_shorthand",
                                                                  "principalNAICS4DigitCode")
)

# https://stackoverflow.com/questions/37174316/how-to-fit-long-text-into-ggplot2-facet-titles



# View(NAICS_summary)
NAICS_summary$NAICS_shorthand<-swr(NAICS_summary$NAICS_shorthand,nwrap = 25)
NAICS_summary$CY<-NAICS_summary$StartCY-1
NAICS3top<-ggplot(subset(NAICS_summary,naics_dollar_rank<=4 |
                          naics_count_rank<=4),
       aes(x=CY,y=def3_HHI_lag1))+#color=NAICS_Code
  geom_line()+
  scale_y_continuous(label=scales::comma)+ 
  # scale_x_continuous(breaks=c(2006,2009,2011,2014))+
  labs(x="Calendar Year",y="Herfindahl-Herschman Index")+ 
  geom_hline(yintercept=c(1500,2500),linetype="dotted")

NAICS3top_paper<-NAICS3top+ facet_wrap(~NAICS_shorthand,ncol=2)
ggsave(NAICS3top_paper,file="..\\Output\\NAICS3top.png",width=4,height=8,dpi=600)
ggsave(NAICS3top_paper,file="..\\Output\\NAICS3top.eps",width=4,height=8,dpi=600)

NAICS3top_pp<-NAICS3top+ facet_wrap(~NAICS_shorthand,ncol=4)
NAICS3top_pp
ggsave(NAICS3top_pp,file="..\\Output\\NAICS3top_pp.png",width=10.5,height=5.5,dpi=600)
ggsave(NAICS3top_pp,file="..\\Output\\NAICS3top_pp.eps",width=10.5,height=5.5,dpi=600)

summary(NAICS_summary$naics_count_rank)


NAICS_summary$NAICS_shorthand<-swr(NAICS_summary$NAICS_shorthand,nwrap = 16)
# NAICS_summary$CY<-factor(paste("'",substring(as.character(NAICS_summary$CY),3,4),sep=""))

NAICS3top8<-ggplot(subset(NAICS_summary,naics_dollar_rank<=8),
       aes(x=CY,y=def3_HHI_lag1))+#color=NAICS_Code
  geom_line()+
  scale_y_continuous(label=scales::comma)+ 
  scale_x_continuous(breaks=c(2007,2012))+
  labs(x="Calendar Year",y="Herfindahl-Herschman Index")+ 
  geom_hline(yintercept=c(1500,2500),linetype="dotted")

NAICS3top8_wide<-NAICS3top8+ facet_grid(.~NAICS_shorthand)
ggsave(NAICS3top8_wide,file="..\\Output\\NAICS3top8.png",width=9.5,height=4,dpi=600)
ggsave(NAICS3top8_wide,file="..\\Output\\NAICS3top8.eps",width=9.5,height=4,dpi=600)

colnames(NAICS_summary)
NAICS_long<-NAICS_summary[,colnames(NAICS_summary) %in% c( "principalnaicscode",
                                                    "def3_HHI_lag1",
                                                    "def3_obl_lag1",
                                                    "def3_ratio_lag1",
                                                    # "US3_avg_sal_lag1",
                                                    "naics_dollar_rank" ,
                                                    "naics_count_rank",
                                                    "principalnaicscodeText",
                                                     "NAICS_shorthand",
                                                    "CY")]
NAICS_long<-melt(NAICS_long, id=c("principalnaicscode","naics_dollar_rank","naics_count_rank","principalnaicscodeText","CY", "NAICS_shorthand"))



#Drop the ratios and average salaries w/ unique values
# NAICS_long<-NAICS_long[NAICS_long$variable %in% c(),]


levels(NAICS_long$variable)<- list("Herfindahl-\nHerschman Index"=c("def3_HHI_lag1"),
                                   "Defense Obligations"=c("def3_obl_lag1"),
                                   "Defense Obligations\nto U.S. Revenue Ratio"=c("def3_ratio_lag1"))

NAICS_long$high<-2500
NAICS_long$high[NAICS_long$variable!="Herfindahl-\nHerschman Index"]<-NA
NAICS_long$low<-1500
NAICS_long$low[NAICS_long$variable!="Herfindahl-\nHerschman Index"]<-NA


NAICS3long<-ggplot(subset(NAICS_long,naics_dollar_rank<=8),
       aes(x=CY,y=value))+#color=NAICS_Code
  geom_line()+
  scale_y_continuous(label=scales::comma)+ 
  scale_x_continuous(breaks=c(2007,2012))+
  labs(x="Calendar Year",y="Detailed Industry Metric")+
  geom_hline(aes(
           yintercept=high),linetype="dotted")+
  geom_hline(aes(
           yintercept=low),linetype="dotted")    



NAICS3long_wide<-NAICS3long+ facet_grid(variable~NAICS_shorthand,scales="free_y")
ggsave(NAICS3long_wide,file="..\\Output\\NAICS3long.png",width=9.5,height=5.5,dpi=600)
ggsave(NAICS3long_wide,file="..\\Output\\NAICS3long.eps",width=9.5,height=5.5,dpi=600)

write.csv(NAICS_summary,file="..\\Output/NAICS3_summary.csv",row.names = FALSE)
```






```{r grouped barplot for variable NAICS3}
Frequency <- as.data.frame(table(def_serv$NAICS3))
Frequency[["Percent_Freq"]] <- round(Frequency[["Freq"]]/sum(Frequency[["Freq"]]),4)*100
colnames(Frequency) <- c("NAICS3", "Count_Freq", "Percent_Freq")
Percent_Obli <- c()
for (i in Frequency[["NAICS3"]]) {
  Percent_Obligation <- round(sum(def_serv[["Action_Obligation.OMB20_GDP18"]][def_serv$NAICS3 == i], na.rm = TRUE)/sum(def_serv[["Action_Obligation.OMB20_GDP18"]], na.rm = TRUE),5)
    Percent_Obli <- c(Percent_Obli, Percent_Obligation)
  }
Frequency[["Percent_Obli"]] <- Percent_Obli*100
NAICS3_Freq <- Frequency

#Add detail description to unique NAICS3 code
NAICS3_Freq <- left_join(NAICS3_Freq, NAICS_Lookup, by = c("NAICS3"="NAICS_Code"))
colnames(NAICS3_Freq)[colnames(NAICS3_Freq)=="NAICS_DESCRIPTION"]<-"Description"
NAICS3_Freq$Description <- as.character(NAICS3_Freq$Description)
NAICS3_Freq$Description <- paste(NAICS3_Freq$NAICS, " - ", NAICS3_Freq$Description)

#Get the top 15 most frequently appeared NAICS3
NAICS3_Freq_top10Freq <- NAICS3_Freq[order(-NAICS3_Freq$Percent_Freq),]
NAICS3_Freq_top10Freq <- NAICS3_Freq_top10Freq[1:10, ]   
NAICS3_Freq_top10Obli <- NAICS3_Freq[order(-NAICS3_Freq$Percent_Obli),]
NAICS3_Freq_top10Obli <- NAICS3_Freq_top10Obli[1:10, ]
NAICS3_Freq_TOP <- rbind(NAICS3_Freq_top10Obli, NAICS3_Freq_top10Freq)
NAICS3_Freq_TOP <- unique(NAICS3_Freq_TOP)  #15 records in total
NAICS3_Freq_TOP <- NAICS3_Freq_TOP[order(-NAICS3_Freq_TOP$Percent_Obli),]
NAICS3_Freq_TOP$Description <- factor(NAICS3_Freq_TOP$Description, rev(NAICS3_Freq_TOP$Description))

#Reshape the dataframe to long format for plot
NAICS3_Freq_TOP <- melt(NAICS3_Freq_TOP, id = c("NAICS3", "Count_Freq", "Description"))

#Generate the plot and add title manually
part_grouped_barplot("NAICS3", NAICS3_Freq_TOP) + ggtitle("Top 15 of the most frequently appeared NAICS3")
```



#### NAICS 6

centered_log_description(def_serv$US6_avg_sal_lag1Const,"dollars")
NA_stats(def_serv,"cl_US6_avg_sal_lag1Const")

NA_stats(def,"l_def6_obl_lag1")
def$l_def6_ratio_lag1[is.nan(def$l_def6_ratio_lag1) | is.infinite(def$l_def6_ratio_lag1)]<-NA
def$cl_def6_ratio_lag1[is.nan(def$cl_def6_ratio_lag1) | is.infinite(def$cl_def6_ratio_lag1)]<-NA
centered_log_description(def$l_def6_ratio_lag1,"obligations")
<!-- centered_log_description(def$l_def6_ratio_lag1) -->
NA_stats(def,"cl_def6_ratio_lag1")

centered_log_description(def$l_US6_avg_sal_lag1,"dollars")
NA_stats(def,"cl_US6_avg_sal_lag1")


```{r NAICS6_Summary, fig.width=7.5 , fig.height=3}
NAICS_summary<-def_serv %>% group_by(NAICS,StartCY,def6_HHI_lag1,def6_obl_lag1,def6_ratio_lag1,US6_avg_sal_lag1) %>%
  dplyr::summarise(annual_action_obligation=sum(Action_Obligation.OMB20_GDP18),
                   annual_count=length(StartCY)) 

top_NAICS <- NAICS_summary %>% group_by(NAICS) %>% 
  dplyr::summarise(naics_action_obligation=sum(annual_action_obligation),
                   naics_count=sum(annual_count)) 
top_NAICS$naics_dollar_rank<-rank(-top_NAICS$naics_action_obligation)
top_NAICS$naics_count_rank<-rank(-top_NAICS$naics_count)


NAICS_summary<-left_join(NAICS_summary,top_NAICS, by="NAICS")

colnames(NAICS_summary)[colnames(NAICS_summary)=="NAICS"]<-"principalnaicscode"

NAICS_summary$principalnaicscode<-as.character(NAICS_summary$principalnaicscode)
NAICS_summary<-as.data.frame(NAICS_summary)


NAICS_summary<-read_and_join_experiment(NAICS_summary,
                                                 lookup_file = "Lookup_PrincipalNAICScode.csv",
                                                 path="https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/",
                                                 dir="economic/",
                                                 by="principalnaicscode",
                                                 skip_check_var=c("principalnaicscodeText",
                                                                  "NAICS_shorthand",
                                                                  "principalNAICS4DigitCode")

)

summary(NAICS_summary$NAICS_shorthand)

# View(NAICS_summary)
NAICS_summary$NAICS_shorthand<-swr(NAICS_summary$NAICS_shorthand,nwrap = 25)
NAICS_summary$CY<-NAICS_summary$StartCY-1
NAICS6top<-ggplot(subset(NAICS_summary,naics_dollar_rank<=4 |
                          naics_count_rank<=4),
       aes(x=CY,y=def6_HHI_lag1))+#color=NAICS_Code
  geom_line()+
  scale_y_continuous(label=scales::comma)+ 
  # scale_x_continuous(breaks=c(2006,2009,2011,2014))+
  labs(x="Calendar Year",y="Herfindahl-Herschman Index")+ 
  geom_hline(yintercept=c(1500,2500),linetype="dotted")

NAICS6top_paper<-NAICS6top+ facet_wrap(~NAICS_shorthand,ncol=2)
ggsave(NAICS6top_paper,file="..\\Output\\NAICS6top.png",width=4,height=8,dpi=600)
ggsave(NAICS6top_paper,file="..\\Output\\NAICS6top.eps",width=4,height=8,dpi=600)

NAICS6top_pp<-NAICS6top+ facet_wrap(~NAICS_shorthand,ncol=4)
NAICS6top_pp
ggsave(NAICS6top_pp,file="..\\Output\\NAICS6top_pp.png",width=10.5,height=5.5,dpi=600)
ggsave(NAICS6top_pp,file="..\\Output\\NAICS6top_pp.eps",width=10.5,height=5.5,dpi=600)

summary(NAICS_summary$naics_count_rank)


NAICS_summary$NAICS_shorthand<-swr(NAICS_summary$NAICS_shorthand,nwrap = 16)
# NAICS_summary$CY<-factor(paste("'",substring(as.character(NAICS_summary$CY),3,4),sep=""))

NAICS6top8<-ggplot(subset(NAICS_summary,naics_dollar_rank<=8),
       aes(x=CY,y=def6_HHI_lag1))+#color=NAICS_Code
  geom_line()+
  scale_y_continuous(label=scales::comma)+ 
  scale_x_continuous(breaks=c(2007,2012))+
  labs(x="Calendar Year",y="Herfindahl-Herschman Index")+ 
  geom_hline(yintercept=c(1500,2500),linetype="dotted")

NAICS6top8_wide<-NAICS6top8+ facet_grid(.~NAICS_shorthand)
ggsave(NAICS6top8_wide,file="..\\Output\\NAICS6top8.png",width=9.5,height=4,dpi=600)
ggsave(NAICS6top8_wide,file="..\\Output\\NAICS6top8.eps",width=9.5,height=4,dpi=600)


colnames(NAICS_summary)
NAICS_long<-NAICS_summary[,colnames(NAICS_summary) %in% c( "principalnaicscode",
                                                    "def6_HHI_lag1",
                                                    "def6_obl_lag1",
                                                    "def6_ratio_lag1",
                                                    # "US6_avg_sal_lag1",
                                                    "naics_dollar_rank" ,
                                                    "naics_count_rank",
                                                    "principalnaicscodeText",
                                                     "NAICS_shorthand",
                                                    "CY")]
NAICS_long<-melt(NAICS_long, id=c("principalnaicscode","naics_dollar_rank","naics_count_rank","principalnaicscodeText","CY", "NAICS_shorthand"))



#Drop the ratios and average salaries w/ unique values
# NAICS_long<-NAICS_long[NAICS_long$variable %in% c(),]


levels(NAICS_long$variable)<- list("Herfindahl-\nHerschman Index"=c("def6_HHI_lag1"),
                                   "Defense Obligations"=c("def6_obl_lag1"),
                                   "Defense Obligations\nto U.S. Revenue Ratio"=c("def6_ratio_lag1"))

NAICS_long$high<-2500
NAICS_long$high[NAICS_long$variable!="Herfindahl-\nHerschman Index"]<-NA
NAICS_long$low<-1500
NAICS_long$low[NAICS_long$variable!="Herfindahl-\nHerschman Index"]<-NA


NAICS6long<-ggplot(subset(NAICS_long,naics_dollar_rank<=8),
       aes(x=CY,y=value))+#color=NAICS_Code
  geom_line()+
  scale_y_continuous(label=scales::comma)+ 
  scale_x_continuous(breaks=c(2007,2012))+
  labs(x="Calendar Year",y="Detailed Industry Metric")+
  geom_hline(aes(
           yintercept=high),linetype="dotted")+
  geom_hline(aes(
           yintercept=low),linetype="dotted")    



NAICS6long_wide<-NAICS6long+ facet_grid(variable~NAICS_shorthand,scales="free_y")
ggsave(NAICS6long_wide,file="..\\Output\\NAICS6long.png",width=9.5,height=5.5,dpi=600)
ggsave(NAICS6long_wide,file="..\\Output\\NAICS6long.eps",width=9.5,height=5.5,dpi=600)

write.csv(NAICS_summary,file="..\\Output/NAICS6_summary.csv",row.names = FALSE)
```

```{r barplot for top 20 most frequently appeared NAICS}
#Prepare dateframe for plot
NAICS_Freq <- as.data.frame(table(def_serv$NAICS))
NAICS_Freq <- NAICS_Freq[order(-NAICS_Freq$Freq),]
NAICS_Freq_TOP20 <- NAICS_Freq[1:20,]   #Get top 20 NAICS has largest frequency count
NAICS_Freq_TOP20$Percent_Freq <- round(NAICS_Freq_TOP20$Freq/sum(NAICS_Freq$Freq),4)*100
colnames(NAICS_Freq_TOP20) <- c("NAICS_Code", "Count_Freq", "Percent_Freq")

#Get detail description for each NAICS code
NAICS_Freq_TOP20 <- left_join(NAICS_Freq_TOP20, NAICS_Lookup, by = "NAICS_Code")
NAICS_Freq_TOP20 <- NAICS_Freq_TOP20[order(-NAICS_Freq_TOP20$Percent_Freq),]
NAICS_Freq_TOP20$NAICS_DESCRIPTION <- factor(NAICS_Freq_TOP20$NAICS_DESCRIPTION, levels = rev(NAICS_Freq_TOP20$NAICS_DESCRIPTION))


Frequency_Plot <- ggplot(data = NAICS_Freq_TOP20, 
                         aes(x = NAICS_Freq_TOP20$NAICS_DESCRIPTION, 
                             y = NAICS_Freq_TOP20$Percent_Freq)) +
                  geom_bar(stat = "identity", position = "dodge", width = 0.8) + 
                  coord_flip() +
                  xlab("") + 
                  ylab("Percent of Frequency") + 
                  theme_grey() + 
                  scale_fill_grey() + 
                  ggtitle("Top 20 of the most frequently appeared NAICS") +
                  theme(text = element_text(size = 10))
Frequency_Plot
```

```{r grouped barplot for NAICS most frequency appeared/has the largest percent obligation }
#Percent frequency/obligation grouped bar plot for variable NAICS
#Prepare dateframe for plot
NAICS_Freq <- def_serv %>% group_by(NAICS) %>% summarise(
  Count_Freq=length(CSIScontractID),
  Action_Obligation.OMB20_GDP18=sum(Action_Obligation.OMB20_GDP18)
)
  
  # NAICS_Freq <- NAICS_Freq[order(-NAICS_Freq$Freq),]
# NAICS_Freq_TOP20 <- NAICS_Freq[1:20,]   #Get top 20 NAICS has largest frequency count
NAICS_Freq$Percent_Freq <- round(NAICS_Freq$Count_Freq/
                                   sum(NAICS_Freq$Count_Freq),4)*100
NAICS_Freq$Percent_Obli <- round(NAICS_Freq$Action_Obligation.OMB20_GDP18/
                                         sum(NAICS_Freq$Action_Obligation.OMB20_GDP18),4)*100

colnames(NAICS_Freq)[colnames(NAICS_Freq)=="NAICS"] <- "NAICS_Code"
NAICS_Freq$NAICS_Code<-factor(NAICS_Freq$NAICS_Code)

#Get detail description for each NAICS code
NAICS_Freq <- left_join(NAICS_Freq, NAICS_Lookup, by = "NAICS_Code")
NAICS_Freq <- NAICS_Freq[order(-NAICS_Freq$Percent_Freq),]
NAICS_Freq$NAICS_DESCRIPTION <- factor(NAICS_Freq$NAICS_DESCRIPTION, levels = rev(NAICS_Freq$NAICS_DESCRIPTION))




memory.limit(56000)


NAICS_Freq_top10Freq <- NAICS_Freq[order(-NAICS_Freq$Percent_Freq),]
NAICS_Freq_top10Freq <- NAICS_Freq_top10Freq[1:10, ]
NAICS_Freq_top10Obli <- NAICS_Freq[order(-NAICS_Freq$Percent_Obli),]
NAICS_Freq_top10Obli <- NAICS_Freq_top10Obli[1:10, ]

NAICS_Freq_TOP <- rbind( NAICS_Freq_top10Obli, NAICS_Freq_top10Freq)
NAICS_Freq_TOP <- unique(NAICS_Freq_TOP)  #18 records in total
NAICS_Freq_TOP[,c(1,4)] <- lapply(NAICS_Freq_TOP[,c(1,4)], function(x) as.character(x))
NAICS_Freq_TOP$NAICS_DESCRIPTION <- paste(NAICS_Freq_TOP$NAICS_Code, " - ", NAICS_Freq_TOP$NAICS_DESCRIPTION)

NAICS_Freq_TOP$NAICS_DESCRIPTION <- factor(NAICS_Freq_TOP$NAICS_DESCRIPTION, levels = rev(NAICS_Freq_TOP$NAICS_DESCRIPTION))
NAICS_Freq_TOP <- melt(NAICS_Freq_TOP, id = c("NAICS_Code","Count_Freq","NAICS_DESCRIPTION"))
#NAICS_Freq_TOP <- merge(NAICS_Freq_top20Freq, NAICS_Freq_top20Obli, by= "NAICS_Code", all=TRUE)

(
NAICS_barPlot <- ggplot(data = NAICS_Freq_TOP, 
                         aes(x = NAICS_DESCRIPTION, 
                             y = value,
                             fill = factor(variable))) +
                  geom_bar(stat = "identity", position = "dodge", width = 0.8) + 
                  coord_flip() +
                  xlab("") + 
                  ylab("") + 
                  theme_grey() + 
                  scale_fill_grey(labels = c("% records", "% obligation"),
                                  guide = guide_legend(reverse = TRUE)) + 
                  ggtitle("Top 18 of the most frequently appeared NAICS") +
                  theme(text = element_text(size = 10),
                        legend.title = element_blank(),
                        legend.position = "bottom",
                        legend.margin = margin(t=-0.8, r=0, b=0.5, l=0, unit = "cm"),
                        legend.text = element_text(margin = margin(r=0.5, unit = "cm")),
                        plot.margin = margin(t=0.3, r=0.5, b=0, l=0.5, unit = "cm"))
)
```



# Missing Data Measures
```{r Sample}

 # load(file="data//def_sample.Rdata")

summary(def_serv$b_Term)
summary(def_serv$b_CBre)
summary(def_serv$lp_OptGrowth) #Missing
summary(def_serv$ExercisedOptions)
summary(def_serv$AnyUnmodifiedUnexercisedOptions)
#Study Variables
summary(def_serv$cl_US6_avg_sal_lag1Const)
summary(def_serv$cl_CFTE)
summary(def_serv$c_pPBSC)
summary(def_serv$c_pOffPSC)
summary(def_serv$c_pairHist)
summary(def_serv$cl_pairCA)
#Controls
summary(def_serv$CompOffr)
summary(def_serv$cl_Offr)
summary(def_serv$cl_Ceil)
summary(def_serv$cl_Days)
summary(def_serv$Veh) 
summary(def_serv$PricingUCA)
summary(def_serv$PlaceCountryISO3)
summary(def_serv$NAICS)
summary(def_serv$NAICS3)
summary(def_serv$Office)
summary(def_serv$Agency)
summary(def_serv$StartCY)
summary(def_serv$cl_def3_HHI_lag1)
summary(def_serv$cl_def3_ratio_lag1)
summary(def_serv$cl_def6_HHI_lag1)
summary(def_serv$cl_def6_obl_lag1)
summary(def_serv$cl_def6_ratio_lag1)
#New Controls
summary(def_serv$cl_OffCA)
summary(def_serv$cl_OffCA)
summary(def_serv$c_pMarket)
summary(def_serv$Crisis)


complete<-
  #Dependent Variables
  !is.na(def_serv$b_Term)& #summary(def_serv$b_Term)
  !is.na(def_serv$b_CBre)&
  !is.na(def_serv$lp_OptGrowth)&
  !is.na(def_serv$ExercisedOptions)&
  !is.na(def_serv$AnyUnmodifiedUnexercisedOptions)&
  #Study Variables
  !is.na(def_serv$cl_US6_avg_sal_lag1Const)&
  !is.na(def_serv$cl_CFTE)&
  !is.na(def_serv$c_pPBSC)&
  !is.na(def_serv$c_pOffPSC)&
  !is.na(def_serv$c_pairHist)&
  !is.na(def_serv$cl_pairCA)&
  #Controls
  !is.na(def_serv$CompOffr)&
  !is.na(def_serv$cl_Offr)&
  !is.na(def_serv$cl_Ceil)&
  !is.na(def_serv$cl_Days)&
  !is.na(def_serv$Veh) &
  !is.na(def_serv$PricingUCA)&
  !is.na(def_serv$PlaceCountryISO3)& #New Variable
  # !is.na(def_serv$b_UCA)& No longer  used
  !is.na(def_serv$NAICS)&
  !is.na(def_serv$NAICS3)&
  !is.na(def_serv$Office)&
  !is.na(def_serv$Agency)&
  !is.na(def_serv$StartCY)&
  !is.na(def_serv$cl_def3_HHI_lag1)&
  !is.na(def_serv$cl_def3_ratio_lag1)&
  !is.na(def_serv$cl_def6_HHI_lag1)&
  !is.na(def_serv$cl_def6_obl_lag1Const)&
  !is.na(def_serv$cl_def6_ratio_lag1)&
  #New Controls
  !is.na(def_serv$cl_OffCA)& #summary(def_serv$cl_OffCA)
  !is.na(def_serv$cl_OffVol)& #summary(def_serv$cl_OffVol)
  !is.na(def_serv$c_pMarket)&  #summary(def_serv$c_pMarket)
  !is.na(def_serv$Crisis)  #summary(def_serv$c_pMarket)




summary(complete)
summary(def_serv$Action_Obligation.OMB20_GDP18)
money<-def_serv$Action_Obligation.OMB20_GDP18
any(def_serv$Action_Obligation.OMB20_GDP18<0)
money[def_serv$Action_Obligation.OMB20_GDP18<0]<-0
sum(def_serv$Action_Obligation.OMB20_GDP18[def_serv$Action_Obligation.OMB20_GDP18<0])

#Overall
length(money[!complete])/length(money)
sum(money[!complete],na.rm=TRUE)/sum(money,na.rm=TRUE)

#What portion of contracts have potential options, 
sum(money[def_serv$AnyUnmodifiedUnexercisedOptions==1],na.rm=TRUE)/
  sum(money,na.rm=TRUE)


#Missing data, how many records
nrow(def_serv[!complete,])/nrow(def_serv)
sum(def_serv[!complete,]$Action_Obligation.OMB20_GDP18.OMB20,na.rm=TRUE)/sum(def_serv$Action.Obligation.OMB20_GDP18,na.rm=TRUE)

#Missing data how much money?
length(money[!complete&def_serv$AnyUnmodifiedUnexercisedOptions==1])/
  length(money[def_serv$AnyUnmodifiedUnexercisedOptions==1])
sum(money[!complete&def_serv$AnyUnmodifiedUnexercisedOptions==1],na.rm=TRUE)/
  sum(money[def_serv$AnyUnmodifiedUnexercisedOptions==1],na.rm=TRUE)




```
