---
title: "Defense Acquisition Trends"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, October 6, 2021"
---

# Setup
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40
if(!exists("full_data"))
  load(file="FPDS_chart_maker//unaggregated_FPDS.Rda")

disa_data<- full_data %>% filter(ContractingSubCustomer=="DISA")
load(file=file.path("..","data","semi_clean","disa.Rda"))

disa_sum<-read_and_join_experiment(data=disa_sum
                                   ,"InformationTechnologyCommercialItemCategory.csv"
                                   ,path="https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/"
                                   ,dir="productorservice/"
                                   ,by=c("informationtechnologycommercialitemcategory"="informationtechnologycommercialitemcategory")
                                   # ,new_var_checked=FALSE
                                   # ,create_lookup_rdata=TRUE
                                   # ,col_types="dddddddddccc"
) 

disa_data$PricingUCA.sumlong<-disa_data$PricingUCA.sum
levels(disa_data$PricingUCA.sumlong)<-list("Firm-Fixed-Price"="FFP",
                                           "Less Common"="Less Common",
                                           "Incentive"="Incentive",
                                           "Other Cost-Based"="Other CB",
                                           "Undefinitized\nContract Award"="UCA",
                                           "Unclear"="Unclear"   )

ds_lc<-prepare_labels_and_colors(disa_sum,path="K:\\Users\\Greg\\Repositories\\Lookup-Tables\\style\\")
ds_ck<-csis360::get_column_key(disa_sum,path="K:\\Users\\Greg\\Repositories\\Lookup-Tables\\style\\")



```

# DISA
```{r DISAspecific}
disa_sum <- deflate(disa_sum,money_var="Action_Obligation_Then_Year",fy_var="fiscal_year",deflator_var="OMB20_GDP20")
colnames(disa_sum)[colnames(disa_sum)=="Action_Obligation_Then_Year_Then_Year"]<-"Action_Obligation_Then_Year"
colnames(disa_sum)[colnames(disa_sum)=="Action_Obligation_Then_Year_OMB20_GDP20"]<-"Action_Obligation_OMB20_GDP20"


disa_sum$ServicesCategory.detail
levels(factor(disa_sum$ServicesCategory.detail))
disa_sum$ServicesCategory.sum<-factor(disa_sum$ServicesCategory.detail)
levels(disa_sum$ServicesCategory.sum)<-list("ICT" ="ICT" ,
                                      "PAMS"  ="PAMS"  ,
                                      "Other Services and R&D"=c("Other Services","ERS","FRS&C","Fuels","MED","R&D"),
                                      "Products"="Products",
                                       "Unlabeled"= "Unlabeled")

## DISA Competition
```{r DISAComp}
disa_data$ServicesCategory.sum<-factor(disa_data$ServicesCategory.detail)
levels(disa_data$ServicesCategory.sum)<-list("ICT" ="ICT" ,
                                      "PAMS"  ="PAMS"  ,
                                      "Other Services and R&D"=c("Other Services","ERS","FRS&C","Fuels","MED","R&D"),
                                      # ""="R&D",
                                      "Products"="Products",
                                       "Unlabeled"= "Unlabeled")

disa_sum<-disa_sum[,!colnames(disa_sum) %in% c("ContractingSubCustomer")]
colnames(disa_sum)[colnames(disa_sum)=="SubCustomer"]<-"ContractingSubCustomer"
disa_sum$FundingAgency[disa_sum$fundingrequestingagencyid=="955P"]<-"DHS"
disa_sum<-read_and_join_experiment(disa_sum,
                            path="https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/",
                            "Agency_AgencyID.csv",
                            dir="",
                            by=c("fundingrequestingagencyid"="AgencyID"),
                            add_var=c("SubCustomer"),#Contracting.Agency.ID
                            skip_check_var=c("Platform","SubCustomer"),
                            guess_max=2000)

colnames(disa_sum)[colnames(disa_sum)=="SubCustomer"]<-"SubFunder"
disa_sum<-replace_nas_with_unlabeled(disa_sum,"SubFunder","Uncategorized")
disa_sum<-csis360::read_and_join_experiment(disa_sum,
                                             "SubCustomer.csv",
                                             by=c("FundingAgency"="Customer","SubFunder"="SubCustomer"),
                                             add_var=c("SubCustomer.platform","SubCustomer.sum"),
                                             path="https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/",
                                             dir="office/",
                                            case_sensitive = FALSE
)
disa_sum<-disa_sum[,!colnames(disa_sum) %in% c("FundingSubAgency.platform","FundingSubAgency.sum")]
colnames(disa_sum)[colnames(disa_sum)=="SubCustomer.platform"]<-"FundingSubAgency.platform"
colnames(disa_sum)[colnames(disa_sum)=="SubCustomer.sum"]<-"FundingSubAgency.sum"

summary(factor(disa_sum$FundingSubAgency.sum))
disa_sum$Funder<-disa_sum$FundingAgency

disa_sum$Funder[disa_sum$FundingAgency =="Defense" & !is.na(disa_sum$FundingAgency)& !is.na(disa_sum$FundingSubAgency.sum)]<-
  disa_sum$FundingSubAgency.sum[disa_sum$FundingAgency =="Defense" & !is.na(disa_sum$FundingAgency) & !is.na(disa_sum$FundingSubAgency.sum)]
disa_sum$Funder[disa_sum$FundingAgency!= "Defense"]<-"Other than DoD"
disa_sum$Funder[disa_sum$FundingSubAgency=="DISA"]<-"DISA"
disa_sum$FunderDISA<-ifelse(disa_sum$FundingSubAgency=="DISA","DISA","Other than DISA")
disa_sum %>% group_by(FundingAgency ) %>% summarise(Action_Obligation_OMB20_GDP20=sum(Action_Obligation_OMB20_GDP20,na.rm=TRUE))
disa_sum %>% group_by(Funder ) %>% summarise(Action_Obligation_OMB20_GDP20=sum(Action_Obligation_OMB20_GDP20,na.rm=TRUE))


disa_sum$Office<-factor(disa_sum$ContractingOfficeID)
levels(disa_sum$Office)<-list("Telecomm Div.\n(HC1013)"="HC1013",
                              "IT Contracting PL83\n(HC1028)"="HC1028" ,
                              "IT Contracting PL84\n(HC1084)"="HC1084" ,
                              "DITCO-PAC\n(HC1019)"="HC1019" ,
                              "DITCO-Europe\n(HC1021)"="HC1021",
                              "DITCO-Alaska\n(HC1022)"="HC1022",
                              "DISA-Ft. Meade\n(HC1046)"="HC1046", 
                              "DISA-Ft. Meade\n(HC1047)"="HC1047", 
                              "J7 White House Comm\n(HC1064)"="HC1064",                              
                              "ZD10"=c("ZD10"   ,"ZD10 "),
                              "ZD11"=c("ZD11"   ,"ZD11 "),
                              "ZD13"=c("ZD13"="ZD13 "),
                              "ZD14"=c("ZD14"="ZD14 "),
                              "ZD15"=c("ZD15"="ZD15 "))
disa_sum$OfficeLoc<-factor(disa_sum$ContractingOfficeID)
levels(disa_sum$OfficeLoc)<-list("Scott AFB"=c("HC1013","HC1028","HC1084"),
                                "Fort Meade"=c("HC1046","HC1047"),
                              "Pearl Harbor"="HC1019" ,
                              "Europe"="HC1021",
                              "Alaska"="HC1022",
                              "Washington, DC"="HC1064",
                              "ZD10"=c("ZD10"   ,"ZD10 "),
                              "ZD11"=c("ZD11"   ,"ZD11 "),
                              "ZD13"=c("ZD13"="ZD13 "),
                              "ZD14"=c("ZD14"="ZD14 "),
                              "ZD15"=c("ZD15"="ZD15 "))
disa_sum$OfficeScott<-factor(disa_sum$ContractingOfficeID)
levels(disa_sum$OfficeScott)<-list("Scott AFB"=c("HC1013","HC1028","HC1084"),
                                "All Other"=c("HC1046","HC1047","HC1019" ,"HC1021","HC1022","HC1064"),
                              "ZD10"=c("ZD10"   ,"ZD10 "),
                              "ZD11"=c("ZD11"   ,"ZD11 "),
                              "ZD13"=c("ZD13"="ZD13 "),
                              "ZD14"=c("ZD14"="ZD14 "),
                              "ZD15"=c("ZD15"="ZD15 "))

disa_sum$OfficeSum<-factor(disa_sum$ContractingOfficeID)
levels(disa_sum$OfficeSum)<-list("Telecomm Div."="HC1013",
                              "IT Contracting PL83"="HC1028" ,
                              "IT Contracting PL84"="HC1084" ,
                              "DITCO OCONUS"=c("HC1019" ,"HC1021","HC1022"),
                                "DISA Fort Meade"=c("HC1046","HC1047"),
                              "J7 White House Comm."="HC1064",
                              "ZD10"=c("ZD10"   ,"ZD10 "),
                              "ZD11"=c("ZD11"   ,"ZD11 "),
                              "ZD13"=c("ZD13"="ZD13 "),
                              "ZD14"=c("ZD14"="ZD14 "),
                              "ZD15"=c("ZD15"="ZD15 "))


```

# DISA



## DISA Competition
```{r DISAComp}

(
DISAComp<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Competition.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_comp.png", DISAComp,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )



write.csv(file="..//Output//DISA_competition.csv",row.names = FALSE,
          # DISAComp$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(DISAComp$data,id_cols=c(Competition.sum),
                        names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))



```


## DISA Vendor Size
```{r DISAVendor}
platpsc %>% group_by(Contracting.Agency.ID,ContractingAgencyText)%>% dplyr::summarize()
(
DISAVendor<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_vendor.png", DISAVendor, 
             width=6.5, height= 4, units="in",size=11
             )

```
## DISA Vehicle
```{r DISAVehicle}

(
DISAVehicle<-build_plot(
  data=disa_sum,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ProductServiceOrRnDarea.sum", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

disa_sum$Vehicle.sum7<-factor(disa_sum$Vehicle.sum7)


(
DISAVehicle<-build_plot(
  data=disa_sum %>% filter(!is.na(Vehicle.AwardTask)),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Vehicle.AwardTask", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)",
       caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis")
)

summary(disa_data$Vehicle)

ggsave600dpi("..//Output//DISA_vehicle.png", DISAVehicle, 
             width=13, height= 6, units="in",size=16
             )

```


## DISA Pricing
```{r DISAPricing}

(
DISAPricing<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="PricingUCA", #color_var
  facet_var="PricingUCA.sumlong", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

# ggsave600dpi("..//Output//DISA_pricing.png", DISAPricing, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//DISA_pricing.png", DISAPricing,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
write.csv(file="..//Output//DISA_pricing.csv",row.names = FALSE,
          DISAPricing$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PricingUCA,PricingUCA.sumlong),
                        names_from=dFYear,values_from=Action_Obligation_OMB20_GDP20))


```

## DISA Info Tech Commercial
```{r DISAcomm}

(
DISAcomm<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  # facet_var="Commercial", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

(
DISAcommLine<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Line Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  # facet_var="Commercial", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


(
DISAcommDetail<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategory", #color_var
  facet_var="Commercial", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

(
DISAcommIT<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategory", #color_var
  facet_var="ITcategory", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


(
DISAcommPSR<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategory", #color_var
  facet_var="ProductServiceOrRnDarea.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


# ggsave600dpi("..//Output//DISA_pricing.png", DISAcomm, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//DISA_comm.png", DISAcomm,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
write.csv(file="..//Output//DISA_comm.csv",row.names = FALSE,
          DISAcomm$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PricingUCA,PricingUCA.sumlong),
                        names_from=dFYear,values_from=Action_Obligation_OMB20_GDP20))


```

## DISA Funder   
```{r Funder}

(
Funder<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2000),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Funder", #color_var
  facet_var="Funder", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_Funder.png", Funder, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_Funder.csv",row.names = FALSE,
          pivot_wider(Funder$data,id_cols=c(Funder.sum,Funder.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_Funder_current.csv",row.names = FALSE,
          disa_data %>% group_by(Funder.sum,ContractingFunder,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Funder.sum,ContractingFunder),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_data$ContractingFunder)
```

#Product/Service/R&D

## DISA Product/Service/R&D
```{r DISAPSR}

(
DISAPSR<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ProductServiceOrRnDarea.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

labels_and_colors<-prepare_labels_and_colors(disa_data)

(
DISAPSR<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ServicesCategory.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//DISA_psr.png", DISAPSR, 
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )

write.csv(file="..//Output//DISA_psr.csv",row.names = FALSE,
          disa_data %>% group_by(ProductServiceOrRnDarea.sum,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea.sum),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

```
## DISA Product/Service/R&D Services
```{r DISAPSRdetail}

(
DISAPSRdetail<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ServicesCategory.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//DISA_psr_detail.png", DISAPSRdetail, 
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )

write.csv(file="..//Output//DISA_psr_detail.csv",row.names = FALSE,
          disa_data %>% group_by(ProductServiceOrRnDarea.sum,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea.sum),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

```

## R&D phase
```{r Services}

(
RnDphase<-build_plot(
  data=disa_data %>% filter(ProductServiceOrRnDarea.sum=="R&D"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ProductServiceOrRnDarea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_psr_RnDPhase.png", RnDphase, 
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
                           

write.csv(file="..//Output//DISA_psr_RnDPhase.csv",row.names = FALSE,
          pivot_wider(RnDphase$data,id_cols=c(ProductServiceOrRnDarea),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20)%>%
            arrange(ProductServiceOrRnDarea))
            

write.csv(file="..//Output//DISA_psr_RnDPhase_current.csv",row.names = FALSE,
          disa_data %>% filter(ProductServiceOrRnDarea.sum=="R&D") %>%
            format_data_for_plot(fy_var="fiscal_year",y_var="Action_Obligation_Then_Year",color_var = "ProductServiceOrRnDarea",
                                 labels_and_colors=labels_and_colors) %>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year)%>%
            arrange(ProductServiceOrRnDarea))

```
## Services
```{r Services}

(
Services<-build_plot(
  data=disa_data %>% filter(ProductServiceOrRnDarea.sum=="Services (Non-R&D)"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ProductServiceOrRnDarea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_psr_Services.png", Services, 
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
                           

write.csv(file="..//Output//DISA_psr_Services.csv",row.names = FALSE,
          pivot_wider(Services$data,id_cols=c(ProductServiceOrRnDarea),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20)%>%
            arrange(ProductServiceOrRnDarea))
            

write.csv(file="..//Output//DISA_psr_Services_current.csv",row.names = FALSE,
          disa_data %>% filter(ProductServiceOrRnDarea.sum=="R&D") %>%
            format_data_for_plot(fy_var="fiscal_year",y_var="Action_Obligation_Then_Year",color_var = "ProductServiceOrRnDarea",
                                 labels_and_colors=labels_and_colors) %>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year)%>%
            arrange(ProductServiceOrRnDarea))

```

## Products
```{r Products}

(
Products<-build_plot(
  data=disa_data %>% filter(ProductServiceOrRnDarea.sum=="Products (All)"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ProductServiceOrRnDarea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_psr_Products.png", Products, 
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
                           

write.csv(file="..//Output//DISA_psr_Products.csv",row.names = FALSE,
          pivot_wider(Products$data,id_cols=c(ProductServiceOrRnDarea),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20)%>%
            arrange(ProductServiceOrRnDarea))
            

write.csv(file="..//Output//DISA_psr_Products_current.csv",row.names = FALSE,
          disa_data %>% filter(ProductServiceOrRnDarea.sum=="R&D") %>%
            format_data_for_plot(fy_var="fiscal_year",y_var="Action_Obligation_Then_Year",color_var = "ProductServiceOrRnDarea",
                                 labels_and_colors=labels_and_colors) %>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year)%>%
            arrange(ProductServiceOrRnDarea))

```
## DISA Product/Service/R&D Services
```{r DISAPSRdetail}

(
DISAPSRdetail<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = TRUE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="fiscal_year", #x_var
  y_var="obligatedAmount_OMB19_19", #VAR.y.variable
  color_var="Office", #color_var
  facet_var="Funder", #facet_var
  column_key=column_key,
  format=FALSE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//OfficePricing.png", OfficePricing, 
             width=12, height= 6, units="in",size=11,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficePricing.csv",row.names = FALSE,
          pivot_wider(OfficePricing$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficePricing_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```


## Funder Commercial
```{r FunderComm}

(
FunderComm<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ServicesCategory.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//DISA_psr_detail.png", DISAPSRdetail, 
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )

write.csv(file="..//Output//DISA_psr_detail.csv",row.names = FALSE,
          disa_data %>% group_by(ProductServiceOrRnDarea.sum,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea.sum),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

```


# Product or Service Detail 
## Top 7 ProdServ
```{r ProdServ}

prodserv<-disa_sum %>% filter(fiscal_year>=2002) %>% group_by(ProductOrServiceCode,ProductOrServiceCodeText,ProductServiceOrRnDarea,ProductServiceOrRnDarea.sum)%>%
  summarise(Action_Obligation_OMB20_GDP20=sum(Action_Obligation_OMB20_GDP20,na.rm=TRUE))


write.csv(prodserv,"..\\output\\DISA_prodserv.csv",row.names = FALSE)
write.csv(prodservcomm,"..\\output\\DISA_prodservComm.csv",row.names = FALSE)

prodservcomm<-disa_sum %>% filter(fiscal_year>=2002) %>% group_by(ProductOrServiceCode,ProductOrServiceCodeText,ProductServiceOrRnDarea,ProductServiceOrRnDarea.sum,Commercial)%>%
  summarise(Action_Obligation_OMB20_GDP20=sum(Action_Obligation_OMB20_GDP20,na.rm=TRUE)) %>%pivot_wider(names_from = Commercial, values_from=Action_Obligation_OMB20_GDP20)

prodserv$rank<-rank(prodserv$Action_Obligation_OMB20_GDP20*-1)

disa_sum$prodserv_detail<-as.character(disa_sum$ServicesCategory.sum)
disa_sum$prodserv_detail[disa_sum$ProductOrServiceCode %in% prodserv$ProductOrServiceCode[prodserv$rank<=7]]<-
  disa_sum$ProductOrServiceCodeText[disa_sum$ProductOrServiceCode %in% prodserv$ProductOrServiceCode[prodserv$rank<=7]]
  

(
DISAProdServdetail<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="prodserv_detail", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)



```
## NAICS
```{r ProdServ}

naics<-disa_sum %>% filter(fiscal_year>=2002) %>% group_by(principalnaicscode,principalnaicscodeText,NAICS_ShortHand)%>%
  summarise(Action_Obligation_OMB20_GDP20=sum(Action_Obligation_OMB20_GDP20,na.rm=TRUE))

write.csv(naics,"..\\output\\DISA_NAICS.csv",row.names = FALSE)

naicsD399<-disa_sum %>% filter(fiscal_year>=2002&ProductOrServiceCode=='D399') %>% group_by(principalnaicscode,principalnaicscodeText,NAICS_ShortHand)%>%
  summarise(Action_Obligation_OMB20_GDP20=sum(Action_Obligation_OMB20_GDP20,na.rm=TRUE))
write.csv(naicsD399,"..\\output\\DISA_NAICSD399.csv",row.names = FALSE)

prodservcomm<-disa_sum %>% filter(fiscal_year>=2002) %>% group_by(ProductOrServiceCode,ProductOrServiceCodeText,ProductServiceOrRnDarea,ProductServiceOrRnDarea.sum,Commercial)%>%
  summarise(Action_Obligation_OMB20_GDP20=sum(Action_Obligation_OMB20_GDP20,na.rm=TRUE)) %>%pivot_wider(names_from = Commercial, values_from=Action_Obligation_OMB20_GDP20)

naics$rank<-rank(naics$Action_Obligation_OMB20_GDP20*-1)

disa_sum$prodserv_detail<-
disa_sum$prodserv_detail[disa_sum$ProductOrServiceCode %in% prodserv$ProductOrServiceCode[prodserv$rank<=7]]<-
  disa_sum$ProductOrServiceCodeText[disa_sum$ProductOrServiceCode %in% prodserv$ProductOrServiceCode[prodserv$rank<=7]]
  

(
DISAProdServdetail<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="prodserv_detail", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)



write.csv(prodserv,"..\\output\\DISA_prodserv.csv",row.names = FALSE)
write.csv(prodservcomm,"..\\output\\DISA_prodservComm.csv",row.names = FALSE)
```

## Hand created
```{r ProdServ}


disa_sum$DISAprodserv<-as.character(disa_sum$ServicesCategory.sum)
disa_sum$DISAprodserv[substr(disa_sum$ProductOrServiceCode,1,1)=="D" ]<-"Other IT and Telecomm"
disa_sum$DISAprodserv[disa_sum$ProductOrServiceCode =="D304" ]<-"Telecomm & Transmission"
disa_sum$DISAprodserv[disa_sum$ProductOrServiceCode =="D316" ]<-"Telecomm Network Mgmt."
disa_sum$DISAprodserv[disa_sum$ProductOrServiceCode =="D319" ]<-"Annual Software Maint."
disa_sum$DISAprodserv[disa_sum$ProductOrServiceCode =="7030" ]<-"Software as a product"
disa_sum$DISAprodserv[disa_sum$DISAprodserv =="Products" ]<-"Other Products"
disa_sum$DISAprodserv[disa_sum$DISAprodserv =="ICT" ]<-"Other ICT Services"


write.csv(prodserv,"..\\output\\DISA_prodserv.csv",row.names = FALSE)
write.csv(prodservcomm,"..\\output\\DISA_prodservComm.csv",row.names = FALSE)


levels(factor(disa_sum$DISAprodserv))
disa_sum$DISAprodserv<-factor(disa_sum$DISAprodserv,
                              levels=c("Telecomm & Transmission", "Telecomm Network Mgmt.","Annual Software Maint.",
                                       "Other IT and Telecomm","Other ICT Services" ,
                                        "PAMS" , "Other Services and R&D","Software as a product",
                                        "Other Products" ,"Unlabeled"))
             

disa_sum$prodserv_detail[disa_sum$ProductOrServiceCode %in% prodserv$ProductOrServiceCode[prodserv$rank<=7]]<-
  disa_sum$ProductOrServiceCodeText[disa_sum$ProductOrServiceCode %in% prodserv$ProductOrServiceCode[prodserv$rank<=7]]
  

(
DISAProdServdetail<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002 & ProductServiceOrRnDarea!="Unlabeled")  ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="DISAprodserv", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)",caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis")
)

ggsave600dpi(DISAProdServdetail,file="..//output//DISA_prodserv.png",  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
```

```{r HandOffice}

(
DISAProdServdetail<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004 & ProductServiceOrRnDarea!="Unlabeled")  ,
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="OfficeSum", #color_var
  facet_var="DISAprodserv", #facet_var
  # column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)",caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis")
)


(
DISAProdServdetail<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004 & ProductServiceOrRnDarea!="Unlabeled")  ,
  chart_geom = "Bar Chart",
  share = TRUE,
  # labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="DISAprodserv", #color_var
  facet_var="OfficeSum", #facet_var
  # column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)",caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis")
)

ggsave600dpi(DISA_prodservdetail,file="..//output//DISA_prodserv.png",  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
```

# Commercial

## DISA Info Tech Commercial PSR
```{r DISAcomm}

(
DISAcommPSR<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategory", #color_var
  facet_var="ServicesCategory.sum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


# ggsave600dpi("..//Output//DISA_pricing.png", DISAcomm, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//DISA_commPSR.png", DISAcomm,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
write.csv(file="..//Output//DISA_comm.csv",row.names = FALSE,
          DISAcomm$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PricingUCA,PricingUCA.sumlong),
                        names_from=dFYear,values_from=Action_Obligation_OMB20_GDP20))


```
## Commercial Vehicle
```{r CommVeh}

(
VehCommDet<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategory", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


(
VehCommSum<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

(
CommVeh<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Commercial", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

# ggsave600dpi("..//Output//DISA_pricing.png", DISAcomm, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//DISA_CommVeh.png", CommVeh,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )

ggsave600dpi("..//Output//DISA_VehCommSum.png", VehCommSum,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )


write.csv(file="..//Output//DISA_CommVeh.csv",row.names = FALSE,
          DISAcomm$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PricingUCA,PricingUCA.sumlong),
                        names_from=dFYear,values_from=Action_Obligation_OMB20_GDP20))

levels(factor(disa_sum$Commercial))
```


## Commercial Competition
```{r CommComp}
summary(factor(disa_sum$CompetitionClassification))
(
CompCommDet<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategory", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


(
CompCommSum<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

(
CommComp<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Commercial", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

# ggsave600dpi("..//Output//DISA_pricing.png", DISAcomm, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//DISA_CommComp.png", CommComp,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )

ggsave600dpi("..//Output//DISA_CompCommSum.png", CompCommSum,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )


write.csv(file="..//Output//DISA_CommVeh.csv",row.names = FALSE,
          DISAcomm$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PricingUCA,PricingUCA.sumlong),
                        names_from=dFYear,values_from=Action_Obligation_OMB20_GDP20))

levels(factor(disa_sum$Commercial))
```


# Office
## DISA Office 
```{r Office}

(
Office<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Office", #color_var
  facet_var="Office", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_Office.png", Office, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_Office.csv",row.names = FALSE,
          pivot_wider(Office$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_Office_current.csv",row.names = FALSE,
          disa_data %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_data$ContractingOffice)
```
## DISA Office  Location
```{r Office}

(
OfficeLoc<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Office", #color_var
  facet_var="OfficeLoc", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_OfficeLoc.png", OfficeLoc, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_Office.csv",row.names = FALSE,
          pivot_wider(Office$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_Office_current.csv",row.names = FALSE,
          disa_data %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_data$ContractingOffice)
```


## DISA Office  Summary
```{r OfficeSum}

(
OfficeSum<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="OfficeSum", #color_var
  facet_var="OfficeScott", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_OfficeSum.png", OfficeSum, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_Office.csv",row.names = FALSE,
          pivot_wider(Office$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_Office_current.csv",row.names = FALSE,
          disa_data %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_data$ContractingOffice)
```

## Office ProdServ
```{r OfficePSR}



(
OfficePSR<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ServicesCategory.sum", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)+facet_wrap(~OfficeSum, ncol=3)



ggsave600dpi("..//Output//DISA_OfficePSR.png", OfficePSR, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficePSR.csv",row.names = FALSE,
          pivot_wider(OfficePSR$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficePSR_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

```
## Office Pricing
```{r OfficePricing}

(
OfficePricing<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="TypeOfContractPricing5Category", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//OfficePricing.png", OfficePricing, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficePricing.csv",row.names = FALSE,
          pivot_wider(OfficePricing$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficePricing_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```
## Office Funder
```{r OfficeFunder}
(
OfficeFunderDISA<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="FunderDISA", #color_var
  facet_var="OfficeSum", #facet_var
  # column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

(
OfficeFunder<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Funder", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)



ggsave600dpi("..//Output//DISA_OfficeFunder.png", OfficeFunder, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficePricing.csv",row.names = FALSE,
          pivot_wider(OfficePricing$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficePricing_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```

## Office Commercial
```{r OfficePricing}

(
OfficeComm<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


(
OfficeCommLine<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = TRUE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

(
OfficeIT<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ITcategory", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//DISA_OfficeComm.png", OfficeComm, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficeComm.csv",row.names = FALSE,
          pivot_wider(OfficeComm$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficeComm_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```

## Office Vehicle
```{r OfficeVehicle}

(
OfficeVehicle<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004 & !is.na(Vehicle.sum7)),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)", caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis")
)


(
OfficeVehicleLine<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = TRUE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)

(
OfficeIT<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ITcategory", #color_var
  facet_var="OfficeSum", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//DISA_OfficeVehicle.png", OfficeVehicle, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficeVehicle.csv",row.names = FALSE,
          pivot_wider(OfficeVehicle$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficeVehicle_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```


# Funder
## Funder Office
```{r FunderOffice}

(
FunderOffice<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="OfficeSum", #color_var
  facet_var="Funder", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


(
FunderOffice<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Line Chart",
  share = TRUE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="OfficeSum", #color_var
  facet_var="Funder", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//OfficeVehicle.png", OfficeVehicle, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficeVehicle.csv",row.names = FALSE,
          pivot_wider(OfficeVehicle$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficeVehicle_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```
For the services, their division by office is relatively even. Army is making more use of PL-84 but Navy and Air Force are picking up as well.

## Funder Commercial

```{r FunderComm}

(
FunderComm<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="Funder", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//DISA_FunderComm.png", FunderComm, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficePricing.csv",row.names = FALSE,
          pivot_wider(OfficePricing$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficePricing_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```

With the exception of Other than DoD, each funder appears to make use of a mix of comemrcial and non-commercial sources.


## Funder PSR
```{r FunderPSR}

(
FunderPSR<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ServicesCategory.sum", #color_var
  facet_var="Funder", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


(
FunderPSR<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Line Chart",
  share = TRUE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="OfficeSum", #color_var
  facet_var="Funder", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


ggsave600dpi("..//Output//DISA_OfficePricing.png", OfficePricing, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficePricing.csv",row.names = FALSE,
          pivot_wider(OfficePricing$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficePricing_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```
The Army stands out nin buying products, generally the services are acquiring ICT. But otherwise not that remarkable.


## Funder Vehicle
```{r FunderVehicle}

(
FunderVehicle<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ds_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Funder", #facet_var
  column_key=ds_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)


(
FunderVehicle<-build_plot(
  data=disa_sum %>% filter(fiscal_year>=2004),
  chart_geom = "Bar Chart",
  share = TRUE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Funder", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2020 $s)")
)+facet_wrap(~Funder)


ggsave600dpi("..//Output//DISA_OfficePricing.png", OfficePricing, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//DISA_OfficePricing.csv",row.names = FALSE,
          pivot_wider(OfficePricing$data,id_cols=c(Office.sum,Office.platform),
                      names_from=fiscal_year,values_from=Action_Obligation_OMB20_GDP20))

write.csv(file="..//Output//DISA_OfficePricing_current.csv",row.names = FALSE,
          disa_sum %>% group_by(Office.sum,ContractingOffice,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Office.sum,ContractingOffice),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

summary(disa_sum$ContractingOffice)
```
With the exception of Other than DoD the patterns seems simialr enought that this breakdown does not add much. Other than DoD is domianted by Other IDV.
# Platform
## DISA  Platform
```{r Platform}

(
Platform<-build_plot(
  data=disa_data,
  chart_geom = "Line Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_platform.png", Platform, 
             width=13, height= 6, units="in",size=16,lineheight = 1.2
             )


write.csv(file="..//Output//DISA_platform_current.csv",row.names = FALSE,
          disa_data %>% group_by(PlatformPortfolio,fiscal_year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(PlatformPortfolio),
                      names_from=fiscal_year,values_from=Action_Obligation_Then_Year))

```



## Platform SubCustomer
```{r PlatformSubCustomer}

(
PlatformSubCustomer<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="SubCustomer.platform", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_platform_subcustomer.png", PlatformSubCustomer, 
             width=6.5, height= 4, units="in",size=11,lineheight = 0.75
             )

```

## Platform PSR
```{r PlatformPSR}

(
PlatformPSR<-build_plot(
  data=disa_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="ProductServiceOrRnDarea.sum", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_platform_PSR.png", PlatformPSR, 
             width=6.5, height= 4, units="in",size=11,lineheight = 0.75
             )

```





## Platform Vendor
```{r PlatformVendor}

(
PlatformVendor<-build_plot(
  data=disa_data %>% filter(PlatformPortfolio!="Unlabeled" ) ,
  chart_geom = "Bar Chart",
  share = TRUE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_platform_vendor.png", PlatformVendor, 
             width=6.5, height= 4, units="in",size=11,lineheight = 0.75
             )

```



## Platform Comp
```{r PlatformComp}

(
PlatformComp<-build_plot(
  data=disa_data %>% filter(PlatformPortfolio!="Unlabeled" ),
  chart_geom = "Bar Chart",
  share = TRUE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  color_var="Competition.multisum", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2020 $s)")
)

ggsave600dpi("..//Output//DISA_platform_comp.png", PlatformComp, 
             width=6.5, height= 4, units="in",size=11,lineheight = 0.75
             )

```
