---
title: "Defense Acquisition Trends"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, October 6, 2021"
---

# Setup
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)
library(openxlsx)
axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

CGAdir<-file.path(get_local_sharepoint_path("DIIG CGA Ukraine Commentary - Documents"),
                  "General\\Data\\")

main.text.size<-1
note.text.size<-1.40
if(!exists("platpscintldef"))
  load(file="../data/clean/platpscintl_FPDS.Rda")
summary(platpscintldef$Fiscal_Year)


if(!exists("platpscdefcd"))
  load(file="../data/clean/platpscdefcd.Rda")
summary(platpscdefcd$Fiscal_Year)
max(platpscdefcd$Fiscal_YQ)

if(!exists("economic"))
  load(file="../data/clean/ProdServPlatformNAICS.rda")

if(!exists("munition"))
  load(file=file.path("..","data","semi_clean","munition_transaction.rda"))

munition_lc<-prepare_labels_and_colors(munition)
munition_ck<-get_column_key(munition)
# save.image("../.RData")
```

# Preprocessing 


## Ukraine cut
```{r Location}
colnames(platpscdefcd)

ukraine_list<-c("1320","1305",
"2350","1410",
"1377","1055",
"1336","1440",
"1390","1337",
"1338","1420",
"1425","1427",
"1430","1450")

if(!"UkraineDIBrelevant" %in% colnames(platpscdefcd))
  platpscdefcd<-read_and_join_experiment(platpscdefcd, "ProjectIDUkraineDIBrelevant.csv",
                                           dir="..\\data\\semi_clean\\",path="",
                                         by="ProjectID",
                                           add_var=c("Project.Name","UkraineDIBrelevant"),
                                           skip_check_var=c("Project.Name","UkraineDIBrelevant"))

ukrplatpsc<-platpscdefcd %>% filter((ProductOrServiceCode %in% ukraine_list
                                      | UkraineDIBrelevant =="Always") & Fiscal_YQ>=2022.2 &
                                      Fiscal_YQ<=2024.1 & ContractingCustomer=="Defense" & 
                                        (is.na(UkraineDIBrelevant) | UkraineDIBrelevant !="Never"))
  # summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22))

economic<-read_and_join_experiment(economic, "ProjectIDUkraineDIBrelevant.csv",
                                           dir="..\\data\\semi_clean\\",path="",
                                         by="ProjectID",
                                           add_var=c("Project.Name","UkraineDIBrelevant"),
                                           skip_check_var=c("Project.Name","UkraineDIBrelevant"))

economic<-economic %>% mutate(IsUkraineRelevant=ifelse((ProductOrServiceCode %in% ukraine_list
                                      | UkraineDIBrelevant =="Always")  &
                                        ContractingCustomer=="Defense" & 
                                        (is.na(UkraineDIBrelevant) | 
                                           UkraineDIBrelevant!="Never"),1,0))

```

## Ukraine Project
```{r PreprocessProject}

summary(factor(ukrplatpsc$ProjectPlatform))

colnames(ukrplatpsc)[colnames(ukrplatpsc)=="Action_Obligation_Then_Year_Then_Year"]<-
  "Action_Obligation_Then_Year"

colnames(ukrplatpsc)[colnames(ukrplatpsc)=="Action_Obligation_Then_Year_OMB23_GDP21"]<-
  "Action_Obligation_OMB24_GDP22"

topproj<-ukrplatpsc %>% group_by (Project.Name) %>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22),
            Action_Obligation_2023=sum(ifelse(Fiscal_Year==2023,Action_Obligation_OMB24_GDP22,0)))%>%
              group_by () %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB24_GDP22)),
                        rank_2023=rank(desc(Action_Obligation_2023)))
topproj %>% arrange(desc(Action_Obligation_OMB24_GDP22))


topproj$TopProject<-
  ifelse(topproj$rank_2023<=7 | topproj$rank_total<=7,topproj$Project.Name,NA)

ukrplatpsc<-left_join(ukrplatpsc,topproj %>% select(-Action_Obligation_OMB24_GDP22,Action_Obligation_2023),
          by=c("Project.Name"))

ukrplatpsc$TopProject[is.na(ukrplatpsc$TopProject) & !is.na(ukrplatpsc$Project.Name)]<-
  "Other Labeled Project"


summary(factor(ukrplatpsc$TopProject))


```
## Ukraine PSC
```{r PreprocessPSC}

summary(factor(ukrplatpsc$ProjectPlatform))

topPSC<-ukrplatpsc %>% group_by (ProductOrServiceCode,ProductOrServiceCodeText) %>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22),
            Action_Obligation_2023=sum(ifelse(Fiscal_Year==2023,Action_Obligation_OMB24_GDP22,0)))%>%
              group_by () %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB24_GDP22)),
                        rank_2023=rank(desc(Action_Obligation_2023)))
topPSC %>% arrange(desc(Action_Obligation_OMB24_GDP22))

topPSC$TopPScode<-
  ifelse(topPSC$rank_2023<=7 | topPSC$rank_total<=7,topPSC$ProductOrServiceCode,NA)
topPSC$TopPStext<-
  ifelse(topPSC$rank_2023<=7 | topPSC$rank_total<=7,topPSC$ProductOrServiceCodeText,NA)


ukrplatpsc<-left_join(ukrplatpsc,topPSC %>% select(-Action_Obligation_OMB24_GDP22,Action_Obligation_2023,-ProductOrServiceCodeText),
          by=c("ProductOrServiceCode"))

ukrplatpsc$TopPScode[is.na(ukrplatpsc$TopPScode) & !is.na(ukrplatpsc$ProductOrServiceCode)]<-
  "Other Labeled PSC"
ukrplatpsc$TopPStext[is.na(ukrplatpsc$TopPStext) & !is.na(ukrplatpsc$ProductOrServiceCode)]<-
  "Other Labeled PSC"

ukrplatpsc$TopPStext<-factor_wrap(ukrplatpsc$TopPStext)

summary(factor(ukrplatpsc$TopPStext))


```

## Ukraine Place State
```{r PreprocessState}

# ukrplatpsc$pop_isna<-is.na(ukrplatpsc$pop_state_code)
# ukrplatpsc$sc_isna<-is.na(ukrplatpsc$PlaceStateCode)
# ukrplatpsc %>% group_by(Fiscal_Year,pop_isna,sc_isna) %>%
#   summarise(n=length(Fiscal_Year))

# summary(factor(ukrplatpsc$ProductOrServiceArea))

topState<-ukrplatpsc %>% group_by (pop_state_code) %>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22),
            Action_Obligation_2023=sum(ifelse(Fiscal_Year==2023,Action_Obligation_OMB24_GDP22,0)))%>%
              group_by () %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB24_GDP22)))
topState %>% arrange(desc(Action_Obligation_OMB24_GDP22))

topState$TopStateAbbr<-
  ifelse(topState$rank_total<=5,topState$pop_state_code,NA)
# topState$TopStateName<-
#   ifelse(topState$rank_2023<=7 | topState$rank_total<=7,topState$PlaceStateCodeText,NA)
ukrplatpsc<-ukrplatpsc[,!colnames(ukrplatpsc) %in% c("Action_Obligation_OMB24_GDP22.x","Action_Obligation_OMB24_GDP22.y",
                                   "Action_Obligation_2023.x","Action_Obligation_2023.y",
  "rank_total.y","rank_total.x","rank_2023.y","rank_2023.x","TopStateAbbr.x","TopStateAbbr.y")]

ukrplatpsc<-left_join(ukrplatpsc,topState %>% select(-Action_Obligation_OMB24_GDP22,Action_Obligation_2023),
          by=c("pop_state_code"))

ukrplatpsc$TopStateAbbr[is.na(ukrplatpsc$TopStateAbbr) & !is.na(ukrplatpsc$pop_state_code)]<-
  "Other Labeled State"
# ukrplatpsc$TopStateName[is.na(ukrplatpsc$TopStateName) & !is.na(ukrplatpsc$pop_state_code)]<-
#   "Other Labeled State"


# summary(factor(ukrplatpsc$TopStateName))


```
## Ukraine Vendor State
```{r PreprocessState}

# ukrplatpsc$pop_isna<-is.na(ukrplatpsc$pop_state_code)
# ukrplatpsc$sc_isna<-is.na(ukrplatpsc$VendorStateCode)
# ukrplatpsc %>% group_by(Fiscal_Year,pop_isna,sc_isna) %>%
#   summarise(n=length(Fiscal_Year))

# summary(factor(ukrplatpsc$ProductOrServiceArea))

topVendorState<-ukrplatpsc %>% group_by (VendorStateCode) %>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22),
            Action_Obligation_2023=sum(ifelse(Fiscal_Year==2023,Action_Obligation_OMB24_GDP22,0)))%>%
              group_by () %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB24_GDP22)))
topVendorState %>% arrange(desc(Action_Obligation_OMB24_GDP22))

topVendorState$topVendorStateAbbr<-
  ifelse(topVendorState$rank_total<=5,topVendorState$VendorStateCode,NA)
# topVendorState$topVendorStateName<-
#   ifelse(topVendorState$rank_2023<=7 | topVendorState$rank_total<=7,topVendorState$VendorStateCodeText,NA)
ukrplatpsc<-ukrplatpsc[,!colnames(ukrplatpsc) %in% c("Action_Obligation_OMB24_GDP22.x","Action_Obligation_OMB24_GDP22.y",
                                   "Action_Obligation_2023.x","Action_Obligation_2023.y",
  "rank_total.y","rank_total.x","rank_2023.y","rank_2023.x","topVendorStateAbbr.x","topVendorStateAbbr.y")]

ukrplatpsc<-left_join(ukrplatpsc,topVendorState %>% select(-Action_Obligation_OMB24_GDP22,Action_Obligation_2023),
          by=c("VendorStateCode"))

ukrplatpsc$topVendorStateAbbr[is.na(ukrplatpsc$topVendorStateAbbr) & !is.na(ukrplatpsc$VendorStateCode)]<-
  "Other Labeled State"
# ukrplatpsc$topVendorStateName[is.na(ukrplatpsc$topVendorStateName) & !is.na(ukrplatpsc$VendorStateCode)]<-
#   "Other Labeled State"


# summary(factor(ukrplatpsc$topVendorStateName))


```

## Place Country
```{r PreprocessCountry}

# summary(factor(platpscintldef$ProductOrServiceArea))
colnames(platpscintldef)[colnames(platpscintldef)=="Fiscal_Year"]<-"Fiscal_Year"
topCountry<-platpscintldef %>% group_by (PlaceISOalpha3,ProductOrServiceArea) %>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22),
            Action_Obligation_2023=sum(ifelse(Fiscal_Year==2023,Action_Obligation_OMB24_GDP22,0)))%>%
              group_by (ProductOrServiceArea) %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB24_GDP22)),
                        rank_2023=rank(desc(Action_Obligation_2023)))
topCountry %>% arrange(desc(Action_Obligation_OMB24_GDP22))

topCountry$TopCountryISO<-
  ifelse(topCountry$rank_2023<=7 | topCountry$rank_total<=7,topCountry$PlaceISOalpha3,NA)
# topCountry$TopCountryName<-
#   ifelse(topCountry$rank_2023<=7 | topCountry$rank_total<=7,topCountry$PlaceCountryCodeText,NA)


platpscintldef<-left_join(platpscintldef,topCountry %>% select(-Action_Obligation_OMB24_GDP22,Action_Obligation_2023),
          by=c("PlaceISOalpha3","ProductOrServiceArea"))

platpscintldef$TopCountryISO[is.na(platpscintldef$TopCountryISO) & !is.na(platpscintldef$PlaceISOalpha3)]<-
  "Other Labeled Country"
# platpscintldef$TopCountryName[is.na(platpscintldef$TopCountryName) & !is.na(platpscintldef$PlaceISOalpha3)]<-
#   "Other Labeled Country"


# summary(factor(platpscintldef$TopCountryName))


```

# Ukraine
## ProdServ
```{r ukr_psc}

export_worksheet(df= ukrplatpsc %>% group_by(
            ProductServiceOrRnDarea,ProductOrServiceCode,ProductOrServiceCodeText)%>%
            # arrange(ProductServiceOrRnDarea,ProductOrServiceCode,ProductOrServiceCodeText))%>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22)),
  xlsx="Weapons_Systems_in_Ukr_Supp.xlsx",
  sheet="PSC",path= "..//Output//Munitions//",
  second_path=CGAdir,
  startRow=2,startCol=1
)


(
PSC<-build_plot(
  data=ukrplatpsc,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="fiscal_quarter",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="TopPStext", #color_var
  facet_var="Fiscal_Year", #facet_var
  alpha_var = "YTD",
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")#+
  # date_x_year_breaks(2000,2022,2,partial_year=2024,partial_label="\nQ1")
  # facet_wrap(facet=~UkraineDIBrelevant, scales="free_y")
)

```
## Topline Graph
```{r topline}

summary(factor(platpscdefcd$PlatformPortfolioUAV))
(
MunitionPlatform<-build_plot(
  data=platpscdefcd %>% filter(
    Fiscal_Year>=2012 & Fiscal_YQ<=2024.1 &
                                 (PlatformPortfolioUAV %in% c("Missile Defense",
                                                              "Ordnance and Missiles")|
                                    UkraineDIBrelevant %in% c("Sometimes","Always"))),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="UkraineDIBrelevant", #color_var
  facet_var="PlatformPortfolioUAV", #facet_var
  alpha_var = "YTD",
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")+
  date_x_year_breaks(2000,2022,2,partial_year=2024,partial_label="\nQ1")
  # +
  # facet_wrap(facet=~PlatformPortfolioUAV, scales="free_y")
)

(
UkraineRelevant<-build_plot(
  data=platpscdefcd %>% filter(Fiscal_Year>=2012 & Fiscal_YQ<=2024.1),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="UkraineDIBrelevant", #color_var
  facet_var="UkraineDIBrelevant", #facet_var
  alpha_var = "YTD",
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")+
  date_x_year_breaks(2000,2022,2,partial_year=2024,partial_label="\nQ1")+
  facet_wrap(facet=~UkraineDIBrelevant, scales="free_y")
)
```
## Platform  Ukraine
```{r Platform}

ukr_data$IsUkraine<-ifelse(fed_data$nationalinterestactioncode=="O22U" &
                             !is.na(ukr_data$nationalinterestactioncode=="O22U"),"UKRAINE MISSION SUPPORT","All Other")

ukr_data %>% group_by(nationalinterestactioncode)%>%
  filter(Fiscal_Year==2022) %>% summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))

(
Platform_Ukr_Bar<-build_plot(
  data=ukr_data %>% filter(Fiscal_Year>=1990),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ukr_lc,
  # NA, #VAR.ncol
  x_var="dFYear",alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="IsUkraine", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=ukr_ck,
  format=TRUE,
  ytextposition=FALSE
)+  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = scales::percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)")
)

ggsave600dpi(path="..//Output//AcqTrends//",filename="Munitions//ukraine_platform_bar.png", Platform_Ukr_Bar, 
             width=11, height= 5.5, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//AcqTrends//",filename="Munitions//ukraine_platform_bar.emf", Platform_Ukr_Bar,
             width=6.5, height= 4, units="in",size=11,lineheight = 1.2
             )

output_TY<-ukr_data %>% group_by(PlatformPortfolio,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(PlatformPortfolio,IsUkraine),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year)%>%arrange(PlatformPortfolio,IsUkraine)

write.csv(file="..//Output//AcqTrends//Munitions//ukraine_platform_current.csv",row.names = FALSE, na = "",
          output_TY)

# wb <- loadWorkbook("..//Output//AcqTrends//DoD_Acq_Trends_Contracts.xlsx")
# createSheet(wb, name = "Platform Portfolio")
# writeData(wb, output_TY, sheet = "Platform Portfolio", startRow = 15, startCol = 1)
# saveWorkbook(wb,file="..//Output//AcqTrends//DoD_Acq_Trends_Contracts.xlsx",overwrite = TRUE)
# rm(wb)

```



## Platform and Project
```{r ukr_psc}
ukrplatpsc$Project.Name[ukrplatpsc$ProjectID==466]<-"PIM"

ukrplatpsc$ProjPSC<-ifelse(is.na(ukrplatpsc$Project.Name),
                           paste(ukrplatpsc$ProductOrServiceCode,ukrplatpsc$ProductOrServiceCodeText,sep="-"),
                           ukrplatpsc$Project.Name)

export_worksheet(df= ukrplatpsc %>% group_by(
            PlatformPortfolio,ProjectID,ProjPSC)%>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22)),
  xlsx="Weapons_Systems_in_Ukr_Supp.xlsx",
  sheet="Plat",path= "..//Output//Munitions//",
  second_path=CGAdir,
  startRow=1,startCol=6
)


(
Proj<-build_plot(
  data=ukrplatpsc,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="fiscal_quarter",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="TopProject", #color_var
  facet_var="Fiscal_Year", #facet_var
  alpha_var = "YTD",
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")#+
  # date_x_year_breaks(2000,2022,2,partial_year=2024,partial_label="\nQ1")
  # facet_wrap(facet=~UkraineDIBrelevant, scales="free_y")
)

```

## Vendor CD
```{r ukr_vendor_CD}

  
export_worksheet(df= ukrplatpsc %>% group_by(
  VendorIsForeign,VendorStateCode)%>%
    # arrange(ProductServiceOrRnDarea,ProductOrServiceCode,ProductOrServiceCodeText))%>%
    summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22)),
  xlsx="Weapons_Systems_in_Ukr_Supp.xlsx",
  sheet="VendState",path= "..//Output//Munitions//",
  second_path=CGAdir,
  startRow=2,startCol=1
)

ukrplatpsc$VendorCD<-ifelse(nchar(ukrplatpsc$prime_award_transaction_recipient_cd_current)<=2 &
                              ukrplatpsc$VendorIsForeign==0,
                            paste(ukrplatpsc$VendorStateCode,ukrplatpsc$prime_award_transaction_recipient_cd_current,sep="-"),
                            ukrplatpsc$prime_award_transaction_recipient_cd_current)


export_worksheet(df= ukrplatpsc %>% group_by(
            VendorIsForeign,VendorStateCode,VendorCD)%>%
            # arrange(ProductServiceOrRnDarea,ProductOrServiceCode,ProductOrServiceCodeText))%>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22)),
  xlsx="Weapons_Systems_in_Ukr_Supp.xlsx",
  sheet="VendState",path= "..//Output//Munitions//",
  second_path=CGAdir,
  startRow=2,startCol=5
)


(
UkrainePlace<-build_plot(
  data=ukrplatpsc,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="fiscal_quarter",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="topVendorStateAbbr", #color_var
  facet_var="Fiscal_Year", #facet_var
  alpha_var = "YTD",
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")#+
  # date_x_year_breaks(2000,2022,2,partial_year=2024,partial_label="\nQ1")
  # facet_wrap(facet=~UkraineDIBrelevant, scales="free_y")
)

```

## Place CD
```{r ukr_place_CD}



ukrplatpsc<-ukrplatpsc %>% mutate(
  PlaceOrOriginIsInternational=case_when(PlaceIsForeign==1 | 
                                        OriginIsInternational==1~ "International",
                                        PlaceIsForeign==0 | 
                                        OriginIsInternational==0~"Domestic",
                                      TRUE ~"Unlabeled"),
  PlaceCD=
    case_when(
      PlaceOrOriginIsInternational=="International"~"International",
      PlaceOrOriginIsInternational=="Unlabeled"~"Unlabeled",
      nchar(prime_award_transaction_place_of_performance_cd_current)<=2 & pop_state_code!=""~
        paste(pop_state_code,prime_award_transaction_place_of_performance_cd_current ,sep="-"),
      TRUE ~ prime_award_transaction_place_of_performance_cd_current),
  PlaceState=case_when(
         PlaceOrOriginIsInternational=="International"~"International",
      PlaceOrOriginIsInternational=="Unlabeled"~"Unlabeled",
   pop_state_code==""~"Unlabeled",
  TRUE~pop_state_code)
  )


  
export_worksheet(df=  ukrplatpsc %>% group_by(
            PlaceOrOriginIsInternational,PlaceState)%>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22)),
  xlsx="Weapons_Systems_in_Ukr_Supp.xlsx",
  sheet="Place",path= "..//Output//Munitions//",
  second_path=CGAdir,
  startRow=2,startCol=1
)

ukrplace<-ukrplatpsc %>%group_by(PlaceOrOriginIsInternational,PlaceState,PlaceCD)%>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22)) %>%
  mutate(PlaceState=ifelse(Action_Obligation_OMB24_GDP22>=0,PlaceState,"Deobligation"),
         PlaceCD=ifelse(Action_Obligation_OMB24_GDP22>=0,PlaceCD,"Deobligation"))%>%
  group_by(PlaceOrOriginIsInternational,PlaceState,PlaceCD) %>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22)) %>%
  mutate(CD_Action_Obligation_OMB24_GDP22=
           ifelse(substr(PlaceCD,3,5)=="-90",0,Action_Obligation_OMB24_GDP22),
         Statewide_Action_Obligation_OMB24_GDP22=
           ifelse(substr(PlaceCD,3,5)=="-90",Action_Obligation_OMB24_GDP22,0)
                                           )%>%
  group_by(PlaceOrOriginIsInternational,PlaceState) %>%
    mutate(Distributed_Statewide_Action_Obligation_OMB24_GDP22=
             ifelse(substr(PlaceCD,3,5)=="-90" |
                       sum(Statewide_Action_Obligation_OMB24_GDP22)<=0,0,
                    #Distributing it proportionally
                    CD_Action_Obligation_OMB24_GDP22/
                      sum(CD_Action_Obligation_OMB24_GDP22) *
               sum(Statewide_Action_Obligation_OMB24_GDP22)
               # /sum(ifelse(substr(PlaceCD,3,5)=="-90",0,1))
               ))%>%filter(Action_Obligation_OMB24_GDP22!=0)

ukrplace$CD_and_Distributed_Action_Obligation_OMB24_GDP22=
  ukrplace$CD_Action_Obligation_OMB24_GDP22+
  ukrplace$Distributed_Statewide_Action_Obligation_OMB24_GDP22
if(sum(ukrplace$Distributed_Statewide_Action_Obligation_OMB24_GDP22,na.rm=TRUE)!=
   sum(ukrplace$Statewide_Action_Obligation_OMB24_GDP22,na.rm=TRUE)){
  stop("Checksum error")
} else if(sum(ukrplace$Action_Obligation_OMB24_GDP22,na.rm=TRUE)!=
   sum(ukrplace$CD_and_Distributed_Action_Obligation_OMB24_GDP22,na.rm=TRUE)){
  stop("Checksum error")
} else
  ukrplace<-ukrplace %>% select(-Statewide_Action_Obligation_OMB24_GDP22)

  

export_worksheet(df= ukrplace,
  xlsx="Weapons_Systems_in_Ukr_Supp.xlsx",
  sheet="Place",path= "..//Output//Munitions//",
  second_path=CGAdir,
  startRow=2,startCol=5
)


(
UkrainePlace<-build_plot(
  data=ukrplatpsc,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="fiscal_quarter",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="TopStateAbbr", #color_var
  facet_var="Fiscal_Year", #facet_var
  alpha_var = "YTD",
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")#+
  # date_x_year_breaks(2000,2022,2,partial_year=2024,partial_label="\nQ1")
  # facet_wrap(facet=~UkraineDIBrelevant, scales="free_y")
)

```


## Breakout
### Project Customer Breakout
```{r ProjPlatBreakout} 
# summary(platpscdefcd$fiscal_quarter)
  log_plot(plot=NULL, df=platpscdefcd %>% filter((ProductOrServiceCode %in% ukraine_list
                                      | UkraineDIBrelevant =="Always") & #Fiscal_YQ<=2023.2
                                        (is.na(UkraineDIBrelevant) | UkraineDIBrelevant !="Never")),
           filename=paste("Ukraine_related_DIB","all_poroject",sep="_"),xlsx="Weapons_Systems_in_Ukr_Supp.xlsx",
           x_var="Fiscal_Year",y_var="Action_Obligation_OMB24_GDP22",
           sheet="AllProj",path=file.path("../output/Munitions/"),second_path=CGAdir,
            csv_then_year=TRUE,excel_then_year = FALSE, excel_y_var=TRUE,excel_formula=TRUE,
           format=TRUE,var_list=c("PlatformPortfolio","Project.Name","ProjectID"),
           output_doc_png=FALSE, output_doc_svg = FALSE
           )

```


### PSC Customer Breakout
```{r PSCcustBreakout} 

  log_plot(plot=NULL, df=platpscdefcd %>% filter((ProductOrServiceCode %in% ukraine_list
                                      | UkraineDIBrelevant =="Always") &# Fiscal_YQ<=2023.2 &
                                        (is.na(UkraineDIBrelevant) | UkraineDIBrelevant !="Never")),
           filename=paste("Ukraine_related_DIB","all_psc",sep="_"),xlsx="Weapons_Systems_in_Ukr_Supp.xlsx",
           x_var="Fiscal_Year",y_var="Action_Obligation_OMB24_GDP22",
           sheet="AllPSC",path=file.path("../output/Munitions/"),second_path=CGAdir,
           csv_then_year=TRUE,excel_then_year = FALSE, excel_y_var=TRUE,excel_formulas = TRUE,
           format=TRUE,var_list=c("ProductOrServiceArea","ProductOrServiceCode","ProductOrServiceCodeText"),
           output_doc_png=FALSE, output_doc_svg = FALSE
           )


```

# NAICS 
## Munitions munitons look
```{r MunitionsNAICS}
bottleneck_list<-c("1320",#AMMUNITION, OVER 125 MM
                #"1305",#AMMUNITION, THROUGH 30 MM
#"2350", COMBAT ASSAULT & TACTICAL VEH
"1410", #GUIDED MISSILES
"1377", #CARTRIDGE & PROPELLANT DEVICES
"1055", #LAUNCHERS, ROCKET AND PYROTECHNI
"1336", #GUIDED MISSILE WARHEADS AND EXPLOSIVE COMPONENTS
"1440", #LAUNCHERS, GUIDED MISSILE
"1390", #	FUZES AND PRIMERS
"1337", # GUIDED MISSILE AND SPACE VEHICLE EXPLOSIVE PROPULSION UNITS, SOLID FUEL; AND COMPONENTS
"1338", #GUIDED MISSILE AND SPACE VEHICLE INERT PROPULSION UNITS, SOLID FUEL; AND COMPONENTS
"1420", #GUIDED MISSILE COMPONENTS
"1425", #GUIDED MISSILE SYSTEMS, COMPLETE
"1427", #	GUIDED MISSILE SUBSYSTEMS
"1430", #	GUIDED MISSILE REMOTE CONT SYSTEMS
"1450" #GUIDED MISSILE HANDLING AND SERVICING EQUIPMENT
) 

economic %>% filter(ProductOrServiceCode %in% ukraine_list)  %>%
  group_by(ProductOrServiceCode,ProductOrServiceCodeText) %>%
  summarise(Action_Obligation=sum(Action_Obligation_OMB24_GDP22,na.rm=TRUE)) %>%
  arrange(ProductOrServiceCode)

ukrnaics<-economic %>% filter(ProductOrServiceCode %in% bottleneck_list)  %>%
  group_by(principalnaicscode,principalnaicscodeText) %>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22,na.rm=TRUE)) %>%
  arrange(-Action_Obligation_OMB24_GDP22)

levels(economic$PlatformPortfolio)
ukrnaicsplat<-economic %>% filter(PlatformPortfolio %in% c("Ordnance and Missiles","Missile Defense"))  %>%
  group_by(principalnaicscode,principalnaicscodeText) %>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22,na.rm=TRUE)) %>%
  arrange(-Action_Obligation_OMB24_GDP22)


  bottleneck_naics<-c(336414,336419,332993,325920,332995)
  
  economic %>% filter(principalnaicscode %in% bottleneck_naics)  %>%
    group_by(principalnaicscode,principalnaicscodeText) %>%
    summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22,na.rm=TRUE)) %>%
    arrange(principalnaicscode)
  
```

### NAICS history
```{r NAICShistory}
economic <- economic %>% mutate(MunitionNAICS=case_when(
  is.na(principalnaicscodeText)~NA,
  principalnaicscode %in% bottleneck_naics ~ principalnaicscodeText ,
  TRUE~"All Other NAICS"
))

(
NAICS<-build_plot(
  data=economic %>% filter(principalnaicscode %in% bottleneck_naics | IsUkraineRelevant ==1),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="MunitionNAICS", #color_var
  facet_var="IsUkraineRelevant", #facet_var
  alpha_var = "YTD",
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+ guides(fill = guide_legend(ncol = 1))+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2022 $s)")#+
  # date_x_year_breaks(2000,2022,2,partial_year=2024,partial_label="\nQ1")
  # facet_wrap(facet=~UkraineDIBrelevant, scales="free_y")
)



(
NAICS<-build_plot(
  data=economic %>% filter(principalnaicscode %in% bottleneck_naics),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="MunitionNAICS", #color_var
  # facet_var="IsUkraineRelevant", #facet_var
  alpha_var = "YTD",
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+ guides(fill = guide_legend(ncol = 1))+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2022 $s)")#+
  # date_x_year_breaks(2000,2022,2,partial_year=2024,partial_label="\nQ1")
  # facet_wrap(facet=~UkraineDIBrelevant, scales="free_y")
)

```

# PSC
```{r PSC}

platpscintldef %>% group_by(Fiscal_Year)%>% filter(ProductOrServiceCode %in% c("1337","1377","1338","1427") & 
                                                     ContractingCustomer=="Defense")%>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))%>%arrange(Fiscal_Year)

```
# Capacity Boosting
## System Dives

### 155mm production
```{r}
artillery<-read.csv(file.path("..","data_raw","USA_Artillery_Production.csv")) %>%filter(!is.na(Monthly.Production))

artillery$Aproximate.Date<-as.Date(artillery$Aproximate.Date,"%m/%d/%Y")
artillery$Monthly.Production<-text_to_number(artillery$Monthly.Production)

(prod155mm<-
  build_plot(artillery %>% filter(Series!="A&S Sept. 2022 Targets"),
           chart_geom = "Line Chart",
           x_var="Aproximate.Date",
           y_var="Monthly.Production",
           alpha_var="Type",
           color_var="Series")+geom_point(aes(x=Aproximate.Date,
                                              y=Monthly.Production,
                                              color=Series),
                                          size=3,
                                          data=
                                            artillery %>% filter(Series!="A&S Sept. 2022 Targets"&
                                                                   Duplicate.Actuals==FALSE)
                                          )+scale_linetype(guide="none")+
  labs(x="Reporting Date or Target Deadline", y="Monthly Production\nof 155mm Ammunition",
       title="Army 155mm Ammunition Production Rates and Targets",
       caption="Sources: Bryan Bender and Lara Seligman, Politico, Dec., 4, 2022;
       Jen Judson, DefenseNews, Mar. 28, 2023; Noah Robertson, DefenseNews, Sept. 15, 2023; 
       Sam Skove, Defense One, Nov. 27, 2023; initial chart by Govini; and CSIS analysis.")+
    scale_x_date(date_breaks = "6 months",date_labels = "'%y\n%b")+
    geom_line(aes(x=Aproximate.Date,
                                              y=Monthly.Production,
                                              color=Series,
                  linetype=Type),linewidth=1.5)+
    theme(legend.position="bottom")
    #,labels = "%Y-%m"
)
ggsave600dpi(prod155mm,file=file.path("..","Output","Munitions","prod155.png"),width=11,height=4,
             size=14,lineheight=1)
ggsave600dpi(prod155mm,file=file.path("..","Output","Munitions","prod155.svg"),width=11,height=4,
             size=14,lineheight=1)
```
### HIMARS

```{r HIMARS}

(
HimarsPSR<-build_plot(
  data=platpscintldef %>% filter(Project.Name=='MLRS'),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=intl_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=intl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2021 $s)")
)

ggsave600dpi("..//Output//Munitions//Himars_psr.png", HimarsPSR, 
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )

ggsave600dpi("..//Output//Munitions//Himars_psr.emf", HimarsPSR, 
             width=6.5, height= 3, units="in",size=11, lineheight=1.2
             )

output_TY<-platpscintldef %>% group_by(Shiny.VendorSize,Fiscal_Year,Project.Name)%>% filter(Project.Name=='MLRS') %>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
  arrange(Fiscal_Year) %>%
          pivot_wider(id_cols=c(Project.Name,Shiny.VendorSize),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year)
write.csv(file="..//Output//Munitions//Himars_psr.csv",row.names = FALSE, na = "",
          output_TY)



# wb <- loadWorkbook("..//Output//DoD_Acq_Trends_Contracts.xlsx", create = TRUE)
# addWorksheet(wb, name = "Area")
#  writeData(wb, output_TY, sheet = "Area", startRow = 14, startCol = 14)
# saveWorkbook(wb)


```


## Munition Multiyear  Obligations
```{r Multiyear_obl}



(
Multiyear<-build_plot(
  data=munition %>% filter(Fiscal_Year>=2000),# & Fiscal_YQ<=2023.2
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="multiyearcontract", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")+
  date_x_year_breaks(2000,2020,2,partial_year=2023,partial_label="\nQ1–Q2")
)

(
Multiyear<-build_plot(
  data=munition %>% filter(Fiscal_Year>=2000),# & Fiscal_YQ<=2023.2
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="baseandexercisedoptionsvalue", #VAR.y.variable
  color_var="multiyearcontract", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Base and Exercised Options (Then Year$s)")+
  date_x_year_breaks(2000,2020,2,partial_year=2023,partial_label="\nQ1–Q2")
)

(
Multiyear<-build_plot(
  data=munition %>% filter(Fiscal_Year>=2000),# & Fiscal_YQ<=2023.2
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="baseandalloptionsvalue", #VAR.y.variable
  color_var="multiyearcontract", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Base and All Options (Then Year $s)")+
  date_x_year_breaks(2000,2020,2,partial_year=2023,partial_label="\nQ1–Q2")
)


ggsave600dpi("..//Output//Munitions//topline_Multiyear.png", Multiyear, 
             width=11, height= 5.5, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi("..//Output//Munitions//topline_Multiyear.svg", Multiyear+
  labs(y="Obligations\n(Constant 2022 $s)"),#+facet_wrap(~SubCustomer.platform,nrow=1), 
             width=6.5, height= 2.25, units="in",size=11,lineheight = 1.2
             )


# full_data %>% filter(SubCustomer.sum=="Army", PlatformPortfolio=="Other Products", Fiscal_Year==2021) %>%
#   group_by(AnyMultiyearText,Competition.multisum) %>% summarise(
#     COVID19obligated=sum(COVID19obligated,na.rm=TRUE),
#     Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22),
#     Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year),
#     
#   )

```

### Munition Detail
```{r Multiyear_obl}



(
Multiyear<-build_plot(
  data=munition %>% filter(Fiscal_Year>=2000),# & Fiscal_YQ<=2023.2
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="multiyearcontract", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")+
  date_x_year_breaks(2000,2020,2,partial_year=2023,partial_label="\nQ1–Q2")
)

(
Multiyear<-build_plot(
  data=munition %>% filter(Fiscal_Year>=2000),# & Fiscal_YQ<=2023.2
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="baseandexercisedoptionsvalue", #VAR.y.variable
  color_var="multiyearcontract", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Base and Exercised Options (Then Year$s)")+
  date_x_year_breaks(2000,2020,2,partial_year=2023,partial_label="\nQ1–Q2")
)

(
Multiyear<-build_plot(
  data=munition %>% filter(Fiscal_Year>=2000),# & Fiscal_YQ<=2023.2
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=munition_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="baseandalloptionsvalue", #VAR.y.variable
  color_var="multiyearcontract", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=munition_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Base and All Options (Then Year $s)")+
  date_x_year_breaks(2000,2020,2,partial_year=2023,partial_label="\nQ1–Q2")
)


ggsave600dpi("..//Output//Munitions//topline_Multiyear.png", Multiyear, 
             width=11, height= 5.5, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi("..//Output//Munitions//topline_Multiyear.svg", Multiyear+
  labs(y="Obligations\n(Constant 2022 $s)"),#+facet_wrap(~SubCustomer.platform,nrow=1), 
             width=6.5, height= 2.25, units="in",size=11,lineheight = 1.2
             )


# full_data %>% filter(SubCustomer.sum=="Army", PlatformPortfolio=="Other Products", Fiscal_Year==2021) %>%
#   group_by(AnyMultiyearText,Competition.multisum) %>% summarise(
#     COVID19obligated=sum(COVID19obligated,na.rm=TRUE),
#     Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22),
#     Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year),
#     
#   )

```