---
title: "Defense Acquisition Trends"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, October 6, 2021"
---

# Setup
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)
# library(XLConnect)
axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40
load(file="../data/clean/Defense_OTA.Rda")



```

# Estimates

## Estimate Prep
```{r EstimatePrep}
OTAquarterly<-read.csv(file.path("..","Data_Raw","OTA_All_FIelds.csv"),skip = 2)
OTAquarterly<-standardize_variable_names(OTAquarterly)
OTAquarterly$Date.Signed<-as.Date(OTAquarterly$Date.Signed,"%m/%d/%Y")

OTAquarterly<-OTAquarterly %>% mutate(fiscal_quarter=lubridate::quarter(Date.Signed,fiscal_start=10),
                        ContractingCustomer=ifelse(Contracting.Department.ID=="9700","Defense","Non-Defense")) %>%
  group_by(Fiscal_Year,fiscal_quarter,ContractingCustomer) %>%
  dplyr::summarize(Action_Obligation=sum(csis360::text_to_number(Dollars.Obligated),na.rm=TRUE)#,
            # minSD=min(Date.Signed),
            # maxSD=max(Date.Signed)
            )%>% filter((fiscal_quarter<=3 | Fiscal_Year<2021)&
                                                Fiscal_Year>=2015 & ContractingCustomer=="Defense") %>%
  arrange(Fiscal_Year,fiscal_quarter)




if(any(is.na(OTAquarterly$Fiscal_Year))) stop("NA Quarters")


OTAquarterly<-deflate(OTAquarterly,money_var = "Action_Obligation",deflator_var="OMB20_GDP20")


```
## Estimate Last Quarter
Create a univariate model that estimates the fourth quarter based on the first three quarters.

This isn't a perfect representation, as the spending in the first three quarters will continue to fluctuate even well after the 90 day delay for DoD has expired. In theory, there could be slightly greater precision by tracking the first three quarters at a consistent point in each year. However, that's not a level of history that can be straightforwardly reconstructed.  

This is also a tiny n, only 6 or so years, and thus an incredibly crude estimate.
```{r Model}


a<-OTAquarterly %>% group_by(Fiscal_Year) %>% filter(Fiscal_Year<2021 & !is.na(fiscal_quarter))%>% summarise(
  q1toq3=sum(ifelse(fiscal_quarter<=3,Action_Obligation_OMB24_GDP22,0)),
  q4=sum(ifelse(fiscal_quarter==4,Action_Obligation_OMB24_GDP22,0)),
             total=sum(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22))
)


m<-lm(data=a,q4~q1toq3)
summary(m)

plot(m)

q1to13_2021<-sum(ifelse(OTAquarterly$fiscal_quarter<=3 & !is.na(OTAquarterly$fiscal_quarter) & OTAquarterly$Fiscal_Year==2021,OTAquarterly$Action_Obligation_OMB24_GDP22,0))

cvalues<-data.frame(q1toq3=q1to13_2021)

p<-predict(m,cvalues,interval="prediction")
e2021<-data.frame(Fiscal_Year=2021,
           fiscal_quarter=4,
           Action_Obligation_Then_Year=NA,
           Action_Obligation_OMB24_GDP22=NA,
           yest=p[1]+q1to13_2021,
           lwr=p[2]+q1to13_2021,
           upr=p[3]+q1to13_2021,
           ContractingCustomer="Defense",
           Actual="Estimate"
           )
rm(q1to13_2021,cvalues)
```


## Topline Estimate
```{r Topline}

OTAquarterly$Actual<-"Actual"
OTAquarterly$lwr<-NA
OTAquarterly$upr<-NA
OTAquarterly$yest<-NA

# build_plot(data=rbind(OTAquarterly,q2021,e2021),
#            x_var="dFYear",
#            y_var="Action_Obligation_OMB24_GDP22",
#            color_var = "fiscal_quarter",
#            facet_var="Actual",
#            chart_geom="Bar Chart")+facet_wrap(~)
OTAquarterlyEst<-rbind(OTAquarterly,e2021)
OTAquarterlyEst$Actual<-factor(OTAquarterlyEst$Actual,levels=c("Estimate","Actual"))
OTAquarterlyEst$fiscal_quarter<-factor(OTAquarterlyEst$fiscal_quarter,c("4","3","2","1"))
OTAquarterlyEst$dFYear<-as.Date(paste("1/1/",as.character(OTAquarterlyEst$Fiscal_Year),sep=""),"%m/%d/%Y")

(ota_topline_qest<-ggplot(data=OTAquarterlyEst %>% filter(Fiscal_Year>=2000) #rbind(OTAquarterly,q2021,e2021),
      )+geom_col( aes(x=dFYear,
           y=Action_Obligation_OMB24_GDP22/1000000000,
           # alpha=Actual,
           fill = fiscal_quarter
       ))+
  # scale_alpha_discrete(range=c(0.4,1))+
  geom_errorbar(aes(x=dFYear,ymin=lwr/1000000000,ymax=upr/1000000000,color = fiscal_quarter))+
    geom_point(aes(x=dFYear,y=yest/1000000000,color = fiscal_quarter))+
    scale_color_discrete("Estimate")+
    labs(x="Fiscal Year",y="Constant FY 2020 $ Billions",fill="Quarter")
)

ggsave600dpi(ota_topline_qest,file=file.path("..","Output","ota_quarterly_est.png"),  
             width=12, height= 6, units="in",size=16, lineheight=1.2
             )

(ota_topline_q<-ggplot(data=OTAquarterlyEst %>% filter(Fiscal_Year>=2000) #rbind(OTAquarterly,q2021,e2021),
      )+geom_col( aes(x=dFYear,
           y=Action_Obligation_OMB24_GDP22/1000000000,
           # alpha=Actual,
           fill = fiscal_quarter
       ))+
  # scale_alpha_discrete(range=c(0.4,1))+
  # geom_errorbar(aes(x=dFYear,ymin=lwr,ymax=upr,color = fiscal_quarter))+
    # geom_point(aes(x=dFYear,y=yest,color = fiscal_quarter))+
    # scale_color_discrete("Estimate")+
    labs(x="Fiscal Year",y="Constant FY 2020 $ Billions",fill="Quarter")
)



write.csv(file="..//Output//OTA//ota_topline_qest.csv",row.names = FALSE,na="",
          OTAquarterlyEst %>%  filter(Fiscal_Year>=2015)%>%
          format_data_for_plot(
                               fy_var="Fiscal_Year",
                               y_var="Action_Obligation_OMB24_GDP22",
                               color_var="fiscal_quarter",
                               # facet="SubCustomer",
                               # labels_and_colors = ota_lc,
                               group=TRUE) %>%
            arrange(Fiscal_Year) %>%
            mutate(Dollars_GDP20=Action_Obligation_OMB24_GDP22/1000000000)%>%
          pivot_wider(id_cols=c(fiscal_quarter),
                      names_from=Fiscal_Year,values_from=Dollars_GDP20) %>% 
            
            # mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=ota_lc$variable[ota_lc$column=="PlatformPortfolio"]))%>%
            # mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=levels(fiscal_quarter),
            #                                 labels=gsub("\\n"," ",levels(PlatformPortfolio))))%>%
                   arrange(fiscal_quarter))


ggsave600dpi(ota_topline_q,file=file.path("..","Output","ota_quarterly.png"),  
             width=12, height= 6, units="in",size=16, lineheight=1.2
             )
```


# Topline


## Topline spend 
```{r}
ota_def$`BaseandAllOptionsValue(TotalContractValue)`
output_TY<-ota_def  %>% select(Fiscal_Year,Action_Obligation_Then_Year,`BaseandAllOptionsValue(TotalContractValue)`)%>%
  group_by(Fiscal_Year)%>%  
  summarise(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE),
            `BaseandAllOptionsValue(TotalContractValue)`=sum(text_to_number(`BaseandAllOptionsValue(TotalContractValue)`),
                                                                    na.rm=TRUE))%>%
  pivot_longer(cols=c(Action_Obligation_Then_Year,`BaseandAllOptionsValue(TotalContractValue)`)) %>%
  pivot_wider(names_from=c(Fiscal_Year))
                                      

wb <- loadWorkbook("..//Output//OTA//DoD_Acq_Trends_OTA.xlsx")
if(!"Topline" %in% getSheetNames("..//Output//OTA//DoD_Acq_Trends_OTA.xlsx"))
  addWorksheet(wb, sheetName = "Topline")
writeData(wb, output_TY, sheet = "Topline", startRow = 1, startCol = 1)
saveWorkbook(wb,"..//Output//OTA//DoD_Acq_Trends_OTA.xlsx",overwrite = TRUE)
rm(wb)
xlcFreeMemory()
            


write.csv(file="..//Output//OTA//ota_topline.csv",row.names = FALSE,na="",
          output_TY)
            
```

## Topline Competition
```{r ToplineComp}

(
ToplineComp<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="Competition.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//topline_comp.png", ToplineComp,  
             width=12, height= 6, units="in",size=11, lineheight=1.2
             )

View(ToplineComp$data)

write.csv(file="..//Output//OTA//topline_competition.csv",row.names = FALSE,
          # ToplineComp$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(ToplineComp$data%>%mutate(Fiscal_Year=year(dFYear)),id_cols=c(Competition.sum),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB24_GDP22))



```


## Topline Vendor Size
```{r ToplineVendor}

(
ToplineVendor<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//topline_vendor.png", ToplineVendor, 
             width=6.5, height= 4, units="in",size=11
             )

```
## Topline Vehicle
```{r ToplineVehicle}

(
ToplineVehicle<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="SimpleArea", #color_var
  facet_var="Vehicle.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)


(
ToplineVehicle<-build_plot(
  data=ota_def %>% filter(!is.na(Vehicle.AwardTask)),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="Vehicle.sum", #color_var
  facet_var="Vehicle.AwardTask", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)",
       caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis")
)

summary(ota_def$Vehicle)

ggsave600dpi("..//Output//OTA//topline_vehicle.png", ToplineVehicle, 
             width=13, height= 4.5, units="in",size=11
             )

```


## Topline Pricing
```{r ToplinePricing}
ota_def$PricingUCA.sumlong<-ota_def$PricingUCA.sum
levels(ota_def$PricingUCA.sumlong)<-list("Firm-Fixed-Price"="FFP",
                                           "Less Common"="Less Common",
                                           "Incentive"="Incentive",
                                           "Other Cost-Based"="Other CB",
                                           "Undefinitized\nContract Award"="UCA",
                                           "Unclear"="Unclear"   )
(
ToplinePricing<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="PricingUCA", #color_var
  facet_var="PricingUCA.sumlong", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

# ggsave600dpi("..//Output//OTA//topline_pricing.png", ToplinePricing, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//OTA//topline_pricing.png", ToplinePricing,  
             width=12, height= 6, units="in",size=11, lineheight=1.2
             )
lubridate::year(ota_def$dFYear)
write.csv(file="..//Output//OTA//topline_pricing.csv",row.names = FALSE,
          ToplinePricing$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(PricingUCA,PricingUCA.sumlong),
                        names_from=dFYear,values_from=Action_Obligation_OMB24_GDP22))


```


## Topline Type of Agreement
```{r TypeOfAgreement}
ota_def$Type_Of_Agreement_sum<-factor(ota_def$Type_Of_Agreement)
levels(ota_def$Type_Of_Agreement_sum)<-list("Prototype"=c("PROTOTYPE","Prototype"),
                                           "Production"=c("PRODUCTION","PRODUCTIO","Production"))

(
ToplineType<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="Type_Of_Agreement_sum", #color_var
  facet_var="Type_Of_Agreement_sum", #facet_var
  # column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

# ggsave600dpi("..//Output//OTA//topline_Type.png", ToplineType, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//OTA//topline_Type.png", ToplineType,  
             width=12, height= 6, units="in",size=11, lineheight=1.2
             )
write.csv(file="..//Output//OTA//topline_Type.csv",row.names = FALSE,
          ToplineType$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(id_cols=c(Type_Of_Agreement_sum),
                        names_from=dFYear,values_from=Action_Obligation_OMB24_GDP22))


```

#Product/Service/R&D

## Topline Product/Service/R&D
```{r ToplinePSR}

(
ToplinePSR<-build_plot(
  data=ota_def %>% filter(Fiscal_Year>=2015& Fiscal_Year<=2022),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="SimpleArea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//ota_topline_psr.png", ToplinePSR, 
             width=5, height= 6, units="in",size=16, lineheight=1.2
             )

ggsave600dpi("..//Output//OTA//ota_topline_psr_keynote.svg", ToplinePSR+
               labs(title="DOD OTAs Obligations\nby Area, 2015-2022"),
             width=6, height= 5.5, units="in", size=20, lineheight = 0.75
             )

ggsave600dpi("..//Output//OTA//ota_topline_psr_keynote.png", ToplinePSR+
               labs(title="DOD OTAs Obligations\nby Area, 2015-2022"),
             width=6, height= 5.5, units="in", size=20, lineheight = 0.75
             )

write.csv(file="..//Output//OTA//ota_topline_psr_cur.csv",row.names = FALSE,
          ota_def %>% group_by(SimpleArea,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(SimpleArea),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year))


```

## PSR Covid
```{r ToplinePSR}

summary(ota_def$SimpleArea)


(
ToplinePSRcovid<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="ProductServiceOrRnDarea.covid", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//ota_psr_covid.png", ToplinePSRcovid, 
             width=12, height= 6, units="in",size=11, lineheight=1.2
             )

write.csv(file="..//Output//OTA//ota_psr_covid.csv",row.names = FALSE,
          ota_def %>% group_by(ProductServiceOrRnDarea.covid,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea.covid),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year))


```

## R&D phase
```{r Services}

(
RnDphase<-build_plot(
  data=ota_def %>% filter(SimpleArea=="R&D"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="ProductServiceOrRnDarea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//psr_RnDPhase.png", RnDphase, 
             width=12, height= 6, units="in",size=11, lineheight=1.2
             )
                           

write.csv(file="..//Output//OTA//psr_RnDPhase.csv",row.names = FALSE,
          pivot_wider(RnDphase$data%>%mutate(Fiscal_Year=year(dFYear)),id_cols=c(ProductServiceOrRnDarea),
                      names_from=dFYear,values_from=Action_Obligation_OMB24_GDP22)%>%
            arrange(ProductServiceOrRnDarea))
            

write.csv(file="..//Output//OTA//psr_RnDPhase_current.csv",row.names = FALSE,
          ota_def %>% filter(SimpleArea=="R&D") %>%
            format_data_for_plot(fy_var="dFYear",y_var="Action_Obligation_Then_Year",color_var = "ProductServiceOrRnDarea",
                                 labels_and_colors=ota_lc) %>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea),
                      names_from=dFYear,values_from=Action_Obligation_Then_Year)%>%
            arrange(ProductServiceOrRnDarea))

```

## R&D phase and OTA
```{r Services}

contract_merge<-ota_def%>%filter(Fiscal_Year >=2015) %>%
  group_by(Fiscal_Year,
                         ProductServiceOrRnDarea,
                         SimpleArea)%>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22))

# 
#   format_data_for_plot(contract_data,
#                      fy_var="Fiscal_Year", #x_var
#                      y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
#                      color_var="ProductServiceOrRnDarea", #color_var
#                      facet_var = "SimpleArea",
#                      labels_and_colors = labels_and_colors
# )
# ota_merge<-format_data_for_plot(ota_def,
#                      fy_var="Fiscal_Year", #x_var
#                      y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
#                      color_var="ProductServiceOrRnDarea", #color_var
#                      facet_var = "SimpleArea",
#                      labels_and_colors = labels_and_colors
# )

ota_merge<-ota_def%>%filter(Fiscal_Year >=2015) %>%
  group_by(Fiscal_Year,
                         ProductServiceOrRnDarea,
                         SimpleArea)%>%
  summarise(Action_Obligation_OMB24_GDP22=sum(Action_Obligation_OMB24_GDP22))


#   format_data_for_plot(ota_def,
#                      fy_var="Fiscal_Year", #x_var
#                      y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
#                      color_var="ProductServiceOrRnDarea", #color_var
#                      facet_var = "SimpleArea",
#                      labels_and_colors = labels_and_colors
# )

ota_merge$type<-"OTA"
colnames(ota_merge)[colnames(ota_merge)=="Fiscal_Year"]<-"Fiscal_Year"
contract_merge$type<-"contract"
merge<-rbind(ota_merge,contract_merge)

(
RnDphase<-build_plot(
  data=merge %>% filter(SimpleArea=="R&D"),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="type", #color_var
  facet_var="ProductServiceOrRnDarea", #facet_var
  column_key=ota_ck,
  format=FALSE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

# ggsave600dpi("..//Output//OTA//contractota_RnDPhase.png", RnDphase, 
#              width=12, height= 6, units="in",size=11, lineheight=1.2
#              )
#                            
# 
write.csv(file="..//Output//OTA//contractota_RnDPhase.csv",row.names = FALSE,
          pivot_wider(RnDphase$data%>%mutate(Fiscal_Year=year(dFYear)),id_cols=c(ProductServiceOrRnDarea,type),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB24_GDP22)%>%
            arrange(ProductServiceOrRnDarea,type))
#             
# 
# write.csv(file="..//Output//OTA//psr_RnDPhase_current.csv",row.names = FALSE,
#           ota_def %>% filter(SimpleArea=="R&D") %>%
#             format_data_for_plot(fy_var="Fiscal_Year",y_var="Action_Obligation_Then_Year",color_var = "ProductServiceOrRnDarea",
#                                  labels_and_colors=ota_lc) %>%
#           pivot_wider(id_cols=c(ProductServiceOrRnDarea),
#                       names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year)%>%
#             arrange(ProductServiceOrRnDarea))

```

## Services
```{r names_from=lubridate::year(dFYear)}

(
Services<-build_plot(
  data=ota_def %>% filter(SimpleArea=="Services (Non-R&D)"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="ProductServiceOrRnDarea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//psr_Services.png", Services, 
             width=12, height= 6, units="in",size=11, lineheight=1.2
             )
                           

write.csv(file="..//Output//OTA//psr_Services.csv",row.names = FALSE,
          pivot_wider(Services$data%>%mutate(Fiscal_Year=year(dFYear)),id_cols=c(ProductServiceOrRnDarea),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB24_GDP22)%>%
            arrange(ProductServiceOrRnDarea))
            

write.csv(file="..//Output//OTA//psr_Services_current.csv",row.names = FALSE,
          ota_def %>% filter(SimpleArea=="R&D") %>%
            format_data_for_plot(fy_var="Fiscal_Year",y_var="Action_Obligation_Then_Year",color_var = "ProductServiceOrRnDarea",
                                 labels_and_colors=ota_lc) %>%
          pivot_wider(id_cols=c(ProductServiceOrRnDarea),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year)%>%
            arrange(ProductServiceOrRnDarea))

```

# SubCustomer
## Topline SubCustomer 
```{r SubCustomer}
# summary(ota_def$Contracting_Agency_Name)
# ota_def$
(
SubCustomer<-build_plot(
  data=ota_def %>% filter(Fiscal_Year>=2015),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="SubCustomer.OTA", #color_var
  # facet_var="SubCustomer.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//ota_subcustomer.png", SubCustomer, 
             width=4.5, height= 6, units="in",size=16,lineheight = 1.2
             )

write.csv(file="..//Output//OTA//ota_subcustomer.csv",row.names = FALSE,
          pivot_wider(SubCustomer$data %>% mutate(Fiscal_Year=year(dFYear)),
                      id_cols=c(SubCustomer.OTA),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB24_GDP22))

write.csv(file="..//Output//OTA//ota_subcustomer_current.csv",row.names = FALSE,
          ota_def %>% group_by(SubCustomer.OTA,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(SubCustomer.OTA),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year)
          ,na="")

summary(ota_def$SubCustomer)
```

## Topline SubCustomer Variant
```{r SubCustomer}
# platpsc$SubCustomer.platform[platpsc$Contracting.Agency.ID==]


(
SubCustomer<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="SubCustomer.OTA", #color_var
  facet_var="SubCustomer.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//ota_subcustomer_detail.png", SubCustomer, 
             width=6.5, height= 5.5, units="in",size=11,lineheight = 1.2
             )

write.csv(file="..//Output//OTA//topline_subcustomer.csv",row.names = FALSE,
          pivot_wider(SubCustomer$data%>%mutate(Fiscal_Year=year(dFYear)),id_cols=c(SubCustomer.sum,SubCustomer.OTA),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB24_GDP22))

write.csv(file="..//Output//OTA//topline_subcustomer_current.csv",row.names = FALSE,
          ota_def %>% group_by(SubCustomer.sum,SubCustomer,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(SubCustomer.sum,SubCustomer),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year))

summary(ota_def$SubCustomer)
```


## SubCustomer Product/Service/R&D
```{r SubCustomerPSR}

(
SubCustomerPSR<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="SimpleArea", #color_var
  facet_var="SubCustomer.sum", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2022 $s)")
)

# ggsave600dpi("..//Output//OTA//subcustomer_PSR.png", SubCustomerPSR, 
#              width=6.5, height= 4, units="in",size=11
#              )
ggsave600dpi("..//Output//OTA//subcustomer_PSR.png", SubCustomerPSR, 
             width=12, height= 6, units="in",size=11,lineheight = 1.2
             )
```



# Platform
## Topline  Platform
```{r Platform}

(
Platform<-build_plot(
  data=ota_def %>% filter(Fiscal_Year>=2015),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  # facet_var="PlatformPortfolio", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//ota_platform.png", Platform, 
             width=6, height= 6, units="in",size=14,lineheight = 1.2
             )



ggsave600dpi("..//Output//OTA//ota_platform_keynote.png", Platform+
               labs(title="DOD OTAs Obligations by\nPlatform, 2015-2022"),
             width=6.5, height= 5.5, units="in", size=20, lineheight = 0.75
             )

ggsave600dpi("..//Output//OTA//ota_platform_keynote.svg", Platform+
               labs(title="DOD OTAs Obligations by\nPlatform, 2015-2022"),
             width=6.5, height= 5.5, units="in", size=20, lineheight = 0.75
             )
  
write.csv(file="..//Output//OTA//ota_platform_current.csv",row.names = FALSE,na="",
          format_data_for_plot(ota_def,
                               fy_var="Fiscal_Year",
                               y_var="Action_Obligation_Then_Year",
                               color_var="PlatformPortfolio",
                               labels_and_colors = ota_lc,
                               group=TRUE) %>%
            arrange(Fiscal_Year) %>%
          pivot_wider(id_cols=c(PlatformPortfolio),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year) %>% 
            # mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=ota_lc$variable[ota_lc$column=="PlatformPortfolio"]))%>%
            mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=levels(PlatformPortfolio),
                                            labels=gsub("\\n"," ",levels(PlatformPortfolio))))%>%
                   arrange(desc(PlatformPortfolio)))
debug(log_plot)
log_plot(plot=Platform, df=ota_def   %>% filter(Fiscal_Year<=2023),
                     filename="acq_fig5_3_OTAplatform",xlsx="DoD_Acq_Trends_Contracts.xlsx",
                     sheet="5-3B OTAplat",path="../output/AcqTrends/", height=3,
                     startRow=1,startCol=12,format=TRUE,
         excel_y_var = TRUE,excel_formulas=TRUE,hist_year=2016,cur_year=2022
         #var_list=c("Source","fiscal_quarter")
         )
```


## Platform SubCustomer
```{r PlatformSubCustomer}

(
PlatformSubCustomer<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="SubCustomer.platform", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+# theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//platform_subcustomer.png", PlatformSubCustomer, 
             width=6.5, height= 4, units="in",size=11,lineheight = 0.75
             )


```

## Platform PSR
```{r PlatformPSR}

(
PlatformPSR<-build_plot(
  data=ota_def,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="SimpleArea", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//platform_PSR.png", PlatformPSR, 
             width=6.5, height= 4, units="in",size=11,lineheight = 0.75
             )

```





## Platform Vendor
```{r PlatformVendor}

(
PlatformVendor<-build_plot(
  data=ota_def %>% filter(PlatformPortfolio!="Unlabeled" ) ,
  chart_geom = "Bar Chart",
  share = TRUE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//platform_vendor.png", PlatformVendor, 
             width=6.5, height= 4, units="in",size=11,lineheight = 0.75
             )

```



## Platform Comp
```{r PlatformComp}

(
PlatformComp<-build_plot(
  data=ota_def %>% filter(PlatformPortfolio!="Unlabeled" ),
  chart_geom = "Bar Chart",
  share = TRUE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="Competition.multisum", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//platform_comp.png", PlatformComp, 
             width=6.5, height= 4, units="in",size=11,lineheight = 0.75
             )

```

# Army
## Army Platform
```{r ArmyPlatform}

(
ArmyPlatform<-build_plot(
  data=ota_def %>% filter(SubCustomer=="Army"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  # facet_var="PlatformPortfolio", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//ota_army_platform.png", ArmyPlatform, 
             width=12, height= 6, units="in",size=11,lineheight = 1.2
             )

  
write.csv(file="..//Output//OTA//ota_army_platform_current.csv",row.names = FALSE,na="",
          format_data_for_plot(ota_def %>% filter(SubCustomer=="Army"),
                               fy_var="Fiscal_Year",
                               y_var="Action_Obligation_Then_Year",
                               color_var="PlatformPortfolio",
                               facet="SubCustomer",
                               labels_and_colors = ota_lc,
                               group=TRUE) %>%
            arrange(Fiscal_Year) %>%
          pivot_wider(id_cols=c(SubCustomer,PlatformPortfolio),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year) %>% 
            # mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=ota_lc$variable[ota_lc$column=="PlatformPortfolio"]))%>%
            mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=levels(PlatformPortfolio),
                                            labels=gsub("\\n"," ",levels(PlatformPortfolio))))%>%
                   arrange(desc(PlatformPortfolio)))

```


# Navy
## Navy Platform
```{r NavyPlatform}

(
NavyPlatform<-build_plot(
  data=ota_def %>% filter(SubCustomer=="Navy"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  # facet_var="PlatformPortfolio", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//ota_Navy_platform.png", NavyPlatform, 
             width=12, height= 6, units="in",size=11,lineheight = 1.2
             )

  
write.csv(file="..//Output//OTA//ota_Navy_platform_current.csv",row.names = FALSE,na="",
          format_data_for_plot(ota_def %>% filter(SubCustomer=="Navy"),
                               fy_var="Fiscal_Year",
                               y_var="Action_Obligation_Then_Year",
                               color_var="PlatformPortfolio",
                               facet="SubCustomer",
                               labels_and_colors = ota_lc,
                               group=TRUE) %>%
            arrange(Fiscal_Year) %>%
          pivot_wider(id_cols=c(SubCustomer,PlatformPortfolio),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year) %>% 
            # mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=ota_lc$variable[ota_lc$column=="PlatformPortfolio"]))%>%
            mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=levels(PlatformPortfolio),
                                            labels=gsub("\\n"," ",levels(PlatformPortfolio))))%>%
                   arrange(desc(PlatformPortfolio)))

```


# Air Force
## Air Force Platform
```{r AirForcePlatform}

(
AirForcePlatform<-build_plot(
  data=ota_def %>% filter(SubCustomer=="Air Force"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=ota_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB24_GDP22", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  # facet_var="PlatformPortfolio", #facet_var
  column_key=ota_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)

ggsave600dpi("..//Output//OTA//ota_air_force_platform.png", AirForcePlatform, 
             width=12, height= 6, units="in",size=11,lineheight = 1.2
             )

  
write.csv(file="..//Output//OTA//ota_air_force_platform_current.csv",row.names = FALSE,na="",
          format_data_for_plot(ota_def %>% filter(SubCustomer=="Air Force"),
                               fy_var="Fiscal_Year",
                               y_var="Action_Obligation_Then_Year",
                               color_var="PlatformPortfolio",
                               facet="SubCustomer",
                               labels_and_colors = ota_lc,
                               group=TRUE) %>%
            arrange(Fiscal_Year) %>%
          pivot_wider(id_cols=c(SubCustomer,PlatformPortfolio),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year) %>% 
            # mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=ota_lc$variable[ota_lc$column=="PlatformPortfolio"]))%>%
            mutate(PlatformPortfolio=factor(PlatformPortfolio,levels=levels(PlatformPortfolio),
                                            labels=gsub("\\n"," ",levels(PlatformPortfolio))))%>%
                   arrange(desc(PlatformPortfolio)))

```