---
title: "Defense Acquisition Trends"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, October 6, 2021"
---

# Setup
First we load the data. The dataset used is a U.S. DOD Contracting dataset derived from FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)
library(svglite)
library(readxl)
library(openxlsx)


axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

local_path<-get_local_lookup_path()

main.text.size<-1
note.text.size<-1.40
if(!exists("pbl_short"))
  load(file="data/clean/pbl_short.Rda")


# if(!"Action_Obligation_OMB25_GDP23" %in% colnames(pbl_short))
#   pbl_short<-deflate(pbl_short, "Action_Obligation_Then_Year",deflator_var="OMB25_GDP23",path="offline")
# colnames(pbl_short)[colnames(pbl_short)=="Action_Obligation_Then_Year_Then_Year"]<-"Action_Obligation_Then_Year"




# if(!"Action_Obligation_OMB25_GDP23" %in% colnames(ota_def))
#   ota_def<-deflate(ota_def, "Action_Obligation_Then_Year",deflator_var="OMB25_GDP23")
# colnames(ota_def)[colnames(ota_def)=="Action_Obligation_Then_Year_Then_Year"]<-"Action_Obligation_Then_Year"

```

# Topline



## Topline Competition
```{r ToplineComp}
pbl_short %>% group_by(Fiscal_Year) %>% summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))
pbl_short %>% filter(Fiscal_Year==2021) %>% group_by(Competition.sum) %>% summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))

(
ToplineCompMulti<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=1991&Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.multisum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # 
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(x="Fiscal Year",
       y="Obligations (Constant 2023 $s)")+
    date_x_year_breaks(1992,2022, by=2)#,partial_year=2024,partial_label="\nOct–Nov")
)

(
ToplineComp<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=1997&Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # 
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(x="Fiscal Year",
       y="Obligations (Constant 2023 $s)")+
    date_x_year_breaks(1998,2022,2)#)#,partial_year=2024,partial_label="\nOct–Nov")
)



(
ToplineCompLine<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=1997&Fiscal_Year<=2024),
  chart_geom = "Line Chart",
  share = TRUE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(x="Fiscal Year",
       y="Obligations (Constant 2023 $s)")+
    date_x_year_breaks(1998,2022, by=2)
)

pbl_short %>% filter(Competition.sum =="Unlabeled" & Fiscal_Year>=2019) %>% group_by(CompetitionClassification)%>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))

log_plot(plot=ToplineComp, df=pbl_short %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig6_5_competition",xlsx="PBL_Contracts.xlsx",
                     sheet="6-5 Comp",path="../output/PBL/", height=3.5,
                     startRow=1,startCol=12,format=TRUE, excel_formulas = TRUE, excel_share = TRUE,
         include_YTD=FALSE#,var_list=c("Vehicle.AwardTask","Vehicle.sum7"),z
         )
```



### Missing Competition
```{r UnlabeledComp}

(
UnlabeledComp<-build_plot(
  data=pbl_short %>% filter(Competition.sum =="Unlabeled"),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="CompetitionClassification", #color_var
  facet_var="Vehicle.sum7", #facet_var
  # column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)

pbl_short %>% filter(Competition.sum =="Unlabeled" & Fiscal_Year>=2019) %>% group_by(CompetitionClassification)%>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))

ggsave600dpi(path="..//Output//PBL//",filename="unlabeled_comp.png", UnlabeledComp,  
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )



write.csv(file="..//Output//PBL//unlabeled_competition.csv",row.names = FALSE, na = "",
          # ToplineComp$data%>% mutate(dFYear=lubridate::year(dFYear))%>%
            pivot_wider(UnlabeledComp$data,id_cols=c(CompetitionClassification,Vehicle.sum7),
                        names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23)
          %>% arrange(CompetitionClassification,Vehicle.sum7))



```







## Topline Vehicle
```{r ToplineVehicle}


pbl_short %>% filter(Vehicle=="Unlabeled Indefinite Delivery Contract (IDC)" ) %>% group_by(ClassifyNumberOfOffers,No.Competition.sum)%>%
  summarise(n=length(Vehicle))


(
ToplineVehicle7<-build_plot(
  data=pbl_short %>% filter(!is.na(Vehicle.AwardTask)),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Vehicle.AwardTask", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Note: Unlabeled not shown. Source: FPDS and CSIS analysis.")
)


(
ToplineVehicle<-build_plot(
  data=pbl_short %>% filter(!is.na(Vehicle.AwardTask)),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Vehicle.sum", #color_var
  facet_var="Vehicle.AwardTask", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Note: Unlabeled not shown. Source: FPDS and CSIS analysis.")
)


log_plot(plot=ToplineVehicle7, df=pbl_short %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig4_X_vehicle",xlsx="PBL_Contracts.xlsx",
                     sheet="4-X Veh",path="../output/PBL/", height=4,
                     startRow=1,startCol=14,format=TRUE,
         var_list=c("Vehicle.AwardTask","Vehicle.sum7"))

```


### Vehicle Plat Breakout
```{r VehPlatBreakout} 
platform_levels<-levels(factor(pbl_short$PlatformPortfolio))
for(p in platform_levels){
  file_p<-gsub("__*","_",gsub("&","and",gsub("[ |,]","_",p)))
  (Breakout<-build_plot(
    data=pbl_short %>% filter(Fiscal_Year>=2000&Fiscal_Year<=2024&PlatformPortfolio==p),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Vehicle.AwardTask", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  theme(legend.position = "right")+
    labs(y="Obligations (Constant 2023 $s)",title=p))

  if(!dir.exists(file.path("../output/PBL/Platform",file_p)))
    dir.create(file.path("../output/PBL/Platform",file_p))
  undebug(log_plot)
  log_plot(plot=Breakout, df=pbl_short  %>% filter(Fiscal_Year<=2024&PlatformPortfolio==p),
           filename=paste(file_p,"vehicle",sep="_"),xlsx=paste("DoD",file_p,"Contracts.xlsx",sep="_"),
           sheet="Veh",path=file.path("../output/PBL/Platform/",file_p), height=3.5,
           startRow=1,startCol=14,format=TRUE,var_list=c("Vehicle.AwardTask","Vehicle.sum7"),
           output_doc_png=TRUE,excel_y_var=TRUE
           )
  
}
```

### Vehicle Cust Breakout
```{r VehCustBreakout} 


subcustomer_levels<-levels(factor(pbl_short$SubCustomer.sum))
for(c in subcustomer_levels){
  file_c<-gsub("__*","_",gsub("&","and",gsub("[ |,]","_",c)))
  (Breakout<-build_plot(
    data=pbl_short %>% filter(Fiscal_Year>=2000&SubCustomer.sum==c& Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Vehicle.AwardTask", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  theme(legend.position = "right")+
    labs(y="Obligations (Constant 2023 $s)",title=c))
  
  if(!dir.exists(file.path("../output/PBL/Customer",file_c)))
    dir.create(file.path("../output/PBL/Customer",file_c))
  
  log_plot(plot=Breakout, df=pbl_short  %>% filter(Fiscal_Year<=2024&SubCustomer.sum==c),
           filename=paste(file_c,"vehicle",sep="_"),xlsx=paste(file_c,"Contracts.xlsx",sep="_"),
           sheet="Veh",path=file.path("../output/PBL/Customer/",file_c), height=3.5,
           startRow=1,startCol=14,format=TRUE,var_list=c("Vehicle.AwardTask","Vehicle.sum7"),
           output_doc_png=TRUE,excel_y_var=TRUE
           )
  
}
```

### Vehicle Cost 
```{r VehCost} 

(
CAS<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="costaccountingstandardsclause", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)
  

```
### Vehicle Current Duration 
```{r VehCurDur} 

(
VehCurDur<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="CurrentDurationIsYear", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)
  
  

(
VehCurDur<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="CurrentDurationCategory", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)
  
  
log_plot(plot=VehCurDur, df=pbl_short  %>% filter(Fiscal_Year<=2024),
                     filename="Veh_CurDur",xlsx="PBL_Contracts.xlsx",
                     sheet="Veh-CurDur",path="../output/PBL/", height=3.5,
                     format=TRUE,output_slide_png=TRUE #,var_list=c("SimpleArea","Competition.multisum")
         )

  
```

### Vehicle Ultimate Duration 
```{r VehCurDur} 

(
VehUltDur<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="UnmodifiedUltimateDurationIsYear", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)
  
  

(
VehUltDur<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="UnmodifiedUltimateDurationCategory", #color_var
  facet_var="Vehicle.sum7", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2022 $s)")
)
  
  
log_plot(plot=VehUltDur, df=pbl_short  %>% filter(Fiscal_Year<=2024),
                     filename="Veh_UltDur",xlsx="PBL_Contracts.xlsx",
                     sheet="Veh-UltDur",path="../output/PBL/", height=3.5,
                     format=TRUE,output_slide_png=TRUE #,var_list=c("SimpleArea","Competition.multisum")
         )

  
```

## Topline Pricing
```{r ToplinePricing}

# pbl_short$PricingUCA.sum<-pbl_short$PricingUCA.sum
# levels(pbl_short$PricingUCA.sum)<-list("Firm Fixed-Price"="FFP",
#                                            "Less Common"="Less Common",
#                                            "Incentive"="Incentive",
#                                            "Other Cost-Based"="Other CB",
#                                            "Undefinitized\nContract Award"="UCA",
#                                            "Unclear"="Unclear"   )
(
ToplinePricing<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PricingUCA", #color_var
  facet_var="PricingUCA.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE,
  #alpha_var="YTD",
)+date_x_year_breaks(2000,2023,7)+#,partial_year=2024,partial_label="\nQ1")
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+facet_wrap(~PricingUCA.sum,nrow=1)+
  labs(y="Obligations\n(Constant 2023 $s)",
       title="DOD Contract Obligations by Pricing Mechanism, FY 2000–FY 2023",
       caption="Note: CB=Cost-Based, FFP=Firm Fixed Price, FP=Fixed-Price, FPLOE=Fixed-Price Level-of-Effort,\nLH=Labor Hours,T&M=Time & Materials, UCA=Undefinitized Contract Award\nSource: FPDS and CSIS analysis.")
)





ggsave600dpi(path="..//Output//PBL//",filename="topline_pricing.png", ToplinePricing,  
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )


log_plot(plot=ToplinePricing+theme(plot.margin = margin(t=0,r=0.25,b=0.1,l=0.1,"inches")), df=pbl_short  %>% filter(Fiscal_Year<=2024),
                     filename="aila_fig54_pricing",xlsx="PBL_Contracts.xlsx",
                     sheet="4-1 Price",path="../output/PBL/", height=3.5,
         output_slide_png = TRUE,
                     format=TRUE,var_list=c("PricingUCA.sum","PricingUCA"),
         excel_formula=TRUE, excel_y_var = TRUE
         )

```


### Pricing UCA History
```{r ToplinePricing}

(
ToplinePricing<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<2025),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PricingUCA", #color_var
  facet_var="PricingUCA.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE,
  # #alpha_var="YTD",
)+date_x_year_breaks(2000,2024,6)+#,partial_year=2024,partial_label="\nQ1")
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+facet_wrap(~PricingUCA.sum,nrow=1)+
  labs(y="Obligations\n(Constant 2023 $s)",
       title="DOD Contract Obligations by Pricing Mechanism, FY 2000–FY 2024",
       caption="Note: CB=Cost-Based, FFP=Firm Fixed Price, FP=Fixed-Price, FPLOE=Fixed-Price Level-of-Effort,\nLH=Labor Hours,T&M=Time & Materials, UCA=Undefinitized Contract Award\nSource: FPDS and CSIS analysis.")
)


  ggsave600dpi(path="..//Output//PBL//",filename="Topline_PricingUCA.png", ToplinePricing,  
               width=6.5, height= 3, units="in",size=12, lineheight=1.2
               )
  
  
  ggsave600dpi(path="..//Output//PBL//",filename="Topline_PricingUCA.svg", ToplinePricing,  
               width=12, height= 5.5, units="in",size=, lineheight=1.2
               )



(
PricingHistory<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year < 2025 & Fiscal_Year>=2000),
  chart_geom = "Line Chart",
  share = TRUE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PricingUCA.sum", #color_var
  # facet_var="PricingUCA.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+#+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right",
        plot.caption = element_text(hjust = 0,face="plain"))+
    date_x_year_breaks(2000,2024,6)+#,partial_year=2024,partial_label="\nQ1")
    # xlim(c(as.Date("1979-01-01"), as.Date("2023-12-30")))+
    # coord_cartesian(xlim = c(as.Date("1980-01-01"), as.Date("2022-01-01"))
  labs(y="Share of Obligations",caption="Source: Federal Procurement Data System (FPDS) and CSIS analysis.")
)


log_plot(plot=PricingHistory, df=pbl_short  %>% filter(Fiscal_Year<2025&Fiscal_Year>=2000),
                     filename="acq_fig8_2_pricing_uca",xlsx="PBL_Contracts.xlsx",
                     sheet="8-2 PriceUCA",path="../output/PBL/", height=3.5,
                     format=TRUE,#,var_list=c("PricingInflation",
         excel_y_var =TRUE,
         excel_share =TRUE
         )


```


### Pricing History
```{r ToplinePricing}

(
PricingHistory<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year < 2025),
  chart_geom = "Line Chart",
  share = TRUE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PricingInflation", #color_var
  # facet_var="PricingUCA.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+#+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right",
        plot.caption = element_text(hjust = 0,face="plain"))+
    date_x_year_breaks(1980,2022,5)+#,partial_year=2024,partial_label="\nQ1")
    # xlim(c(as.Date("1979-01-01"), as.Date("2023-12-30")))+
    # coord_cartesian(xlim = c(as.Date("1980-01-01"), as.Date("2022-01-01"))
  labs(y="Share of Obligations",caption="Source: Federal Procurement Data System (FPDS) and CSIS analysis.")
)



log_plot(plot=PricingHistory, df=pbl_short  %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig8_2_pricing_history",xlsx="PBL_Contracts.xlsx",
                     sheet="8-2 PriceHist",path="../output/PBL/", height=3.5,
                     format=TRUE#,var_list=c("PricingInflation")
         )


```



### Pricing Plat Breakout
```{r PricingPlatBreakout} 
platform_levels<-levels(factor(pbl_short$PlatformPortfolio))

for(p in platform_levels){
  file_p<-gsub("__*","_",gsub("&","and",gsub("[ |,]","_",p)))
  (Breakout<-build_plot(
    data=pbl_short %>% filter(Fiscal_Year>=2000&Fiscal_Year<=2024&PlatformPortfolio==p),
    chart_geom = "Bar Chart",
    share = FALSE,
    labels_and_colors=pbl_lc,
    # NA, #VAR.ncol
    x_var="dFYear", #x_var
    y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
    color_var="PricingUCA", #color_var
    facet_var="PricingUCA.sum", #facet_var
    column_key=pbl_ck,
    format=TRUE,
    ytextposition=FALSE,
    #alpha_var="YTD",
  )+date_x_year_breaks(2000,2023,6)+#,partial_year=2024,partial_label="\nQ1")
    theme(legend.position = "right")+
    labs(y="Obligations (Constant 2023 $s)",title=p))

  if(!dir.exists(file.path("../output/PBL/Platform",file_p)))
    dir.create(file.path("../output/PBL/Platform",file_p))
  undebug(log_plot)
  log_plot(plot=Breakout, df=pbl_short  %>% filter(Fiscal_Year<=2024&PlatformPortfolio==p),
           filename=paste(file_p,"pricing",sep="_"),xlsx=paste("DoD",file_p,"Contracts.xlsx",sep="_"),
           sheet="Price",path=file.path("../output/PBL/Platform/",file_p), height=3.5,
           startRow=1,startCol=14,format=TRUE,var_list=c("PricingUCA.sum","PricingUCA"),
           output_doc_png=TRUE,excel_y_var=TRUE
           )
  
}
```

### Pricing Cust Breakout
```{r PriceCustBreakout} 
subcustomer_levels<-levels(factor(pbl_short$SubCustomer.sum))
for(c in subcustomer_levels){
  file_c<-gsub("__*","_",gsub("&","and",gsub("[ |,]","_",c)))
  (Breakout<-build_plot(
    data=pbl_short %>% filter(Fiscal_Year>=2000&SubCustomer.sum==c& Fiscal_Year<=2024),
    chart_geom = "Bar Chart",
    share = FALSE,
    labels_and_colors=pbl_lc,
    # NA, #VAR.ncol
    x_var="dFYear", #x_var
    y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
    color_var="PricingUCA", #color_var
    facet_var="PricingUCA.sum", #facet_var
    column_key=pbl_ck,
    format=TRUE,
    ytextposition=FALSE,
    #alpha_var="YTD",
  )+date_x_year_breaks(2000,2023,6)+#,partial_year=2024,partial_label="\nQ1")
    theme(legend.position = "right")+
    labs(y="Obligations (Constant 2023 $s)",title=c))
  
  if(!dir.exists(file.path("../output/PBL/Customer",file_c)))
    dir.create(file.path("../output/PBL/Customer",file_c))
  
  log_plot(plot=Breakout, df=pbl_short  %>% filter(Fiscal_Year<=2024&SubCustomer.sum==c),
           filename=paste(file_c,"pricing",sep="_"),xlsx=paste(file_c,"Contracts.xlsx",sep="_"),
           sheet="Price",path=file.path("../output/PBL/Customer/",file_c), height=3.5,
           startRow=1,startCol=14,format=TRUE,var_list=c("PricingUCA.sum","PricingUCA"),
           output_doc_png=TRUE,excel_y_var=TRUE
           )
  
}
```

## Topline Commercial
```{r Commercial}
pbl_short$AnyCommercialText<-factor(pbl_short$AnyCommercial)
levels(pbl_short$AnyCommercialText)<-list(
  "Not Classified\nas Commercial"="N",
  "Non-development\nor Commercial Similar"= "NonDev",
  "Any Commercial\nClassification"="Y"
  
)

(
Commercial<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="AnyCommercialText", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")+
  date_x_year_breaks(2000,2022,2)#)#,partial_year=2024,partial_label="\nOct–Nov")
)


log_plot(plot=Commercial+labs(y="Obligations\n(Constant 2023 $s)"), df=pbl_short %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig5_4_commercial",xlsx="PBL_Contracts.xlsx",
                     sheet="5-4 Comm",path="../output/PBL/", height=2.5,
                     startRow=1,startCol=12,format=TRUE,#var_list=c("SimpleArea","Competition.multisum")
         )



```

## Topline Duration
```{r Duration}

pbl_short$CurrentDurationIsYear<-factor(pbl_short$CurrentDurationCategory)
levels(pbl_short$CurrentDurationIsYear)<-list(
   "<=1 year" =c("<=2 Months", ">2-7 Months"  ,">7-12 Months"),
   ">1 year"=c(">1-2 Years",   ">2-4 Years",  ">4 years")
)
pbl_short$UnmodifiedUltimateDurationIsYear<-factor(pbl_short$UnmodifiedUltimateDurationCategory)
levels(pbl_short$UnmodifiedUltimateDurationIsYear)<-list(
   "<=1 year" =c("<=2 Months", ">2-7 Months"  ,">7-12 Months"),
   ">1 year"=c(">1-2 Years",   ">2-4 Years",  ">4 years")
)

(
CurDuration<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = TRUE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="CurrentDurationCategory", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Share of Obligations")+
     date_x_year_breaks(2007,2023,2)#)#,partial_year=2024,partial_label="\nOct–Nov")

)

(
UnmDuration<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2007 & Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = TRUE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="UnmodifiedUltimateDurationCategory", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Share of Obligations",
       title="Market Share of DOD Contracts by Initial Award\nor Task Order Ultimate Duration, FY 2007-FY 2023")+
      date_x_year_breaks(2007,2023,2)#)#,partial_year=2024,partial_label="\nOct–Nov")

)

log_plot(plot=UnmDuration, df=pbl_short  %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig8_3_UmdDuration",xlsx="PBL_Contracts.xlsx",
                     sheet="8-3 Dur",path="../output/PBL/", height=3.5,
                     startRow=1,startCol=12,format=TRUE,
         output_slide_png = TRUE, suppress_doc_svg_text = "title"
         #,var_list=c("PricingInflation"),
         )


log_plot(plot=UnmDuration, df=pbl_short  %>% filter(Fiscal_Year<=2024),
                     filename="nps_fig06_UmdDuration",xlsx="DoD_2024_NPS.xlsx",
                     sheet="9 Dur",path="../output/PBL/",
         height=2.75,include_YTD=FALSE,suppress_doc_svg_text = "title",
                     startRow=1,format=TRUE,excel_y_var=TRUE,excel_formulas = TRUE,
         output_slide_png=TRUE
         )
```

## Topline Multi-Year
### Multi-Year setup
```{r Multiyear_Setup}
    pbl_short<-pbl_short%>% mutate(multiyearcontracttext=factor(multiyearcontract,levels=c("0","1"),
                              labels=c("Not Multi-Year","Multi-Year Contract")))

pbl_short$multiyearcontracttext[is.na(pbl_short$multiyearcontract)&
                             pbl_short$Vehicle %in% c("BOA","BPA","FSS","GWAC","PO","DO") ]<-"Not Multi-Year"
  # "MULTIPLE AWARD IDC"  "SINGLE AWARD IDC"   "Unlabeled IDC"        "DCA"    "DO"   


# pbl_short %>% group_by(Vehicle) %>%
#   dplyr::summarise(multiyearcontracttext=sum(
#     ifelse(multiyearcontracttext=="Multi-Year Contract",Action_Obligation_OMB25_GDP23,0),na.rm=TRUE))



pbl_short<-pbl_short %>% group_by(Fiscal_Year,Vehicle.sum7)%>%
  mutate(pPlatFYear=Action_Obligation_OMB25_GDP23/sum(Action_Obligation_OMB25_GDP23,na.rm=TRUE))
```
### Topline Multi-year


```{r Multi-Year}
pbl_short<-pbl_short%>% mutate(multiyearcontracttext=factor(multiyearcontract,levels=c("0","1"),
                              labels=c("Not Multi-Year","Multi-Year Contract")))


(
MultiYear<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="multiyearcontract", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")+
  date_x_year_breaks(2000,2022,2)#)#,partial_year=2024,partial_label="\nOct–Nov")
)

ggsave600dpi(path="..//Output//PBL//",filename="topline_Multiyear.png", MultiYear, 
             width=11, height= 5.5, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//PBL//",filename="topline_Multiyear.svg", MultiYear+
  labs(y="Obligations\n(Constant 2023 $s)"),#+facet_wrap(~SubCustomer.platform,nrow=1), 
             width=6.5, height= 2.25, units="in",size=11,lineheight = 1.2
             )


# pbl_short %>% filter(SubCustomer.sum=="Army", PlatformPortfolio=="Other Products", Fiscal_Year==2021) %>%
#   group_by(AnyMultiyearText,Competition.multisum) %>% summarise(
#     COVID19obligated=sum(COVID19obligated,na.rm=TRUE),
#     Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
#     Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year),
#     
#   )

```

## Topline GFE

### GFE setup
```{r GFE}

pbl_short$gfe_gfp_value<-factor(pbl_short$gfe_gfp_code)
levels(pbl_short$gfe_gfp_value)<-list(
   "No Government Furnished"="N",
  "Transaction uses\nGovernment Furnished\nEquipment or Property"="Y"
 
)

```


### Topline GFE
```{r GFE}


(
GFE<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="gfe_gfp_value", #color_var
  # facet_var="SubCustomer.platform", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")+
  date_x_year_breaks(2000,2022,2)#)#,partial_year=2024,partial_label="\nOct–Nov")
)


log_plot(plot=GFE+labs(y="Obligations\n(Constant 2023 $s)"), df=pbl_short %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig5_4_GFE",xlsx="PBL_Contracts.xlsx",
                     sheet="5-4 GFE",path="../output/PBL/", height=2.5,
                     startRow=1,startCol=12,format=TRUE,#var_list=c("SimpleArea","Competition.multisum")
         )



```

## Topline Cost Accounting
```{r SubCustomer}


(
CAS<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2001 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="costaccountingstandardsclause", #color_var
  facet_var="SubCustomer.platform", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)


(
CAS<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2007 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="costaccountingstandardsclause", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)


(
CAS<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2007 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.sum", #color_var
  facet_var="costaccountingstandardsclause", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)


(
CAS<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2007 & Fiscal_Year<=2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="AnyCommercial", #color_var
  facet_var="costaccountingstandardsclause", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)


```


#Product/Service/R&D

## Topline Product/Service/R&D
```{r ToplinePSR}

(
ToplinePSR<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year<=2024 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  # #alpha_var="YTD",
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SimpleArea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Note: Unlabeled product, service, and R&D areas not shown.\nSource: FPDS and CSIS analysis.")+
  date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1",)
)


log_plot(plot=ToplinePSR+facet_wrap(~SimpleArea), df=pbl_short %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig3_1_area",xlsx="PBL_Contracts.xlsx",
                     sheet="3-1 Area",path="../output/PBL/", height=3.5,
                     startRow=1,startCol=12,format=TRUE,#var_list=c("SimpleArea","Competition.multisum"),
         excel_y_var = TRUE,excel_formulas = TRUE
         )

```


## PSR Plat Breakout
```{r PSRplatBreakout} 
platform_levels<-levels(factor(pbl_short$PlatformPortfolio))
for(p in platform_levels){
  file_p<-gsub("__*","_",gsub("&","and",gsub("[ |,]","_",p)))
  (Breakout<-build_plot(
    data=pbl_short %>% filter(Fiscal_Year>=2000&PlatformPortfolio==p& Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  #alpha_var="YTD",
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SimpleArea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",title=p)+
  date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1")
)

  if(!dir.exists(file.path("../output/PBL/Platform",file_p)))
    dir.create(file.path("../output/PBL/Platform",file_p))
  
  log_plot(plot=Breakout, df=pbl_short  %>% filter(Fiscal_Year<=2024&PlatformPortfolio==p),
           filename=paste(file_p,"PSR",sep="_"),xlsx=paste("DoD",file_p,"Contracts.xlsx",sep="_"),
           sheet="PSR",path=file.path("../output/PBL/Platform/",file_p), height=3.5,
           startRow=1,startCol=13,format=TRUE,#,var_list=c("PricingUCA.sum","PricingUCA"),
           output_doc_png=TRUE,excel_y_var=TRUE
           )
  
}
```

## PSR Cust Breakout
```{r PSRcustBreakout} 
subcustomer_levels<-levels(factor(pbl_short$SubCustomer.sum))
for(c in subcustomer_levels){
  file_c<-gsub("__*","_",gsub("&","and",gsub("[ |,]","_",c)))
  (Breakout<-build_plot(
    data=pbl_short %>% filter(Fiscal_Year>=2000&SubCustomer.sum==c& Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  #alpha_var="YTD",
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SimpleArea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",title=c)+
  date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1")
)

  if(!dir.exists(file.path("../output/PBL/Customer",file_c)))
    dir.create(file.path("../output/PBL/Customer",file_c))
  
  log_plot(plot=Breakout, df=pbl_short  %>% filter(Fiscal_Year<=2024&SubCustomer.sum==c),
           filename=paste(file_c,"PSR",sep="_"),xlsx=paste(file_c,"Contracts.xlsx",sep="_"),
           sheet="PSR",path=file.path("../output/PBL/Customer/",file_c), height=3.5,
           startRow=1,startCol=13,format=TRUE,#,var_list=c("PricingUCA.sum","PricingUCA"),
           output_doc_png=TRUE,excel_y_var=TRUE
           )
  
}
```

## Services
```{r Services}
summary(factor(pbl_short$ServicesCategory.sum))
(
Services<-build_plot(
  data=pbl_short %>% filter(SimpleArea=="Services" & Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  #alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="ProductServiceOrRnDarea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  date_x_year_breaks(1990,2020,5)+#,partial_year=2024,partial_label="\nQ1")
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)


            
log_plot(plot=Services, df=pbl_short  %>% filter(Fiscal_Year<=2024 &SimpleArea=="Services (Non-R&D)"),
                     filename="acq_fig3_3_services",xlsx="PBL_Contracts.xlsx",
                     sheet="3-3 Serv",path="../output/PBL/", height=3.5,
                     startRow=1,startCol=12,format=TRUE,#,var_list=c("SimpleArea","Competition.multisum")
         )

```

## PSR Pricing
```{r PSR_pricing}


(
PSRpricing_dollar<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & Fiscal_Year <= 2024 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PricingUCA.sum", #color_var
  facet_var="SimpleArea", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE,
  share=FALSE
)+theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.",
       title="DOD Contract Obligations by Pricing Mechanism, FY 2000–FY 2023")
)

ggsave600dpi(path="..//Output//PBL//",filename="psr_pricing_dollar.png", PSRpricing_dollar, 
             width=6.5, height= 5, units="in",size=11, lineheight=1.2
             )


(
SimpleVendor_share<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 &Fiscal_Year<=2024 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PricingUCA.sum", #color_var
  facet_var="SimpleArea", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE,
  share=TRUE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.")
)




log_plot(plot=Services, df=pbl_short  %>% filter(Fiscal_Year<=2024 &SimpleArea=="Services (Non-R&D)"),
                     filename="aila30_pricing",xlsx="PBL_Contracts.xlsx",
                     sheet="PSR-price",path="../output/PBL/", height=3.5,
                     format=TRUE,output_slide_png=TRUE #,var_list=c("SimpleArea","Competition.multisum")
         )
```

## PSR Vendor size 
```{r PSR_vendorsize}


(
SimpleVendor_dollar<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year<=2021 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  facet_var="SimpleArea", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE,
  share=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April of 2020\n and thus did not make the cutofff for inclusion in FY2020.\nMcDonnell Douglas is grouped with the Big-5.")
)

ggsave600dpi(path="..//Output//PBL//",filename="psr_vendorsize_dollar.png", SimpleVendor_dollar, 
             width=6.5, height= 5, units="in",size=11, lineheight=1.2
             )


(
SimpleVendor_share<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year<=2021 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  facet_var="SimpleArea", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE,
  share=TRUE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.")
)


ggsave600dpi(path="..//Output//PBL//",filename="psr_vendorsize_share.png", SimpleVendor_share, 
             width=6.5, height= 5, units="in",size=11, lineheight=1.2
             )

```


## PSR Competition
```{r PSRcomp_plat}
summary(pbl_short$SimpleArea)


(
PSRComp_bar<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=1991 & Fiscal_Year<=2024 & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.multisum", #color_var
  facet_var="SimpleArea", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "bottom")+
  labs(x="Fiscal Year",
       y="Obligations (Constant 2023 $s)",
       title="DOD Contract Obligations by Extent of Competition, FY 1991–FY 2023")+
    date_x_year_breaks(1993,2023,by=6)#,partial_year=2024,partial_label="\nQ1")
)


(
PSRComp_line<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=1991 & Fiscal_Year<=2024 & SimpleArea!="Unlabeled"),
  chart_geom = "Line Chart",
  share = TRUE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.multisum", #color_var
  facet_var="SimpleArea", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "bottom")+
  labs(x="Fiscal Year",y="Share of Obligations")+
    date_x_year_breaks(1993,2023,by=6)#,partial_year=2024,partial_label="\nQ1")
)

ggsave600dpi(path="..//Output//PBL//",filename="PSRComp_line.png", PSRComp_line, 
             width=6.5, height= 5, units="in",size=12, lineheight=1.2
             )


ggsave("..//Output//PBL//PSRComp_both.svg", 
             gridExtra::grid.arrange(
               PSRComp_bar+labs(caption = NULL,x=NULL,title=NULL)+theme(legend.position = "none"),
               PSRComp_line), 
             width=6.5, height= 5, units="in"
)

ggsave("..//Output//PBL//PSRComp_both_keynote.png", 
             gridExtra::grid.arrange(
               PSRComp_bar+labs(
                  y="Obligations\n(Const. 2023 $s)",
               caption = NULL,x=NULL)+theme(legend.position = "none",text=element_text(size=20)),
               PSRComp_line+labs(y="Share of\nObl.")+theme(text=element_text(size=20),
               plot.caption = element_text(size=round(20 * 5/6,0))
               )),
             width=13, height= 5.5, units="in" #, size=20, lineheight = 0.75
             )

ggsave("..//Output//PBL//acq_fig6_6_PSR_competition.svg", 
             gridExtra::grid.arrange(
               PSRComp_bar+labs(
                 title=NULL,
                  y="Obligations\n(Constant 2023 $s)",
               caption = NULL,x=NULL)+theme(legend.position = "none",text=element_text(size=12),
                                            plot.margin = margin(t=0,b=0,l=0.1,r=0.5,unit="inches")),
               PSRComp_line+labs(y="Share of\nObligations",caption=NULL)+theme(text=element_text(size=12),
               plot.caption = element_text(size=round(20 * 5/6,0)),
                                           plot.margin = margin(t=0,b=0,l=0.1,r=0.5,unit="inches"))),
             width=6.5, height= 4.5, units="in" #, size=20, lineheight = 0.75
             )


log_plot(plot=PSRComp_bar, df=pbl_short  %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig6_6_PSR_competition",xlsx="PBL_Contracts.xlsx",
                     sheet="6-6 PSRcomp",path="../output/PBL/", height=3.5,
                     startRow=1,startCol=13,format=TRUE,var_list=c("SimpleArea","Competition.multisum"),
         output_doc_svg=FALSE,excel_y_var = TRUE, excel_formulas = TRUE, excel_share = TRUE,
         include_YTD=FALSE
         )
```
## PSR Multi-Year
```{r ToplinePricing}

(
PSRMultiYear<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 ),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="multiyearcontracttext", #color_var
  facet_var="SimpleArea",
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)

pbl_short<-pbl_short %>% group_by(Fiscal_Year,SimpleArea)%>%
  mutate(pPlatFYear=Action_Obligation_OMB25_GDP23/sum(Action_Obligation_OMB25_GDP23,na.rm=TRUE))
(
PSRMultiYearShare<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=2000 & SimpleArea!="Unlabeled"&
                             (is.na(multiyearcontract)|multiyearcontract==1)),
  chart_geom = "Line Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="pPlatFYear", #VAR.y.variable
  color_var="multiyearcontracttext", #color_var
  facet_var="SimpleArea",
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Share of Obligations")+
    scale_y_continuous(labels = percent)
)


ggsave600dpi(path="..//Output//PBL//",filename="PSR_MultiYear.png", PSRMultiYear,  
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )

ggsave600dpi(path="..//Output//PBL//",filename="PSR_MultiYearShare.png", PSRMultiYearShare,  
             width=6.5, height= 4, units="in",size=12, lineheight=1.2
             )

write.csv(file="..//Output//PBL//PSRMultiYearShare.csv",row.names = FALSE, na = "",
  pivot_wider(PSRMultiYearShare$data %>% 
                        arrange(dFYear) %>% mutate(Fiscal_Year=lubridate::year(dFYear)),
                      id_cols=c(SimpleArea,multiyearcontracttext),
                      names_from=Fiscal_Year,values_from=pPlatFYear)%>%
  arrange(SimpleArea,multiyearcontracttext))
  


```


# SubCustomer
## Topline SubCustomer 
```{r SubCustomer}

(
SubCustomer<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SubCustomer.JPO", #color_var
  facet_var="SubCustomer.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       title="DOD Contract Obligations by DOD Component, FY 2000-FY 2024") +date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1")
)

log_plot(plot=SubCustomer+facet_wrap(~SubCustomer.sum,nrow=1)+
           date_x_year_breaks(1990,2020,8),#,partial_year=2024,partial_label="\nQ1"),
         df=pbl_short %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig2_3_subcustomer",xlsx="PBL_Contracts.xlsx",
                     sheet="2-3 Cust",path="../output/PBL/", height=3.5,
                     startRow=1,startCol=13,format=TRUE,var_list=c("SubCustomer.sum","SubCustomer.JPO")
         )




log_plot(plot=SubCustomer+facet_wrap(~SubCustomer.sum,nrow=1)+
           date_x_year_breaks(1990,2022,8), df=pbl_short %>% filter(Fiscal_Year<=2024),
                     filename="nps_fig04_component",xlsx="DOD_2024_NPS.xlsx",
                     sheet="4 Cust",path="../output/PBL/",
         height=3,include_YTD=FALSE,suppress_doc_svg_text="title",
                     startRow=1,format=TRUE,excel_y_var=TRUE,excel_formulas = TRUE,
         output_slide_png=TRUE
         )

```

## SuCustomer Plat Breakout
```{r CustomerPlatBreakout} 
platform_levels<-levels(factor(pbl_short$PlatformPortfolio))
for(p in platform_levels){
  file_p<-gsub("__*","_",gsub("&","and",gsub("[ |,]","_",p)))
  (Breakout<-build_plot(
    data=pbl_short %>% filter(Fiscal_Year>=2000&PlatformPortfolio==p& Fiscal_Year<=2024),
chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SubCustomer.JPO", #color_var
  facet_var="SubCustomer.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)") +date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1")
)
  if(!dir.exists(file.path("../output/PBL/Platform",file_p)))
    dir.create(file.path("../output/PBL/Platform",file_p))
  
  log_plot(plot=Breakout, df=pbl_short  %>% filter(Fiscal_Year<=2024&PlatformPortfolio==p),
           filename=paste(file_p,"subcustomer",sep="_"),xlsx=paste("DoD",file_p,"Contracts.xlsx",sep="_"),
           sheet="Cust",path=file.path("../output/PBL/Platform/",file_p), height=3.5,
           startRow=1,startCol=13,format=TRUE,#,var_list=c("PricingUCA.sum","PricingUCA"),
           output_doc_png=TRUE,excel_y_var=TRUE
           )
  
}
```


## SubCustomer Product/Service/R&D
```{r SubCustomerPSR}

(
SubCustomerPSR<-build_plot(
  data=pbl_short,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SimpleArea", #color_var
  facet_var="SubCustomer.sum", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2023 $s)")
)

# ggsave600dpi(path="..//Output//PBL//",filename="subcustomer_PSR.png", SubCustomerPSR, 
#              width=6.5, height= 4, units="in",size=11
#              )
ggsave600dpi(path="..//Output//PBL//",filename="subcustomer_PSR.png", SubCustomerPSR, 
             width=12, height= 6, units="in",size=12,lineheight = 1.2
             )
```



# Platform
## Topline  Platform
```{r Platform}
(
Platform<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=1990 & Fiscal_Year<=2024),
  chart_geom = "Line Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(1990,2020,8)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)",
       title="DOD Contract Obligations by Platform Portfolio, FY 2000-FY 2024")
)


(
Platform_Bar<-build_plot(
  data=pbl_short %>% filter(Fiscal_Year>=1990 & Fiscal_Year<=2024),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=pbl_lc,
  # NA, #VAR.ncol
  x_var="dFYear",##alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  facet_var="PlatformPortfolio", #facet_var
  column_key=pbl_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(1990,2020,8)+#,partial_year=2024,partial_label="\nQ1")   
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)",
       title="DOD Contract Obligations by Platform Portfolio, FY 2000-FY 2024")
)


log_plot(plot=Platform_Bar+theme(plot.margin = margin(t=0,r=0.25,b=0.1,l=0.1,"inches")), df=pbl_short   %>% filter(Fiscal_Year<=2024),
                     filename="acq_fig3_2_platform",xlsx="PBL_Contracts.xlsx",
                     sheet="3-2 Plat",path="../output/PBL/", height=3.5,
                     startRow=1,startCol=12,format=TRUE#var_list=c("Source","fiscal_quarter"),
         )


log_plot(plot=Platform_Bar+theme(plot.margin = margin(t=0,r=0.25,b=0.1,l=0.1,"inches")), df=pbl_short   %>% filter(Fiscal_Year<=2024),
                     filename="nps_fig03_platform",xlsx="DoD_2024_NPS.xlsx",
                     sheet="3 Plat",path="../output/PBL/",
         height=3.5,include_YTD=FALSE,suppress_doc_svg_text="title",output_slide_png=TRUE,
                     startRow=1,format=TRUE,excel_y_var=TRUE,excel_formulas = TRUE,
         output_doc_svg=TRUE
         )


```

