---
title: "Shipbuilding Trends"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "May 5, 2025"
---

# Setup
First we load the data. The dataset used is a U.S. DOD Contracting dataset derived from FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)
library(svglite)
library(readxl)

library(openxlsx)

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

local_path<-get_local_lookup_path()

main.text.size<-1
note.text.size<-1.40
if(!exists("shippscintldef"))
  load(file="../data/clean/Defense_Ship_FPDS.Rda")



# if(!"Action_Obligation_OMB25_GDP23" %in% colnames(shippscintldef))
#   shippscintldef<-deflate(shippscintldef, "Action_Obligation_Then_Year",deflator_var="OMB25_GDP23",path="offline")
# colnames(shippscintldef)[colnames(shippscintldef)=="Action_Obligation_Then_Year_Then_Year"]<-"Action_Obligation_Then_Year"




if(!exists("ota_def")|!exists("def_kota"))
  load(file="../data/clean/Defense_OTA.Rda")


# if(!"Action_Obligation_OMB25_GDP23" %in% colnames(ota_def))
#   ota_def<-deflate(ota_def, "Action_Obligation_Then_Year",deflator_var="OMB25_GDP23")
# colnames(ota_def)[colnames(ota_def)=="Action_Obligation_Then_Year_Then_Year"]<-"Action_Obligation_Then_Year"




#Manual import Greenbook data
toa<-readxl::read_excel(path=file.path("..","data_raw","FY24 6-1_DoD TOA by Title.xlsx"),skip=4)
request<-readxl::read_excel(path=file.path("..","data_raw","FY24 1-1.xlsx"),skip=3)
toa<-toa[sapply(toa[,2],function(x) substr(x,start=1,stop=21))==
            "Total Current Dollars" & !is.na(toa[,2]),c(-1,-3)]
colnames(toa)<-gsub("FY ","",colnames(toa))
colnames(toa)<-gsub("\r\nEnacted","",colnames(toa))
colnames(toa)[colnames(toa)=="...2"]<-"Series"
toa<-pivot_longer(toa,  cols=-Series, names_to="Fiscal_Year", values_to="Total_Obligation_Authority")
toa$Total_Obligation_Authority<-toa$Total_Obligation_Authority*1000000
# debug(deflate)

online_path<-file.path(get_local_sharepoint_path("DIIG Teamsite - Shared Documents"),"2024 - Acquisition Trends","Data and Figures")



load(file="../data/clean/Defense_OTA.Rda")
```

# Topline


## Topline Competition
```{r ToplineComp}
shippscintldef %>% group_by(Fiscal_Year) %>% summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))

(
ToplineCompMulti<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=1991&Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.multisum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # 
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(x="Fiscal Year",
       y="Obligations (Constant 2023 $s)")+
    date_x_year_breaks(1992,2022, by=2)#,partial_year=2024,partial_label="\nOct–Nov")
)

(
ToplineComp<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=1997&Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # 
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(x="Fiscal Year",
       y="Obligations (Constant 2023 $s)")+
    date_x_year_breaks(1998,2022,2)#)#,partial_year=2024,partial_label="\nOct–Nov")
)



(
ToplineCompLine<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=1997&Fiscal_YQ<2024),
  chart_geom = "Line Chart",
  share = TRUE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.sum", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(x="Fiscal Year",
       y="Obligations (Constant 2023 $s)")+
    date_x_year_breaks(1998,2022, by=2)
)

shippscintldef %>% filter(Competition.sum =="Unlabeled" & Fiscal_Year>=2019) %>% group_by(CompetitionClassification)%>%
  summarise(Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23))

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_comp.png", ToplineComp,  
             width=11, height= 5.5, units="in",size=14, lineheight=1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_comp.emf", ToplineComp+theme(legend.position = "right"),  
             width=6.5, height= 3, units="in",size=11, lineheight=1.2
             )


ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_comp_multi.png", ToplineCompMulti,  
             width=11, height= 5.5, units="in",size=14, lineheight=1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_comp_multi.svg", ToplineCompMulti,  
             width=6.5, height= 4, units="in",size=12, lineheight=1.2
             )



ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_comp_multi.emf", ToplineCompMulti+theme(legend.position = "right"),  
             width=6.5, height= 3, units="in",size=11, lineheight=1.2
             )


ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_comp_square.png", ToplineComp,  
             width=6, height= 5, units="in",size=14, lineheight=1.2
             )


log_plot(plot=ToplineComp, df=shippscintldef %>% filter(Fiscal_YQ<2024),
                     filename="acq_fig6_5_competition",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="6-5 Comp",path="../output/Shipbuilding/", height=3.5,
                     startRow=1,startCol=12,format=TRUE, excel_formulas = TRUE, excel_share = TRUE,
         include_YTD=FALSE,second_path = online_path#,var_list=c("Vehicle.AwardTask","Vehicle.sum7"),z
         )
```








## Topline Vehicle
```{r ToplineVehicle}


shippscintldef %>% filter(Vehicle=="Unlabeled Indefinite Delivery Contract (IDC)" ) %>% group_by(ClassifyNumberOfOffers,No.Competition.sum)%>%
  summarise(n=length(Vehicle))


(
ToplineVehicle7<-build_plot(
  data=shippscintldef %>% filter(!is.na(Vehicle.AwardTask)),
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Vehicle.sum7", #color_var
  facet_var="Vehicle.AwardTask", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Note: Unlabeled not shown. Source: FPDS and CSIS analysis.")
)


(
ToplineVehicle<-build_plot(
  data=shippscintldef %>% filter(!is.na(Vehicle.AwardTask)),
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Vehicle.sum", #color_var
  facet_var="Vehicle.AwardTask", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Note: Unlabeled not shown. Source: FPDS and CSIS analysis.")
)


ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vehicle7.png", ToplineVehicle7, 
             width=13, height= 4.5, units="in",size=11
             )

write.csv(file="..//Output//Shipbuilding//topline_vehicle7.csv",row.names = FALSE, na = "",
          ToplineVehicle7$data%>% 
            mutate(Fiscal_Year=lubridate::year(dFYear),
                   bAction_Obligation_OMB25_GDP23=Action_Obligation_OMB25_GDP23/1000000000)%>%
            pivot_wider(id_cols=c(Vehicle.sum7,Vehicle.AwardTask),
                        names_from=Fiscal_Year,values_from=bAction_Obligation_OMB25_GDP23)%>%
            arrange(Vehicle.sum7,Vehicle.AwardTask))


ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vehicle.png", ToplineVehicle, 
             width=13, height= 4.5, units="in",size=11
             )

write.csv(file="..//Output//Shipbuilding//topline_vehicle.csv",row.names = FALSE, na = "",
          ToplineVehicle$data%>% mutate(Fiscal_Year=lubridate::year(dFYear),
                                       bAction_Obligation_OMB25_GDP23=Action_Obligation_OMB25_GDP23/1000000000)%>%
            pivot_wider(id_cols=c(Vehicle.sum,Vehicle.AwardTask),
                        names_from=Fiscal_Year,values_from=bAction_Obligation_OMB25_GDP23)%>%
            arrange(Vehicle.sum,Vehicle.AwardTask))

log_plot(plot=ToplineVehicle7, df=shippscintldef %>% filter(Fiscal_YQ<2024),
                     filename="acq_fig4_X_vehicle",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="4-X Veh",path="../output/Shipbuilding/", height=4,
                     startRow=1,startCol=14,format=TRUE,
         var_list=c("Vehicle.AwardTask","Vehicle.sum7"))

```



## Topline Pricing
```{r ToplinePricing}

# shippscintldef$PricingUCA.sumlong<-shippscintldef$PricingUCA.sum
# levels(shippscintldef$PricingUCA.sumlong)<-list("Firm Fixed-Price"="FFP",
#                                            "Less Common"="Less Common",
#                                            "Incentive"="Incentive",
#                                            "Other Cost-Based"="Other CB",
#                                            "Undefinitized\nContract Award"="UCA",
#                                            "Unclear"="Unclear"   )
(
ToplinePricing<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2000 & Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PricingUCA", #color_var
  facet_var="PricingUCA.sum", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE,
  alpha_var="YTD",
)+date_x_year_breaks(2000,2023,7)+#,partial_year=2024,partial_label="\nQ1")
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+facet_wrap(~PricingUCA.sum,nrow=1)+
  labs(y="Obligations\n(Constant 2023 $s)",
       title="DOD Contract Obligations by Pricing Mechanism, FY 2000–FY 2023",
       caption="Note: CB=Cost-Based, FFP=Firm Fixed Price, FP=Fixed-Price, FPLOE=Fixed-Price Level-of-Effort,\nLH=Labor Hours,T&M=Time & Materials, UCA=Undefinitized Contract Award\nSource: FPDS and CSIS analysis.")
)





ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_pricing.png", ToplinePricing,  
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )


log_plot(plot=ToplinePricing+theme(plot.margin = margin(t=0,r=0.25,b=0.1,l=0.1,"inches")), df=shippscintldef  %>% filter(Fiscal_YQ<2024),
                     filename="aila_fig54_pricing",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="4-1 Price",path="../output/Shipbuilding/", height=3.5,second_path=online_path,
         output_slide_png = TRUE,
                     format=TRUE,var_list=c("PricingUCA.sum","PricingUCA"),
         excel_formula=TRUE, excel_y_var = TRUE
         )

```





## Topline Commercial
```{r Commercial}
shippscintldef$AnyCommercialText<-factor(shippscintldef$AnyCommercial)
levels(shippscintldef$AnyCommercialText)<-list(
  "Not Classified\nas Commercial"="N",
  "Non-development\nor Commercial Similar"= "NonDev",
  "Any Commercial\nClassification"="Y"
  
)

(
Commercial<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2000 & Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="AnyCommercialText", #color_var
  # facet_var="SubCustomer.platform", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")+
  date_x_year_breaks(2000,2022,2)#)#,partial_year=2024,partial_label="\nOct–Nov")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_commercial.png", Commercial, 
             width=11, height= 5.5, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_commercial.svg", Commercial+
  labs(y="Obligations\n(Constant 2023 $s)"),#+facet_wrap(~SubCustomer.platform,nrow=1), 
             width=6.5, height= 2.25, units="in",size=11,lineheight = 1.2
             )


log_plot(plot=Commercial+labs(y="Obligations\n(Constant 2023 $s)"), df=shippscintldef %>% filter(Fiscal_YQ<2024),
                     filename="acq_fig5_4_commercial",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="5-4 Comm",path="../output/Shipbuilding/", height=2.5,
                     startRow=1,startCol=12,format=TRUE,#var_list=c("SimpleArea","Competition.multisum")
         )


shippscintldef %>% filter(SubCustomer.sum=="Army", PlatformPortfolio=="Other Products", Fiscal_Year==2021) %>%
  group_by(AnyCommercialText,Competition.multisum) %>% summarise(
    COVID19obligated=sum(COVID19obligated,na.rm=TRUE),
    Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
    Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year),
    
  )

```

## Topline Duration
```{r Duration}

shippscintldef$CurrentDurationIsYear<-factor(shippscintldef$CurrentDurationCategory)
levels(shippscintldef$CurrentDurationIsYear)<-list(
   "<=1 year" =c("<=2 Months", ">2-7 Months"  ,">7-12 Months"),
   ">1 year"=c(">1-2 Years",   ">2-4 Years",  ">4 years")
)
shippscintldef$UnmodifiedUltimateDurationIsYear<-factor(shippscintldef$UnmodifiedUltimateDurationCategory)
levels(shippscintldef$UnmodifiedUltimateDurationIsYear)<-list(
   "<=1 year" =c("<=2 Months", ">2-7 Months"  ,">7-12 Months"),
   ">1 year"=c(">1-2 Years",   ">2-4 Years",  ">4 years")
)

(
CurDuration<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2000 & Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = TRUE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="CurrentDurationCategory", #color_var
  # facet_var="SubCustomer.platform", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Share of Obligations")+
     date_x_year_breaks(2007,2023,2)#)#,partial_year=2024,partial_label="\nOct–Nov")

)

(
UnmDuration<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2007 & Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = TRUE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="UnmodifiedUltimateDurationCategory", #color_var
  # facet_var="SubCustomer.platform", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Share of Obligations",
       title="Market Share of DOD Contracts by Initial Award\nor Task Order Ultimate Duration, FY 2007-FY 2023")+
      date_x_year_breaks(2007,2023,2)#)#,partial_year=2024,partial_label="\nOct–Nov")

)


ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_CurDuration.png", CurDuration, 
             width=11, height= 5.5, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_CurDuration.svg", CurDuration,#+facet_wrap(~SubCustomer.platform,nrow=1), 
             width=6.5, height= 3, units="in",size=11,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_UnmDuration.png", UnmDuration,#+facet_wrap(~SubCustomer.platform,nrow=1), 
             width=6.5, height= 3, units="in",size=11,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_UnmDuration.svg", UnmDuration,#+facet_wrap(~SubCustomer.platform,nrow=1), 
             width=6.5, height= 3, units="in",size=11,lineheight = 1.2
             )

write.csv(file="..//Output//Shipbuilding//then_year_csv//topline_CurDuration_current.csv",row.names = FALSE, na = "",
          shippscintldef %>% group_by(CurrentDurationCategory,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(CurrentDurationCategory),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year)%>%
            arrange(CurrentDurationCategory))


log_plot(plot=UnmDuration, df=shippscintldef  %>% filter(Fiscal_YQ<2024),
                     filename="acq_fig8_3_UmdDuration",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="8-3 Dur",path="../output/Shipbuilding/", height=3.5,
                     startRow=1,startCol=12,format=TRUE,
         output_slide_png = TRUE, suppress_doc_svg_text = "title"
         #,var_list=c("PricingInflation"),
         )


log_plot(plot=UnmDuration, df=shippscintldef  %>% filter(Fiscal_YQ<2024),
                     filename="nps_fig06_UmdDuration",xlsx="DoD_2024_NPS.xlsx",
                     sheet="9 Dur",path="../output/Shipbuilding/NPS2024/",second_path=online_path,
         height=2.75,include_YTD=FALSE,suppress_doc_svg_text = "title",output_slide_png=TRUE,
                     startRow=1,format=TRUE,excel_y_var=TRUE,excel_formulas = TRUE,
         output_slide_png=TRUE,suppress_doc_svg_text = "title"
         )
```

## Topline Multi-Year
```{r Multi-Year}
shippscintldef<-shippscintldef%>% mutate(multiyearcontracttext=factor(multiyearcontract,levels=c("0","1"),
                              labels=c("Not Multi-Year","Multi-Year Contract")))


(
MultiYear<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2000 & Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="multiyearcontract", #color_var
  # facet_var="SubCustomer.platform", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")+
  date_x_year_breaks(2000,2022,2)#)#,partial_year=2024,partial_label="\nOct–Nov")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_Multiyear.png", Multiyear, 
             width=11, height= 5.5, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_Multiyear.svg", Multiyear+
  labs(y="Obligations\n(Constant 2023 $s)"),#+facet_wrap(~SubCustomer.platform,nrow=1), 
             width=6.5, height= 2.25, units="in",size=11,lineheight = 1.2
             )


# shippscintldef %>% filter(SubCustomer.sum=="Army", PlatformPortfolio=="Other Products", Fiscal_Year==2021) %>%
#   group_by(AnyMultiyearText,Competition.multisum) %>% summarise(
#     COVID19obligated=sum(COVID19obligated,na.rm=TRUE),
#     Action_Obligation_OMB25_GDP23=sum(Action_Obligation_OMB25_GDP23),
#     Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year),
#     
#   )

```


```{r ToplinePricing}
    shippscintldef<-shippscintldef%>% mutate(multiyearcontracttext=factor(multiyearcontract,levels=c("0","1"),
                              labels=c("Not Multi-Year","Multi-Year Contract")))

shippscintldef$multiyearcontracttext[is.na(shippscintldef$multiyearcontract)&
                             shippscintldef$Vehicle %in% c("BOA","BPA","FSS","GWAC","PO","DO") ]<-"Not Multi-Year"
  # "MULTIPLE AWARD IDC"  "SINGLE AWARD IDC"   "Unlabeled IDC"        "DCA"    "DO"   


# shippscintldef %>% group_by(Vehicle) %>%
#   dplyr::summarise(multiyearcontracttext=sum(
#     ifelse(multiyearcontracttext=="Multi-Year Contract",Action_Obligation_OMB25_GDP23,0),na.rm=TRUE))



shippscintldef<-shippscintldef %>% group_by(Fiscal_Year,Vehicle.sum7)%>%
  mutate(pPlatFYear=Action_Obligation_OMB25_GDP23/sum(Action_Obligation_OMB25_GDP23,na.rm=TRUE))
```

## Topline GFE
```{r GFE}

shippscintldef$gfe_gfp_value<-factor(shippscintldef$gfe_gfp_code)
levels(shippscintldef$gfe_gfp_value)<-list(
   "No Government Furnished"="N",
  "Transaction uses\nGovernment Furnished\nEquipment or Property"="Y"
 
)

```



### GFE Competition
```{r GFEcomp}
summary(shippscintldef$gfe_gfp_code)
(
GFEcomp<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2007 & Fiscal_YQ<2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="No.Competition.sum", #color_var
  facet_var="gfe_gfp_value", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")+
    scale_x_date(breaks=as.Date(c(paste(seq(2000,2021,3),"-01-01",sep=""))),
                                                   date_labels="'%y")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="platform_GFE.png", GFEplat, 
             width=12, height= 6, units="in",size=12,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="platform_GFE.svg", GFEplat, 
             width=6.5, height= 4.5, units="in",size=11,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="platform_GFE.emf", GFEplat, 
             width=6.5, height= 4.5, units="in",size=11,lineheight = 1.2
             )


# write.csv(file="..//Output//Shipbuilding//platform_GFE.csv",row.names = FALSE, na = "",
#           pivot_wider(GFEplat$data,id_cols=c(PlatformPortfolio,gfe_gfp_value),
#                       names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23))

write.csv(file="..//Output//Shipbuilding//platform_GFE_current.csv",row.names = FALSE, na = "",
          shippscintldef %>% group_by(PlatformPortfolio,gfe_gfp_value,Fiscal_Year)%>%
            filter(Fiscal_Year>=2004 & Fiscal_YQ<2024)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(PlatformPortfolio,gfe_gfp_value),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year))

summary(shippscintldef$ContractingSubCustomer)
```


## Topline Cost Accounting
```{r SubCustomer}


(
CAS<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2001 & Fiscal_YQ<2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="costaccountingstandardsclause", #color_var
  facet_var="SubCustomer.platform", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)


(
CAS<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2007 & Fiscal_YQ<2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="costaccountingstandardsclause", #color_var
  facet_var="PlatformPortfolio", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)


(
CAS<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2007 & Fiscal_YQ<2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Competition.detail", #color_var
  facet_var="costaccountingstandardsclause", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)


(
CAS<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2007 & Fiscal_YQ<2024) ,
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="AnyCommercial", #color_var
  facet_var="costaccountingstandardsclause", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_subcustomer.png", SubCustomer, 
             width=12, height= 6, units="in",size=12,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_subcustomer.svg", SubCustomer+facet_wrap(~SubCustomer.sum,nrow=1), 
             width=6.5, height= 4, units="in",size=11,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_subcustomer.emf", SubCustomer+facet_wrap(~SubCustomer.sum,nrow=1), 
             width=6.5, height= 4, units="in",size=11,lineheight = 1.2
             )


write.csv(file="..//Output//Shipbuilding//topline_subcustomer.csv",row.names = FALSE, na = "",
          pivot_wider(SubCustomer$data,id_cols=c(SubCustomer.sum,SubCustomer.platform),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB25_GDP23))

write.csv(file="..//Output//Shipbuilding//topline_subcustomer_current.csv",row.names = FALSE, na = "",
          shippscintldef %>% group_by(SubCustomer.sum,ContractingSubCustomer,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(SubCustomer.sum,ContractingSubCustomer),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year))

summary(shippscintldef$ContractingSubCustomer)
```


#Product/Service/R&D

## Topline Product/Service/R&D
```{r ToplinePSR}

(
ToplinePSR<-build_plot(
  data=shippscintldef %>% filter(Fiscal_YQ<2024 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  # alpha_var="YTD",
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SimpleArea", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Note: Unlabeled product, service, and R&D areas not shown.\nSource: FPDS and CSIS analysis.")+
  date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1",)
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_psr.png", ToplinePSR, 
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_psr.svg", ToplinePSR, 
             width=6.5, height= 3, units="in",size=11, lineheight=1.2
             )

log_plot(plot=ToplinePSR+facet_wrap(~SimpleArea), df=shippscintldef %>% filter(Fiscal_YQ<2024),
                     filename="acq_fig3_1_area",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="3-1 Area",path="../output/Shipbuilding/", height=3.5,
                     startRow=1,startCol=12,format=TRUE,#var_list=c("SimpleArea","Competition.multisum"),
         excel_y_var = TRUE,excel_formulas = TRUE
         )

```


## Topline Product/Service/R&D by ShipCategory
```{r ToplinePSR}

(
ShipCategory<-build_plot(
  data=shippscintldef %>% filter(Fiscal_YQ<2024 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  # alpha_var="YTD",
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="ShipCategory", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Note: Unlabeled product, service, and R&D areas not shown.\nSource: FPDS and CSIS analysis.")+
  date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1",)
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="ShipCategory_psr.png", ShipCategory, 
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="ShipCategory_psr.svg", ShipCategory, 
             width=6.5, height= 3, units="in",size=11, lineheight=1.2
             )

log_plot(plot=ShipCategory, df=shippscintldef %>% filter(Fiscal_YQ<2024),
                     filename="ShipCategory_breakout",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="ShipCategory",path="../output/Shipbuilding/", height=3.5,
                     startRow=1,startCol=12,format=TRUE,#var_list=c("SimpleArea","Competition.multisum"),
         excel_y_var = TRUE,excel_formulas = TRUE
         )
```
# ROK/Japan Specific Look
##**Setup**
```{r JapanROK}
shippscintldef %>% filter(
  #(ParentHQISOalpha3 %in% c("JPN", "ROK") & !is.na(ParentHQISOalpha3))|
  ##NOTE: THIS DF IS CURRENTLY MISSING ParentHQ, which is tough for this work
    (VendorISOalpha3 %in% c("JPN", "ROK") & !is.na(VendorISOalpha3)) |
    (PlaceISOalpha3 %in% c("JPN", "ROK") & !is.na(PlaceISOalpha3)) |
    (OriginISOalpha3 %in% c("JPN", "ROK") & !is.na(OriginISOalpha3)))%>%
  group_by(ContractingAgencyName) %>%
  summarise(Action_Obligation_OMB25_GDP23=
              sum(Action_Obligation_OMB25_GDP23))



```
## Japan/ROK Aspected shipbuilding
```{r JapanROKChart}
(
ShipCategory<-build_plot(
  data=shippscintldef %>% filter(
  #(ParentHQISOalpha3 %in% c("JPN", "ROK") & !is.na(ParentHQISOalpha3))|
  ##NOTE: THIS DF IS CURRENTLY MISSING ParentHQ, which is tough for this work
    (VendorISOalpha3 %in% c("JPN", "ROK") & !is.na(VendorISOalpha3)) |
    (PlaceISOalpha3 %in% c("JPN", "ROK") & !is.na(PlaceISOalpha3)) |
    (OriginISOalpha3 %in% c("JPN", "ROK") & !is.na(OriginISOalpha3)) &
      Fiscal_YQ<2024 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  # alpha_var="YTD",
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="ShipCategory", #color_var
  #facet_var="VendorISOalpha3", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Note: Unlabeled product, service, and R&D areas not shown.\n Currently does not include cases where ROK or Japanese firms own U.S. subsidiaries.\nSource: FPDS and CSIS analysis.")+
  date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1",)
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="ROKJapanShipCategory_psr.png", ShipCategory, 
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="ROKJapanShipCategory_psr.svg", ShipCategory, 
             width=6.5, height= 3, units="in",size=11, lineheight=1.2
             )

log_plot(plot=ShipCategory, df=shippscintldef %>% filter(
              (VendorISOalpha3 %in% c("JPN", "ROK") & !is.na(VendorISOalpha3)) |
              (PlaceISOalpha3 %in% c("JPN", "ROK") & !is.na(PlaceISOalpha3)) |
              (OriginISOalpha3 %in% c("JPN", "ROK") & !is.na(OriginISOalpha3)) &
              Fiscal_YQ<2024 & !is.na(SimpleArea) & SimpleArea!="Unlabeled"),
              filename="ShipCategory_breakout",xlsx="ROKJapanDOD_Shipbuilding_Contracts.xlsx",
                     sheet="ShipCategory",path="../output/Shipbuilding/", height=3.5,
                     startRow=1,startCol=12,format=TRUE,#var_list=c("SimpleArea","Competition.multisum"),
         excel_y_var = TRUE,excel_formulas = TRUE
         )

```
# SubCustomer
## Topline SubCustomer 
```{r SubCustomer}

(
SubCustomer<-build_plot(
  data=shippscintldef %>% filter(Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="SubCustomer.JPO", #color_var
  facet_var="SubCustomer.sum", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       title="DOD Contract Obligations by DOD Component, FY 1990-FY 2023") +date_x_year_breaks(1990,2020,5)#,partial_year=2024,partial_label="\nQ1")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_subcustomer.png", SubCustomer, 
             width=12, height= 6, units="in",size=12,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_subcustomer.svg", SubCustomer+facet_wrap(~SubCustomer.sum,nrow=1), 
             width=6.5, height= 4, units="in",size=11,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_subcustomer_keynote.svg", SubCustomer+
               facet_wrap(~SubCustomer.sum,nrow=1)+
               labs(title="DOD Contract Obligations by Component, 1990–2023")+
               date_x_year_breaks(1990,2020,8),#,partial_year=2024,partial_label="\nQ1"), 
             width=13, height= 5.5, units="in", size=20, lineheight = 0.75
             )

log_plot(plot=SubCustomer+facet_wrap(~SubCustomer.sum,nrow=1)+
           date_x_year_breaks(1990,2020,8),#,partial_year=2024,partial_label="\nQ1"),
         df=shippscintldef %>% filter(Fiscal_YQ<2024),
                     filename="acq_fig2_3_subcustomer",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="2-3 Cust",path="../output/Shipbuilding/", height=3.5,
                     startRow=1,startCol=13,format=TRUE,var_list=c("SubCustomer.sum","SubCustomer.JPO")
         )




log_plot(plot=SubCustomer+facet_wrap(~SubCustomer.sum,nrow=1)+
           date_x_year_breaks(1990,2022,8), df=shippscintldef %>% filter(Fiscal_YQ<2024),
                     filename="nps_fig04_component",xlsx="DOD_2024_NPS.xlsx",
                     sheet="4 Cust",path="../output/Shipbuilding/",second_path=online_path,
         height=3,include_YTD=FALSE,suppress_doc_svg_text="title",
                     startRow=1,format=TRUE,excel_y_var=TRUE,excel_formulas = TRUE,
         output_slide_png=TRUE
         )

```

## Subcustomer Vendor size NTDC
```{r Subcustomer_vendorsize}


(
CustVendor_dollar<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2007 & Fiscal_YQ<=2023.2 & !is.na(SubCustomer.platform) & SubCustomer.platform!="Unlabeled"),
  chart_geom = "Bar Chart",
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="VendorSize.NTDC", #color_var
  facet_var="SubCustomer.platform", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE,
  reverse_color = TRUE,
  share=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="Subcustomer_vendorsize_dollar.png", CustVendor_dollar, 
             width=6.5, height= 5, units="in",size=11, lineheight=1.2
             )


(
CustVendor_share<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2007 &  Fiscal_YQ<=2023.2 & !is.na(SubCustomer.platform) & SubCustomer.platform!="Unlabeled"),
  chart_geom = "Bar Chart",
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23",
  color_var="VendorSize.NTDC", #color_var
  facet_var="SubCustomer.platform", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE,
  share=TRUE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.")
)


ggsave600dpi(path="..//Output//Shipbuilding//",filename="Subcustomer_vendorsize_share.png", CustVendor_share, 
             width=6.5, height= 5, units="in",size=11, lineheight=1.2
             )

```

# Platform
## Topline  Platform
```{r Platform}
(
Platform<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=1990 & Fiscal_YQ<2024),
  chart_geom = "Line Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  facet_var="PlatformPortfolio", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(1990,2020,8)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)",
       title="DOD Contract Obligations by Platform Portfolio, FY 1990-FY 2023")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_platform.png", Platform, 
             width=12, height= 6, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_platform.svg", Platform, 
             width=6.5, height= 4, units="in",size=11,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_platform.emf", Platform+geom_line(
  size=1,aes(x=dFYear,y=Action_Obligation_OMB25_GDP23,color=PlatformPortfolio)),
             width=6.5, height= 4, units="in",size=11,lineheight = 1.2
             )


(
Platform_Bar<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=1990 & Fiscal_YQ<2024),
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="PlatformPortfolio", #color_var
  facet_var="PlatformPortfolio", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+date_x_year_breaks(1990,2020,8)+#,partial_year=2024,partial_label="\nQ1")   
  theme(legend.position = "none")+
  labs(y="Obligations (Constant 2023 $s)",
       title="DOD Contract Obligations by Platform Portfolio, FY 1990-FY 2023")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_platform_bar.png", Platform_Bar, 
             width=11, height= 5.5, units="in",size=14,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_platform_bar.emf", Platform_Bar,
             width=6.5, height= 4, units="in",size=11,lineheight = 1.2
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_platform_bar_keynote.svg", Platform_Bar+
               labs(title="DOD Contract Obligations by Platform Portfolio, FY 2000–FY 2023"),
             width=13, height= 5.5, units="in", size=20, lineheight = 0.75
             )


log_plot(plot=Platform_Bar+theme(plot.margin = margin(t=0,r=0.25,b=0.1,l=0.1,"inches")), df=shippscintldef   %>% filter(Fiscal_YQ<2024),
                     filename="acq_fig3_2_platform",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="3-2 Plat",path="../output/Shipbuilding/", height=3.5,
                     startRow=1,startCol=12,format=TRUE#var_list=c("Source","fiscal_quarter"),
         )


log_plot(plot=Platform_Bar+theme(plot.margin = margin(t=0,r=0.25,b=0.1,l=0.1,"inches")), df=shippscintldef   %>% filter(Fiscal_YQ<2024),
                     filename="nps_fig03_platform",xlsx="DoD_2024_NPS.xlsx",
                     sheet="3 Plat",path="../output/Shipbuilding/NPS2024/",second_path=online_path,
         height=3.5,include_YTD=FALSE,suppress_doc_svg_text="title",output_slide_png=TRUE,
                     startRow=1,format=TRUE,excel_y_var=TRUE,excel_formulas = TRUE,
         output_doc_svg=TRUE
         )


```


# Vendor Size


## Topline Vendor Size
```{r ToplineVendor}

(
ToplineVendor<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=1991& Fiscal_YQ<2024  ),
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  alpha_var="YTD",
  # facet_var="Competition.sum", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE,
  #reverse_color=TRUE
)+date_x_year_breaks(1990,2020,5,partial_year=2023,partial_label="\nQ1-Q2")+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Source: FPDS and CSIS analysis.")
)

(
ToplineVendor_line<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=1991&Fiscal_YQ<2024),
  chart_geom = "Line Chart",
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  # facet_var="Competition.sum", #facet_var
  alpha_var="YTD",
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE,
  share=TRUE,
  #reverse_color=TRUE
)+date_x_year_breaks(1990,2019,5)+#,partial_year=2024,partial_label="\nQ1")
    
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April of 2020\n and thus did not make the cutofff for inclusion in FY2020.")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor_wide.png", ToplineVendor+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April 2020 and thus did not make the cutofff for inclusion in FY2020."), 
             width=12, height= 6, units="in",size=12,lineheight=1
             )


ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor_cq.png", ToplineVendor+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutofff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor_cq.svg", ToplineVendor+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutofff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor.png", ToplineVendor, 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor.eps", ToplineVendor+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutofff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )



log_plot(plot=ToplineVendor, df=shippscintldef  %>% filter(Fiscal_YQ<2024 ),
                     filename="acq_fig6_X_vendor",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="6-X Vend",path="../output/Shipbuilding/", height=3.5,
                     startRow=1,startCol=12,format=TRUE,#,var_list=c("SimpleArea","Competition.multisum")
         )



```



### Topline Vendor International for Shipbuilding (of MRO)
```{r ToplineVendor}


(
ToplineVendorIntl<-build_plot(
  #data=shippscintldef %>% filter(Fiscal_Year>=2000& Fiscal_YQ<=2024),
 data=shippscintldef %>% filter(Fiscal_Year>=2000& Fiscal_YQ<=2024.2 
                                #& ShipCategory == "MRO")
                      )%>%
                              mutate(YTD=ifelse(Fiscal_Year==2024,"YTD","Full Year")),# & Fiscal_Year<=2021
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="VendorSize_Intl", #color_var
  facet_var="VendorSize_Intl", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = scales::date_format("'%y"))+
  date_x_year_breaks(2000,2022,3,partial_year=2024,partial_label="\nQ1–Q2")+
    
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       title="U.S. Navy MRO Contract Obligations by Vendor Size, FY 2000–FY 2024",       caption="Source: FPDS and CSIS analysis.")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor_intl_square.png", ToplineVendorIntl+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis."), 
             width=6, height= 5, units="in",size=12,lineheight=1
             )

ggsave600dpi(path="..//Output//Shipbuilding//",
             filename="topline_vendor_shipbuilding.svg", ToplineVendorIntl+
               labs(title="Shipbuilding Contract Obligations, FY 2000–FY 2024"),
             width=9, height= 5.5, units="in", size=20, lineheight = 0.75
             )

log_plot(plot=ToplineVendorIntl, df=shippscintldef  %>% filter(Fiscal_YQ<=2023.2),
                     filename="shipbuilding_contracts_topline",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="6-1 VendIntl",path="../output/Shipbuilding/", height=3.5,
         excel_y_var = TRUE, excel_formulas = TRUE,
                     format=TRUE,#,var_list=c("SimpleArea","Competition.multisum")
         )


log_plot(plot=ToplineVendorIntl, df=shippscintldef %>% filter(Fiscal_YQ<=2023.2),
                     filename="shipbuilding_logplot_toplinevendor",xlsx="DoD_2024_NPS.xlsx",
                     sheet="5a VendIntl",path="../output/Shipbuilding/NPS2024/",
         height=3,include_YTD=TRUE,second_path=online_path,
                     startRow=1,format=TRUE,excel_y_var=TRUE,excel_formulas = TRUE,
         suppress_doc_svg_text="title",output_slide_png=TRUE,
         output_doc_svg=TRUE
         )


```


### Topline Vendor NTDC
```{r ToplineVendor}

summary(shippscintldef$Shiny.VendorSize)
shippscintldef<-shippscintldef %>% mutate(VendorSize_NTDC=factor(case_when(
  Shiny.VendorSize %in% c("Big Five","Small")~Shiny.VendorSize,
  IsEntityTraditional==0~"Medium or Large Non-Traditional",
  Shiny.VendorSize %in% c("Medium")~"Medium Traditional",
  Shiny.VendorSize %in% c("Large")~"Large Traditional"
)))

fedpsc_lc<-prepare_labels_and_colors(shippscintldef,path="offline")
fedpsc_ck<-get_column_key(shippscintldef,path="offline")

(
ToplineVendorNTDC<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year>=2007& Fiscal_YQ<=2023.2 )%>%
                              mutate(YTD=ifelse(Fiscal_Year==2023,"YTD","Full Year")),# & Fiscal_Year<=2021
  chart_geom = "Bar Chart",
  share = FALSE,
labels_and_color=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="VendorSize_NTDC", #color_var
  # facet_var="Competition.sum", #facet_var
column_key = fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE,
  reverse_color=TRUE
)+scale_x_date("Fiscal Year",labels = scales::date_format("'%y"))+
  date_x_year_breaks(2007,2022,3,partial_year=2023,partial_label="\nQ1–Q2")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       title="DOD Contract Obligations by Vendor Size, FY 2000–FY 2023 Q1-Q2",
       caption="Source: FPDS and CSIS analysis.")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor_ntdc_square.png", ToplineVendorNTDC+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis."), 
             width=6, height= 5, units="in",size=12,lineheight=1
             )

ggsave600dpi(path="..//Output//Shipbuilding//",
             filename="topline_vendor_NTDC_keynote.svg", ToplineVendorNTDC+
               labs(title="DOD Contract Obligations, FY 2000–FY 2023 Q2"),
             width=9, height= 5.5, units="in", size=20, lineheight = 0.75
             )

log_plot(plot=ToplineVendorNTDC, df=shippscintldef  %>% filter(Fiscal_YQ<=2023.2),
                     filename="acq_fig6_1_vendor_NTDC",xlsx="DOD_Shipbuilding_Contracts.xlsx",
                     sheet="6-1 VendNTDC",path="../output/Shipbuilding/", height=3.5,
         excel_y_var = TRUE, excel_formulas = TRUE,
                     format=TRUE,#,var_list=c("SimpleArea","Competition.multisum")
         )


log_plot(plot=ToplineVendorNTDC, df=shippscintldef %>% filter(Fiscal_YQ<=2023.2),
                     filename="nps_fig08_vendor_NTDC",xlsx="DoD_2024_NPS.xlsx",
                     sheet="5 VendNTDC",path="../output/Shipbuilding/NPS2024/",
         height=3,include_YTD=TRUE,second_path=online_path,
                     startRow=1,format=TRUE,excel_y_var=TRUE,excel_formulas = TRUE,
         suppress_doc_svg_text="title",output_slide_png=TRUE,
         output_doc_svg=TRUE
         )

```

## Big 5 Breakout
```{r ToplineVendor}

big5<-read.delim(file.path("..","data","semi_clean","Defense_Vendor.sp_TopVendorHistoryCustomer.txt"),sep="\t")
big5<-read_and_join_experiment(big5,lookup_file="Lookup_ParentID.csv",
                               path="C:\\Users\\gsand\\Repositories\\Lookup-Tables\\",
                                 # "https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/",
                               dir="vendor/",           
                               add_var = c("Top6","IsPreTop6"),#"USAID region",
                               by=c("ParentID"="ParentID"),
                               skip_check_var=c("Top6","IsPreTop6"),
                               # missing_file="missing_DSCA_iso.csv"
)
big5<-big5 %>% filter(Top6==1|IsPreTop6==1)
big5$Big5<-big5$ParentID
big5$Big5[big5$JointVenture==1]<-"Big 5 Joint Venture"
big5$Big5[big5$Big5=="LOCKHEED"]<-"LOCKHEED MARTIN"
big5$Big5[big5$Big5=="GRUMMAN"]<-"NORTHROP GRUMMAN"
big5$SumOfobligatedAmount<-text_to_number(big5$SumOfobligatedAmount)
big5_wide <-big5 %>% group_by(Big5,Fiscal_Year) %>% filter(Fiscal_Year>=1990) %>%
  summarise(Action_Obligation=sum(SumOfobligatedAmount,na.rm=TRUE)) %>%
  pivot_wider(id_cols=Big5,names_from=Fiscal_Year,values_from=Action_Obligation) 

write.csv(big5_wide,file=file.path("..","Output","Shipbuilding","big5_wide.csv"),row.names=FALSE)

(
ToplineVendor<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year<=2020),
  chart_geom = "Bar Chart",
  share = FALSE,
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"),date_breaks = "2 years")+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",
       caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April 2020 and thus did not make the cutofff for inclusion in FY2020.")
)

(
ToplineVendor_line<-build_plot(
  data=shippscintldef %>% filter(Fiscal_Year<=2020),
  chart_geom = "Line Chart",
    labels_and_colors=fedpsc_lc,
  # NA, #VAR.ncol
  x_var="dFYear",#alpha_var="YTD", #x_var
  y_var="Action_Obligation_OMB25_GDP23", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  # facet_var="Competition.sum", #facet_var
  column_key=fedpsc_ck,
  format=TRUE,
  ytextposition=FALSE,
  share=TRUE
)+date_x_year_breaks(2000,2022,2)+#,partial_year=2024,partial_label="\nQ1")   
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April of 2020\n and thus did not make the cutofff for inclusion in FY2020.")
)

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor_wide.png", ToplineVendor+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April 2020 and thus did not make the cutofff for inclusion in FY2020."), 
             width=12, height= 6, units="in",size=12,lineheight=1
             )


ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor_cq.png", ToplineVendor+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutofff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor_cq.svg", ToplineVendor+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutofff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor.png", ToplineVendor, 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

ggsave600dpi(path="..//Output//Shipbuilding//",filename="topline_vendor.eps", ToplineVendor+
  labs(y="Obligations (Constant 2023 $s)",caption="Source: FPDS and CSIS analysis.\nNote: The merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutofff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )


write.csv(file="..//Output//Shipbuilding//topline_vendor_cur.csv",row.names = FALSE, na = "",
          shippscintldef %>% group_by(Shiny.VendorSize,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
          pivot_wider(id_cols=c(Shiny.VendorSize),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year)%>% arrange(Shiny.VendorSize))


write.csv(file="..//Output//Shipbuilding//topline_vendor.csv",row.names = FALSE, na = "",
          ToplineVendor$data%>% mutate(Fiscal_Year=lubridate::year(dFYear),
                                       bAction_Obligation_OMB25_GDP23=Action_Obligation_OMB25_GDP23/1000000000)%>%
            pivot_wider(id_cols=c(Shiny.VendorSize),
                        names_from=Fiscal_Year,values_from=bAction_Obligation_OMB25_GDP23)%>%arrange(Shiny.VendorSize))

```

