c---
title: "Software"
author: "Greg Sanders"
date: "2022-10-29"
output: html_document
---

# Setup
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40

load(file="../data/clean/sw_FPDS.Rda")

# detail_lc<-prepare_labels_and_colors(platpscintldef)#,path="K:\\Users\\Greg\\Repositories\\Lookup-Tables\\style\\")
# detail_ck<-get_column_key(platpscintldef)#,path="K:\\Users\\Greg\\Repositories\\Lookup-Tables\\style\\")
# column_key<-get_column_key(platpscintldef,path="K:\\Users\\Greg\\Repositories\\Lookup-Tables\\style\\")
# detail_lc<-prepare_labels_and_colors(platpscintldef,path="K:\\Users\\Greg\\Repositories\\Lookup-Tables\\style\\")
# detail_ck<-get_column_key(platpscintldef,path="K:\\Users\\Greg\\Repositories\\Lookup-Tables\\style\\")
```

## SW agency
```{r PreprocessPSC}


topAgency<-sw %>% group_by (Contracting_Agency_ID,ContractingAgencyName,Customer) %>% #,PlatformPortfolio
  summarise(Action_Obligation_OMB23_GDP21=sum(Action_Obligation_OMB23_GDP21),
            Action_Obligation_2020=sum(ifelse(Fiscal_Year==2020,Action_Obligation_OMB23_GDP21,0)))%>%
              group_by (Customer) %>%
    mutate(rank_total=rank(desc(Action_Obligation_OMB23_GDP21)),
                        rank_2020=rank(desc(Action_Obligation_2020)))
topAgency %>% arrange(desc(Action_Obligation_OMB23_GDP21))

topAgency$TopAgencyID<-
  ifelse(topAgency$rank_2020<=7 | topAgency$rank_total<=7,topAgency$Contracting_Agency_ID,NA)
topAgency$TopAgencyText<-
  ifelse(topAgency$rank_2020<=7 | topAgency$rank_total<=7,topAgency$ContractingAgencyName,NA)


sw<-left_join(sw,topAgency %>% select(-Action_Obligation_OMB23_GDP21,Action_Obligation_2020),
          by=c("Contracting_Agency_ID","Customer"))

sw$TopAgencyID[is.na(sw$TopAgencyID) & !is.na(sw$Contracting_Agency_ID)]<-
  "Other Labeled Agency"
sw$TopAgencyText[is.na(sw$TopAgencyText) & !is.na(sw$Contracting_Agency_ID)]<-
  "Other Labeled Agency"

sw$TopAgencyText<-factor_wrap(factor(sw$TopAgencyText))

summary(sw$TopAgencyText)


```

#Software

## Product vs. Service
```{r ProdServ}


sw$SWpsc<-as.character(sw$SimpleArea)
sw$SWpsc[sw$ProductOrServiceCode =="D319" ]<-"Annual Software Maint."
# sw$SWpsc[sw$ProductOrServiceCode =="D317" ]<-"Annual Software Maint."
sw$SWpsc[sw$ProductOrServiceCode =="7030" ]<-"Software as a product"
sw$SWpsc[sw$ProductOrServiceCode =="D305" ]<-"Teleprocessing / Cloud Computing"
sw$SWpsc[sw$ProductOrServiceCode %in% c("D302","D307","D308","D313","D317","D318","D399","H170","H970","J070","R413")]<-"Software Development Related"
sw$SWpsc[sw$SWpsc =="Services" ]<-"Other ADP Services"
sw$SWpsc<-factor(sw$SWpsc)
#D317
#D399, R413

sw %>% 
  group_by(SWpsc,ProductOrServiceCode,ProductOrServiceCodeText)%>% summarise(o=sum(Action_Obligation_OMB23_GDP21))

write.csv(sw %>% filter(Fiscal_Year>=2000) %>%
  group_by(SWpsc,ProductOrServiceCode,ProductOrServiceCodeText,Fiscal_Year)%>% summarise(o=sum(Action_Obligation_OMB23_GDP21))%>%#/1000000000
    arrange(Fiscal_Year)%>%pivot_wider(id_cols=c(SWpsc,ProductOrServiceCode,ProductOrServiceCodeText),
                names_from=Fiscal_Year,values_from=o)%>%arrange(SWpsc,ProductOrServiceCode,ProductOrServiceCodeText)
  ,file="..\\output\\Software_Prodserv.csv",row.names = FALSE)


sw %>% filter (ProductOrServiceCode %in% c("D317","D319")) %>%  #D317 not included
  group_by(SWpsc,ProductOrServiceCode,ProductOrServiceCodeText)%>% summarise(o=sum(Action_Obligation_OMB23_GDP21))


sw %>% filter (ProductOrServiceCode %in% c("7030","D302","D307","D308","D313","D317","D318","D319","H170","J070","R413")) %>% 
  group_by(SWpsc,ProductOrServiceCode,ProductOrServiceCodeText)%>% summarise(o=sum(Action_Obligation_OMB23_GDP21))

sw<-sw %>% filter(ProductOrServiceCode %in% c("D305", "D317","D319", "7030","D302","D307","D308","D313","D317","D318","D319","D399","H170","H970","J070","R413"))

# platpscintldef$SimpleArea
# platpscintldef$SWpsc<-as.character(platpscintldef$SimpleArea)
# platpscintldef$SWpsc[substr(platpscintldef$ProductOrServiceCode,1,1)=="D" ]<-"Other IT and Telecomm"
# platpscintldef$SWpsc[substr(platpscintldef$ProductOrServiceCode,1,2)=="70" ]<-"Other ADP EQPT/SOFTWARE/SUPPLIES AND EQPT"
# # platpscintldef$SWpsc[platpscintldef$ProductOrServiceCode =="D304" ]<-"Telecomm & Transmission"
# # platpscintldef$SWpsc[platpscintldef$ProductOrServiceCode =="D316" ]<-"Telecomm Network Mgmt."
# platpscintldef$SWpsc[platpscintldef$ProductOrServiceCode =="D319" ]<-"Annual Software Maint."
# platpscintldef$SWpsc[platpscintldef$ProductOrServiceCode =="D305" ]<-"Teleprocessing, Timeshare, Cloud Computing, and High Performance Computing"
# platpscintldef$SWpsc[platpscintldef$ProductOrServiceCode =="7030" ]<-"Software as a product"
# platpscintldef$SWpsc[platpscintldef$SWpsc =="Products" ]<-"Other Products"
# platpscintldef$SWpsc[platpscintldef$SWpsc =="Services" ]<-"Other Services"
# 
# platpscintldef %>%group_by(SWpsc)%>%
#   dplyr::summarise(o=sum(Action_Obligation_OMB23_GDP21))
# levels(factor(platpscintldef$SWpsc))
# any(platpscintldef$ProductOrServiceCode=="D305")
# 
# levels(factor(platpscintldef$SWpsc))
# platpscintldef$SWpsc<-factor(platpscintldef$SWpsc,
#                               levels=c("Annual Software Maint.",
#                                        "Teleprocessing, Timeshare, Cloud Computing, and High Performance Computing",
#                                        "Other IT and Telecomm"  ,
#                                        "Other Services" ,
#                                        "Software as a product" ,
#                                        "Other ADP EQPT/SOFTWARE/SUPPLIES AND EQPT",
#                                        "Other Products"  ,
#                                        "R&D"))
#                              


(
SWpscdetail<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002 & ProductServiceOrRnDarea!="Unlabeled" &
                            !SWpsc %in% c("Other Services" ,"Other Products","R&D" ))  ,
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="ProductOrServiceCode", #color_var
  facet_var="SWpsc", #facet_var
  # column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis.")
)

# platpscintldef$ContractingAgencyText
# platpscintldef$ContractingAgencyTextSwr<-factor_wrap(platpscintldef$ContractingAgencyText)



# write.csv(file="..//Output//Software_prodserv_comm.csv",row.names = FALSE,na = "",
#           arrange(pivot_wider(SWpscdetail$data %>% 
#                         arrange(dFYear) %>% mutate(Fiscal_Year=lubridate::year(dFYear)),
#                       id_cols=c(SWpsc,Commercial),
#                       names_from=Fiscal_Year,values_from=Action_Obligation_OMB23_GDP21),SWpsc,Commercial))

ggsave600dpi(SWpscdetail,file="..//output//Software_prodserv.png",  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )
# ggsave600dpi(SWpscdetail,file="..//output//Software_prodserv.eps",  
#              width=13, height= 6, units="in",size=16, lineheight=1.2
#              )
```



## Customer 
```{r DoDsoftware}
summary(factor(sw$Customer))

sw %>% filter(Customer=="Other Agencies") %>% group_by(ProductOrServiceCodeText,TopAgencyText) %>% 
  summarise(Action_Obligation_OMB23_GDP21=sum(Action_Obligation_OMB23_GDP21))

(
SWpscdetail<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2000 )  ,
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="SWpsc", #color_var
  facet_var="Customer", #facet_var
  # column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis.")#+
    # facet_wrap(~ContractingAgencyTextSwr,ncol=4)
)

ggsave600dpi(SWpscdetail,file="..//output//Software_Customer.png",  
             width=13, height= 6, units="in",size=8, lineheight=1.2
             )
ggsave600dpi(SWpscdetail,file="..//output//Software_Customer_Agency.eps",  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )

write.csv(file="..//Output//Software_Customer.csv",row.names = FALSE,na = "",
          SWpscdetail$data %>% mutate(#Fiscal_Year=lubridate::year(dFYear),
                                bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(Customer,SWpsc),
                      names_from=Fiscal_Year,values_from=bAction_Obligation_OMB23_GDP21)%>%
            arrange(Customer,SWpsc),na="")

```
## DoD Component 
```{r DoDsoftware}


(
SWpscDoDcomp<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2000 & Customer=="Defense")  ,
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="SWpsc", #color_var
  facet_var="TopAgencyText", #facet_var
  # column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(caption="Note: Unlabeled not shown. Source: FPDS; CSIS analysis.")#+
    # facet_wrap(~ContractingAgencyTextSwr,ncol=4)
)

ggsave600dpi(SWpscDoDcomp,file="..//output//Software_Defense_Agency.png",  
             width=13, height= 6, units="in",size=8, lineheight=1.2
             )
ggsave600dpi(SWpscDoDcomp,file="..//output//Software_Defense_Agency.eps",  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )

write.csv(file="..//Output//SWpscDoDcomp.csv",row.names = FALSE,na = "",
          SWpscDoDcomp$data %>% mutate(#Fiscal_Year=lubridate::year(dFYear),
                                bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(TopAgencyText,SWpsc),
                      names_from=Fiscal_Year,values_from=bAction_Obligation_OMB20_GDP20)%>%
            arrange(TopAgencyText,SWpsc))

```


##  Competition
```{r SoftwareComp}

(
SoftwareComp<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2000),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="Fiscal_Year", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Competition.sum", #color_var
  facet_var="SWpsc", #facet_var
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "bottom")+
  labs(y="Obligations (Constant 2021 $s)")
)

ggsave600dpi("..//Output//Software_comp.png", SoftwareComp,  
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )



write.csv(file="..//Output//Software_competition.csv",row.names = FALSE,na = "",
          SoftwareComp$data %>% mutate(#Fiscal_Year=lubridate::year(dFYear),
                                bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(SWpsc,Competition.sum),
                      names_from=Fiscal_Year,values_from=bAction_Obligation_OMB23_GDP21)%>%
            arrange(SWpsc,Competition.sum),na="")

```


##  Vendor Size
```{r SoftwareVendor}
library(scales)
(
SoftwareVendor<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2000),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  facet_var="SWpsc", #facet_var
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(
       caption="Source: FPDS; CSIS Analysis.\nNote: The Merger of Raytheon and United Technologies took place in April of 2020 and thus did not make the cutoff for inclusion in FY2020.")
)

(
SoftwareVendor_line<-build_plot(
  data=sw,
  chart_geom = "Line Chart",
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Shiny.VendorSize", #color_var
  facet_var="SWpsc", #facet_var
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE,
  share=TRUE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(caption="Source: FPDS; CSIS Analysis.\nNote: The Merger of Raytheon and United Technologies took place in April of 2020\n and thus did not make the cutoff for inclusion in FY2020.")
)

ggsave600dpi("..//Output//Software_vendor_wide.png", SoftwareVendor+
  labs(caption="Source: FPDS; CSIS Analysis.\nNote: The Merger of Raytheon and United Technologies took place in April of 2020 and thus did not make the cutoff for inclusion in FY2020."), 
             width=12, height= 6, units="in",size=12,lineheight=1
             )


ggsave600dpi("..//Output//Software_vendor_cq.png", SoftwareVendor+
  labs(caption="Source: FPDS; CSIS Analysis.\nNote: The Merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutoff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )


ggsave600dpi("..//Output//Software_vendor_Federal.png", SoftwareVendor+theme(legend.position = "bottom")+
               labs(y="Federal Obligations (Constant 2021 $s)",caption="Source: FPDS; CSIS Analysis.\nNote: The Merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutoff for inclusion in FY2020."),  
             width=6, height= 5.5, units="in",size=12, lineheight=1.2
             )

ggsave600dpi("..//Output//Software_vendor_cq.eps", SoftwareVendor+
  labs(caption="Source: FPDS; CSIS Analysis.\nNote: The Merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutoff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

ggsave600dpi("..//Output//Software_vendor.png", SoftwareVendor, 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

ggsave600dpi("..//Output//Software_vendor.eps", SoftwareVendor+
  labs(caption="Source: FPDS; CSIS Analysis.\nNote: The Merger of Raytheon and United Technologies took place in April\nof 2020 and thus did not make the cutoff for inclusion in FY2020."), 
             width=6.5, height= 4, units="in",size=11,lineheight=1
             )

# 
# write.csv(file="..//Output//Software_vendor_cur.csv",row.names = FALSE,na = "",
#           sw %>% group_by(Shiny.VendorSize,Fiscal_Year)%>%
#             dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE)/1000000000)%>%
#           pivot_wider(id_cols=c(Shiny.VendorSize),
#                       names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year)%>% arrange(Shiny.VendorSize))
# 



write.csv(file="..//Output//Software_vendor.csv",row.names = FALSE,na = "",
          SoftwareVendor$data %>% mutate(Fiscal_Year=lubridate::year(dFYear),
                                bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(SWpsc,Shiny.VendorSize),
                      names_from=Fiscal_Year,values_from=bAction_Obligation_OMB23_GDP21)%>%
            arrange(SWpsc,Shiny.VendorSize),na="")


```
##  Vehicle
```{r SoftwareVehicle}


(
SoftwareVehicle<-build_plot(
  data=sw %>% filter(!is.na(Vehicle.AwardTask)),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Vehicle.sum", #color_var
  second_var="Vehicle.AwardTask", #facet_var
  facet_var="SWpsc",
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(
       caption="Note: Unlabeled not shown. Source: FPDS; CSIS Analysis.")
)

summary(sw$Vehicle)

ggsave600dpi("..//Output//Software_vehicle.png", SoftwareVehicle, 
             width=13, height= 4.5, units="in",size=11
             )

write.csv(file="..//Output//Software_vehicle.csv",row.names = FALSE,na = "",
          SoftwareVehicle$data%>% mutate(Fiscal_Year=lubridate::year(dFYear),
                                       bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            pivot_wider(id_cols=c(SWpsc,Vehicle.sum,Vehicle.AwardTask),
                        names_from=Fiscal_Year,values_from=bAction_Obligation_OMB23_GDP21)%>%arrange(SWpsc,Vehicle.sum,Vehicle.AwardTask))

```


##  Pricing
```{r SoftwarePricing}

sw$PricingUCA.sumlong<-sw$PricingUCA.sum
levels(sw$PricingUCA.sumlong)<-list("Firm-Fixed-Price"="FFP",
                                           "Less Common"="Less Common",
                                           "Incentive"="Incentive",
                                           "Other Cost-Based"="Other CB",
                                           "Undefinitized\nContract Award"="UCA",
                                           "Unclear"="Unclear"   )
  (
SoftwarePricing<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2000),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="PricingUCA", #color_var
  # second_var="PricingUCA.sumlong", #facet_var
  facet_var="SWpsc",
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2021 $s)")
)

# ggsave600dpi("..//Output//Software_pricing.png", SoftwarePricing, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//Software_pricing.png", SoftwarePricing,  
             width=12, height= 6, units="in",size=12, lineheight=1.2
             )


write.csv(file="..//Output//Software_pricing.csv",row.names = FALSE,na = "",
          SoftwarePricing$data %>% mutate(Fiscal_Year=lubridate::year(dFYear),
                                bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(SWpsc,PricingUCA),
                      names_from=Fiscal_Year,values_from=bAction_Obligation_OMB23_GDP21)%>%
            arrange(SWpsc,PricingUCA),na="")
```


## Info Tech Commercial
```{r Softwarecomm}

(
SoftwareComm<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002 & Customer %in% c("GSA")),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="SWpsc", #facet_var
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Defense & GSA Obligations (Constant 2021 $s)")
)


(
SoftwareComm<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="SWpsc", #facet_var
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Defense & GSA Obligations (Constant 2021 $s)")
)

(
DefSoftwareComm<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002 & Customer %in% c("Defense")),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="SWpsc", #facet_var
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Defense Obligations (Constant 2021 $s)")
)


(
SoftwareCommLine<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002 & Customer %in% c("Defense","GSA")),
  chart_geom = "Line Chart",
  share = TRUE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Commercial", #color_var
  facet_var="SWpsc", #facet_var
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Defense & GSA Obligations (Constant 2021 $s)")
)


(
SoftwareCommDetail<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002 & Customer %in% c("Defense","GSA")),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategoryText", #color_var
  facet_var="Commercial", #facet_var
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Defense & GSA Obligations (Constant 2021 $s)")
)

(
SoftwareCommIT<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002  & Customer %in% c("Defense","GSA")),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategoryText", #color_var
  facet_var="ITcategory", #facet_var
  second_var = "SWpsc",
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Obligations (Constant 2021 $s)")
)


(
SoftwarecommPSCdetail<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002  & Customer %in% c("Defense","GSA")),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="informationtechnologycommercialitemcategoryText", #color_var
  second_var="SWpsc", #facet_var
  facet_var="Commercial",
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Defense & GSA Obligations (Constant 2021 $s)")
)


# ggsave600dpi("..//Output//Software_pricing.png", SoftwareComm, 
#              width=6.5, height= 4, units="in",size=11
#              )


ggsave600dpi("..//Output//Software_comm.png", SoftwareComm,  
             width=13, height= 6, units="in",size=16, lineheight=1.2
             )


write.csv(file="..//Output//Software_comm.csv",row.names = FALSE,na = "",
          SoftwareComm$data %>% mutate(Fiscal_Year=lubridate::year(dFYear),
                                bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(SWpsc,Commercial),
                      names_from=Fiscal_Year,values_from=bAction_Obligation_OMB23_GDP21)%>%
            arrange(SWpsc,Commercial),na="")



ggsave600dpi("..//Output//Software_def_comm_paper.png", DefSoftwareComm+
               labs(y="Obligations (Constant 2021 $s)"),  
             width=6.5, height= 3, units="in",size=11, lineheight=1.2
             )
# ggsave600dpi("..//Output//Software_comm_paper.eps", SoftwareComm,  
#              width=13, height= 3.75, units="in",size=16, lineheight=1.2
#              )

ggsave600dpi("..//Output//Software_comm_Defense.png", DefSoftwareComm+
               labs(y="Defense Obligations (Constant 2021 $s)")+theme(legend.position = "bottom"),  
             width=6.5, height= 5.5, units="in",size=12, lineheight=1.2
             )

ggsave600dpi("..//Output//Software_comm_DefenseGSA.png", SoftwareComm+
               labs(y="Defense & GSA Obligations (Constant 2021 $s)")+theme(legend.position = "bottom"),  
             width=6.5, height= 5.5, units="in",size=12, lineheight=1.2
             )


output_TY<-sw %>% filter(Fiscal_Year>=2002  & Customer %in% c("Defense")) %>% group_by(Commercial,SWpsc,Fiscal_Year)%>%
            dplyr::summarize(Action_Obligation_Then_Year=sum(Action_Obligation_Then_Year,na.rm=TRUE))%>%
  arrange(Fiscal_Year) %>%
          pivot_wider(id_cols=c(SWpsc,Commercial),
                      names_from=Fiscal_Year,values_from=Action_Obligation_Then_Year) %>%
  arrange(SWpsc,Commercial)
write.csv(file="..//Output//Software_comm_Defense_cur.csv",row.names = FALSE, na = "",
          output_TY)



write.csv(file="..//Output//Software_DefenseGSA_comm.csv",row.names = FALSE,na = "",
          SoftwareComm$data%>% mutate(Fiscal_Year=lubridate::year(dFYear),
                                bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(Commercial,SWpsc),
                      names_from=Fiscal_Year,values_from=bAction_Obligation_OMB23_GDP21)%>%
            arrange(Commercial,SWpsc),na="")

```

#### Commercial Component
```{r Softwarecomm}

(
SoftwareCommAgency<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002 & Customer %in% c("Defense")),
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Commercial", #color_var
  second_var="SWpsc", #facet_var
  facet_var="TopAgencyText",
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Defense Obligations (Constant 2021 $s)")+
   theme(strip.text.y = element_text(angle=0))
)


(
SoftwareCommAgencyLine<-build_plot(
  data=sw %>% filter(Fiscal_Year>=2002 & Customer %in% c("Defense")),
  chart_geom = "Line Chart",
  share = TRUE,
  labels_and_colors=sw_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="Commercial", #color_var
  second_var="SWpsc", #facet_var
  facet_var="TopAgencyText",
  column_key=sw_ck,
  format=TRUE,
  ytextposition=FALSE
)+#scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right")+
  labs(y="Defense Obligations (Constant 2021 $s)")+
     theme(strip.text.y = element_text(angle=0))
)

         

# 
ggsave600dpi("..//Output//SoftwareCommDefAgency.png", SoftwareCommAgency,
             width=13, height= 6, units="in",size=12, lineheight=1.2
             )

write.csv(file="..//Output//SoftwareCommDefAgency.csv",row.names = FALSE,na = "",
          SoftwareCommAgency$data%>% mutate(Fiscal_Year=lubridate::year(dFYear),
                                bAction_Obligation_OMB23_GDP21=Action_Obligation_OMB23_GDP21/1000000000)%>%
            arrange(Fiscal_Year)%>%
          pivot_wider(id_cols=c(TopAgencyText,SWpsc,Commercial),
                      names_from=Fiscal_Year,values_from=bAction_Obligation_OMB23_GDP21)%>%
            arrange(TopAgencyText,SWpsc,Commercial),na="")

```


## Project
```{r Land}
summary(factor(drone$ProjectPlatform))
# drone$Fiscal_Year
# 
# topplat<-drone %>% filter(PlatformPortfolio=="Ships & Submarines") %>% group_by (ProjectName) %>%
#   summarise(Action_Obligation_OMB20_GDP20=sum(Action_Obligation_OMB20_GDP20),
#             Action_Obligation_2020=sum(ifelse(Fiscal_Year==2020,Action_Obligation_OMB20_GDP20,0))
#             )%>% mutate(rank_total=rank(desc(Action_Obligation_OMB20_GDP20)),
#                         rank_2020=rank(desc(Action_Obligation_2020)))
# topplat %>% arrange(desc(Action_Obligation_OMB20_GDP20))
# 
# drone$TopShipProject<-
#   ifelse(drone$ProjectName %in% topplat$ProjectName[topplat$rank_2020<=7 | topplat$rank_total<=7],
#          drone$ProjectName,NA)
# drone$TopShipProject[is.na(drone$TopShipProject) & !is.na(drone$ProjectName)]<-
#   "Other Labeled Project"
# summary(factor(drone$TopShipProject))



# Inflation
## Fuel
```{r Fuel}

# PlaceIsForeign
# full_data$PlaceStateRegion
# replace_nas_with_unlabeled(factor(full_data$PlaceIsForeign,levels=c(1,0),labels=c("Performed Abroad","Performed in the U.S."))

full_data$SimpleArea.fuels<- as.character( full_data$SimpleArea)
full_data$SimpleArea.fuels[full_data$ProductServiceOrRnDarea=="Fuels"]<-"Fuels"
summary(factor(full_data$SimpleArea.fuels))
full_data$SimpleArea.fuels<-factor(full_data$SimpleArea.fuels,
                                           levels=c("Services (Non-R&D)" ,
                                                   "R&D",
                                                   "Products (All)",
                                                   "Fuels",
                                                   "Unlabeled" ),
                                           labels=c("Services (Non-R&D)" ,
                                                   "R&D",
                                                   "Products (Non-Fuels)",
                                                   "Fuels",
                                                   "Unlabeled" ))
summary(factor(full_data$SimpleArea.fuels))
labels_and_colors<-prepare_labels_and_colors(full_data,path="C:\\Users\\gsand\\Repositories\\Lookup-Tables\\style\\")
column_key<-get_column_key(full_data,path="C:\\Users\\gsand\\Repositories\\Lookup-Tables\\style\\")


(
psrfuel<-build_plot(
  data=full_data,
  chart_geom = "Bar Chart",
  share = FALSE,
  labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="SimpleArea.fuels", #color_var
  # facet_var="TopPStext", #facet_var
  column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  # theme(legend.position = "none")+
  labs(y="Obligations (Constant 2021 $s)",
              caption = "Source: FPDS, CSIS Analysis, OMB GDP deflators.")
)

  ggsave600dpi(filename = "..//Output//PSRfuels.png", psrfuel,  
               width=12, height= 5.6, units="in",size=18, lineheight=1.2,
               bg="transparent"
               )

write.csv(file="..//Output//PSRfuels.csv",row.names = FALSE, na = "",
  pivot_wider(psrfuel$data %>% 
                        arrange(dFYear) %>% mutate(Fiscal_Year=lubridate::year(dFYear)),
                      id_cols=c(SimpleArea.fuels),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB23_GDP21)%>%
    arrange(SimpleArea.fuels))


(
fuel<-build_plot(
  data=full_data %>% filter(ProductOrServiceArea=="Fuels")%>% 
    mutate(PlaceIsForeign=factor(PlaceIsForeign,levels=c(1,0),labels=c("Performed Abroad","Performed in the U.S."))),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="PlaceStateRegion", #color_var
  # facet_var="TopPStext", #facet_var
  # column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  # theme(legend.position = "none")+
  labs(y="Obligations (Constant 2021 $s)",
       caption = "Source: FPDS, CSIS Analysis, OMB GDP deflators.")
)


(
fuel<-build_plot(
  data=full_data %>% filter(ProductOrServiceArea=="Fuels")%>% 
    mutate(PlaceIsForeign=factor(PlaceIsForeign,levels=c(1,0),labels=c("Performed Abroad","Performed in the U.S."))),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="PlaceIsForeign", #color_var
  # facet_var="TopPStext", #facet_var
  # column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  # theme(legend.position = "none")+
  labs(y="Obligations (Constant 2021 $s)")
)

ggsave600dpi("..//Output//Deep_Dives/Inflation/defense_fuel_place.png", fuel+labs(title="DoD Contract Obligations for Fuels", caption="Source: FPDS and CSIS analysis."), 
             width=6.5, height= 3.5, units="in",size=12,lineheight = 1
             )


write.csv(file="..//Output//Deep_Dives/Inflation/defense_fuel_place.csv",row.names = FALSE,na = "",
          fuel$data%>% mutate(Fiscal_Year=lubridate::year(dFYear))%>%
          pivot_wider(id_cols=c(PlaceIsForeign),
                      names_from=Fiscal_Year,values_from=Action_Obligation_OMB23_GDP21))



(
fuel_psc<-build_plot(
  data=platpscintldef %>% filter(ProductOrServiceArea=="Fuels")%>% 
    mutate(PlaceIsForeign=factor(PlaceIsForeign,levels=c(1,0),labels=c("Performed Abroad","Performed in the U.S."))),
  chart_geom = "Bar Chart",
  share = FALSE,
  # labels_and_colors=labels_and_colors,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  y_var="Action_Obligation_OMB23_GDP21", #VAR.y.variable
  color_var="ProductOrServiceCodeText", #color_var
  # facet_var="TopPStext", #facet_var
  # column_key=column_key,
  format=TRUE,
  ytextposition=FALSE
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  # theme(legend.position = "none")+
  labs(y="Obligations (Constant 2021 $s)")
)

```


## Pricing History
```{r ToplinePricing}
load(file="../data/clean/pricing_historical.Rda")
# full_data$PricingUCA.sumlong<-full_data$PricingUCA.sum
# levels(full_data$PricingInflation)<-list("FFP"="FFP",
#                                            "Less Common"="Less Common",
#                                            "Cost-Based"="Cost-Based",
#                                            "FP-Econ. Price Adj. "="Other CB",
#                                            "Undefinitized\nContract Award"="UCA",
#                                            "Unclear"="Unclear"   )
(
HistoricPricing<-build_plot(
  data=pricing %>% filter(Fiscal_Year>=1979 & Fiscal_Year<=2021 ),
  chart_geom = "Line Chart",
  share = TRUE,
  labels_and_colors=pricing_lc,
  # NA, #VAR.ncol
  x_var="dFYear", #x_var
  # y_var="Action_Obligation_OMB20_GDP20", #VAR.y.variable
  y_var="Action_Obligation", #VAR.y.variable
  color_var="PricingInflation", #color_var
  # facet_var="PricingUCA.sumlong", #facet_var
  column_key=pricing_ck,
  format=TRUE,
  ytextposition=FALSE,
)+scale_x_date("Fiscal Year",labels = date_format("'%y"))+
  # theme(strip.text.y = element_text(angle=0))+
 # theme(axis.text.x = element_text(angle=90))+
 #    scale_y_continuous("Percent of Obligations", labels = percent_format(accuracy=1))+
 #      facet_grid(.~Competition.sum ,scales="free_x", space="free_x"
 #             )+labs(title=NULL,
  # x="Fiscal Year",
  # y="Percent of Obligations",
  # color="Competition")+
  theme(legend.position = "right",rect = element_rect(fill = "transparent",))
  # labs(y="Obligations (Constant 2021 $s)")
)

# ggsave600dpi("..//Output//topline_pricing.png", ToplinePricing, 
#              width=6.5, height= 4, units="in",size=11
#              )


  ggsave600dpi("..//Output//HistoricPricing.png", HistoricPricing,  
               width=12, height= 5.6, units="in",size=18, lineheight=1.2,
               bg="transparent"
               )

write.csv(file="..//Output//HistoricPricing.csv",row.names = FALSE, na = "",
  pivot_wider(HistoricPricing$data %>% 
                        arrange(dFYear) %>% mutate(Fiscal_Year=lubridate::year(dFYear)),
                      id_cols=c(PricingInflation),
                      names_from=Fiscal_Year,values_from=Action_Obligation)%>%
    arrange(PricingInflation))


```

